### 2017-04-07 draft/ms_v1.tex
Draft version 1

% Version 0; Only rough outline by SH
% Version 1; First draft by SH

%% ------------------------------------------------------------------------------------ %% 
\documentclass[useamsfonts]{pasj01}
\twocolumn

%% ------------------------------------------------------------------------------------ %% 
% Packages
\usepackage{url}    
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{morefloats}
\usepackage{xspace}
\usepackage[usenames, dvipsnames]{xcolor}

% Package Settings
%\usepackage{hyperref}
%\hypersetup{colorlinks=true,
%            citecolor=cyan,
%            linkcolor=cyan,
%            filecolor=magenta,      
%            urlcolor=cyan}
%\urlstyle{same}
%% ------------------------------------------------------------------------------------ %%

% Figure extension
\DeclareGraphicsExtensions{.pdf,.png,.eps}

%%%%%%%%%%%%: User Defined Commands %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\amin{$^\prime$}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\sb{mag~arcsec$^{-2}$}
\def\lsun{$L_\odot$}
\def\msun{$M_\odot$}
\def\sigs{$\sigma_*$}

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}

\def\logms{{$\log (M_{\star}/M_{\odot})$}~}
\def\mstar{{$M_{\star}$}~}
\def\logmh{{$\log (M_{\mathrm{halo}}/M_{\odot})$}~}
\def\m2l{{$M_{\star}/L_{\star}$}~}

\def\redm{\texttt{redMaPPer}}
\def\hscpipe{\texttt{hscPipe}}
\def\synpipe{\texttt{SynPipe}}
\def\cmodel{\texttt{cModel}}
\def\forced{\texttt{forced}}
\def\unforced{\texttt{unforced}}
\def\tract{\texttt{Tract}}
\def\visit{\texttt{Visit}}
\def\tracts{\texttt{Tracts}}
\def\visits{\texttt{Visits}}
\def\galsim{\texttt{G}{\scriptsize \texttt{AL}}\texttt{S}{\scriptsize \texttt{IM}}}
\def\hst{{\textit{HST}}}

%% ------------------------------------------------------------------------------------ %%

% Commenting:
%% ------------------------------------------------------------------------------------ %% 
\newcommand{\plan}[1]{\textcolor{blue} {\textbf{#1}}}
\newcommand{\todo}[1]{\textcolor{red} {\textbf{#1}}}
\newcommand{\song}[1]{\textcolor{cyan} {\textbf{#1}}}
\newcommand{\addref}{{\textcolor{red}{\textbf{REF}}}}
\newcommand{\term}[1]{\textbf{\texttt{#1}}}

%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %%

\begin{document}

\SetRunningHead{Huang et al.}{HSC-SSP SynPipe}

\Received{$\langle$April 2017$\rangle$}
\Accepted{$\langle$2017$\rangle$}
\Published{$\langle$2017$\rangle$}

%%%%%%%%%%%%: Title and Affiliations %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
\title{HSC Synthetic Pipeline I: Basic Design and Characterization of the 
       Photometric Performance of HSC}

\author{Song Huang \altaffilmark{1,2}
        Alexie Leauthaud \altaffilmark{1,2},
        Ryoma Murata \altaffilmark{1, 4}, 
        Jim Bosch \altaffilmark{3},
        Paul Price \altaffilmark{3},
        Robert Lupton \altaffilmark{3},
        Rachel Mandelbaum \altaffilmark{5},
        Claire Lackner \altaffilmark{1},
        Steven Bickerton \altaffilmark{1},
        Satoshi Miyazaki \altaffilmark{6} 
        HSC Collaboration \altaffilmark{7}}                                          
%% ------------------------------------------------------------------------------------ %%

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
    Universe, The University of Tokyo Institutes for Advanced Study, 
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
\altaffiltext{2}{Department of Astronomy and Astrophysics, University of California, 
    Santa Cruz, 1156 High Street, Santa Cruz, CA 95064 USA}
\altaffiltext{3}{Department of Astrophysical Sciences, Princeton University, 
    4 Ivy Lane, Princeton, NJ 08544}
\altaffiltext{4}{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
\altaffiltext{5}{McWilliams Center for Cosmology, Department of Physics, 
    Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\altaffiltext{6}{SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
    Tokyo, 181--8588, Japan}
\altaffiltext{7}{Other affiliations}

\email{song.huang@ipmu.jp}
%% ------------------------------------------------------------------------------------ %%

%%%%%%%%%%%%: Abstract and Keywords %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
\KeyWords{Surveys, 
          Methods: observational, 
          Techniques: photometric}

\maketitle

%% ------------------------------------------------------------------------------------ %% 
\begin{abstract}

    The Subaru Strategy Survey Program (SSP) is an ambitious wide-area, multi-band 
    survey using the Hyper Suprime-Cam (HSC) on Subaru telescope.
    At the imaging depth of this survey, it becomes challenging to achieve accurate,
    unbiased, and consistent photometry across all five bands. 
    In this work, we present \synpipe{}, a \texttt{Python}-based, flexible framework 
    that interfaces with the HSC data reduction pipeline (\hscpipe{}) and test its 
    performance via injecting synthetic objects to the single-\texttt{visit} HSC images. 
    We use the coadd images in two \tracts{} from the Wide layer with representative 
    seeing conditions to demonstrate the usage of \synpipe{} and examine the general 
    photometric performance of \texttt{hscpipe}. 
    We find that the typical uncertainties of HSC \forced{} PSF photometry for stars 
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$ 
    mag (1\%-5\% accuracy in the $i$-band). 
    For synthetic single-{S\'{e}rsic\ } model galaxies, the typical uncertainties of 
    HSC forced \cmodel{} photometry range from 0.14 mag at $i{\sim}20.0$ mag to 
    0.20 mag at $i{\sim} 25.2$ mag. 
    Over the range of colors and magnitudes in these tests, we find that both \forced{} 
    PSF and \cmodel{} photometry provide unbiased estimates of colors that are robust 
    against different seeing conditions. 
    Finally, we also noticed that 1) the degree that a object is blended with others 
    impact the photometric accuracy, especially for stars.  
    Highly blended object tends to have larger photometric uncertainty, systematically 
    underestimated flux, and slightly biased color. 
    2) a relative high fraction of faint stars (${\sim}20$\% at $i>22.5$ mag) could be 
    misclassified as extended objects. 
    3) the shape and size estimates for galaxies using \cmodel{} suffer from strong 
    biases.

\end{abstract}
%% ------------------------------------------------------------------------------------ %%

%%%%%%%%%%%%: Main Text %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
\section{Introduction}
    \label{sec:intro}

    %% Background 
    Wide-field, multi-band imaging surveys have stepped onto the central stage of 
    modern astrophysics and cosmology in the past decade. 
    They also have a bright future as many ambitious projects are being carried out 
    or planned, like the Large Synoptic Survey Telescope 
    (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey 
    Telescope 
    (WFIRST; \citealt{Dressler2012})\footnote{\url{https://wfirst.gsfc.nasa.gov/}}, 
    and the \textit{Euclid} project 
    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}.
    Among many ongoing efforts, the Subaru Strategic Program 
    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}
    using the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of 
    the Subaru telescope is the most efficient one in term of Etendue. 
    These surveys together will greatly help us test cosmological models, trace the 
    evolution of galaxies, study the stellar structure of our Milky Way, and discover 
    large number of interesting transient objects.

    %% Challenges
    Before we can tackle any outstanding scientific question, we first need to learn 
    how to handle the huge amount of data generated by these projects, and achieve 
    accurate photometric measurements of different types of objects.  
    This target becomes increasingly challenging in the age of modern imaging 
    surveys. 
    The cameras that carry these surveys are often made up of multiple 
    charge-coupled devices (CCDs) with slightly different characteristics and have 
    large field-of-view (FoV) over not perfectly flat focus plane.
    During the observation, the seeing and background conditions always show spatial 
    and temporal variations across the FoV.
    The full-depletion, thick CCD adopted by these cameras enables long exposure time 
    and excellent sensitivity in the red-end, but they often have the so-called 
    ``brighter-fatter'' effect (\citealt{Antilogus2014}) which means the size of bright
    stars are enlarged.
    All these issues make accurate astrometric and photometric calibration, 
    background subtraction, and point spread function (PSF) modeling intrinsically
    difficult (e.g. \citealt{Schlafly2012}).
    In addition, the multi-epoch, multi-band nature of these surveys also complicate 
    the data reduction as one needs to pay special attentions to the processes of 
    image stacking, multi-band object detection and measurements. 
    Furthermore, as ongoing surveys reach to much deeper surface brightness level, 
    the number of objects in unit area, especially faint object, becomes much higher.
    Not only that, it is much more common to have objects that overlap each other at
    different levels (which is often referred to as ``blended''). 
    Both situations ask for improved methods for photometric measurements than the ones
    used in previous, shallower surveys.

%% ------------------------------------------------------------------------------------ %%     
    %% Reason
    These challenges mentioned above are not just technical details, they are crucial 
    systematics to key scientific goals of these surveys. 
    For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001}) 
    is a powerful tool to measure the large-scale distribution of dark matter and 
    follow its evolution. 
    The WL measurements critically depend on the ability to model PSF and measure the
    shape of background galaxies in high precision (e.g. \citealt{Mandelbaum2015}). 
    Also, photometric redshift measurement (e.g. \citealt{Benitez2000, Bolzonella2000,
    Ilbert2009}) is fundamentally important for studying the evolution of galaxies; 
    and the ``drop-out'' method is very useful in selecting high-redshift galaxies 
    (e.g. \citealt{Steidel1996}). 
    Both methods are based on accurate multi-band photometric measurements. 
    The list goes on and on, but it becomes clear that we need to develop frameworks 
    to oversee the data reduction process of modern imaging surveys. 
    Several tools with similar goals have been developed (e.g. \citealt{Chang2015, 
    Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}).

    %% Organization    
    In this work, we present \synpipe{}, a \texttt{Python}-based 
    software to test the data reduction quality of the HSC--SSP (will be referred to 
    as the HSC survey) using synthetic objects.   
    \synpipe{} is designed to be a flexible framework that has many applications 
    and can help future developments of the HSC data reduction pipeline.
    Here, after briefly introducing the HSC survey and the current status of 
    data reduction (Section \ref{sec:ssp}), we explain the design and implementation 
    of \synpipe{} (Section \ref{sec:synpipe}), then we demonstrate its usage via 
    straightforward tests (Section \ref{sec:test}) that focus on the general 
    photometric quality for both synthetic stars and galaxies 
    (Section \ref{sec:result}). 
    Finally, we summary the work and discuss future developments in the 
    Section \ref{sec:summary}.

    \synpipe{} code, along with basic documents and a few examples are available 
    on GitHub at: \url{https://github.com/dr_guangtou/synpipe}.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Flowchart
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_flowchart_new}
    \end{center}
    \caption{
        Illustration of the basic procedures of \synpipe{}.  
        Grey color boxes indicate the required inputs at different stages. 
        Blue box is for the \texttt{addFakes.py} step when \synpipe{} injects simulated
        images of synthetic objects onto single frame image. 
        We show an example CCD image with and without synthetic objects on it 
        (highlighted by green circles).
        Red boxes are for the following image coadding and multiband measurement steps
        using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}. 
        We show a small piece of coadd image with synthetic objects on it.    
        The figure on the right side of the middle row shows the spatial relation 
        between \tract{} (outlined by the black dashed lines; each small region 
        is a \texttt{Patch}) and all the \visits{} that contribute to it 
        (each \visit{} has its own unique color; each small region has the size 
        of a CCD).
        }
    \label{fig:flowchart}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Hyper-Suprime Cam Subaru Strategic Program}
    \label{sec:ssp}

    %% Basic
    Taking advantage of the new prime focus camera on the 8.2m Subaru telescope, 
    the ambitious HSC survey consists of three layers. 
    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broadband 
    ($grizy$; Kawanomoto\etal in prep.). 
    The Deep (4 separated fields; ${\sim}27$ deg$^2$) and UltraDeep (2 separated 
    fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters 
    and employ slightly different survey strategy. 
    Please refers to the survey description paper for more detailed information
    (Strauss\etal in prep.).

    The HSC camera (\citealt{Miyazaki2012}) is made up of 112 full-depletion thick CCDs 
    for science and another 12 for guiding and focusing. 
    It provides a circular FoV with 1.5 deg diameter. 
    Each CCD contains 2048$\times$4096 pixels distributed in 4 amplifiers. 
    The pixel size equals to 0.168\asec{} on the sky.

    The HSC collaboration just released the first 1.7 years of data to public (DR1; 
    \citealt{HSCDR1})\footnote{\url{https://hsc_release.mtk.nao.ac.jp}}.
    For this work, we will focus on the Wide layer whose major scientific goals include
    WL cosmology, galaxy evolution since $z{\sim}1$, and studies of galaxy clusters. 
    The current Wide layer includes ${\sim}108$ deg$^2$ of sky that are isolated in 
    6 different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
    \footnote{A small AEGIS field is also observed for calibration purpose.}.
    Most of these fields are close to the equator with the exception of the HECTOMAP 
    field. 
    In the Wide layer, the $g$ and $r$ bands have 10 mins exposure broken into 4 
    dithers\footnote{Large, ${\sim}1/3$ of FoV dither pattern is used to ensure 
    uniform coverage.}; for the rest 3 bands, 20 mins exposure time and 6 dithers are 
    used\footnote{Several 30s exposures are taken to improve the dynamic range.}. 
    The survey prioritizes the observations so that the $i$-band can have excellent 
    seeing condition to help accurate shape measurements for WL. 
    The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{}, 
    and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit.
    For more details of the data status, please see the data release paper 
    (\citealt{HSCDR1}).  
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%     
\section{The HSC Data Reduction Pipeline}
    \label{ssec:hscpipe}

    The HSC survey data is currently reduced by \hscpipe{} \texttt{v4.0.5}, a 
    version of the LSST reduction pipeline (\citealt{Ivezic2008, Axelrod2010, 
    Juric2015}), which is described in detail in Bosch\etal (in prep.). 
    Since \synpipe{} is intrinsically connected to the complex data reduction 
    processes in \hscpipe{}, here we briefly introduce the main steps along with 
    a few key HSC/LSST terminologies.

    \begin{enumerate}

        \item \textbf{Single-\texttt{Visit~}Processing}: 
            Each individual exposure is called a \term{Visit} and is assigned with 
            an even integer. 
            After initial data screening (in background, seeing, and transparency; 
            Furusawa\etal in prep.), \hscpipe{} detrends these data (subtraction 
            of overscan, bias, and dark; flatfielding), generates variance and mask 
            images, subtracts background, and provides initial astrometric and 
            photometric calibrations.  
            \textbf{The spatially varying PSF models, photometric zeropoints, and the 
            World Coordinate System (WCS; \citealt{WCS1, WCS2}) corrected for optical 
            distortion will be used by \synpipe{}}.

        \item \textbf{Multi-\texttt{Visit~}Processing}:
            Then, \hscpipe{} then warps and mosaics these reduced CCD images into 
            much deeper \texttt{coadd} images while improving the astrometric and 
            photometric calibrations via processes similar to the \"{u}ber-calibration 
            in SDSS \citep{Padmanabhan2008}. 
            \textbf{\synpipe{} will use these improved calibrations.}
            \hscpipe{} organizes these \texttt{coadd} images into equi-area 
            rectangular regions that are pre-defined as an iso-latitude tessellation 
            and are referred to as \tract{}. 
            One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of 
            sky, and adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
            Each \tract{} is further divided into $9\times9$ \texttt{Patches}. 
            A \texttt{Patch} is a $4200\times4200$ pixels rectangular region, and
            adjacent \texttt{Patches} overlap each other by 100 pixels.
            \textbf{The \tract{} and \texttt{Patch} are basic units to deal 
            with HSC \texttt{coadd} images and \synpipe{} tests.}

        \item \textbf{Multi-band Measurements}: 
            To achieve consistent photometry across all filters, \hscpipe{} first 
            detects and deblends objects on \texttt{coadd} images in each band 
            independently (the \unforced{} measurements). 
            The above-threshold pixels for each object is referred to as 
            \texttt{footprint}.
            Then, \hscpipe{} merges the \texttt{footprints} and flux peaks in different
            bands, and selects a reference band for each object based on its $S/N$ in 
            each band (usually it is the $i$-band). 
            With the centroids, shape, and other non-amplitude parameters fixed at the
            reference values, \hscpipe{} perform \forced{} photometry which is 
            optimized to generate accurate colors.

        \item \textbf{HSC Photometry}: 
            The multiband catalogs generated by \hscpipe{} contains various photometric 
            information (see \citealt{HSCDR1} for details). 
            \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{} 
            photometry.}
            \texttt{psf} photometry should provide the most appropriate magnitudes and
            colors for point sources.
            Improved based on the SDSS version (\citealt{Lupton2001, Abazajian2004}), 
            the HSC \cmodel{}{} algorithm (described in Bosch\etal in prep.) fits the 
            flux distribution of each object using a combination of a de~Vaucouleur 
            and an exponential component taking the PSF convolution into accounts.
            \cmodel{} is designed to yield accurate colors for galaxies. 
            In addition, the star--galaxy separation task is performed based on the 
            difference between the \texttt{psf} and \cmodel{}{} magnitudes.

    \end{enumerate}

    The quality of the DR1 data have been vetted in \citet{HSCDR1} via cross-checking 
    with the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1 
    imaging survey (\citealt{Schlafly2012, Tonry2012, Magnier2013}), examining the 
    behaviors of the stellar sequence and the shape of the PSF models. 
    Generally speaking, the PSF photometry is accurate to 1--2\% level, and the 
    astrometry is accurate to ${\sim}10$ and 40 max internally and externally.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{SynPipe Overview}
    \label{sec:synpipe}

%% ------------------------------------------------------------------------------------ %% 
\subsection{Basic Design of \synpipe{}}
    \label{ssec:design}

    As summarized above and described in greater detail in Bosch\etal (in prep.),
    \hscpipe{} is a complex data reduction pipeline that still faces many challenges 
    and is under active development.
    Unlike most photometric pipeline on the market, it involves high-level reduction 
    processes that produce not only deep \texttt{coadd} images but also a series of 
    science-ready catalogs. 
    To faithfully test \hscpipe{} and these data products, we make sure the 
    \synpipe{} satisfies a few basic standards:

    \begin{itemize}

        \item \textbf{Realistic Images}: 
            Instead of using the fully generative approach to simulate full HSC-like 
            images from the ground up (e.g. \citealt{Chang2015}), \synpipe{} injects
            synthetic objects to the observed image so that all the realistic 
            features of the real data (e.g. blended objects; approximity to bright 
            object, bleeding trails, other optical artifacts \etal) can be included 
            in the test. 
            The impact of these features can be important to any topic that cares 
            about the selection function and completeness of samples 
            (e.g. WL analysis; stellar mass function of galaxies). 
            In \synpipe{}, point source is simulated using the HSC PSF model, 
            and realistic model of galaxy is modelled by the modular galaxy image 
            simulation toolkit, \galsim{} (\citealt{Rowe2015})
            \footnote{\url{https://github.com/GalSim_developers/GalSim}}.

        \item \textbf{Authentic Data Processing}:
            To follow the data reduction process as close as possible, we choose to 
            start from the single-\visit{} images instead of directly putting
            synthetic objects on the final \texttt{coadd} images 
            (e.g. \citealt{Suchyta2016}).
            Through this approach, subtle effects like the seeing differences among 
            \visits{} and small errors in astrometric calibration can be taken 
            into accounts. 
            All the synthetic objects will experience all the steps for detection, 
            deblending, stacking, and measurement just like any real object. 
            This can be important for challenging tasks like the WL measurements
            or the detection of high-$z$ galaxies. 
            The only downside of this choice is that it will certainly slow down the 
            test for \texttt{coadd} images as it needs to inject synthetic object 
            to all the \visits{} that contribute to a \tract{}.

        \item \textbf{Flexible Capabilities}:
            To make \synpipe{} useful for HSC users with various scientific goals, 
            we make sure it is flexible enough. 
            Although we provide default catalogs to generate samples of synthetic stars 
            and galaxies with realistic magnitude and color distributions along with 
            tools to help work on data release of HSC survey, the user is allowed to 
            be creative in term of providing input catalogs and design the tests. 
            As we are speaking, \synpipe{} is being used in a wide range of 
            scientific applications (see Section \ref{sec:summary} for details).

    \end{itemize}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\subsection{Implementation of \synpipe{}} 
    \label{ssec:flowchart}

    In this section, we will go through the implementation of \synpipe{} tests in 
    details (see Fig \ref{fig:flowchart}).

%% ------------------------------------------------------------------------------------ %%     
\subsubsection{Preparation}
    \label{sssec:prep}

    To start a \synpipe{} test, the user needs to provide:

    \begin{itemize}

        \item \textbf{Information about the data}: User needs to provide the 
            location of the HSC images and a list of \visits{} for the
            test.  
            For test of the \texttt{coadd} images, \synpipe{} can help user identify 
            all the \visits{} that contribute to one \tract{} in certain
            band. 
            It also provides tools to create optional bad-pixel mask (e.g. bright 
            object, bleeding trail, \etal) for specific \tract{} to avoid 
            putting synthetic objects on problematic regions.

        \item \textbf{Input catalog} in \texttt{FITS} format that contain necessary 
            information like the coordinate, magnitude, and other model parameters. 
            For certain sample of synthetic objects, \synpipe{} can help randomly 
            distribute them in a selected rectangular region with desired number 
            density. 
            If necessary, overlaps of synthetic objects can be greatly reduced 
            via setting a minimum distance between any two of them. 
            \synpipe{} can also help put synthetic objects on an evenly separated 
            coordinate grid, which is very useful for certain test 
            (e.g. Murata\etal in prep.).

    \end{itemize}

    For the synthetic object, \synpipe{} provides the following choices:

    \begin{itemize}

        \item \textbf{Point source}: 
            \synpipe{} simply uses the PSF model from \hscpipe{} as model for 
            point source like star or QSO. 
            \hscpipe{} uses a special version of \texttt{PSFEx} 
            (\citealt{Bertin2011, Bertin2013}) to characterize the PSF as a function 
            of the position so that a PSF model can be reconstructed for any location 
            on the image. 
            User only needs to provide the integrated magnitude to simulate 
            point sources.

        \item \textbf{Single- or Double-\ser{} model for galaxy}: 
            \texttt{SynPipe} uses \galsim{} \texttt{v1.4} (\citealt{Rowe2015}) to 
            simulate galaxy. 
            \galsim{} is an image simulation tool that has been well tested during 
            the GRavitational lEnsing Accuracy Testing 3 (GREAT3; 
            \citealt{Mandelbaum2014}). 
            Right now, \synpipe{} allows synthetic galaxy to be modelled by single 
            or double components that are described by the \citet{Sersic1963} 
            profile.  
            The \ser{} profile is flexible enough to describe the overall flux 
            distributions of galaxies near and far, early-type or late-type. 
            Double-\ser{} model can further simulate galaxy with more realistic 
            structural details (e.g. bulge$+$disk).
            For each \ser{} component, user needs to provide the magnitude, 
            effective radius ($R_{\mathrm{e}}$; in unit of arcsec), \ser{} index 
            ($n_{\mathrm{Ser}}$), axis ratio ($\mathrm{b}/\mathrm{a}$), and position 
            angle (PA).
            External shear can also be applied to synthetic galaxy ($g_1$ and $g_2$; 
            see \citealt{Rowe2015} for more details).

        \item \textbf{Models or real images of galaxy from the GREAT3 challenge}: 
            In stead of providing detailed model information for each galaxy, \synpipe{}
            also allows users to choose from the parametric models or real 
            high-resolution images of galaxies used in the GREAT3 WL challenge. 
            The images are from the \hst{}/ACS F814W ($I$-band) images of the galaxies 
            in the COSMOS field (e.g. \citealt{Scoville2007}). 
            These ACS exposures are 50\% completed down to $I=26.0$ mag in aperture with 
            0.5\asec{} diameter.  
            The depth and excellent resolution (0.09\asec FWHM) make it adequate to test 
            galaxies at Wide depth in HSC survey.
            In addition to the real cutout image, the COSMOS galaxies with 
            $I_{\mathrm{Auto}}\leq25.2$ mag are modelled via method developed by
            \citet{Lackner2012}, and the best parametric model for each of them is 
            selected between the single-\ser{} and the \ser{} bulge$+$Exponential disk 
            ones. 
            Information for these models are stored in the 
            \texttt{GalSim.COSMOSCatalog()} catalogs. 
            To use them, user can provide the ID number of the COSMOS galaxies in the 
            input catalog, or simply let \synpipe{} randomly select them for you.

    \end{itemize}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%     
\subsubsection{Injection of Synthetic Objects to Single-\visit{} Image}
    \label{sssec:addFakes}

    With the input catalog and information about the test data, \synpipe{} first 
    injects synthetic objects to single exposure images (step \texttt{addFakes.py}; 
    see the middle panel of Fig \ref{fig:flowchart}). 
    For each \visit{}, \synpipe{} goes through all the individual CCD images 
    that belong to it, and decides which synthetic objects from the input catalog need
    to be injected. 
    \synpipe{} makes use of the \textit{initial astrometric calibration} of each single 
    \visit{} to convert the input coordinates into locations on the CCD image. 
    Using the available models, \synpipe{} will reconstruct the PSF at the position of 
    each injected object.
    To convert the input magnitudes of synthetic objects into fluxes on the image, 
    \synpipe{} also uses the photometric zeropoint from single-\visit{} 
    calibration.

    For point sources, \synpipe{} generates a rectangular cutout image of the PSF model 
    with appropriate size and correct total flux. 
    For galaxy described by single- or double-\ser{} models, \synpipe{} passes the input 
    \ser{} index and effective radius to the \galsim{}\texttt{.Sersic} function to 
    create a \ser{} component.
    After stretching and rotating it to expected axis ratio and position angle 
    via the \texttt{shear} and \texttt{rotate} methods, \synpipe{} assigns correct flux 
    to this component. 
    For double-\ser{} model, \galsim{}\texttt{.Add} method is used to combine the two 
    \ser{} components together. 
    For parametric models from the GREAT3 catalog, \synpipe{} utilizes the 
    \texttt{COSMOSCatalog.makeGalaxy} method to generate corresponding model, 
    and the \galsim{}\texttt{.RealGalaxy} method is used for the case of real 
    high-resolution image. 
    If necessary, additional shear ($g_1$ and $g_2$) can be applied to the model at this 
    point. 
    Then, \synpipe{} passes the reconstructed PSF image into a 
    \galsim{}\texttt{InterpolatedImage} object and convolves it with the galaxy model  
    using \galsim{}\texttt{.Convolve}. 
    After this, \synpipe{} uses \galsim{}\texttt{.drawImage} method to create the image 
    of the simulated galaxy. 
    Component with high \ser{} index ($n_{\mathrm{Ser}} > 4$) often requires large image 
    size to cover most of its total flux, so \synpipe{} allows user to truncate model 
    at certain radius (N$\times R_{\mathrm{e}}$). 
    It will also give warning information when component with $n_{\mathrm{Ser}} > 6$ is 
    encountered. 
    Such model takes much longer time to achieve accurate PSF convolution, and is usually 
    not realistic galaxy model.

    \synpipe{} then shifts the image of synthetic object according to is location on the 
    CCD on a pixel-by-pixel basis; it also crops the images when necessary. 
    Afterwards, \synpipe{} adds appropriate noise to the image based on the pixels it 
    covers and the calibration information of the detector, and create a variance image 
    that reflects the influence of the synthetic object. 
    Since each HSC CCD consists of four amplifiers with different characteristics, 
    \synpipe{} carefully creates corresponding gain map to provide accurate noise level. 
    Finally, \synpipe{} adds the noise-added image and the variance map to the original 
    CCD data while also adding a new \texttt{FAKE} mask bit to the mask plane. 
    On the middle panel of Fig \ref{fig:flowchart}, we demonstrate the result of the 
    \texttt{addFakes.py} step by showing an example CCD image before and after the 
    synthetic objects are injected. 
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%     
\subsubsection{Stacking and Multi-band Measurements}
    \label{sssec:multiband}

    These newly generated sing-\visits{} images have the same format and data 
    structure of the real HSC data, therefore \synpipe{} can directly feed them 
    to the rest steps of \hscpipe{}. 
    The \texttt{stack.py} step takes the improved astrometric and photometric 
    calibrations for each \visit{} from the original reduction and create 
    \texttt{coadd} images with synthetic objects on them. 
    Then the \texttt{multiBand.py} step will process these \texttt{coadd} images and 
    provide standard mulit-band measurements in FITS catalogs that are grouped by 
    \texttt{Patch} ID.

    Using the infrastructures provided by \hscpipe{}, the above processes can be 
    easily parallelized, and the overall efficiency of \synpipe{} is similar to the
    real data reduction process. 
    They also generate the same amount of images and catalog data with the original 
    one.

    As the last step, \synpipe{} matches the input catalog to the results within a 
    radius that is specified by the user, and merge all the \unforced{} and 
    \forced{} measurements from all the \texttt{Patches} together. 
    Unmatched object from the input catalog is also passed to the result catalog with 
    special label. 
    In case of multiple matches, user can choose between only returning the nearest 
    one or returning all objects within the matching radius (the nearest one is 
    labeled).  
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Star Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_sample}
    \end{center}
    \caption{
        Magnitude and color distributions of the synthetic stars. 
        \textbf{Upper panel} shows the 5-band magnitude distributions of the COSMOS 
        stars (filled histograms) and the resampled stars (dashed lines). 
        \textbf{Lower panel} shows their color-color distributions 
        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$). 
        We show the number density distribution of the COSMOS stars in hexagonal bins, 
        and use contours for the resampled stars.
        }
    \label{fig:star_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Galaxy Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sample}
    \end{center}
    \caption{
        Distributions of 5-band magnitudes (\textbf{upper panel}) and other properties 
        (\texttt{lower panel}; from left to right are the \ser{} index, axis ratio, 
        effective radius in arcsec, the $g-r$ and $r-z$ colors) of the synthetic 
        galaxies.
        Objects used for the \textbf{Tract} with good seeing (filled histograms) and 
        the one with bad seeing (dashed line) have almost identical distributions.
        }
    \label{fig:galaxy_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Generation of Synthetic Dataset}
    \label{sec:test}

    Here we demonstrate the application of \synpipe{} via testing the basic performance 
    of HSC photometry for both stars and galaxies.

%% ------------------------------------------------------------------------------------ %% 
\subsection{Test Data}

    Given the design of \synpipe{} and the data volume of HSC DR1\footnote{${\sim}70$ 
    TB of images}, it is not realistic to test the whole dataset. 
    For this work, we select two \tracts{} in HSC Wide regions 
    that fit the following criteria:

    \begin{enumerate}

        \item Not at the edge of any Wide region, so the full \tract{} is 
            useful for test.

        \item Not bothered by extremely bright ($i<12$ mag), saturated star.

        \item Can represent good and bad seeing condition in the current $i$-band
            data of HSC survey.  
            For the same star or galaxy, different seeing conditions affect its 
            central S/N on the \texttt{coadd} images, hence it also impacts the 
            detection and deblending processes in \hscpipe{}. 
            Therefore, it is useful to show the photometric uncertainties under 
            different seeing conditions.

    \end{enumerate}

    \noindent These regions are: 
    \tract{}$=9699$ in the VVDS field (median FWHM$=0.449$\asec{} in $i$-band; 
    will be referred as \texttt{goodSeeing}) and
    \tract{}$=8764$ in the XMM-LSS field (median FWHM$=0.700$\asec{}; 
    \texttt{badSeeing}). 
    \tract{}$=9699$ also has better seeing in both $r$ and $z$-band; 
    their seeing conditions in $g$ and $y$ bands are very similar.    
    For both \tracts{}, the \texttt{coadd} image in each band includes data from 
    20--40 \visits{}.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\subsection{Input Models for Stars and Galaxies}
    \label{ssec:inputs}

    In this work, we use objects from the high-resolution \hst{}/ACS observations of 
    the COSMOS field to build input catalogs of realistic synthetic stars and galaxies 
    with appropriate completeness for the Wide survey and reasonable five-band colors.

    For stars, we choose to use the sample from \citet{Leauthaud2007}. 
    The authors select stars with clean photometry from the COSMOS images using not 
    only the \texttt{SExtractor} stellar classification index (\texttt{CLASS\_STAR}), 
    but also the peak surface brightness above background (\texttt{MU\_MAX}) and 
    half-light radius (\texttt{RHL}).
    The classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag.  
    We match this sample of stars with the HSC UltraDeep--COSMOS data that currently 
    reaches to about ${\sim}27.2$ mag in $i$-band. 
    After filtering the matched sample through basic quality cuts (see \ref{app:qc}),
    we gather 5-band HSC photometry for 14472 stars.
    To get a larger sample for the test, we resample the their 5-band magnitudes
    distributions using the \texttt{astroML} (\citealt{astroml}) alternative 
    implementation of the \texttt{extreme-deconvolution} algorithm developed by 
    \citet{Bovy2011}
    \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to 
    generate 100000 synthetic stars. 
    In Fig \ref{fig:star_sample}, we show the magnitude and color distributions of 
    the real COSMOS stars are nicely recovered by the resampled stars in all 
    five-band magnitude and two color-color space.

    As for synthetic galaxies, we choose to use the single-\ser{} model of galaxies
    in the COSMOS field that have $I_{F814W} \leq 25.2$ mag. 
    These models are created via method developed by \citet{Lackner2012} on the 
    \textit{HST}/ACS images, and are included in \galsim{}. 
    Each model is described by a total of 5 parameters: magnitude, effective radius, 
    \ser{} index, axis ratio, and position angle. 
    Although the single-\ser{} model is not always the best choice, its flexibility 
    enables it to reasonably describe the flux distribution of most galaxies.
    Also its simplicity makes it easy to diagnose potential problems of the
    \cmodel{} photometry. 
    We exclude a tiny fraction of ill-behaved models that have very high \ser{} 
    index ($n_{\mathrm{Ser}} > 6.0$) or very low central surface brightness 
    ($\mu_{i} < 24.0$\sb). 
    We further match this COSMOS sample with the HSC UltraDeep--COSMOS data. 
    after removing the objects with problematic photometry, we obtain the a sample of 
    58210 synthetic galaxies with realistic 5-band HSC photometry. 
    As shown in Fig \ref{fig:galaxy_sample}, the majority of these galaxies are 
    faint ($i<24.0$ mag) and barely resolved ($R_{\mathrm{e}}< 1.0$\asec) galaxies. 
    This sample is appropriate to test the general behaviours of photometry in 
    \hscpipe{}, but is lack of relative bright galaxies ($i<20.5$ mag).

    We then create input catalogs via randomly distribute these synthetic stars and 
    galaxies into the regions covered by the good and bad seeing \tracts{}. 
    For stars (galaxies), we choose to use number density of 1000 (500)
    per CCD.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\subsection{Running \synpipe{} Test}
    \label{ssec:running}

    We conduct these tests on the cluster (\texttt{Master}) at Kavli-IPMU using 
    the HSC DR1 data stored there. 
    The \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in each 
    band; same process takes longer for the test of galaxies (${\sim}3.0$ hours per
    \tract{} in each band) as the \galsim{} simulation is more time consuming. 
    The \texttt{stack.py} and \texttt{multiBand.py} together take ${\sim}3.5$ hours
    per \tract{}.

    We match the results with the input catalogs using a 2 pixels matching radius 
    to generate output catalogs for \forced{} and \unforced{} photometry 
    in each band. 
    We also match the input catalogs with the original HSC catalogs to identify the 
    ``ambiguously blended'' objects that are right on top of the flux peak of a real 
    object.  
    These objects are useful in the WL-related statistical tests (see Murata et al. 
    in prep. for more details), but will not help test photometry, hence they will 
    be excluded later

    The detailed log of the entire tests can be found here:
    \url{goo.gl/VINOVP}.
    User should be able to reproduce the results presented in this work using this 
    information. 
    It can also serve as a brief manual for running \synpipe{} test.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Results on Photometric Performance}
    \label{sec:result}

    Here we show the general performance of \hscpipe{} for stars (galaxies) 
    mainly through the \forced{} PSF (\cmodel{}) photometry. 
    Although \hscpipe{} provides more options (e.g. aperture and Kron photometry), 
    these two are the most appropriate and relevant ones for magnitude and colors of 
    star and galaxy as they consider the effects of PSF in different bands, 
    and are consistent across all bands in terms of position and shape.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Magnitude v.s S/N for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
    \end{center}
    \caption{
        Relations between input magnitudes (\textbf{left}: $i$-band; \textbf{right}: 
        $g$-band) of synthetic stars and the $log(S/N)$ measured by \hscpipe{} PSF 
        photometry.  
        Hexagonal binned density plots and contours show the distributions for 
        stars in the \tract{} with good and bad seeing. 
        The highly blended stars are highlighted using scatter plots. 
        A grey dashed line marks $S/N = 5$.
        }
    \label{fig:star_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Accuracy of Forced PSF Magnitudes
\begin{figure*}
    \begin{center}
        \includegraphics[width=16cm]{fig/synpipe_psf_mag}
    \end{center}
    \caption{
        Accuracies of the \texttt{hscpipe} PSF photometry for synthetic stars measured
        by the difference between input and output \forced{} PSF magnitudes. 
        Plot [a, b, c, d, e] shows the results for [$g$, $r$, $i$, $z$, $y$]-band. 
        In each plot, left panel shows the relation between input magnitude and 
        magnitude difference. 
        Hexagonal binned density plot and contour are for the synthetic galaxies from 
        good and bad seeing \tracts{}. 
        Highly blended objects are highlighted using scattered plot. 
        The long-dashed line marks zero magnitude difference, while the pair of 
        dashed lines outline the running-median of PSF magnitude errors 
        (including the uncertainties in aperture correction). 
        Right panel shows the distributions of the magnitude differences for objects 
        in good (filled) and bad (solid line) seeing \tracts{}. 
        The dashed line is for the distribution of highly blended objects. 
        }
    \label{fig:psf_mag}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Difference between the Unforced and Forced Magnitudes
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_diff}
    \end{center}
    \caption{
        The magnitude differences between the \unforced{} and \forced{}
        PSF photometry for synthetic stars in $g$- (\textbf{left} and $y$-band 
        (\textbf{right}). 
        Other formats are identical to the plots in Fig \ref{fig:psf_mag}.
        }
    \label{fig:psf_diff}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Accuracies of the PSF color
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_color}
    \end{center}
    \caption{
        Accuracies of the color measurements for synthetic stars via the differences
        between input and \forced{} PSF colors. 
        The \textbf{Upper panels} and \textbf{lower panels} are for $g-i$ and $i-y$ 
        colors separately.
        The \textbf{left} column shows the relation between input magnitude and 
        the color difference, and the \textbf{right} one uses the input colors as
        x--axis instead. 
        Other formats are identical to the plot in Fig \ref{fig:psf_mag}.
        }
    \label{fig:psf_color}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Color-Color Distributions of the Input and Measurements for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_cdist}
    \end{center}
    \caption{
        Evaluations of the accuracy of color measurements for synthetic stars using 
        the color-color distributions. 
        \textbf{Left} uses $(g-r)$ v.s. $(r-i)$ colors, and the \textbf{right} one 
        uses $(i-z)$ and $(z-y)$ colors. 
        The filled contours and shaded histograms reflect the distributions for input 
        colors. 
        The empty contours and solid-line histograms show the distributions recovered 
        by \hscpipe{}. 
        }
    \label{fig:psf_cdist}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%     
\subsection{PSF photometry of Stars}
    \label{ssec:psf}

    In \hscpipe{}, the PSF magnitude is derived using matched-filter method that 
    depends on the best-fit PSF model and uses the Lanczos interpolation to shift 
    PSF model. 
    The error of PSF magnitude from \hscpipe{} only considers the per-pixel noise, 
    not the uncertainty of the centroid. 
    \hscpipe{} also estimates aperture correction for PSF photometry. 
    For more details please see Section 4.9.5 of Bosch\etal (in prep.).

    In our tests, we randomly inject ${\sim}100000$ stars to each \tract{} in all 
    five-bands. 
    Among these stars, ${\sim}3$--$4$\% of them locate within 2 pixels to the centroids
    of real objects. 
    We remove them from the sample to avoid confusion in the comparisons. 
    After this step, there are still ${\sim}1$--$3$\% of the remaining synthetic stars 
    have no match in the \synpipe{} outputs. 
    They could be either below the detection threshold or ambiguously blended with real
    objects. 
    The input $i$-band magnitudes of these unmatched stars are on average ${\sim}0.9$
    mag fainter than the matched ones. 
    The fraction of unmatched stars is slightly higher in the bad seeing \tract{},
    which is consistent with the expectation of seeing-dependent limit magnitude,  
    although the difference in not very significant.     
    For the matched stars, we select the primary detections 
    (\texttt{detect.is-primary=True}) that have good photometric quality 
    (see Appendix \ref{app:qc} for details). 
    This gives us ${\sim}83000$ stars in each \tract{}.

    Next, we isolate the stars that are misidentified by \hscpipe{} as extended 
    objects using the \texttt{classification.extendedness} parameter in each band. 
    The fraction of misclassification is ${\sim}8$--$15$\%, and clearly depends on 
    seeing conditions. 
    For the same reason, $g$-band has the highest fraction of misclassification, 
    while $i$-band is recommended for selecting point sources.  
    The misclassified stars are on average ${\sim}1$ mag fainter than the others.
    We exclude them from the photometric comparison below, and will further discuss 
    the star--galaxy separation issue in Section \ref{ssec:sg}.

    In the following comparisons, we will always show the results from the 
    \textbf{good seeing} and \textbf{bad seeing} \tracts{} separately, because it 
    is important to understand the impact of seeing on photometric accuracies, 
    and to test whether \hscpipe{} can deliver unbiased photometry under different 
    seeing conditions.

    Besides seeing, ``blendedness'' ($b$; parameter that describes on what level 
    the flux distribution of one object is affected by others; please see 
    Appendix \ref{app:defineb} for precise definition, and see Murata\etal in prep. 
    for details) is another factor that influences the photometric accuracy. 
    We therefore separate the samples into relative isolated and highly blended 
    groups based on the $b$ values. 
    Assuming zero pixel noise, $b$ of object $A$ reflects the fraction of flux 
    within the \texttt{Footprint} of $A$ that comes from other objects.  
    Ideally, $b=0$ means perfect isolation, and $b{\sim}1$ means completely 
    confused with other object. 
    Here we use $b>0.05$ to define blended stars (${\sim}4$--$9$\%). 
    Fraction of highly blended stars slightly increases in the bad seeing \tract{}. 
    We highlight these stars separately as well, and will discuss more about the 
    impact of blendedness in Section \ref{ssec:blendedness}.

\subsubsection{Input magnitude and the $\mathrm{S}/\mathrm{N}$ of PSF photometry}

    \begin{itemize}

        \item In Fig \ref{fig:star_sn}, we show the relations between the input
            magnitude and the $\mathrm{S}/\mathrm{N}$ recovered by \hscpipe{}
            photometry in $g$- and $i$-band.

        \item \plan{Define $\mathrm{S}/\mathrm{N}$, quickly explain the purpose.}

        \item \plan{At fixed input magnitude, PSF $\mathrm{S}/\mathrm{N}$ depends 
            on seeing conditions. 
            For $i$-bands, the two \tracts{} have quite different seeing. 
            And bad seeing leads to clearly lower $\mathrm{S}/\mathrm{N}$.}

        \item \plan{Briefly discuss the detection limit of point sources. 
            Basically consistent with the reported values in \citet{HSCDR1}.}

        \item \plan{Blendedness can reduce the $\mathrm{S}/\mathrm{N}$ a little.}

    \end{itemize}

\subsubsection{Accuracy of PSF magnitude}

    \begin{itemize}

        \item In Fig \ref{fig:psf_mag}, we evaluate the accuracies of \hscpipe{} PSF 
            magnitudes in all five bands.

        \item \plan{The overall performance of PSF photometry is good. 
            In $i$-band, the median magnitude difference is around ${\sim}0.015$ mag
            (${\sim}1.5$\% accuracy) at $i_{\mathrm{Input}}{\sim}19.0$ mag. 
            At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of PSF 
            magnitude is around $3$\%. 
            Down to $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy is 
            around 7\%.
            This is consistent with the external check in \citet{HSCDR1}.}

        \item \plan{At fixed input magnitude, the accuracy does not strongly depends
            on filters. 
            The only exception is the $y$-band, which has slightly worse accuracy. 
            At $y_{\mathrm{Input}}{\sim}23.5$, the average accuracy is already close 
            to $10$\%.}
            \todo{Possible causes? background noise? Worse PSF model?}

       \item \plan{The \forced{} PSF magnitude provides unbiased estimates for
           isolated stars. 
           For $grzy$-bands, the median magnitude difference is ${\sim}0.002$ mag, 
           and can be ignored.}

       \item \plan{Using $i$-band as example, although worse seeing leads to 
           lower $\mathrm{S}/\mathrm{N}$, it does not strongly impact the 
           accuracy of the PSF magnitude. 
           The bad seeing \tract{} suggests almost identical accuracy comparing
           to the good seeing one.}

       \item \plan{However, the story for highly blended stars is quite different. 
           \hscpipe{} systematically under-estimate the total flux of highly blended
           stars by $0.05$--$0.10$ mag at fixed input magnitude.}

       \item \plan{We also test the \unforced{} PSF photometry in all five 
           bands. 
           The results suggest very similar accuracy.
           We highlight the differences between \forced{} and 
           \unforced{} PSF photometry in Fig \ref{fig:psf_diff}. 
           The overall difference is quite small, but it seems that \hscpipe{} 
           \unforced{} PSF photometry recovers slightly more flux at very 
           faint end.} 
           \todo{Move the figure to appendix?}

    \end{itemize}

\subsubsection{Accuracy of the PSF colors}

    \begin{itemize}

        \item \plan{Briefly explain why PSF colors are important; we focus on the 
            \forced{} PSF colors here}

        \item The results for accuracy of \forced{} PSF colors are shown in 
            Fig \ref{fig:psf_color} and Fig \ref{fig:psf_cdist}.

        \item \plan{In Fig \ref{fig:psf_color}, we investiage how \forced{}
            PSF colors depend on input magnitude and colors using both $(g-i)$ and 
            $(i-y)$ colors. 
            Results suggest \hscpipe{} \forced{} PSF photometry can provide 
            accurate and unbiased colors for stars in our tests.
            The uncertainties do not show any significant dependence on neither input
            magnitude nor color.}

        \item \plan{For $(g-i)$ color, average uncertainty around 
            $i_{\mathrm{Input}}{\sim}19.0$ mag is ${\sim}0.025$ mag. 
            The uncertainty increases to ${\sim}0.11$ mag at
            $i_{\mathrm{Input}}{\sim}25.0$ mag. 
            Results for $(i-y)$ color is similar.}

        \item \plan{In Fig \ref{fig:psf_cdist}, we use the results from the bad 
            seeing \tract{} to show that the \forced{} PSF photometry 
            can accurately recover the color-color sequences of stars down to 
            $i{\sim}25$ mag.}

        \item \plan{Accuracy of \forced{} PSF photometry apparently does not 
            strongly depend on seeing condition. 
            Impact from blendedness on PSF color is less serious than the magnitude, 
            although highly blended stars still show worse color accuracy and 
            systematically bluer (redder) $(g-i)$ ($i-y$) colors. 
            \unforced{} PSF photometry show similar but slightly worse 
            accuracy than the \forced{} ones. }

    \end{itemize}

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Magnitude v.s S/N for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sn}
    \end{center}
    \caption{
        Relations between input magnitudes (\textbf{left}: $i$-band; \textbf{right}: 
        $g$-band) of synthetic galaxies and the $log(S/N)$ measured by \hscpipe{}
        \cmodel{} photometry.  
        Other formats are very similar to Fig \ref{fig:star_sn}
        }
    \label{fig:cmodel_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Accuracy of Forced cModel Magnitudes for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=16cm]{fig/synpipe_galaxy_mag}
    \end{center}
    \caption{
        Accuracies of the \texttt{hscpipe} \cmodel{} photometry for synthetic 
        galaxies measured by the difference between input and output \forced{} 
        \cmodel{} magnitudes. 
        Plot [a, b, c, d, e] shows the results for [$g$, $r$, $i$, $z$, $y$]-band. 
        Other formats are identical to Fig \ref{fig:psf_mag}.
        }
    \label{fig:cmodel_mag}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Difference between the Unforced and Forced Magnitudes
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_cmodel_diff}
    \end{center}
    \caption{
        The magnitude differences between the \unforced{} and \forced{}
        \cmodel{} photometry for synthetic galaxies in $g$- (\textbf{left} and 
        $y$-band (\textbf{right}). 
        Other formats are identical to the plots in Fig \ref{fig:psf_diff}.
        }
    \label{fig:cmodel_diff}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Accuracies of the cModel color for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_color}
    \end{center}
    \caption{
        Accuracies of the color measurements for synthetic galaxies via the 
        differences between input and \forced{} \cmodel{} colors. 
        The \textbf{Upper panels} and \textbf{lower panels} are for $g-i$ and $i-y$ 
        colors separately.
        The \textbf{left} column shows the relation between input magnitude and 
        the color difference, and the \textbf{right} one uses the input colors as
        x--axis instead. 
        Other formats are identical to the plot in Fig \ref{fig:psf_color}.        
        }
    \label{fig:cmodel_color}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Color-Color Distributions of the Input and Measurements for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_cdist}
    \end{center}
    \caption{
        Evaluations of the accuracy of color measurements for synthetic galaxies 
        using the color-color distributions. 
        \textbf{Left} uses $(g-r)$ v.s. $(r-i)$ colors, and the \textbf{right} one 
        uses $(i-z)$ and $(z-y)$ colors. 
        The filled contours and shaded histograms reflect the distributions for input 
        colors. 
        The empty contours and solid-line histograms show the distributions recovered 
        by \hscpipe{} \cmodel{} photometry.
        }
    \label{fig:galaxy_cdist}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%     
\subsection{cModel photometry of Galaxies}
    \label{ssec:cmodel}

    \cmodel{} algorithm is the primary photometric method for galaxies in 
    \hscpipe{} that can be seen as an improved version of the SDSS \cmodel{} 
    photometry. 
    For more details, please see Section 4.9.8 of Bosch\etal (in prep.). 
    Basically, \cmodel{} tries to fit each object using a combination of de Vaucouleur
    and exponential profiles that are approximated by multiple Gaussian profiles. 
    Despite the limitation of the \cmodel{} method (e.g. sensitive to background 
    subtraction and deblender failure), it can deliver robust PSF-corrected fluxes and 
    colors for galaxies.

    \begin{itemize}

        \item \plan{${\sim}2$--$3$\% of the injected synthetic galaxies are 
            ambiguously blended with real objects.}

        \item \plan{Excluding the ambiguously blended ones, ${\sim}4$--$8$\% of the 
            remaining synthetic galaxies do not have any match.
            The unmatched galaxies are systematically fainter than the matched ones.
            And the fraction of unmatched synthetic galaxies is also slightly higher 
            in the bad seeing \tract{} than the one with good seeing.
            Similarly, $g$- and $i$-band have higher fraction of unmatched objects.
            }

       \item \plan{From the rest of the matched galaxies, we only keep the primary 
           detections (\texttt{detect.is-primary=True}) and the ones with clean 
           photometry (see Appendix \ref{app:qc} for details). 
           For each \tract{}, there are ${\sim}30000$ galaxies left.}

       \item \plan{A tiny fraction of synthetic galaxies is misclassified as 
           point sources by \hscpipe{}. 
           And the fraction of misclassifications seems to increase with seeing 
           (${\sim}1$\% in good seeing \tract{}; ${\sim}4$\% in bad seeing \tract{}). 
           We will further discuss in Section \ref{ssec:sg}.}

       \item \plan{We also use $b>0.05$ to define samples of highly blended galaxies.
           Since synthetic galaxies are more extended, their distribution of $b$
           skew more toward the higher value. 
           About ${\sim}7$--$9$\% of galaxies are highly blended by this standard.
           The $g$-band has significantly higher fraction of highly blended objects.}

    \end{itemize}

\subsubsection{Input magnitude and the $\mathrm{S}/\mathrm{N}$ of \cmodel{} photometry}

    \begin{itemize}

        \item In Fig \ref{fig:cmodel_sn}, we show the relations between the input
            magnitude and the $\mathrm{S}/\mathrm{N}$ recovered by \cmodel{}
            photometry in $g$- and $i$-band.

        \item \plan{Define $\mathrm{S}/\mathrm{N}$. 
                    Unlike point sources, at fixed total magnitude, the 
                    synthetic galaxies have a range of size and shape that 
                    lead to different average surface brightness. 
                    Comparing to stars, at the same input magnitude, synthetic
                    galaxies have lower average $\mathrm{S}/\mathrm{N}$ and larger 
                    scatter. }

        \item \plan{Seeing condition still impacts the $\mathrm{S}/\mathrm{N}$ of
                    galaxies}

        \item \plan{Blendedness can reduce the $\mathrm{S}/\mathrm{N}$ a little.}

        \item \plan{Briefly discuss the detection limit of point sources. 
            Basically consistent with the reported values in \citet{HSCDR1}.
            Although at $i{\sim}25.2$, the average $\mathrm{S}/\mathrm{N}$ is quite high,
            small fraction of galaxies will have very low $\mathrm{S}/\mathrm{N}$.}

    \end{itemize}

\subsubsection{Accuracy of the \cmodel{} magnitude}

    \begin{itemize}

        \item In Fig \ref{fig:cmodel_mag}, we evaluate the accuracies of the \forced{}
            \cmodel{} magnitudes in all five bands.

        \item \plan{Generally speaking, the \forced{} \cmodel{} provides good estimates 
            of magnitudes for galaxies between 20.0 and 25.0 magnitude in all filters and 
            different seeing conditions. }

        \item \plan{For $i$-band the absolute flux accuracy is around 7\% level at 
            $i{\sim}21.0$ mag, and it increases to ${\sim}10$\% at $i{\sim}25.0$ mag.
            The \forced{} \cmodel{} photometry slightly underestimate the total flux of 
            galaxies at $21.0 < i < 23.0$ mag. 
            The average magnitude difference is at 0.04 mag level. 
            For $i > 23.0$ mag, the \forced{} \cmodel{} photometry is unbiased.}

        \item \plan{The \forced{} \cmodel{} magnitude error from \hscpipe{} only considers 
            the per pixel noise, but not the systematic uncertainties involved in the 
            modeling fitting process.
            Therefore it is no surprise that the typical uncertainty from the \synpipe{} 
            test is larger than the magnitude error.}

        \item \plan{The accuracies of the \forced{} \cmodel{} magnitudes in other bands 
            are similar to the $i$-band.  
            The only exception is for galaxies with $y<24.0$ mag where \forced{} \cmodel{}
            seems to overestimate the flux slightly.}

        \item \plan{For galaxies with $i < 20.0$, the statistics are uncertain due to small 
            sample size}

        \item \plan{Unlike the synthetic stars, the highly blended synthetic galaxies only 
            have slightly biased photometry, where \forced{} \cmodel{} underestimates the 
            fluxes of these galaxies by ${\sim}0.05-0.10$ mag. 
            High blendedness does lead to larger scatter in photometric uncertainties.}

       \item \plan{We also test the \unforced{} \cmodel{} photometry in all five bands, 
           and the results suggest similar accuracies.
           We highlight the differences between \forced{} and 
           \unforced{} \cmodel{} photometry in Fig \ref{fig:cmodel_diff}.}

    \end{itemize}

\subsubsection{Accuracy of the \cmodel{} color}

    \begin{itemize}

        \item \plan{Briefly explain why \cmodel{} colors are important.}

        \item The results for accuracy of \forced{} \cmodel{} colors are shown in 
            Fig \ref{fig:cmodel_color} and Fig \ref{fig:cmodel_cdist}.

        \item \plan{\forced{} \cmodel{} photometry provides accurate and unbiased 
            colors for galaxies at $20.0 < i < 25.0$ mag at different seeing conditions.
            The accuracies of colors also do not show dependence on input colors. 
            }

        \item \plan{For $(g-i)$ color, average uncertainty around 
            $i_{\mathrm{Input}}{\sim}21.0$ mag is ${\sim}0.04$ mag. 
            The uncertainty increases to ${\sim}0.11$ mag at
            $i_{\mathrm{Input}}{\sim}25.0$ mag. 
            Results for $(i-y)$ color is similar.}

        \item \plan{High blendedness can increase the uncertainties of the color 
            and bias the color measurements. 
            The highly blended galaxies on average show slightly bluer $(g-i)$ colors 
            and redder $(i-y)$ colors comparing to the input values.}

        \item \plan{In Fig \ref{fig:cmodel_cdist}, we show that the \forced{} \cmodel{} 
            photometry can reasonably recover the color-color distributions of galaxies 
            down to $i{\sim}25$ mag.
            }

    \end{itemize}

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Astrometric Calibration
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_astrometry}
    \end{center}
    \caption{
        Astrometric accuracy for synthetic star (\textbf{left}) and galaxy 
        (\textbf{right}) via the differences in R.A and Dec between the input
        coordinates and the ones measured on the coadd images. 
        Hexagonal bins (filled histogram) and contours (solid-line histogram) are for 
        the synthetic objects from \tracts{} with good and bad seeing conditions. 
        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.
        }
    \label{fig:astrometry}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Star-Galaxy Separation
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_star_galaxy}
    \end{center}
    \caption{
        Illustrates the problems with current star--galaxy separation method in 
        \hscpipe{} which is based on the magnitude difference between the PSF and 
        \cmodel{} photometry. 
        \textbf{Left} plot is for the synthetic stars. 
        Hexagonal bins and filled histogram show distributions of correctly classified 
        synthetic stars in the good seeing \tract{}. 
        The scatter plot (dashed-line histogram) and contour (solid-line histogram) 
        show distributions of synthetic stars that are misclassified as extended 
        objects in \tracts{} with bad and good seeing conditions. 
        \textbf{Right} one is for synthetic galaxies. 
        Here the hexagonal bins (filled histogram) and contours (solid-line histogram)
        are for galaxies from good and bad seeing \tracts{}. 
        The scatter plot and dashed-line histogram are for synthetic galaxies that are 
        misclassified as point sources.
        Zero magnitude difference is highlighted using dashed lines on both plots.
        }
    \label{fig:sg}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Relations between Blendedness and Photomertic Errors
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_blendedness_err}
    \end{center}
    \caption{
        Shows the relationships between the $\log(\mathrm{Blendedness})$ parameter
        and the photometric accuracies for synthetic stars (\textbf{upper row}) and 
        galaxies (\textbf{lower row}). 
        \textbf{Left} column is for uncertainties of PSF or \cmodel{} magnitude, 
        and the \textbf{right} one is for uncertainties of $(g-i)$ color. 
        Hexagonal bins and contours show results for good and bad seeing 
        \tracts{}.
        $\log(\mathrm{Blendedness}) = -1.0$ is marked using vertical dashed line. 
        }
    \label{fig:blend}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: Compare with the behaviours of the Kron photometry for galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_kron}
    \end{center}
    \caption{
        Basic performance of the Kron photometry for synthetic galaxies. 
        \textbf{Left} shows the accuracy in $i$-band. 
        magnitude. The format is identical to Fig \ref{fig:galaxy_mag}.
        \textbf{Right} shows the accuracy of the $(g-i)$ color using 
        Kron photometry. 
        Other formats are identical to Fig \ref{fig:cmodel_color}.
        }
    \label{fig:galaxy_kron}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%% Fig: HSC cModel has problem recovering the size and shape of galaxies
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_ba}
    \end{center}
    \caption{
        Shows the accuracy of the weighted axis ratio measurements for synthetic 
        galaxies using \cmodel{} photometry. 
        \textbf{Left} shows the relation between the input $(b/a)$ and the 
        uncertainties of $(b/a)$ estimates. 
        \textbf{Right} shows the relation between input magnitude of synthetic galaxy
        and the $(b/a)$ uncertainties. 
        Contours are for the default test with \texttt{usePixelWeights=False}, and the 
        hexagonal bins are used for same tests with \texttt{usePixelWeights=True}.
        }
    \label{fig:galaxy_ba}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%

\section{Results on Other Performance}
    \label{sec:others}

%% ------------------------------------------------------------------------------------ %%     
\subsection{Astrometric Calibration} 
    \label{ssec:astrometry}

    \begin{itemize}

        \item \plan{Explain what we are testing here; and why it is useful}

        \item In Fig \ref{fig:astrometry}, we briefly look into the accuracies 
            of the astrometric comparison for both synthetic stars and galaxies in 
            \tracts{} with both good and bad seeing.

        \item \plan{We see small astrometric offsets in both R.A and Dec directions
            that show small differences between the two \tracts{}.
            The average offset is at ${\sim}10$--20 mas, which is consistent with 
            the estimate in \citet{HSCDR1}}.

    \end{itemize}

%% ------------------------------------------------------------------------------------ %%     
\subsection{Star-Galaxy Separation}
    \label{ssec:sg}

    \begin{itemize}

        \item \plan{Explain how star--galaxy separation is done in \hscpipe{}, and 
            why it is difficult at faint magnitudes.}

        \item In Fig \ref{fig:sg}, we highlight the misclassified stars and galaxies 
            on the relations between the input magnitude and 
            $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$.

        \item \plan{The fraction of misclassified stars show dependence on both 
            input magnitude and seeing.}

        \item \plan{Most of the misclassified galaxies have $i > 24.0$. 
            The fraction of misclassification and distribution of 
            $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$ for synthetic galaxies also depend on 
            seeings}.

    \end{itemize}

%% ------------------------------------------------------------------------------------ %%     
\subsection{Blendedness and Photometric Errors}
    \label{ssec:blendedness}

    \plan{Briefly explain the definition of blendedness}

    \plan{Relationship between magnitude and blendedness}

    \plan{How blendedness affects the photometric uncertainties}

%% ------------------------------------------------------------------------------------ %%     
\subsection{Comparing to Kron photometry}

    \plan{Uses $i$-band as example to briefly discuss Kron photometry}

    \plan{Although magnitude for galaxies is Ok, the color becomes worse}

%% ------------------------------------------------------------------------------------ %%     
\subsection{Shape and Structural Parameters of Galaxies}
    \label{ssec:shape}

    \plan{Explain why the current \cmodel{}{} algorithm has problem with measuring 
          the size and shape of galaxies}

    \plan{Briefly showcase the problem, and how small change of \hscpipe{} 
          configuration can improve the situation}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{Summary and Conclusion}
    \label{sec:summary}

    %% Short summary
    The on-going HSC survey just had its first public data release, and is still 
    producing increasingly larger amount of high-quality imaging data. 
    To help achieve the designed goals of the survey and facilitate scientific 
    outputs, we develop \synpipe{}, a flexible framework that is based on the 
    \hscpipe{} to exam the data reduction process and check the accuracy of all the
    pipeline outputs.
    \synpipe{} injects synthetic stars and galaxies to the desired locations on the
    single-\visit{} images with the help of the original astrometric and 
    photometric calibrations.
    These data are then processed by \hscpipe{} to generate the coadd images and 
    all the photometric measurements. 
    In this way, \synpipe{} can simulate the realistic data reduction process
    to an extent that many subtle systematical effects can be taken into 
    consideration, which is helpful for the outstanding scientific goals of the HSC 
    survey. 
    In this work, we choose two \tracts{} in the HSC/Wide layer with 
    representative seeing conditions (good/bad) to test the general behaviors of HSC 
    photometry for both stars and galaxies.

    From these tests, we find:

    \begin{enumerate}

        \item The \forced{} PSF photometry provides excellent magnitude and color 
            measurements for isolated stars at $18.0 < i < 25.0$. 
            The typical uncertainties of HSC forced PSF photometry for stars range 
            from around 0.01 mag at $i{\sim}18.0$ mag to 0.08 mag at $i{\sim}25.0$ 
            mag (1\%-7\% accuracy in the $i$-band).            
            The \forced{} PSF photometry can accurately recover the color--color 
            sequences for stars.

        \item The \forced{} \cmodel{} photometry is reliable for synthetic galaxies 
            with realistic distributions of structural parameters and colors at 
            $20.0 < i < 25.0$ mag. 
            The average accuracy of \forced{} \cmodel{} magnitude ranges from 
            ${\sim}7$\% at $i{\sim}20.0$ mag to ${\sim}10$\% at $i{\sim}25.0$. 
            The \forced{} \cmodel{} colors for galaxies are accurate and unbiased. 
            The accuracies of colors do not show dependence on input magnitude and 
            color.

        \item The \forced{} PSF and \cmodel{} photometry are robust against different 
            seeing conditions, despite that worse seeing leads to lower 
            $\mathrm{S}/\mathrm{N}$ at fixed input magnitude.

        \item High blendedness ($b>0.1$) impacts the accuracy of both PSF and \cmodel{}
            photometry, especially for stars.
            For highly blended stars, the \forced{} PSF photometry on average 
            overestimate the magnitudes of stars by 0.1–-0.2 mag. 
            For galaxies, high-blendedness typically adds an additional 0.05 mag 
            uncertainty in both magnitude and color estimates.

    \end{enumerate}

    Meanwhile, we also notice a few issues in the current \hscpipe{}:

    \begin{enumerate}

        \item The performance of current star--galaxy separation algorithm in \hscpipe{}
            is not perfect, especially at faint magnitude end and under poor seeing 
            condition.  
            The fraction of stars that are misclassified as extended objects is still 
            quite high ($>20$\% at $i> 22.5$ mag).

        \item The \cmodel{} setting right now (\texttt{usePixelWeights=True}) results 
            in very biased estimates of shape and size for galaxies, especially for the 
            relative faint ones. 
            The axis ratio of galaxy using \cmodel{} is highly overestiamted while 
            the effective radius is underestimated. 
            We show that, using \texttt{usePixelWeights=True} instead and significantly 
            improve this situation. 
            However, it may impact the accuracy of deblender, which we will test in the 
            future.

    \end{enumerate}

    The HSC collaboration is working on improving these issues in the future version 
    of \hscpipe{} and the following data release.  
    Meanwhile, we suggest the users of HSC data to keep these caveats in mind. 
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%     
    %% Other applications
    Although we mainly focus on the general behaviors of photometric measurements here, 
    \synpipe{} is quite flexible and has plenty of other applications for any HSC 
    dataset.  
    For instance, in a following paper, Murata\etal (in prep.) uses \synpipe{} to test 
    the impacts of extremely blended objects on the WL measurements. 
    Also, \citep{Niikura2017} applies \synpipe{} to the high-cadence HSC observations 
    of M31 to help the search of interesting microlensing events. 
    At this moment, it is also being used to help select high-$z$ Lyman-break galaxies 
    and Lyman-$\alpha$ emitters (Ono\etal in prep.; Kono\etal in prep); identify 
    low surface brightness dwarf galaxies (Greco\etal in prep); and test photometric 
    and WL measurements around nearby clusters (Chiu\etal in prep).

    %% Caveats
    In the end, it is worth brief discussing the limitations of the current \synpipe{}:

    \begin{enumerate}

        \item \citet{HSCDR1} points out that \hscpipe{} tends to over-subtract the
            background around bright objects. 
            Unfortunately, \synpipe{} now takes the original background subtraction on 
            the single-\visit{} image for granted, hence lacks the capability to 
            test or help improve this problem.

        \item Right now, \synpipe{} simply adopts the PSF measured by \hscpipe{} and 
            use it for model of point source and PSF convolution for galaxy. 
            Hence it can not be used to test how the uncertainty of the PSF modeling 
            affects the photometry and shape measurements. 
            This could be important for regions with exquisite seeing that makes the 
            PSF modeling difficult, and for accurate WL measurements.

        \item \synpipe{} now works in ``unit'' of \visit{} for single exposure 
            test, and \tract{} for test of \texttt{coadd} images. 
            In case of tests that focus on specific regions that are much smaller than
            the size of \visit{} or \tract{} (e.g. quality of photometry 
            around rich galaxy clusters), the usage of \synpipe{} often leads to 
            low efficiency.

    \end{enumerate}

    %% Future developments
    Right now, both \hscpipe{} and \synpipe{} still undergo active development, 
    and \synpipe{} will update accordingly to provide photometric benchmark for 
    each data release of HSC survey, and help \hscpipe{} improve. 
    At the same time, we are also working on improving the efficiency of \synpipe{}.
    Since subtle effects involved in the image stacking process are not the concerns 
    of many topics, we will update \synpipe{} so that it can directly inject 
    synthetic objects to the coadd images and speed up these tests.

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%

\begin{ack}
    \label{sec:ack}

    % HSC part
    The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of 
    Japan and Taiwan, and Princeton University.  
    The HSC instrumentation and software were developed by the National Astronomical 
    Observatory of Japan (NAOJ), the Kavli Institute for the Physics and Mathematics of
    the Universe (Kavli IPMU), the University of Tokyo, the High Energy Accelerator 
    Research Organization (KEK), the Academia Sinica Institute for Astronomy and 
    Astrophysics in Taiwan (ASIAA), and Princeton University.
    Funding was contributed by the FIRST program from Japanese Cabinet Office, the 
    Ministry of Education, Culture, Sports, Science and Technology (MEXT), the Japan 
    Society for the Promotion of Science (JSPS), Japan Science and Technology Agency 
    (JST), the Toray Science  Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton 
    University.

    % LSST software part
    This paper makes use of software developed for the Large Synoptic Survey Telescope. 
    We thank the LSST Project for making their code available as free software at 
    http://dm.lsstcorp.org.

    % Pan-STARRS1 part
    The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the 
    Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, 
    the Max-Planck Society and its participating institutes, the Max Planck Institute 
    for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, 
    Garching, The Johns Hopkins University, Durham University, the University of 
    Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, 
    the Las Cumbres Observatory Global Telescope Network Incorporated, the National 
    Central University of Taiwan, the Space Telescope Science Institute, the National 
    Aeronautics and Space Administration under Grant No. 
    NNX08AR22G issued through the Planetary Science Division of the NASA Science 
    Mission Directorate, the National Science Foundation under Grant No. AST-1238877, 
    the University of Maryland, and Eotvos Lorand University (ELTE) and the Los Alamos 
    National Laboratory.

    % Software part
    This research made use of
    {\texttt{Astropy}}, 
        a community-developed core Python package for Astronomy (\citealt{Astropy}; 
        \url{http://www.astropy.org/}); 
    {\texttt{astroML}}, 
        a machine learning library for astrophysics (\citealt{astroml};
        \url{http://www.astroml.org/});
    {\texttt{SciPy}},
        an open source scientific tools for Python (\citealt{SciPy}; 
        \url{http://www.scipy.org/});
    {\texttt{NumPy}}, 
        a fundamental package for scientific computing with Python (\citealt{NumPy}; 
        \url{http://www.numpy.org/});
    {\texttt{Matplotlib}}, 
        a 2-D plotting library for Python (\citealt{Matplotlib}; 
        \url{http://matplotlib.org/});
    {\texttt{scikit-learn}},
        a machine-learning library in Python (\citealt{scikit-learn}; 
        \url{http://scikit_learn.org/}).

\end{ack}
%% ------------------------------------------------------------------------------------ %%

%%%%%%%%%%: Bibliographic Section %%%%%%%%%%

%\bibliography{synpipe}

%% ------------------------------------------------------------------------------------ %% 
\bibliographystyle{apj}

%% ------------------------------------------------------------------------------------ %% 
\begin{thebibliography}{}
    \label{sec:ref}
    \expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

    %% A %%
    \bibitem[Abazajian et al.(2004)]{Abazajian2004} Abazajian, K., Adelman-McCarthy, 
             J.~K., Ag{\"u}eros, M.~A., et al.\ 2004, \aj, 128, 502

    \bibitem[Aihara et al.(2017)]{HSCDR1} Aihara, H., Armstrong, R., Bickerton, S., 
             et al.\ 2017, arXiv:1702.08449

    \bibitem[Antilogus et al.(2014)]{2014JInst...9C3048A} Antilogus, P., Astier, P., 
             Doherty, P., Guyonnet, A., \& Regnault, N.\ 2014, Journal of 
             Instrumentation, 9, C03048

    \bibitem[Astropy Collaboration et al.(2013)]{Astropy} Astropy Collaboration, 
             Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33

    \bibitem[Axelrod et al.(2010)]{Axelrod2010} Axelrod, T., Kantor, J., Lupton, 
             R.~H., \& Pierfederici, F.\ 2010, \procspie, 7740, 774015

    %% B %% 
    \bibitem[Bartelmann \& Schneider(2001)]{Bartelmann2001} Bartelmann, M., \& 
             Schneider, P.\ 2001, \physrep, 340, 291

    \bibitem[Ben{\'{\i}}tez(2000)]{Benitez2000} Ben{\'{\i}}tez, N.\ 2000, \apj, 
             536, 571

    \bibitem[Bertin(2011)]{Bertin2011} Bertin, E.\ 2011, Astronomical Data Analysis 
             Software and Systems XX, 442, 435

    \bibitem[Bertin(2013)]{Bertin2013} Bertin, E.\ 2013, Astrophysics Source 
             Code Library, ascl:1301.001

    \bibitem[Bolzonella et al.(2000)]{Bolzonella2000} Bolzonella, M., Miralles, J.-M., 
            \& Pell{\'o}, R.\ 2000, \aap, 363, 476

    \bibitem[Bovy Jo et al.(2011)]{Bovy2011} Bovy Jo, Hogg, D.~W., \& Roweis, 
             S.~T.\ 2011, Annals of Applied Statistics, 5,

    %% C %%
    \bibitem[Chang et al.(2015)]{Chang2015} Chang, C., Busha, M.~T., Wechsler, R.~H., 
             et al.\ 2015, \apj, 801, 73

    %% D %%
    \bibitem[Dressler et al.(2012)]{Dressler2012} Dressler, A., Spergel, D., Mountain,
             M., et al.\ 2012, arXiv:1210.7809

    %% G %% 
    \bibitem[Greisen \& Calabretta(2002a)]{WCS1} Greisen, E.~W., \& Calabretta, M.~R.\ 
             2002, \aap, 395, 1061

    \bibitem[Calabretta \& Greisen(2002b)]{WCS2} Calabretta, M.~R., \& Greisen, E.~W.\ 
             2002, \aap, 395, 1077

    %% H %% 
    \bibitem[Hunter (2007)]{Matplotlib} Hunter J. D., 2007, Computing In Science \& 
             Engineering, 9, 90

    %% I %% 
    \bibitem[Ilbert et al.(2009)]{Ilbert2009} Ilbert, O., Capak, P., Salvato, 
             M., et al.\ 2009, \apj, 690, 1236

    \bibitem[Ivezic et al.(2008)]{Ivezic2008} Ivezic, Z., Axelrod, T., Brandt, W.~N., 
             et al.\ 2008, Serbian Astronomical Journal, 176, 1

    %% J %%     
    \bibitem[Jones et al.(2001)]{SciPy} Jones E., Oliphant T., Peterson P., et al., 
             2001, SciPy: Open source scientific tools for Python, 
             \url{http://www.scipy.org/}

    \bibitem[Juri{\'c} et al.(2015)]{Juric2015} Juri{\'c}, M., Kantor, J., Lim, K., 
             et al.\ 2015, arXiv:1512.07914

    %% K %% 
    \bibitem[Kaiser \& Squires(1993)]{Kaiser1993} Kaiser, N., \& Squires, G.\ 
             1993, \apj, 404, 441

    %% L %%
    \bibitem[Lackner \& Gunn(2012)]{Lackner2012} Lackner, C.~N., \& Gunn, J.~E.\ 
             2012, \mnras, 421, 2277

    \bibitem[Laureijs et al.(2012)]{Laureijs2012} Laureijs, R., Gondoin, P., Duvet, L., 
             et al.\ 2012, \procspie, 8442, 84420T

    \bibitem[Leauthaud et al.(2007)]{Leauthaud2007} Leauthaud, A., Massey, R., 
             Kneib, J.-P., et al.\ 2007, \apjs, 172, 219

    \bibitem[Lupton et al.(2001)]{Lupton2001} Lupton, R., Gunn, J.~E., Ivezi{\'c}, 
             Z., Knapp, G.~R., \& Kent, S.\ 2001, Astronomical Data Analysis Software 
             and Systems X, 238, 269

    %% M %%
    \bibitem[Magnier et al.(2013)]{Magnier2013} Magnier, E.~A., Schlafly, E., 
             Finkbeiner, D., et al.\ 2013, \apjs, 205, 20

    \bibitem[Mandelbaum et al.(2014)]{Mandelbaum2014} Mandelbaum, R., Rowe, B., 
            Bosch, J., et al.\ 2014, \apjs, 212, 5

    \bibitem[Mandelbaum et al.(2015)]{Mandelbaum2015} Mandelbaum, R., Rowe, B., 
             Armstrong, R., et al.\ 2015, \mnras, 450, 2963

    \bibitem[Miyazaki et al.(2012)]{Miyazaki2012} Miyazaki, S., Komiyama, Y., Nakaya, 
             H., et al.\ 2012, \procspie, 8446, 84460Z

    %% N %%
    \bibitem[Niikura et al.(2017)]{Niikura2017} Niikura, H., Takada, M., Yasuda, N., 
             et al.\ 2017, arXiv:1701.02151

    %% P %% 
    \bibitem[Padmanabhan et al.(2008)]{Padmanabhan2008} Padmanabhan, N., Schlegel, 
             D.~J., Finkbeiner, D.~P., et al.\ 2008, \apj, 674, 1217-1233

    \bibitem[Pedregosa et al.(2011)]{scikit-learn} Pedregosa F., et al., 2011, 
             Journal of Machine Learning Research, 12, 2825

    %% R %%                       
    \bibitem[Rowe et al.(2015)]{Rowe2015} Rowe, B.~T.~P., Jarvis, M., Mandelbaum, R., 
             et al.\ 2015, Astronomy and Computing, 10, 121

    %% S %%         
    \bibitem[Schlafly et al.(2012)]{Schlafly2012} Schlafly, E.~F., Finkbeiner, D.~P.,
             Juri{\'c}, M., et al.\ 2012, \apj, 756, 158

    \bibitem[Scoville et al.(2007)]{Scoville2007} Scoville, N., Abraham, R.~G., 
             Aussel, H., et al.\ 2007, \apjs, 172, 38

    \bibitem[S{\'e}rsic(1963)]{Sersic1963} S{\'e}rsic, J.~L.\ 1963, Boletin de la 
             Asociacion Argentina de Astronomia La Plata Argentina, 6, 41

    \bibitem[Suchyta et al.(2016)]{Suchyta2016} Suchyta, E., Huff, E.~M., Aleksi{\'c}, 
             J., et al.\ 2016, \mnras, 457, 786

    \bibitem[Steidel et al.(1996)]{Steidel1996} Steidel, C.~C., Giavalisco, M., 
             Pettini, M., Dickinson, M., \& Adelberger, K.~L.\ 1996, \apjl, 462, L17

    %% T %%
    \bibitem[The Dark Energy Survey Collaboration(2005)]{DES2005} The Dark Energy 
             Survey Collaboration 2005, arXiv:astro-ph/0510346

    \bibitem[Tonry et al.(2012)]{Tonry2012} Tonry, J.~L., Stubbs, C.~W., Lykke, K.~R., 
             et al.\ 2012, \apj, 750, 99

    %% V %%                  
    \bibitem[VanderPlas et al.(2014)]{astroml} VanderPlas, J., Fouesneau, M., \& 
             Taylor, J.\ 2014, Astrophysics Source Code Library, ascl:1407.018

    %% W %% 
    \bibitem[Walt et al.(2011)]{NumPy} Walt S. v. d., Colbert S. C., Varoquaux G., 
             2011, Computing in Science and Engg., 13, 22

\end{thebibliography}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\appendix
%% ------------------------------------------------------------------------------------ %% 
\section{Quality Control of Synthetic Objects}
    \label{app:qc}

    To select synthetic stars and galaxies from the results to test the photometry, 
    we apply some basic quality control cuts here.

    The HSC survey defines the full--depth \& full--color regions (\texttt{FDFC}) to 
    make sure the data used for science reach the expected number of exposures in each 
    band 
    ($\mathtt{(\#gri\ \geq\ 4)\ and\ (\#yz\ \geq\ 6)\ and\ (Limiting\ imag> 25.6)}$). 
    And, the two \tracts{} we used in this work are almost entirely covered in 
    the \texttt{FDFC} region so we do not apply this cut.  
    We apply the following cuts to the matched synthetic objects"

    \begin{itemize}

        \item[ ] \texttt{ idetect\_is\_primary==True }
        \item[ ] \texttt{ ideblend\_skipped==False }
        \item[ ] \texttt{ iflags\_badcentroid==False }
        \item[ ] \texttt{ icentroid\_sdss\_flags==False }
        \item[ ] \texttt{ iflags\_pixel\_edge==False }
        \item[ ] \texttt{ iflags\_pixel\_interpolated\_center==False }
        \item[ ] \texttt{ iflags\_pixel\_saturated\_center==False }
        \item[ ] \texttt{ iflags\_pixel\_cr\_center==False }
        \item[ ] \texttt{ iflags\_pixel\_bad==False }
        \item[ ] \texttt{ iflags\_pixel\_suspect\_center==False }
        \item[ ] \texttt{ iflags\_pixel\_clipped\_any==False }
        \item[ ] \texttt{ iflags\_pixel\_bright\_object\_center ==False }

    \end{itemize}

    \todo{Details for stars and galaxies}

%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{$b$: The Blendedness Parameter}
    \label{app:defineb}

    To evaluate at what degree an object is blended with others, \hscpipe{} introduces
    the blendedness parameter: $b$ (\texttt{[grizy]blendedness\_abs\_flux}). 
    Please refer to Bosch\etal (in prep.) and Murata\etal (in prep.) for more details, 
    here we briefly explain the definition.

    For object ${\rm A}$: 
    \begin{eqnarray*}
        b({\rm A}) \equiv
        1-\frac{\int_{\mathbb{R}^2} {\rm d}x~ {\rm d}y\ \mathcal{N}_{\mathrm{A}}({\bf x}\ |\  \mu_{\mathrm{A}}, {\bf\Sigma}_{\mathrm{A}}) 
        F_{\mathrm{A}}({\bf x})}{\int_{\mathbb{R}^2} {\rm d}x~ {\rm d}y\ \mathcal{N}_{\mathrm{A}}({\bf x}\ |\  \mu_{\mathrm{A}},
        {\bf\Sigma}_{\rm{A}}) F_{\rm{total}}({\bf x})},      
        \label{eq:defineb}
    \end{eqnarray*}

    \noindent 
    where $\mathcal{N}_{\rm{A}}({ \bf x }\ |\  \mu_{\rm{A}}, {\bf\Sigma}_{\rm{A}})$ 
    is a 2-D Gaussian function at pixel position $\bf x$, $\mu_{\mathrm{A}}$ is the 
    estimated centroid of object ${\rm A}$, and covariance ${\bf \Sigma}_{\mathrm{A}}$ 
    is estimated based on the Gaussian-weighted adaptive second moments of object 
    ${\rm A}$ (no PSF correction). 
    $F_{\mathrm{total}}({\bf x })$ and $F_{\rm{A}}({\bf x })$ are pixels values of 
    ${\rm A}$ before and after \hscpipe{} deblending process.

    By definition, the parameter is bound from 0 to 1. 
    When the deblending process is carried out correctly, the $b({\rm A})$ parameter 
    reflects the fraction of fluxes that comes from other objects in the 
    region of ${\rm A}$.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
%%%%%%%%%%%: Possible Tables %%%%%%%%%%%%%
%\input{table1.tex}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\label{lastpage}
\end{document}
%% ------------------------------------------------------------------------------------ %%

### 2017-04-09 draft/ms_v1.tex
Draft: PSF magnitude accuracies

@@
 \def\hst{{\textit{HST}}}
+\def\s2n{{$\mathrm{S}/\mathrm{N}$}}
 
@@
 
-    \begin{itemize}
-
-        \item In Fig \ref{fig:star_sn}, we show the relations between the input
-            magnitude and the $\mathrm{S}/\mathrm{N}$ recovered by \hscpipe{}
-            photometry in $g$- and $i$-band.
-
-        \item \plan{Define $\mathrm{S}/\mathrm{N}$, quickly explain the purpose.}
-
-        \item \plan{At fixed input magnitude, PSF $\mathrm{S}/\mathrm{N}$ depends 
-            on seeing conditions. 
-            For $i$-bands, the two \tracts{} have quite different seeing. 
-            And bad seeing leads to clearly lower $\mathrm{S}/\mathrm{N}$.}
-
-        \item \plan{Briefly discuss the detection limit of point sources. 
-            Basically consistent with the reported values in \citet{HSCDR1}.}
-
-        \item \plan{Blendedness can reduce the $\mathrm{S}/\mathrm{N}$ a little.}
-
-    \end{itemize}
+    We first briefly discuss the relationship between input magnitude and the
+    signal-to-noise ratio of the output PSF photometry.
+    Here, we simply define the \s2n{} as
+    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band
+    without considering the aperture correction.
+    This will help us visualize
+    1) the detection limit for point sources,
+    2) the impact of seeing condition on PSF photometric,
+    3) and the scatter of photometric accuracies at fixed input magnitude given all
+       the realistic features of HSC images (e.g. background subtraction, nearby
+       object, optical artefacts).
+    We show the results for $g$- and $i$-band in Fig \ref{fig:star_sn}, and find tight
+    relations in both bands.
+
+    As expected, we clearly see that the seeing condition impacts the \s2n{} of point
+    sources at fixed input magnitude.
+    In $i$-band, the \tract{} with slightly worse seeing (0.7\asec{}) shows systematically
+    lower \s2n{} comparing to the one with better seeing (0.5\asec{}).
+    As for the $g$-band, since the two \tracts{} share similar seeings now, they also
+    follow similar relations.
+    We also see that the blendedness can also affect accuracies of PSF photometry.
+    In $i$-band, the highly blendend synthetic stars scatter toward lower \s2n{} at
+    fixed magnitude.
+    Interestingly, the effect is not obvious in $g$-band, suggeting the deblending
+    process and photometric quality of blended objects also depend on seeing condition.
+
+    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ and
+    $i$-band at average seeing condition, which is consistent with the values found
+    in \citet{HSCDR1}.
+    At the same time, it is worth reminding the users of HSC data that the detection
+    limit will show spatial variations due to the seeing conditions.
 
@@
 
-    \begin{itemize}
-
-        \item In Fig \ref{fig:psf_mag}, we evaluate the accuracies of \hscpipe{} PSF 
-            magnitudes in all five bands.
-
-        \item \plan{The overall performance of PSF photometry is good. 
-            In $i$-band, the median magnitude difference is around ${\sim}0.015$ mag
-            (${\sim}1.5$\% accuracy) at $i_{\mathrm{Input}}{\sim}19.0$ mag. 
+    Now, we will look into the accuracies of PSF magnitudes in all five bands
+    independently.
+    In Fig \ref{fig:psf_mag}, we show the relations between the input magnitude and the
+    magnitude difference from the \hscpipe{} \forced{} PSF photometry.
+
+    The overall performance of PSF photometry is excellent.
+    In $i$-band, the median magnitude difference for \tract{} with 0.5\asec{} seeing is
+    around ${\sim}0.015$ mag (${\sim}1.5$\% accuracy) at
+    $i_{\mathrm{Input}}{\sim}19.0$ mag.
     At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of PSF
-            magnitude is around $3$\%. 
-            Down to $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy is 
-            around 7\%.
-            This is consistent with the external check in \citet{HSCDR1}.}
-
-        \item \plan{At fixed input magnitude, the accuracy does not strongly depends
-            on filters. 
-            The only exception is the $y$-band, which has slightly worse accuracy. 
-            At $y_{\mathrm{Input}}{\sim}23.5$, the average accuracy is already close 
-            to $10$\%.}
-            \todo{Possible causes? background noise? Worse PSF model?}
-
-       \item \plan{The \forced{} PSF magnitude provides unbiased estimates for
-           isolated stars. 
-           For $grzy$-bands, the median magnitude difference is ${\sim}0.002$ mag, 
-           and can be ignored.}
-
-       \item \plan{Using $i$-band as example, although worse seeing leads to 
-           lower $\mathrm{S}/\mathrm{N}$, it does not strongly impact the 
-           accuracy of the PSF magnitude. 
-           The bad seeing \tract{} suggests almost identical accuracy comparing
-           to the good seeing one.}
-
-       \item \plan{However, the story for highly blended stars is quite different. 
-           \hscpipe{} systematically under-estimate the total flux of highly blended
-           stars by $0.05$--$0.10$ mag at fixed input magnitude.}
-
-       \item \plan{We also test the \unforced{} PSF photometry in all five 
-           bands. 
-           The results suggest very similar accuracy.
-           We highlight the differences between \forced{} and 
-           \unforced{} PSF photometry in Fig \ref{fig:psf_diff}. 
-           The overall difference is quite small, but it seems that \hscpipe{} 
-           \unforced{} PSF photometry recovers slightly more flux at very 
-           faint end.} 
-           \todo{Move the figure to appendix?}
-
-    \end{itemize}
+    magnitud keeps at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
+    Down to $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy descreases to
+    ${\sim}7$\% level with an average ${\sim}0.072$ mag difference.
+    The \tract{} with worse seeing shows similar accuracy of PSF photometry at
+    $i_{\mathrm{Input}}<23.5$ mag.
+    At faint end, the accuracy becomes slightly worse: ${\sim}5$\% accuracy around
+    $i_{\mathrm{Input}}{\sim}24.0$ mag; and ${\sim}11$\% accuracy around
+    $i_{\mathrm{Input}}{\sim}25.2$ mag.
+    \citet{HSCDR1} evaluates the accuracy of PSF photometry via external comparisons
+    with the PS1 PV2 and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
+    which is consistent with our results.
+    At fainter magnitude, external comparisons become difficult due to the lack of deep
+    imaging data at HSC level and the impact of the color-term when comparing photometry
+    using different filters.
+    The results from \synpipe{} hence provide more useful evaluations down to the
+    detection limit\footnote{Strictly speaking, the uncertainties here should be
+    considered as lower limit as the \synpipe{} now does not consider the uncertainties
+    in PSF modeling.}.
+
+    We also see that the accuracy of PSF photometry does not strongly depend on filters.
+    The forced PSF magnitude in $r$ and $z$-band have very similar accuracy with
+    $i$-band (1.5-4.0\% at $19.0 < r_{\mathrm{Input}} < 24.0$ mag, ${\sim}8$\% down to
+    $r_{\mathrm{Input}}{\sim}25.2$ mag;
+    1.0-5.0\% at $19.0 < z_{\mathrm{Input}} < 24.0$ mag, ${\sim}10$\% down to
+    $z_{\mathrm{Input}}{\sim}25.2$ mag).
+    The accuracies in $g$- and $y$-band become slightly worse (
+    1.5-7.0\% at $19.0 < g_{\mathrm{Input}} < 24.0$ mag, ${\sim}13$\% down to
+    $g_{\mathrm{Input}}{\sim}25.2$ mag;
+    1.5-5.0\% at $19.0 < y_{\mathrm{Input}} < 23.0$ mag, ${\sim}12$\% down to
+    $y_{\mathrm{Input}}{\sim}24.0$ mag;), but the differences can be attributed to the
+    differences in seeing conditions.
+
+    For relative isolated stars, \hscpipe{} provides unbiased PSF photometry down to
+    very faint magnitude in $i$- and $z$-band.
+    For $g$-, $r$-, and $y$-band, we find small offsets in the distributions of magnitude
+    differences, which indicates \hscpipe{} tends to underestimate the fluxes of stars
+    in these bands by ${\sim}0.01-0.02$ mag.
+    Although the exact cause of this offset is unclear (could still be related to
+    differenecs in seeing), it will not affect the accuracies of magnitudes of colors.
+
+    At the same time, the story for highly blended stars is very different.
+    \hscpipe{} on average systematically underestimates the total fluxes of them by
+    $0.05$--$0.10$ mag at fixed input magnitude.
+    We see the same effect in all bands, and the impact of blendedness becomes
+    increasingly significant at fainter magnitde.
+    It is therefore important to keep this in mind when using PSF photometry for point
+    sources in HSC data.
+
+    We also test the \unforced{} PSF photometry in all five bands, and find very similar
+    accuracies.
+    During the measurement of \forced{} PSF photometry, \hscpipe{} fixes the centroid
+    of the PSF model across all five band.
+    Therefore, the magnitude difference between \forced{} and \unforced{} PSF magnitudes
+    indicates the photometric uncertainties induced by differences in the accuracies of
+    astrometric calibrations and PSF modeling among different bands.
+    We highlight the differences between \forced{} and \unforced{} PSF photometry of
+    $g$- and $y$-band in Fig \ref{fig:psf_diff}.
+    The overall difference is very small ($<0.01$ mag), but it also suggest that
+    \hscpipe{} \unforced{} PSF photometry systematically recovers slightly more fluxes
+    at very faint end.
 

### 2017-04-10 draft/ms_v1.tex
Draft: PSF color

@@
     We also see that the blendedness can also affect accuracies of PSF photometry.
-    In $i$-band, the highly blendend synthetic stars scatter toward lower \s2n{} at
+    In $i$-band, the highly blended synthetic stars scatter toward lower \s2n{} at
     fixed magnitude.
-    Interestingly, the effect is not obvious in $g$-band, suggeting the deblending
+    Interestingly, the effect is not obvious in $g$-band, suggesting the deblending
     process and photometric quality of blended objects also depend on seeing condition.
@@
     At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of PSF
-    magnitud keeps at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
-    Down to $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy descreases to
+    magnitude keeps at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
+    Down to $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
     ${\sim}7$\% level with an average ${\sim}0.072$ mag difference.
@@
     Although the exact cause of this offset is unclear (could still be related to
-    differenecs in seeing), it will not affect the accuracies of magnitudes of colors.
+    differences in seeing), it will not affect the accuracies of magnitudes of colors.
 
@@
     We see the same effect in all bands, and the impact of blendedness becomes
-    increasingly significant at fainter magnitde.
+    increasingly significant at fainter magnitude.
     It is therefore important to keep this in mind when using PSF photometry for point
@@
 
-    \begin{itemize}
-
-        \item \plan{Briefly explain why PSF colors are important; we focus on the
-            \forced{} PSF colors here}
-
-        \item The results for accuracy of \forced{} PSF colors are shown in
-            Fig \ref{fig:psf_color} and Fig \ref{fig:psf_cdist}.
-
-        \item \plan{In Fig \ref{fig:psf_color}, we investiage how \forced{}
-            PSF colors depend on input magnitude and colors using both $(g-i)$ and
-            $(i-y)$ colors.
-            Results suggest \hscpipe{} \forced{} PSF photometry can provide
-            accurate and unbiased colors for stars in our tests.
-            The uncertainties do not show any significant dependence on neither input
-            magnitude nor color.}
-
-        \item \plan{For $(g-i)$ color, average uncertainty around
-            $i_{\mathrm{Input}}{\sim}19.0$ mag is ${\sim}0.025$ mag.
-            The uncertainty increases to ${\sim}0.11$ mag at
-            $i_{\mathrm{Input}}{\sim}25.0$ mag.
-            Results for $(i-y)$ color is similar.}
-
-        \item \plan{In Fig \ref{fig:psf_cdist}, we use the results from the bad
-            seeing \tract{} to show that the \forced{} PSF photometry
-            can accurately recover the color-color sequences of stars down to
-            $i{\sim}25$ mag.}
-
-        \item \plan{Accuracy of \forced{} PSF photometry apparently does not
-            strongly depend on seeing condition.
-            Impact from blendedness on PSF color is less serious than the magnitude,
-            although highly blended stars still show worse color accuracy and
-            systematically bluer (redder) $(g-i)$ ($i-y$) colors.
-            \unforced{} PSF photometry show similar but slightly worse
-            accuracy than the \forced{} ones. }
-
-    \end{itemize}
+    Color measurement based on PSF photometry is the most appropriate one for point
+    sources, and is therefore important to many scientific goals of the HSC survey
+    (e.g. study of the Milky Way structure, selection of unique stellar objects or
+    high-redshift quasars, and the accurate star--galaxy separation).
+
+    In Fig \ref{fig:psf_color}, we evaluate the accuracies of the \forced{} $(g-i)$
+    and $(i-y)$ PSF colors via comparing the error in color measurements with both
+    input magnitudes and input colors.
+    These results suggest that \hscpipe{} provides accurate and unbiased PSF color
+    estimates for synthetic stars with realistic color distributions down to very faint
+    magnitude.
+    For $(g-i)$ color, the average uncertainty around $i_{\mathrm{Input}}{\sim}19.0$ mag
+    is ${\sim}0.025$ mag, and increases to ${\sim}0.11$ mag at
+    $i_{\mathrm{Input}}{\sim}24.0$ mag.
+    The results are very similar for the $(i-y)$ color.
+    We also find that the accuracies of PSF colors do not depend on the input colors of
+    the synthetic stars or the seeing conditions.
+    For instance, the accuracy of $(g-i)$ color for \tract{} with bad seeing only becomes
+    slightly worse in the very faint end (${\sim}0.14$ mag at
+    $i_{\mathrm{Input}}{\sim}24.0$ mag) comparing to the results for good seeing \tract{}.
+
+    We further illustrate the accuracies of PSF colors via comparing the distributions
+    of colors for the input synthetic stars and the ones recovered by \hscpipe{}
+    (see Fig \ref{fig:psf_cdist}).
+    Using four different colors and two color--color planes, we show that the \forced{}
+    PSF colors can accurately reproduce the distributions of all four colors and the
+    2-D color-color distributions.
+
+    As for the highly blended stars, on Fig \ref{fig:psf_color}, we see that on average
+    they still have larger uncertainties in colors comparing to the relative isolated
+    ones.
+    For $(g-i)$ color, the average color uncertainty is ${\sim}0.1$ mag larger for the
+    highly blended stars at fixed input magnitude.
+    However, the biases in color measurements for these stars are less severe than
+    the magnitude measurements.
+    Although the blended stars still show slightly bluer (redder) $(g-i)$ ($(i-y)$)
+    colors comparing to the isolated ones and the input values, the differences in the
+    distributions of color uncertainties of blended and isolated stars are less striking
+    than the ones for magnitude differences.
 
@@
 
-    \plan{Briefly explain the definition of blendedness}
-
+    \plan{Review the definition of blendedness and explain why it is important.}
     \plan{Relationship between magnitude and blendedness}

### 2017-04-10 draft/ms_v1.tex
Draft: small changes in abstract

@@
     performance via injecting synthetic objects to the single-\texttt{visit} HSC images.
-    We use the coadd images in two \tracts{} from the Wide layer with representative
-    seeing conditions to demonstrate the usage of \synpipe{} and examine the general
-    photometric performance of \texttt{hscpipe}.
+    We use coadd images in two \tracts{} from the Wide layer with representative
+    seeing conditions to demonstrate the implementation of \synpipe{} and examine the 
+    general photometric performance of \texttt{hscpipe}.
     We find that the typical uncertainties of HSC \forced{} PSF photometry for stars
     range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
-    mag (1\%-5\% accuracy in the $i$-band).
-    For synthetic single-{S\'{e}rsic\ } model galaxies, the typical uncertainties of
-    HSC forced \cmodel{} photometry range from 0.14 mag at $i{\sim}20.0$ mag to
+    mag (1\%-7\% accuracy in the $i$-band).
+    For synthetic galaxies with single-\ser{} model, typical uncertainties of the
+    forced \cmodel{} photometry range from 0.14 mag at $i{\sim}20.0$ mag to
     0.20 mag at $i{\sim} 25.2$ mag.
-    Over the range of colors and magnitudes in these tests, we find that both \forced{}
-    PSF and \cmodel{} photometry provide unbiased estimates of colors that are robust
-    against different seeing conditions.
-    Finally, we also noticed that 1) the degree that a object is blended with others
-    impact the photometric accuracy, especially for stars.
+    Over the colors and magnitudes ranges used in these tests, we find that both 
+    \forced{} PSF and \cmodel{} photometry provide unbiased estimates of colors that 
+    are robust in different seeing conditions.
+    Finally, we notice a few issues in the current \hscpipe{} that are worth keeping
+    in mind when using HSC data: 
+    1) the degree that a object is blended with others impacts the photometric 
+    accuracy, especially for point sources.
     Highly blended object tends to have larger photometric uncertainty, systematically
     underestimated flux, and slightly biased color.
-    2) a relative high fraction of faint stars (${\sim}20$\% at $i>22.5$ mag) could be
+    2) a relative high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
     misclassified as extended objects.

### 2017-04-11 draft/ms_v1.tex
CModel: basic statistics

@@
     For more details, please see Section 4.9.8 of Bosch\etal (in prep.).
-    Basically, \cmodel{} tries to fit each object using a combination of de Vaucouleur
+    In short, \cmodel{} tries to fit each object using a combination of de Vaucouleur
     and exponential profiles that are approximated by multiple Gaussian profiles.
@@
 
-    \begin{itemize}
-
-        \item \plan{${\sim}2$--$3$\% of the injected synthetic galaxies are
-            ambiguously blended with real objects.}
-
-        \item \plan{Excluding the ambiguously blended ones, ${\sim}4$--$8$\% of the
-            remaining synthetic galaxies do not have any match.
-            The unmatched galaxies are systematically fainter than the matched ones.
-            And the fraction of unmatched synthetic galaxies is also slightly higher
-            in the bad seeing \tract{} than the one with good seeing.
-            Similarly, $g$- and $i$-band have higher fraction of unmatched objects.
-            }
-
-       \item \plan{From the rest of the matched galaxies, we only keep the primary
-           detections (\texttt{detect.is-primary=True}) and the ones with clean
-           photometry (see Appendix \ref{app:qc} for details).
-           For each \tract{}, there are ${\sim}30000$ galaxies left.}
-
-       \item \plan{A tiny fraction of synthetic galaxies is misclassified as
-           point sources by \hscpipe{}.
-           And the fraction of misclassifications seems to increase with seeing
-           (${\sim}1$\% in good seeing \tract{}; ${\sim}4$\% in bad seeing \tract{}).
-           We will further discuss in Section \ref{ssec:sg}.}
-
-       \item \plan{We also use $b>0.05$ to define samples of highly blended galaxies.
-           Since synthetic galaxies are more extended, their distribution of $b$
-           skew more toward the higher value.
-           About ${\sim}7$--$9$\% of galaxies are highly blended by this standard.
-           The $g$-band has significantly higher fraction of highly blended objects.}
-
-    \end{itemize}
+    In our tests, we randomly inject ${\sim}40000$ synthetic galaxies into each 
+    \tract{}, and select samples for photometric comparisons in a similar way to the
+    stars. 
+    First, ${\sim}2$--$3$\% of the synthetic galaxies are ambiguously blended with 
+    real objects, and are hence removed from the sample. 
+    Among the rest of the sample, ${\sim}2$--$7$\% do not have any match in the 
+    \synpipe{} results in different \tracts{} and filters. 
+    The fraction of unmatched objects is slightly higher for the $g$- and $y$-band. 
+    For the same filter, the fraction is always higher for the bad seeing \tract{}.
+    The magnitudes of the unmatched galaxies are systematically fainter than the 
+    matched ones. 
+    In $i$-band, the median input magnitudes for matched and unmatched galaxies are 
+    $24.0$ mag and $24.6$ mag.
+
+    After selecting the matched synthetic galaxies with primary detection and 
+    clean photometry (see Appendix \ref{app:qc} for details), we have ${\sim}30000$
+    galaxies in each \tract{} for comparison.  
+    Among these objects, only $<1$\% is misclassified as point sources by \hscpipe{}
+    in the good seeing \tract{}.  
+    However, for the bad seeing one, the fraction increases to $4$\%.  
+    The median input magnitude for these misclassified sources is ${\sim}24.9$ mag 
+    in $i$-band, significantly fainter than the median of others.  
+    We will further discuss this in Section \ref{ssec:sg}.
+
+    We also use $b>0.1$ to define samples of highly blended galaxies.
+    Due to the extended nature, the distributions of $b$ for synthetic galaxies are 
+    very different from stars, and skew toward higher values (especially for the 
+    bad-seeing \tract{}). 
+    About ${\sim}7$--$9$\% of synthetic galaxies are highly blended by this standard.
+    The fraction is only slightly higher in the bad-seeing \tract{}, and the 
+    $g$-band has the highest fraction of highly blended galaxies. 
+    We highlight the highly blended ones in comparisons, and there are more relevant 
+    discussions in Section \ref{ssec:blendedness}.
+
+    Although these galaxies span in very wide large ranges of magnitude and 
+    structural parameters, the majority of them are faint 
+    ($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec). 
+    The photometric quality of these galaxies is very challenging, and also crucial
+    to several key scientific goals of the HSC survey. 
+    At the same time, these samples are unable to provide enough amounts of 
+    bright or large galaxies to test. 
+    We will supplement results for these galaxies using better samples for them 
+    in the future.
 

### 2017-04-12 draft/ms_outline.tex
CModel: S/N

% Version 0; Only rough outline by SH

\documentclass{pasj01}

%% ------------------------------------------------------------------------------------ %% 
% Packages
%\usepackage{emulateapj5}
%\usepackage{apjfonts}
%\usepackage{amssymb, amsmath}
%\usepackage{graphicx}
\usepackage{url}
%\usepackage{CJK}    
\usepackage{natbib}
\usepackage{hyperref}
\usepackage[usenames]{color}

% Package Settings
\bibliographystyle{apj}
\hypersetup{colorlinks=true,
            citecolor=cyan,
            linkcolor=cyan,
            filecolor=magenta,      
            urlcolor=cyan}
\urlstyle{same}
%% ------------------------------------------------------------------------------------ %%

% Figure extension
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

%%%%%%%%%%%%: User Defined Commands %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
% Song Huang's definition 
\def\arcsec{{\prime\prime}}
\def\arcmin{{\prime}}
\def\degree{{\circ}}
\def\h{\hskip -3 mm}
\def\amin{$^\prime$}
\def\asec{$^{\prime\prime}$}
\def\deg{$^{\circ}$}
\def\ddeg{{\rlap.}$^{\circ}$}
\def\dsec{{\rlap.}$^{\prime\prime}$}
\def\hst{{\textit{HST}}}
\def\lax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$<$}}}$}}
\def\gax{{$\mathrel{\hbox{\rlap{\hbox{\lower4pt\hbox{$\sim$}}}\hbox{$>$}}}$}}
\def\simlt{\lower.5ex\hbox{$\; \buildrel < \over \sim \;$}}
\def\simgt{\lower.5ex\hbox{$\; \buildrel > \over \sim \;$}}
\def\micron{{$\mu$m}}
\def\perang{\AA$^{-1}$}
\def\peryr{yr$^{-1}$}
\def\sb{mag~arcsec$^{-2}$}
\def\lsun{$L_\odot$}
\def\msun{$M_\odot$}
\def\sigs{$\sigma_*$}

\def\etal{{\ et al.~}}
\def\galfit{{\tt GALFIT}}
\def\ser{{S\'{e}rsic\ }}
\def\redm{\texttt{redMaPPer}~}
\def\synpipe{\texttt{SynPipe}~}
\def\redbcg{{$\Lambda \ge 30$}}
\def\nonbcg{{$\Lambda < 20$}}
\def\logms{{$\log (M_{\star}/M_{\odot})$}~}
\def\mstar{{$M_{\star}$}~}
\def\logmh{{$\log (M_{\mathrm{Halo}}/M_{\odot})$}~}
\def\m2l{{$M_{\star}/L_{\star}$}~}
%% ------------------------------------------------------------------------------------ %%

% Commenting:
%% ------------------------------------------------------------------------------------ %% 
\definecolor{gray}{rgb}{0.6, 0.6, 0.6}
\newcommand{\plan}[1]{\textcolor{blue} {\textbf{#1}}}
\newcommand{\todo}[1]{\textcolor{red} {\textbf{#1}}}
\newcommand{\song}[1]{\textcolor{gray} {\textbf{#1}}}
\newcommand{\addref}{{\textcolor{red}{REF}}}

%%%%%%%%%%%%: Header and Version %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %%

\begin{document}

\SetRunningHead{Huang et al.}{HSC-SSP SynPipe}

\Received{$\langle$April 2017$\rangle$}
%\Accepted{$\langle$2017$\rangle$}
%\Published{$\langle$2017$\rangle$}

%%%%%%%%%%%%: Title and Affiliations %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
\title{SynPipe: Synthetic Object Pipeline for the Hyper Suprime-Cam 
       Strategy Survey Program}

\author{Song Huang \altaffilmark{1,2}
        Alexie Leauthaud \altaffilmark{1,2}, 
        Claire Lackner \altaffilmark{1},
        Jim Bosch \altaffilmark{3},
        Paul Price \altaffilmark{3},
        Steven Bickerton \altaffilmark{1},
        Ryoma Murata \altaffilmark{1, 4}, 
        Rachel Mandelbaum \altaffimark{5},
        HSC Collaboration \altaffilmark{6},
        }                                          
%% ------------------------------------------------------------------------------------ %%

\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the 
    Universe, The University of Tokyo Institutes for Advanced Study, 
    the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
\altaffiltext{2}{Department of Astronomy and Astrophysics, University of California, 
    Santa Cruz, 1156 High Street, Santa Cruz, CA 95064 USA}
\altaffiltext{3}{Department of Astrophysical Sciences, Princeton University, 
    4 Ivy Lane, Princeton, NJ 08544}
\altaffiltext{4}{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
\altaffiltext{5}{McWilliams Center for Cosmology, Department of Physics, 
    Carnegie Mellon University, Pittsburgh, PA 15213, USA}
\altaffiltext{6}{Other affiliations}

\email{song.huang@ipmu.jp}
%% ------------------------------------------------------------------------------------ %%

%%%%%%%%%%%%: Abstract and Keywords %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
\KeyWords{Surveys, 
          Methods: observational, 
          Techniques: photometric}

\maketitle

%% ------------------------------------------------------------------------------------ %% 
\begin{abstract}
    The Subaru Strategy Survey Program (SSP) is an ambitious multiband imaging
          survey using the Hyper Suprime-Cam (HSC).
          The HSC collaboration has developed sophisticated data reduction pipeline
          that will also be used by the Large Synoptic Survey Telescope. 
          Here we introduce the SynPipe: a flexible framework to test the performance 
          of HSC pipeline using synthetic stellar and extended objects. 
          Through injecting synthetic objects to images from individual exposures, 
          SynPipe creates realistic coadd images and photometric measurements for them
          In this work, we demonstrate the basic photometric performance of HSC pipeline
          using synthetic stars and galaxies close to the expected detection limit of 
          SSP Wide survey. 
          SynPipe is also being used to test the selection of background galaxies for 
          weak lensing analysis, the detection of high redshift dropouts, and photometry 
          of low surface brightness objects.
\end{abstract}
%% ------------------------------------------------------------------------------------ %%

%%%%%%%%%%%%: Main Text %%%%%%%%%%%%

%% ------------------------------------------------------------------------------------ %% 
\section{Introduction}
    \label{sec:intro}

    \todo{SSP/HSC background \citealt{Suchyta2016}}
    \begin{itemize}
        \item \plan{Why large imaging survey? Basic scientific application: cosmology, 
                    galaxy evolution, galactic structure, and trasient objects.} 
        \item \plan{Brief background about HSC and SSP. 
                    Could borrow a few paragraph from the camera and survey design paper, 
                    rewrite in slightly different way.}
        \item \plan{Accurate photometry becomes very challenging, hence requires careful 
                    systematic tests.}
        \item \plan{Briefly mentions similar efforts from DES collaboration. e.g. 
                    \texttt{Balrog} (\citep{Suchyta2016}) and there is another one\ldots}
    \end{itemize}

%% ------------------------------------------------------------------------------------ %%

\section{HSC Pipeline Overview}

    \todo{Brief introduction of the HSC pipeline.}
    \begin{itemize}
        \item \plan{Basic workflow of the HSC pipeline, 
                    can borrow something from Jim's paper, and rewrite in our own words.}
        \item \plan{Emphasize the new algorithms used by HSC pipeline, and the 
                    improvements compared with other surveys.}
        \item \plan{Explain the most important features that are worth testing:
                    1. Detection of sources down to the survey limit;
                    2. PSF magnitude and colors for stellar objects;
                    3. cModel photometry for galaxies;
                    4. Impact of ``blendedness'' on photometry;
                    5. Impact of proximity to bright stars on photometry (?)
                    6. Star-Galaxy separation (?)}   
    \end{itemize}

%% ------------------------------------------------------------------------------------ %%

\section{SynPipe Overview}

    \plan{The following paragraph is prepared for the weak lensing shape catalog paper, 
          only show here as a place holder \ldots}

    \begin{itemize}
        \item \plan{Basic design of SynPipe:
                    1. Flexible, highly integrated with HSC pipeline;
                    2. Why we want to inject synthetic objects onto single 
                       exposures instead of directly putting them on coadd?}
        \item \plan{Since we simulate the real data reduction process as much 
                    as possible, SynPipe will generate the same amount of data
                    as the real HSC pipeline.  We do not plan to apply SynPipe
                    to the entire HSC survey, but use it to test the performance 
                    of HSC pipeline on a representative subset of data.}         
    \end{itemize}

    \todo{Need a flow-chart to visualize the procedures of SynPipe}

    To evaluate the performence of \texttt{hscPipe}, including the photometry and shape 
    measurements that are related to weak lensing analysis, we design a flexible framework 
    (\texttt{SynPipe}\footnote{https://github.com/clackner2007/fake-sources}) to conduct 
    systematic tests by injecting simulated images of galaxies on to the HSC images.  
    \texttt{SynPipe} read positions and detailed model information of the fake objects from an
    input catalog.  By default, it provides the functions to help you randomly inject objects 
    on a single \texttt{Tract} according to required number density, or put fake objects on 
    an evenly separated grid given expected distance between objects.

    \texttt{SynPipe} uses \texttt{GalSim\ v1.4} (Rowe\ et al.\ 2015) as backend to reliably
    simulate images of fakes objects.  So far, the fake object can be either star or galaxies
    that are described by single- or double-{S\'{e}rsic} models.  In stead of providing the
    model parameters in the input catalog, we also support the parametric models of
    $I_{\mathrm{F814W}} \leq 25.2$ COSMOS galaxies provided by
    \texttt{GalSim.COSMOSCatalog()}, which is very similar to the input catalog of the
    \texttt{GREAT3} challenge (Mandelbaum\ et al.\ 2013).   Using model identifications in the
    input catalog, \texttt{GalSim} will generate images of the best parametric models (either
    single-{S\'{e}rsic} or {S\'{e}rsic}-bulge plus exponential disk).  Also, external shear
    can be added to fake object in the form of $g1$ and $g2$.  For model with high
    {S\'{e}rsic} index, the simulated image can truncate after certain times of the effective
    radius by request to improve the speed.

    To make the image simulation process as realistic as possible, \texttt{SynPipe} injects
    fake objects directly onto images of individual CCD at the single exposure level, instead
    of putting them to the already stacked, final image products (e.g. Suchyta\ et al.\ 2015).
    In this way, the fake objects from different single exposures will go through the exactly
    same detecting, stacking, and measuring procedures as real ones.  Hence, the pipeline
    results on fake objects can share very similar systematical effects as real ones, which is
    important for tests related to weak lensing analysis.

    Given certain input fake object, \texttt{SynPipe} converts the model magnitude into flux
    in requested HSC filter using the available photometric calibration.  For fake galaxy, we
    convolve the simulated image with PSF model estimated by \texttt{hscPipe} at the desired
    coordinate; and we model fake star by simply scaling the PSF model to the input flux.
    Then, we add the PSF-convolved snapshot to all single CCD images that overlaps with it
    according to available WCS information.  At the edge of the CCD, the simulated image will
    be clipped before adding to it.  Meanwhile, \texttt{SynPipe} adds a new mask plane
    (\texttt{FAKE}) on the existed one to highlight the regions affected by fake objects.
    After these fake-object-added images being reduced by \texttt{hscPipe}, we match the input
    coordinates of fake objects with the output catalogs within certain radius.  Cases of
    unmatched objects and multiple matches can be saved too when necessary.

    Using the infrastructures provided by \texttt{hscPipe}, the above process (e.g. the 
    injection of fake objects) can be easily parallelized.  Hence, the overall efficiency of
    \texttt{SynPipe} is almost identical with the reduction processes of real data.

%% ------------------------------------------------------------------------------------ %%

\section{Test Design}

\todo{A lot to discuss here....}

\subsection{Selection of HSC Data}

    For this work, we focus on the HSC WIDE fields that have reached the designed 
    depth (covered by more than 4 exposures in $g$ and $r$ bands; and more than 6 
    exposures in $i$, $z$, and $y$ bands) in all five bands. 
    They represent the majority of images of HSC survey, and they are of great 
    scientific importance.  
    Also, for now, the HSC DEEP and UDEEP layers have not reached the expected depth.

    During the image co-adding process, the celestial sphere is broken into a set 
    of fixed square regions referred as \texttt{Tract}, which are similar in size 
    to the field of view of the HSC camera. 
    Each \texttt{Tract} further contains $9\times9$ sub-regions named \texttt{Patch}. 
    And each \texttt{Patch} is $4200\times4200$ pixels in size. 
    Since we choose to make the \texttt{SynPipe} as realistic as possible, the volume 
    of data it creates is also the same with the real reduction.  
    For this reason, it is obviously not realistic to test the entire HSC WIDE 
    dataset.  
    But for the purpose of testing the photometric performance, representative subset
    of data is all we need. 
    For a single \texttt{Tract}, we can easily tens of thousands of objects 
    (actual number depends on the magnitude and size) for our tests.

    Since the detection and measurement of objects close to the detection limit 
    strongly depends on the seeing; and the PSF photometry for point sources,  
    the \texttt{cModel} photometry for extended sources both depend on the PSF 
    model, we will test two \texttt{Tracts} that represent good and bad seeing 
    conditions in the $i$-band.  
    We focus on the $i$-band seeing because, as the default band for weak lensing 
    analysis, the $i$-band images are always observed under ideal seeing condition,
    and they are often used as the reference image in the multiband photometry of 
    \texttt{hscPipe}.

    We choose \texttt{Tract} 8522 as example of field with bad $i$-band seeing 
    (average seeing is $\sim 0.9^{\arcsec}$); and \texttt{Tract} 9698 for regions 
    with good seeing ($\sim 0.6^{\arcsec}$; given the pixel size of HSC, the PSF 
    is not under-sampled).

\subsection{Synthetic Stellar Object}

    For stellar objects, we make very simple assumption

    \begin{itemize}
        \item \plan{We simulate stellar object using the reconstructed PSF model given 
                    the desired coordinates at individual exposure level.  
                    The spatial variantion of seeing, and seeing difference among all 
                    exposures are naturally taken into account.}
        \item \plan{\textbf{Magnitude distribution}:
                    1: If we just want to test the PSF magnitude, we can use very 
                           simple distribution of magnitude, e.g flat distribution 
                           between 21 to 27 magnitude.
                    2: If we want to also focus on the detection limits and 
                           star-galaxy separation at faint end, we can inject more 
                           faint stars.  (e.g. Claire used to just inject large number 
                           of 26, 27 magnitude stars, and see how many are recovered).}
        \item \plan{\textbf{Color distribution}:
                    1: We can just make all color equal 0.0. This way, we can still 
                       test the PSF magnitude in each band independently.
                    2: Magnitude-dependent color distribution from ``real'' stars. 
                       This could be taken from other studies, or from the observed
                       HSC stars.  The only issue is that at very faint end, do we have
                       reliable information about the color distribution ? 
                       (and does it matter?)}
        \item \plan{\textbf{Number of Stars}:
                    For point sources, we can afford adding a large amount into one Tract. 
                    (e.g. 500-1000 per CCD). 
                    SH will check papers from other projects to see how many is considered 
                    large enough}
    \end{itemize}

\subsection{Synthetic Galaxy}

    \todo{\textbf{There are multiple decisions to be made here!!}}
    \begin{itemize}
        \item \plan{\textbf{Types of Synthetic Galaxies}:
                    1. Only single-\ser object or also want to try bulge$+$disk model? 
                    2. Besides the single-\ser model, which is ``more realistic'', do 
                       we want to test basic Exp and deV models.  
                       The Exp and deV models can be used to sanity-check the cModel 
                       photometry.  I have done this before, and the results look quite 
                       reasonable for \texttt{hscPipe\ v3.8.5}.}
        \item \plan{\textbf{Separate the low-\ser and high-\ser index ones?}
                    In the tests conducted by SH, the accuracy of cModel photometry shows
                    clear dependence on \ser index.  
                    In some of the tests, SH has separated the sample into two groups using
                    \ser index lower/higher than 2.5 to highlight such difference. 
                    If we will only single-\ser model, SH prefers to use this approach; 
                    If we choose to test Exp and deV models as while, it may not be necessary 
                    to do so; we can still show the dependece of systematical error on 
                    \ser index.}
        \item \plan{\textbf{Magnitude Distribution and Limit}:
                    Since we will be using Claire's catalog from COSMSO galaxies, we can 
                    simply randomly sample the given mangitude distribution.  
                    But, the amount of galaxies that are brighter than 22.0 mag is quite small, 
                    if we want to have reliable statistics at the bright end, we can also 
                    test the bright and faint galaxies separately.  SH has done this before. 
                   }
        \item \plan{\textbf{Structural Parameters}:
                    1. \ser index should be between 0.5 and 5.0.  
                       There are galaxies that appear to be more extended than that, 
                       but SH thinks single-\ser is no longer appropriate model for them.
                    2. Should have limit on effective radius (actually, the average surface 
                       brightness within effective radius) to exclude too ``diffuse'' objects.  
                       There are interesting diffuse galaxies, but in Claire's catalog, most 
                       of the diffuse models are due to problematic fitting results, especially 
                       at the faint end.  SH thinks that they should be removed.}
        \item \plan{\textbf{Color Distribution}:
                    1. Should mention that color gradient is not considered here.  
                       (which is possible if we change the size and/or \ser index in different 
                       band, or use different colors for bulge and disk.
                    2. Again, we could assume all color equal 0.0, and focus on the photometry 
                       in each band separately. 
                    3. Or we can use naive, but ``reasonable'' color: e.g. bluer color for 
                       low-\ser objects; redder color for high-\ser objects, which is used by SH
                       for previous test.
                    4. In principle, we can use the rich photometric data in COSMOS to come 
                       up with a realistic multiband catalog for Claire's model.}
       \item \plan{\textbf{Blendedness of Galaxies}:
                   1. We can avoid blending between two fake galaxies by designing the input 
                      catalog more carefully; or inject fake galaxies on a grid with large 
                      separation.
                   2. To test the impact of blendedness on the photometry, SH used to separate 
                      the galaxies with large blendedness from the pipeline. Meanwhile, we 
                      can only add fake galaxies near real objects, or adding pairs of fake 
                      objects.}
    \end{itemize}

\subsection{Running SynPipe Test}

    \plan{Briefly explain how the SynPipe runs are conducted.}
    \todo{Do we want to run afterburner.py, and test the color using PSF-matched 
          aperture photometry?}

    \begin{itemize}
        \item \plan{Prepare input catalogs, avoid adding fake objects on pixels affected 
                    by saturated or interpolated masks.} 
        \item \plan{Run stack.py and multiband.py using the default configuration of 
                    HSC pipeline; Do we also want to test the cModel photometry using 
                    per-pixel variance information?  Or should we try to turn on the 
                    garbage suppression?}
        \item \plan{Briefly explain the matching processes:
                    1. Match the input catalog with the pipeline outputs using 2 pixel 
                       matching radius; In case of multiple matches, all matches are kept 
                       in the catalog, but only the closest one is used for comparison.
                    2. Match the input catalog with the pipeline results from data without 
                       synthetic objects using a slightly larger matching radius.  This is 
                       mainly to see how many synthetic objects are heavily ``contaminated''
                       with the real objects.}
    \end{itemize}

%% ------------------------------------------------------------------------------------ %%

\section{Results}

\subsection{Detection Limits of Point Sources (Optional)}

    \plan{It seems to SH that, if we seriously want to discuss this topic, we need to 
          design the tests very carefully; and the detection limits of point sources can 
          be tested using the ``sky object''. 
          But, we can still say a few words here.  Excluding the synthetic stars affected 
          by problematic pixels and real objects, we can simply summarize the fraction of 
          detected point sources at different magnitude and seeing condition.  
          We can also show a few examples of undetected stars.}

\subsection{Star-Galaxy Separation (Optional)}

    \plan{Again, this topic itself should deserve its own paper, and I know that Jose has 
          made a lot of improvements.  
          However, it is quite straightforward for SH to briefly mention something:
              1. Fraction of stars that are classified as galaxies; Their magnitude and 
                 blendedness distributions.
              2. Fraction of galaxies that are classified as stars; Their magnitude, 
                 blendedness, and structural parameter distributions. 
                 (In SH's previous test, faint, exponential-like galaxies are slightly 
                 more likely to be classified as stars)}

\subsection{Photometric Performance}

\subsubsection{General Behaviours (Optional)}

    \begin{itemize}
        \item \plan{What fraction of stars have failed PSF magnitude (should be very low)}
        \item \plan{What fraction of galaxies have failed (1) Kron, (2) cModel photometry;
                    Their magnitude, blendedness, structural parameter distributions; 
                    (In SH's previous tests, there are still a few percents of fake galaxies 
                     that have failed cModel; and it is slightly more likely for galaxy with 
                     high \ser index to have failed Kron or cModel.)}
    \end{itemize}

\subsubsection{PSF photometry of Stars}

    \begin{itemize}
        \item \plan{Magnitude v.s. $\Delta$(Magnitude) for different seeing conditions.}
        \item \plan{Magnitude v.s. $\Delta$(Color); Color v.s. $\Delta$(Color) for 
                    different seeing conditions.}
        \item \plan{Discuss the impact from ``blendedness'' and bright object masks.}
    \end{itemize}

\subsubsection{Kron photometry of Galaxies}

    \begin{itemize}
        \item \plan{Magnitude v.s. $\Delta$(Magnitude) for different seeing conditions.
                    Can also separate them into low- and high-\ser index groups.}
        \item \plan{Magnitude v.s. $\Delta$(Color); Color v.s. $\Delta$(Color) for 
                    different seeing conditions; 
                    Can also separate them into low- and high-\ser index groups.}
        \item \plan{Discuss the impact from ``blendedness'' and bright object masks.}
    \end{itemize}

\subsubsection{cModel photometry of Galaxies}

    \begin{itemize}
        \item \plan{Magnitude v.s. $\Delta$(Magnitude) for different seeing conditions.
                    Can also separate them into low- and high-\ser index groups.}
        \item \plan{Magnitude v.s. $\Delta$(Color); Color v.s. $\Delta$(Color) for 
                    different seeing conditions; 
                    Can also separate them into low- and high-\ser index groups.}
        \item \plan{Discuss the impact from ``blendedness'' and bright object masks.}
        \item \plan{If we decide to test the Exp and deV models, we can show results for 
                    cmolde.exp and cmodel.dev photometry first}
    \end{itemize}

\subsubsection{Color using PSF-matched Aperture Photometry (Optional)}

    \todo{Depends on whether we want to test the afterburner.}

    \plan{Focus on whether the afterburner results can help improve the accuracy of 
          color for galaxies, especially the ones with very high blendedness.}

\subsubsection{Shape and Structural Parameters of Galaxies (Optional)}

    \todo{Decide whether to include this.}
    \plan{Using the default pipeline configuration, cModel still shows serious biases in 
          recovering the size and shape of galaxies.  We can:
          1. Do not show results here, but mention a few words in the Future Plans section 
             below: ``We are aware that the cModel and the configuration has some issues, 
             we will use SynPipe to see if we can improve this.''
          2. Show the results, explain the main reasons for these problems, and use it as 
             a warning to people who want to use these results.
          3. Comparisons with the results from test using the per-pixel variance information 
             for cModel.  (SH's previous test during the Taipei meeting shows clear 
             improvements)
          }

    \plan{Relationship between the fracDev and the \ser index of galaxies (or other parameters).  
          In SH's previous test, fracDev is only useful to separate low- and high-\ser index 
          galaxies when they are brighter than 21 mag in i-band.}

%% ------------------------------------------------------------------------------------ %%

\section{Conclusions and Future Plans}

    \plan{Summary of the paper}
    \begin{itemize}
        \item \plan{Basically the information in abstract, but in different way.}
        \item \plan{Summarize the basic performance of HSC pipeline into a few 
                    bullet points.} 
    \end{itemize}

    \plan{Other applications of the SynPipe (just mentioned a few here)}
    \begin{itemize}
        \item \plan{Can be used as a standard QA tools for future data release and 
                    pipeline update;  Can be used to tweak configuration of pipeline
                    to improve the photometry of certain objects (useful for 
                    other HSC users).}
        \item \plan{Ryoma Murata's tests and other tests related to weak lensing shape 
                    catalog.}
        \item \plan{Ono-san's test on the detection of dropouts (have not contacted 
                    Ono-san to see if he want to be mentioned here)}
        \item \plan{Johnny Greco and SH's test about the detection of ultra-diffuse 
                    galaxies (UDG).}
    \end{itemize}

    \plan{Further improvements of the SynPipe}
    \begin{itemize}
        \item \plan{More flexible, realistic models for galaxies.}
        \item \plan{For many purposes, it should be Ok to directly inject synthetic 
                    objects onto the deepCoadd images. 
                    This can improve the efficiency.}
        \item \plan{Only do photometric measurements on objects that overlap the FAKE
                    mask plane.  This can improve the efficiency of SynPipe.}
        \item \plan{Right now, the SynPipe applies PSF convolution to synthetic object 
                    using the exactly ``accurate'' PSF model from HSC pipeline. 
                    We can simulate the typical PSF model uncertainty by reconstructing 
                    PSF model using a different location on the same Visit.}
        \item \plan{Accuracy of background subtraction has not been taken into account}
    \end{itemize}

%% ------------------------------------------------------------------------------------ %%

\begin{ack}

    The Hyper Suprime-Cam (HSC) collaboration includes the astronomical communities of 
    Japan and Taiwan, and Princeton University.  
    The HSC instrumentation and software were developed by the National Astronomical 
    Observatory of Japan (NAOJ), the Kavli Institute for the Physics and Mathematics of
    the Universe (Kavli IPMU), the University of Tokyo, the High Energy Accelerator 
    Research Organization (KEK), the Academia Sinica Institute for Astronomy and 
    Astrophysics in Taiwan (ASIAA), and Princeton University.
    Funding was contributed by the FIRST program from Japanese Cabinet Office, the 
    Ministry of Education, Culture, Sports, Science and Technology (MEXT), the Japan 
    Society for the Promotion of Science (JSPS), Japan Science and Technology Agency 
    (JST), the Toray Science  Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton 
    University.

    This paper makes use of software developed for the Large Synoptic Survey Telescope. 
    We thank the LSST Project for making their code available as free software at 
    http://dm.lsstcorp.org.

    The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the 
    Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office, 
    the Max-Planck Society and its participating institutes, the Max Planck Institute 
    for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics, 
    Garching, The Johns Hopkins University, Durham University, the University of 
    Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics, 
    the Las Cumbres Observatory Global Telescope Network Incorporated, the National 
    Central University of Taiwan, the Space Telescope Science Institute, the National 
    Aeronautics and Space Administration under Grant No. 
    NNX08AR22G issued through the Planetary Science Division of the NASA Science 
    Mission Directorate, the National Science Foundation under Grant No. AST-1238877, 
    the University of Maryland, and Eotvos Lorand University (ELTE) and the Los Alamos 
    National Laboratory.

    This research made use of
    \href{http://www.scipy.org/}{\texttt{SciPy}},
      an open source scientific tools for Python (\citealt{SciPy});
    \href{http://www.numpy.org/}{\texttt{NumPy}}, 
      a fundamental package for scientific computing with Python (\citealt{NumPy});
    \href{http://matplotlib.org/}{\texttt{Matplotlib}}, 
      a 2-D plotting library for Python (\citealt{Matplotlib});
    \href{http://www.astropy.org/}{\texttt{Astropy}}, a community-developed 
      core Python package for Astronomy (\citealt{AstroPy}); 
    \href{http://scikit-learn.org/stable/index.html}{\texttt{scikit-learn}},
      a machine-learning library in Python (\citealt{scikit-learn}); 
    \href{http://www.astroml.org/}{\texttt{astroML}}, 
      a machine learning library for astrophysics (\citealt{astroML});
    \href{https://ipython.org}{\texttt{IPython}}, 
      an interactive computing system for Python (\citealt{IPython}).

\end{ack}

%%%%%%%%%%: Bibliographic Section %%%%%%%%%%

%\bibliography{synpipe}

%% ------------------------------------------------------------------------------------ %%

\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[Aihara et al.(2017)]{HSCDR1} Aihara, H., Armstrong, R., Bickerton, S., et al.\ 
         2017, arXiv:1702.08449

\bibitem[Chang et al.(2015)]{Chang2015} Chang, C., Busha, M.~T., Wechsler, R.~H., et al.\ 
         2015, \apj, 801, 73

\bibitem[Suchyta et al.(2016)]{Suchyta2016} Suchyta, E., Huff, E.~M., Aleksi{\'c}, J., 
         et al.\ 2016, \mnras, 457, 786

\end{thebibliography}
%% ------------------------------------------------------------------------------------ %%

%%%%%%%%%%: Appendix Section %%%%%%%%%%%%

%\appendix

%\section{A. Derive average mass-to-light ratio using \texttt{iSEDFit}}

%%%%%%%%%%%: Possible Tables %%%%%%%%%%%%%
%\input{table1.tex}

\label{lastpage}
\end{document}

### 2017-04-12 draft/ms_v1.tex
CModel: S/N

@@
 
-\subsubsection{Input magnitude and the $\mathrm{S}/\mathrm{N}$ of \cmodel{} photometry}
-
-    \begin{itemize}
-
-        \item In Fig \ref{fig:cmodel_sn}, we show the relations between the input
-            magnitude and the $\mathrm{S}/\mathrm{N}$ recovered by \cmodel{}
-            photometry in $g$- and $i$-band.
-
-        \item \plan{Define $\mathrm{S}/\mathrm{N}$.
-                    Unlike point sources, at fixed total magnitude, the
-                    synthetic galaxies have a range of size and shape that
-                    lead to different average surface brightness.
-                    Comparing to stars, at the same input magnitude, synthetic
-                    galaxies have lower average $\mathrm{S}/\mathrm{N}$ and larger
-                    scatter. }
-
-        \item \plan{Seeing condition still impacts the $\mathrm{S}/\mathrm{N}$ of
-                    galaxies}
-
-        \item \plan{Blendedness can reduce the $\mathrm{S}/\mathrm{N}$ a little.}
-
-        \item \plan{Briefly discuss the detection limit of point sources.
-            Basically consistent with the reported values in \citet{HSCDR1}.
-            Although at $i{\sim}25.2$, the average $\mathrm{S}/\mathrm{N}$ is quite high,
-            small fraction of galaxies will have very low $\mathrm{S}/\mathrm{N}$.}
-
-    \end{itemize}
+\subsubsection{Input magnitude and the \s2n{} of \cmodel{} photometry}
+
+    In Fig \ref{fig:cmodel_sn}, we first show the relations between the input 
+    magnitudes and the \s2n{} of the synthetic galaxies estimated by the ratio 
+    between \cmodel{} flux and its uncertainties from \hscpipe{}. 
+    Since these galaxies are extended objects, the \s2n{} here should be treated 
+    as the average \s2n{} which is different from the \s2n{} of stars using PSF 
+    photometry.
+
+    We still use $i$- and $g$-band as examples. 
+    Comparing to the similar figure for stars, the most obvious difference is that
+    at fixed input magnitude, the \s2n{} distribution of galaxies show much larger
+    scatter than stars.  
+    At the same total flux, galaxy can have different size and shape, and 
+    naturally leads to differences in their peak and average \s2n{}.  
+    This also makes it difficult to have a clear definition of ``detection limit'' 
+    for galaxies. 
+    For $i$-band, the typical \s2n{} for synthetic galaxies at the magnitude limit 
+    of our sample ($25.2$ mag) is ${\sim}20$, but the low-\s2n{} tail has already 
+    reached to the \s2n{}$=5$ boundary.  
+    This suggests that, although HSC Wide can detect galaxies as faint as 
+    $i{\sim}26.0$ mag, the sample will become highly incomplete. 
+    Furthermore, it can also introduce bias into the selection as galaxies with 
+    certain structural properties are harder to detect than others. 
+    \todo{Add average \s2n{} of the high and low \ser{} index galaxies at 
+    $23.8 < i < 24.2$ mag.}
+    Users of HSC survey data who want to select flux-limited samples of galaxies,
+    or intend to study the population of faint (e.g. high-$z$) galaxies should
+    keep this in mind.
+
+    Similar to the synthetic stars, worse seeing condition can also lead to 
+    noticeable decrease of \s2n{} at the same magnitude (see the figure for
+    $i$-band). 
+    Meanwhile, the highly blended synthetic galaxies do not show significantly 
+    different \s2n{} distributions here.
 

### 2017-04-12 draft/ms_v1.tex
CModel: magnitude

@@
 \newcommand{\term}[1]{\textbf{\texttt{#1}}}
+
+\newcommand{\plus}{\raisebox{.4\height}{\scalebox{.6}{+}}}
+\newcommand{\minus}{\raisebox{.4\height}{\scalebox{.8}{-}}}
 
@@
     Generally speaking, the PSF photometry is accurate to 1--2\% level, and the
-    astrometry is accurate to ${\sim}10$ and 40 max internally and externally.
+    astrometry is accurate to ${\sim}10$ and 40 mas internally and externally.
 
@@
 
-\subsubsection{Input magnitude and the $\mathrm{S}/\mathrm{N}$ of PSF photometry}
+\subsubsection{Input magnitude and the \s2n{} of PSF photometry}
 
@@
     The overall performance of PSF photometry is excellent.
-    In $i$-band, the median magnitude difference for \tract{} with 0.5\asec{} seeing is
+    In $i$-band, the median magnitude difference for \tract{} with 0.45\asec{} seeing is
     around ${\sim}0.015$ mag (${\sim}1.5$\% accuracy) at
@@
 
-    \begin{itemize}
-
-        \item In Fig \ref{fig:cmodel_mag}, we evaluate the accuracies of the \forced{}
-            \cmodel{} magnitudes in all five bands.
-
-        \item \plan{Generally speaking, the \forced{} \cmodel{} provides good estimates
-            of magnitudes for galaxies between 20.0 and 25.0 magnitude in all filters and
-            different seeing conditions. }
-
-        \item \plan{For $i$-band the absolute flux accuracy is around 7\% level at
-            $i{\sim}21.0$ mag, and it increases to ${\sim}10$\% at $i{\sim}25.0$ mag.
-            The \forced{} \cmodel{} photometry slightly underestimate the total flux of
-            galaxies at $21.0 < i < 23.0$ mag.
-            The average magnitude difference is at 0.04 mag level.
-            For $i > 23.0$ mag, the \forced{} \cmodel{} photometry is unbiased.}
-
-        \item \plan{The \forced{} \cmodel{} magnitude error from \hscpipe{} only considers
-            the per pixel noise, but not the systematic uncertainties involved in the
-            modeling fitting process.
-            Therefore it is no surprise that the typical uncertainty from the \synpipe{}
-            test is larger than the magnitude error.}
-
-        \item \plan{The accuracies of the \forced{} \cmodel{} magnitudes in other bands
-            are similar to the $i$-band.
-            The only exception is for galaxies with $y<24.0$ mag where \forced{} \cmodel{}
-            seems to overestimate the flux slightly.}
-
-        \item \plan{For galaxies with $i < 20.0$, the statistics are uncertain due to small
-            sample size}
-
-        \item \plan{Unlike the synthetic stars, the highly blended synthetic galaxies only
-            have slightly biased photometry, where \forced{} \cmodel{} underestimates the
-            fluxes of these galaxies by ${\sim}0.05-0.10$ mag.
-            High blendedness does lead to larger scatter in photometric uncertainties.}
-
-       \item \plan{We also test the \unforced{} \cmodel{} photometry in all five bands,
-           and the results suggest similar accuracies.
-           We highlight the differences between \forced{} and
-           \unforced{} \cmodel{} photometry in Fig \ref{fig:cmodel_diff}.}
-
-    \end{itemize}
+    In Fig \ref{fig:cmodel_mag}, we illustrate the photometric uncertainties of the 
+    \cmodel{} magnitudes in each band using the same format with 
+    Fig \ref{fig:psf_mag}.
+
+    The overall performance of \cmodel{} photometry is very reasonable all the way 
+    down to $i_{\mathrm{Input}}=25.2$ mag. 
+    Comparing to the qualities of PSF photometry for stars, the magnitude differences
+    of \cmodel{} show much larger scatter. 
+    Given the diversity of properties of these galaxies and the complexities in the 
+    model-fitting process, this difference is expected.  
+    At the same time, we can see that the \cmodel{} algorithm in \hscpipe{} can 
+    provide unbiased and consistent photometry for galaxies in different bands and 
+    seeing conditions.
+
+    In $i$-band, the median flux uncertainties of \forced{} \cmodel{} is ${\sim}7$\% 
+    in the good-seeing \tract{} at $i_{\mathrm{Input}}{\sim}20.0$ mag, 
+    and ${\sim}9$\% at $i_{\mathrm{Input}}{\sim}24.0$ mag.  
+    Down to $i_{\mathrm{Input}}{\sim}25.0$ mag, the median uncertainty maintains 
+    at ${\sim}11$\% level. 
+    For the bad-seeing \tract{}, the performance is very similar in $i$-band. 
+    From $i_{\mathrm{Input}}{\sim}20.0$ to $25.0$ mag, the median magnitude difference
+    between output and input values changes from \plus{}$0.041$ mag to 
+    \minus{}$0.005$ mag, which suggests that \forced{} \cmodel{} photometry is 
+    unbiased down to very faint end. 
+    It is worth noting that the photometric uncertainties estimated by \synpipe{}
+    are significantly larger than the fiducial error from \hscpipe{} that does not 
+    take into account the systematically uncertainties involved in the modeling 
+    fitting process. 
+    Although the synthetic galaxies here are described by the simple single-\ser{} 
+    model, \cmodel{} algorithm can only approximate them to certain accuracy, 
+    especially when the noise level, deblending uncertainty, and priors of model 
+    parameters are considered. 
+    Given that the real galaxies are more complex in structural details, these 
+    uncertainties should be treated as lower limits.
+
+    The performance of \forced{} \cmodel{} photometry is very consistent across all
+    filters. 
+    For $g$, $r$, and $z$-band, the photometric uncertainties are very similar to 
+    the ones for $i$-band between $20.0$ to $25.0$ mag. 
+    The \forced{} \cmodel{} magnitudes are also unbiased for these 3 filters 
+    across the entire input magnitude range. 
+    The uncertainties for $y$-band are slightly large, range from 9-17\% in the 
+    same magnitude bins. 
+    In addition, \forced{} \cmodel{} tends to overestimate the total flux in $y$-band
+    at $y_{\mathrm{Input}}>24.0$ mag. 
+    Mean magnitude differences change from \minus{}0.06 at 24.0 mag to \minus{}0.22
+    mag at 25.0 mag.  
+    Both worse seeing condition and higher background noise level can make it more 
+    difficult to detect faint object on $y$-band image.
+    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} in $y$-band
+    is already close to the detection threshold.
+
+    As mentioned, the statistics for brighter galaxies are very uncertain due to 
+    small sample size. 
+    However, we do notice that, at $i_{\mathrm{Input}}<20.0$, the \forced{} 
+    \cmodel{} photometry shows larger uncertainty and starts to systematically 
+    underestimate the total flux.  
+    This problem is confirmed via comparing with more carefully derived total fluxes 
+    for bright galaxies (e.g. \citealt{HSCDR1}, Huang\etal in prep.). 
+    It relates to the known issues of \hscpipe{} (e.g. over-deblend around bright 
+    objects; inappropriate weighting of priors in \cmodel{}), but it may also suggest
+    that, at the imaging depth of HSC, assumptions in \cmodel{} are no longer the 
+    best choice in modeling these galaxies (e.g. for massive elliptical galaxies; 
+    see Huang\etal in prep.~for more details).
+
+    For the highly blended synthetic galaxies, we also see systematically 
+    underestimated total flux (average offset ${\sim}0.1$ mag) and larger scatter 
+    of photometric uncertainty in all five bands.  
+    Meanwhile, the contrast between relative isolated and highly blended galaxies 
+    in photometric performance is no longer as staggering as the one for synthetic
+    stars (Fig \ref{fig:psf_mag}).
+
+    We also test the \unforced{} \cmodel{} photometry in all five bands, and the 
+    results suggest similar accuracies.
+    We highlight the differences between \forced{} and \unforced{} \cmodel{} 
+    photometry in $g$- and $y$-band in Fig \ref{fig:cmodel_diff}.
+    The only noticeable difference is for galaxies brighter than $24.0$ mag in 
+    $g$-band, their \forced{} \cmodel{} magnitudes are systematically brighter than 
+    the \unforced{} ones.
 

### 2017-04-12 draft/ms_v1.tex
Comments: Ono-san on other synpipe applications

@@
     of M31 to help the search of interesting microlensing events.
-    At this moment, it is also being used to help select high-$z$ Lyman-break galaxies
-    and Lyman-$\alpha$ emitters (Ono\etal in prep.; Kono\etal in prep); identify
-    low surface brightness dwarf galaxies (Greco\etal in prep); and test photometric
-    and WL measurements around nearby clusters (Chiu\etal in prep).
+    At this moment, it is also being used to estimate the completeness of the selections 
+    for high-$z$ Lyman-break galaxies (LBG) and Lyman- $\alpha$ emitters 
+    (Ono\etal in prep.; Konno\etal in prep), check the dependence of the detection and 
+    completeness of high-$z$ LBG pairs on the pair separation (Harikane\etal in prep.),
+    identify low surface brightness dwarf galaxies (Greco\etal in prep),
+    and test photometric and WL measurements around nearby clusters (Chiu\etal in prep).
 

### 2017-04-14 draft/ms_v1.tex
Song: CModel color & astrometry

@@
         }
-    \label{fig:galaxy_cdist}
+    \label{fig:cmodel_cdist}
 \end{figure*}
@@
 
+%% ------------------------------------------------------------------------------------ %%
 \subsubsection{Input magnitude and the \s2n{} of \cmodel{} photometry}
@@
     certain structural properties are harder to detect than others. 
-    \todo{Add average \s2n{} of the high and low \ser{} index galaxies at 
-    $23.8 < i < 24.2$ mag.}
     Users of HSC survey data who want to select flux-limited samples of galaxies,
@@
 
+%% ------------------------------------------------------------------------------------ %%
 \subsubsection{Accuracy of the \cmodel{} magnitude}
@@
 
+%% ------------------------------------------------------------------------------------ %%   
 \subsubsection{Accuracy of the \cmodel{} color}
 
-    \begin{itemize}
-
-        \item \plan{Briefly explain why \cmodel{} colors are important.}
-
-        \item The results for accuracy of \forced{} \cmodel{} colors are shown in
-            Fig \ref{fig:cmodel_color} and Fig \ref{fig:cmodel_cdist}.
-
-        \item \plan{\forced{} \cmodel{} photometry provides accurate and unbiased
-            colors for galaxies at $20.0 < i < 25.0$ mag at different seeing conditions.
-            The accuracies of colors also do not show dependence on input colors.
-            }
-
-        \item \plan{For $(g-i)$ color, average uncertainty around
-            $i_{\mathrm{Input}}{\sim}21.0$ mag is ${\sim}0.04$ mag.
-            The uncertainty increases to ${\sim}0.11$ mag at
-            $i_{\mathrm{Input}}{\sim}25.0$ mag.
-            Results for $(i-y)$ color is similar.}
-
-        \item \plan{High blendedness can increase the uncertainties of the color
-            and bias the color measurements.
-            The highly blended galaxies on average show slightly bluer $(g-i)$ colors
-            and redder $(i-y)$ colors comparing to the input values.}
-
-        \item \plan{In Fig \ref{fig:cmodel_cdist}, we show that the \forced{} \cmodel{}
-            photometry can reasonably recover the color-color distributions of galaxies
-            down to $i{\sim}25$ mag.
-            }
-
-    \end{itemize}
-
+    The consistent and accurate five-band \cmodel{} colors from \hscpipe{} are crucial 
+    to the photometric redshift and spectral energy distribution (SED) fitting results. 
+    They are also key to the selection of high-$z$ Lyman-break galaxies (LBG) and 
+    and many other interesting objects.
+
+    In Fig \ref{fig:cmodel_color}, we demonstrate the accuracies of \forced{} $(g-i)$
+    and $(i-y)$ \cmodel{} colors in the same format for synthetic stars 
+    (Fig \ref{fig:psf_color}).
+    These plots show that \hscpipe{} can provide reliable \cmodel{} colors for 
+    synthetic galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag. 
+    For $(g-i)$ colors, average uncertainty around $i_{\mathrm{Input}}{\sim}21.0$ mag 
+    is ${\sim}0.04$ mag.
+    The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
+    Results for $(i-y)$ colors are similar.
+
+    The performance of \forced{} \cmodel{} color does not show dependence on seeing
+    condition, and is unbiased across the ranges for input total magnitude and color.
+    The only noticeable feature is that the $(i-y)$ color at 
+    $i_{\mathrm{Input}}>24.0$ is slightly overestimated. 
+    As mentioned above, this is not surprise given the shallower imaging depth of 
+    $y$-band.    
+    At the same time, high blendedness of synthetic galaxies can still increase the 
+    uncertainties of the color and bias the color measurements.
+    The highly blended galaxies on average show slightly bluer $(g-i)$ 
+    colors and redder $(i-y)$ colors than the input values.
+
+    Similar to Fig \ref{fig:psf_cdist}, we also compare the color--color distributions 
+    of the input and output \forced{} \cmodel{} values in Fig \ref{fig:cmodel_cdist}. 
+    The general distributions of colors are well recovered despite the accuracy is 
+    not as good as the one for stars, especially on the $(i-z)$ v.s. $(z-y)$ plane. 
+    It is expected given the narrow dynamical ranges of these colors among red filters.
+    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$ 
+    colors at the very ``blue'' end, while overestimate the $(i-y)$ color at very 
+    red end.
+
+    In the end, we should point out that we assume constant color for the entire galaxy.  
+    In reality, different colors for individual components and smooth color gradient 
+    can really complicated the situation, hence the uncertainties of \cmodel{} colors 
+    here should be considered as lower limits.
 %% ------------------------------------------------------------------------------------ %%
@@
 
-\section{Results on Other Performance}
+\section{Results on Other Aspects of \hscpipe{}}
     \label{sec:others}
+
+    In this section, we briefly discuss a few other issues of \hscpipe{} that relates 
+    to astrometric calibration, star-galaxy separation, and measurements of galaxy 
+    shape to demonstrate the ranges of topics can be tested by \synpipe{}
 
@@
 
-    \begin{itemize}
-
-        \item \plan{Explain what we are testing here; and why it is useful}
-
-        \item In Fig \ref{fig:astrometry}, we briefly look into the accuracies
-            of the astrometric comparison for both synthetic stars and galaxies in
-            \tracts{} with both good and bad seeing.
-
-        \item \plan{We see small astrometric offsets in both R.A and Dec directions
-            that show small differences between the two \tracts{}.
-            The average offset is at ${\sim}10$--20 mas, which is consistent with
-            the estimate in \citet{HSCDR1}}.
-
-    \end{itemize}
+    For \synpipe{} test, we inject synthetic objects to single \visit{} images using 
+    the less accurate, initial astrometric calibration. 
+    During the image stacking step, the joint calibration process will improve the 
+    astrometric solutions. 
+    Therefore the differences between the input and output coordinates from \synpipe{}
+    can help understand the systematic effect of this step.
+
+    In Fig \ref{fig:astrometry}, we plot the distributions of astrometric offsets for 
+    both synthetic stars and galaxies in good- and bad-seeing \tracts{}. 
+    Small systematic offsets at ${\sim}10$--20 mas can be noticed in either direction. 
+    The two \tracts{} apparently show different systematic offsets. 
+    In the same \tracts{}, synthetic stars and galaxies show very similar offsets, 
+    although the scatter for galaxies is slightly larger due to their extended nature.
 
@@
     \label{ssec:sg}
+
+    As we already mentioned, star--galaxy separation is important for cosmology survey,
+    and becomes increasingly difficult for fainter and fainter objects.
 

### 2017-04-14 draft/ms_v1.tex
Song: Star-galaxy separation

@@
     As we already mentioned, star--galaxy separation is important for cosmology survey,
-    and becomes increasingly difficult for fainter and fainter objects.
-
-    \begin{itemize}
-
-        \item \plan{Explain how star--galaxy separation is done in \hscpipe{}, and
-            why it is difficult at faint magnitudes.}
-
-        \item In Fig \ref{fig:sg}, we highlight the misclassified stars and galaxies
-            on the relations between the input magnitude and
-            $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$.
-
-        \item \plan{The fraction of misclassified stars show dependence on both
-            input magnitude and seeing.}
-
-        \item \plan{Most of the misclassified galaxies have $i > 24.0$.
-            The fraction of misclassification and distribution of
-            $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$ for synthetic galaxies also depend on
-            seeings}.
-
-    \end{itemize}
+    and becomes increasingly difficult at very faint magnitude ($i<24.0$ mag). 
+    In \hscpipe{}, the star--galaxy classification primarily depends on the extendedness 
+    value that is measured by the magnitude difference between PSF and \cmodel{} 
+    photometry in $i$-band. 
+    For more details about this algorithm, please see Section 4.9.9 in Bosch\etal 
+    (in prep.).
+
+    In Fig \ref{fig:sg}, we show the current status of star--galaxy classification  
+    via comparing the input magnitude with the difference between PSF and \cmodel{} 
+    magnitudes for both synthetic stars and galaxies, and highlight the distributions 
+    for misclassified objects. 
+    As described in earlier sections, $>20$\% of synthetic stars at 
+    $i_{\mathrm{Input}}>23.0$ mag is misclassified as extended objects, while only a 
+    tiny fraction of faint synthetic galaxies ($i_{\mathrm{Input}}>24.0$) are 
+    misclassified. 
+    This confirms that the current star--galaxy classification strategy in \hscpipe{}
+    results in galaxy sample with \textbf{high completeness} and star sample 
+    with \textbf{high purity}.
+
+    It it also easy to notice that seeing condition strongly modify the distributions 
+    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$, where worse seeing clearly make it 
+    more difficult to separate star and galaxy.  
+    This implies that the completeness/purity of star and galaxy sample at faint end
+    may depend on seeing, which deserve the attention of HSC users who care about 
+    these properties.
+
+    In the next data release, \hscpipe{} will include a better star--galaxy classifier
+    that is based on Machine Learning method takes the shape and color information 
+    into account. 
+    We will test its improvement using \synpipe{} in the future.
 
@@
 
-    \plan{Review the definition of blendedness and explain why it is important.}
-    \plan{Relationship between magnitude and blendedness}
-
-    \plan{How blendedness affects the photometric uncertainties}
+    In the above sections, we have pointed out the impact of high blendedness on 
+    photometry through a small sample of highly blended objects.  
+    Here, in Fig \ref{fig:blend}, we further explore the effect of blendedness via 
+    directly plot it against the uncertainties of magnitudes and colors for both stars 
+    and galaxies.
 

### 2017-04-14 draft/ms_v1.tex
Song: blendedness v.s. error

@@
     Here, in Fig \ref{fig:blend}, we further explore the effect of blendedness via 
-    directly plot it against the uncertainties of magnitudes and colors for both stars 
-    and galaxies.
+    directly plotting it against the uncertainties of magnitudes and colors.
+
+    For both PSF and \cmodel{} magnitude, we can see clear trends that high-blendeness
+    ($b>0.05$ or $0.1$) objects have systematically underestimated total fluxes. 
+    This effect is particularly strong for stars. 
+    As for colors, higher blendedness still result in higher uncertainties for both 
+    stars and galaxies, but the trends are different. 
+    For stars, highly blended ones have clearly overestimated $(g-i)$ colors, and the 
+    highly blended galaxies seem to have bluer $(g-i)$ colors than the true values.
+
+    These blendedness-related uncertainties are not included in the photometric errors
+    released by \hscpipe{}.  
+    We therefore remind the HSC users of treating the highly blended object with 
+    greater caution.
 
@@
 
+    In SDSS, the structural parameters
+
+    The CModel galaxy fitting algorithm utilizes a Bayesian prior on radius and ellipticity, largely as a way to regularize fits to low S/N and/or poorly-resolved galaxies.
+When combining this with the likelihood to form the posterior probability (which is then
     \plan{Explain why the current \cmodel{}{} algorithm has problem with measuring

### 2017-04-14 draft/ms_v1.tex
Song: Finish the results; add Susan's edits in

@@
 \newcommand{\term}[1]{\textbf{\texttt{#1}}}
+\newcommand{\susan}[1]{\textcolor{magenta} {\textbf{#1}}}
 
@@
 %% ------------------------------------------------------------------------------------ %%
-\title{HSC Synthetic Pipeline I: Basic Design and Characterization of the
-       Photometric Performance of HSC}
+\title{HSC Synthetic Pipeline I: Basic Design and Characterization of HSC
+       Photometric Performance}
 
@@
 
-    The Subaru Strategy Survey Program (SSP) is an ambitious wide-area, multi-band
-    survey using the Hyper Suprime-Cam (HSC) on Subaru telescope.
-    At the imaging depth of this survey, it becomes challenging to achieve accurate,
-    unbiased, and consistent photometry across all five bands.
-    In this work, we present \synpipe{}, a \texttt{Python}-based, flexible framework
-    that interfaces with the HSC data reduction pipeline (\hscpipe{}) and test its
-    performance via injecting synthetic objects to the single-\texttt{visit} HSC images.
-    We use coadd images in two \tracts{} from the Wide layer with representative
-    seeing conditions to demonstrate the implementation of \synpipe{} and examine the 
-    general photometric performance of \texttt{hscpipe}.
-    We find that the typical uncertainties of HSC \forced{} PSF photometry for stars
+   The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band
+    survey using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
+      At SSP's imaging depth \susan{quantify?}, it is challenging to achieve accurate,
+    unbiased, and consistent photometry across all five bands. To improve data processing and achieve accurate photometric measurements, we have developed
+   \synpipe{}, a \texttt{Python}-based, flexible framework
+    that interfaces with the HSC data reduction pipeline (\hscpipe{}) to process data from the first public HSC--SSP data release.
+\susan{I expected to see something in the abstract that clarifies why this is Pipeline I; does this suggestion accomplish that?} We test  \synpipe{}
+    performance by injecting synthetic objects into single-\texttt{visit} HSC images.
+    We use coadded images in two Wide layer \tracts{} with representative
+    seeing conditions to demonstrate  \synpipe{} implementation and to examine  \texttt{hscpipe}'s 
+    general photometric performance.
+    We find that uncertainties of HSC \forced{} PSF photometry for stars typically
     range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
     mag (1\%-7\% accuracy in the $i$-band). 
-    For synthetic galaxies with single-\ser{} model, typical uncertainties of the
-    forced \cmodel{} photometry range from 0.14 mag at $i{\sim}20.0$ mag to
+    For synthetic galaxies based on a single-\ser{} model, uncertainties of the
+    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag to
     0.20 mag at $i{\sim} 25.2$ mag.
-    Over the colors and magnitudes ranges used in these tests, we find that both 
-    \forced{} PSF and \cmodel{} photometry provide unbiased estimates of colors that 
+    Over the color and magnitude ranges used in the  \synpipe{} tests, we find that both 
+    \forced{} PSF and \cmodel{} photometry provide unbiased color estimates that 
     are robust in different seeing conditions.
-    Finally, we notice a few issues in the current \hscpipe{} that are worth keeping
+    We also notice a few issues in the current \hscpipe{} that are worth keeping
     in mind when using HSC data: 
-    1) the degree that a object is blended with others impacts the photometric 
+    1) The degree to which an object is blended with others impacts the photometric 
     accuracy, especially for point sources.
-    Highly blended object tends to have larger photometric uncertainty, systematically
+    Highly blended objects tend to have larger photometric uncertainty, systematically
     underestimated flux, and slightly biased color.
-    2) a relative high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
+    2) A relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
     misclassified as extended objects.
-    3) the shape and size estimates for galaxies using \cmodel{} suffer from strong
+    3) The shape and size estimates for galaxies using \cmodel{} suffer from strong
     biases.
@@
     Wide-field, multi-band imaging surveys have stepped onto the central stage of
-    modern astrophysics and cosmology in the past decade.
-    They also have a bright future as many ambitious projects are being carried out
-    or planned, like the Large Synoptic Survey Telescope
+    modern astrophysics and cosmology over the past decade.
+    They also have a bright future on many current and planned ambitious projects, such as the Large Synoptic Survey Telescope
     (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
@@
     Among many ongoing efforts, the Subaru Strategic Program
-    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}
-    using the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
-    the Subaru telescope is the most efficient one in term of Etendue.
-    These surveys together will greatly help us test cosmological models, trace the
+    (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
+    uses the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
+    the Subaru telescope, is the most efficient in terms of etendue.
+    Together, these surveys will greatly help us test cosmological models, trace the
     evolution of galaxies, study the stellar structure of our Milky Way, and discover
-    large number of interesting transient objects.
+    a large number of interesting transient objects.
 
     %% Challenges
-    Before we can tackle any outstanding scientific question, we first need to learn
-    how to handle the huge amount of data generated by these projects, and achieve
+    Before we can tackle any outstanding scientific questions, we must first learn
+    how to handle the huge \susan{quantify? Or is "huge" a common descriptor for data in your field?} amount of data generated by these projects as well as achieve
     accurate photometric measurements of different types of objects.
-    This target becomes increasingly challenging in the age of modern imaging
-    surveys.
-    The cameras that carry these surveys are often made up of multiple
-    charge-coupled devices (CCDs) with slightly different characteristics and have
-    large field-of-view (FoV) over not perfectly flat focus plane.
-    During the observation, the seeing and background conditions always show spatial
+    Data handling becomes increasingly challenging in the age of modern imaging
+    surveys, in part due to variations and effects related to the cameras' charge-coupled devices (CCDs).
+    The cameras are often made up of multiple
+  CCDs, each with slightly different characteristics, and have
+    large fields-of-view (FoV) over not perfectly flat focus planes.
+    During  observation, the seeing and background conditions always show spatial
     and temporal variations across the FoV.
-    The full-depletion, thick CCD adopted by these cameras enables long exposure time
+    The full-depletion, thick CCDs selected for the cameras enable long exposure times
     and excellent sensitivity in the red-end, but they often have the so-called
-    ``brighter-fatter'' effect (\citealt{Antilogus2014}) which means the size of bright
-    stars are enlarged.
-    All these issues make accurate astrometric and photometric calibration,
+    ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that bright
+    stars appear larger than they are.
+   These variations and effects make accurate astrometric and photometric calibration,
     background subtraction, and point spread function (PSF) modeling intrinsically
-    difficult (e.g. \citealt{Schlafly2012}).
-    In addition, the multi-epoch, multi-band nature of these surveys also complicate
-    the data reduction as one needs to pay special attentions to the processes of
-    image stacking, multi-band object detection and measurements.
-    Furthermore, as ongoing surveys reach to much deeper surface brightness level,
-    the number of objects in unit area, especially faint object, becomes much higher.
-    Not only that, it is much more common to have objects that overlap each other at
-    different levels (which is often referred to as ``blended'').
-    Both situations ask for improved methods for photometric measurements than the ones
+    difficult (e.g., \citealt{Schlafly2012}).
+    The multi-epoch, multi-band nature of the surveys also complicate
+    data reduction because the scientist must pay special attention to
+    image stacking, multi-band object detection, and measurement processes.
+     Furthermore, as ongoing surveys reach to increasingly deeper surface brightness levels,
+    the number of objects, especially faint objects, in a unit area, becomes much higher.
+   In addition, it is much more common to observe objects that overlap each other at
+    different levels (a phenomenon often referred to as ``blended'').
+    These modern imaging survey challenges call for photometric measurement methods that are more powerful and precise than those
     used in previous, shallower surveys.
@@
     %% Reason
-    These challenges mentioned above are not just technical details, they are crucial
-    systematics to key scientific goals of these surveys.
+    The challenges are not merely technical details; their resolution is crucial
+     to achieving the surveys' key scientific goals.
     For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
-    is a powerful tool to measure the large-scale distribution of dark matter and
-    follow its evolution.
-    The WL measurements critically depend on the ability to model PSF and measure the
-    shape of background galaxies in high precision (e.g. \citealt{Mandelbaum2015}).
-    Also, photometric redshift measurement (e.g. \citealt{Benitez2000, Bolzonella2000,
-    Ilbert2009}) is fundamentally important for studying the evolution of galaxies;
+    is a powerful tool for measuring the large-scale distribution of dark matter and
+    following its evolution.
+    However, WL measurements critically depend on the ability to model PSF and measure the
+    shape of background galaxies with high precision (e.g., \citealt{Mandelbaum2015}).
+    The photometric redshift measurement (e.g., \citealt{Benitez2000, Bolzonella2000,
+    Ilbert2009}) is fundamentally important for studying the evolution of galaxies,
     and the ``drop-out'' method is very useful in selecting high-redshift galaxies
-    (e.g. \citealt{Steidel1996}).
-    Both methods are based on accurate multi-band photometric measurements.
-    The list goes on and on, but it becomes clear that we need to develop frameworks
+    (e.g., \citealt{Steidel1996}).
+    However, both of those methods are based on accurate multi-band photometric measurements.
+    There are many other examples, but these are sufficient to demonstrate that we need to develop new frameworks
     to oversee the data reduction process of modern imaging surveys.
-    Several tools with similar goals have been developed (e.g. \citealt{Chang2015,
+    Several tools with similar goals have been developed (e.g., \citealt{Chang2015,
     Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}).
+\susan{Clarify why you mention the DES tools; e.g., does synpipe build on these tools?
+Do they demonstrate the effectiveness of developing new frameworks?
+Why are they insufficient for the HSC survey tasks?}
 
     %% Organization
-    In this work, we present \synpipe{}, a \texttt{Python}-based
-    software to test the data reduction quality of the HSC--SSP (will be referred to
-    as the HSC survey) using synthetic objects.
-    \synpipe{} is designed to be a flexible framework that has many applications
-    and can help future developments of the HSC data reduction pipeline.
-    Here, after briefly introducing the HSC survey and the current status of
-    data reduction (Section \ref{sec:ssp}), we explain the design and implementation
-    of \synpipe{} (Section \ref{sec:synpipe}), then we demonstrate its usage via
+  To test the data reduction quality of the HSC--SSP (hereafter referred to
+    as the HSC survey) using synthetic objects, we have designed \synpipe{}, a \texttt{Python}-based
+    software that
+  is a flexible framework with many applications
+    that can help future developments of the HSC data reduction pipeline as well as HSC Synthetic Pipeline I.
+    Below, we briefly introduce the HSC survey and the current status of
+    data reduction (Section \ref{sec:ssp}),  explain  \synpipe{}  design and implementation (Section \ref{sec:synpipe}), and demonstrate \synpipe{} usage via
     straightforward tests (Section \ref{sec:test}) that focus on the general
@@
     (Section \ref{sec:result}).
-    Finally, we summary the work and discuss future developments in the
+ We then summarize the work and discuss future developments in 
     Section \ref{sec:summary}.
 
-    \synpipe{} code, along with basic documents and a few examples are available
+   The  \synpipe{} code, along with basic documents and a few examples, is available
     on GitHub at: \url{https://github.com/dr_guangtou/synpipe}.
+\susan{Is this URL correct?
+I got a 404 Page Not Found when I tried it.
+I think the underscore needs to be replaced with a hyphen: https://github.com/dr-guangtou/synpipe}
 %% ------------------------------------------------------------------------------------ %%
@@
     \caption{
-        Illustration of the basic procedures of \synpipe{}.
-        Grey color boxes indicate the required inputs at different stages.
-        Blue box is for the \texttt{addFakes.py} step when \synpipe{} injects simulated
-        images of synthetic objects onto single frame image.
+        Illustration of  \synpipe{} basic procedures.
+        Grey  boxes indicate the required inputs at different stages.
+        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects simulated
+        images of synthetic objects onto a single-frame image. 
         We show an example CCD image with and without synthetic objects on it
         (highlighted by green circles).
-        Red boxes are for the following image coadding and multiband measurement steps
+        Red boxes depict the subsequent image coadding and multiband measurement steps
         using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
-        We show a small piece of coadd image with synthetic objects on it.
+        We show a small piece of coadded image with synthetic objects on it.
         The figure on the right side of the middle row shows the spatial relation
         between \tract{} (outlined by the black dashed lines; each small region
-        is a \texttt{Patch}) and all the \visits{} that contribute to it
-        (each \visit{} has its own unique color; each small region has the size
-        of a CCD).
+        is a \texttt{Patch}) and all the \visits{} that contribute to it. (Each \visit{} has a  unique color; each small region is the size
+        of a CCD.)
         }
@@
 %% ------------------------------------------------------------------------------------ %%
-\section{Hyper-Suprime Cam Subaru Strategic Program}
+\section{Hyper-Suprime Cam Subaru Strategic Program (HSC Survey)}
     \label{sec:ssp}
@@
     %% Basic
-    Taking advantage of the new prime focus camera on the 8.2m Subaru telescope,
-    the ambitious HSC survey consists of three layers.
-    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broadband
+    Taking advantage of the new prime focus camera on the 8.2 m \susan{Style preference: space between value and m? Hyphenate?} Subaru telescope,
+    the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
+    The Wide layer will map a total of ${\sim}1400$ deg$^2$ of sky in five broad bands
     ($grizy$; Kawanomoto\etal in prep.).
@@
     fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
-    and employ slightly different survey strategy.
-    Please refers to the survey description paper for more detailed information
-    (Strauss\etal in prep.).
-
-    The HSC camera (\citealt{Miyazaki2012}) is made up of 112 full-depletion thick CCDs
-    for science and another 12 for guiding and focusing.
-    It provides a circular FoV with 1.5 deg diameter.
+    and employ a slightly different surveying strategy.
+     Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the HSC collaborators.
+
+    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick CCDs: 112 for science and another 12 for guiding and focusing.
+    The camera has a circular FoV with a 1.5 deg diameter.
     Each CCD contains 2048$\times$4096 pixels distributed in 4 amplifiers.
-    The pixel size equals to 0.168\asec{} on the sky.
-
-    The HSC collaboration just released the first 1.7 years of data to public (DR1;
-    \citealt{HSCDR1})\footnote{\url{https://hsc_release.mtk.nao.ac.jp}}.
-    For this work, we will focus on the Wide layer whose major scientific goals include
+    The pixel size is equal to 0.168\asec{} on the sky.
+
+   In February 2017, the HSC collaboration  released the first 1.7 years of data to the public (DR1;
+    \citealt{HSCDR1})\footnote{\url{https://hsc_release.mtk.nao.ac.jp }}.\susan{URL is incorrect. Replace underscore with hyphen and add /doc: https://hsc-release.mtk.nao.ac.jp/doc/}
+    For our work, we  focused on data from the Wide layer and the related major scientific goals, which include
     WL cosmology, galaxy evolution since $z{\sim}1$, and studies of galaxy clusters.
-    The current Wide layer includes ${\sim}108$ deg$^2$ of sky that are isolated in
+    The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
     6 different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
-    \footnote{A small AEGIS field is also observed for calibration purpose.}.
-    Most of these fields are close to the equator with the exception of the HECTOMAP
-    field.
-    In the Wide layer, the $g$ and $r$ bands have 10 mins exposure broken into 4
-    dithers\footnote{Large, ${\sim}1/3$ of FoV dither pattern is used to ensure
-    uniform coverage.}; for the rest 3 bands, 20 mins exposure time and 6 dithers are
-    used\footnote{Several 30s exposures are taken to improve the dynamic range.}.
+    \footnote{A small AEGIS field is also observed for calibration purposes.}.
+    Except for the HECTOMAP field, the regions are all close to the equator. 
+        In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into 4
+    dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
+    uniform coverage.}; for the remaining 3 bands, 20 mins of exposure time and 6 dithers are
+    used\footnote{Several 30 s exposures are taken to improve the dynamic range.}.
     The survey prioritizes the observations so that the $i$-band can have excellent
-    seeing condition to help accurate shape measurements for WL.
+    seeing conditions to help make accurate WL shape measurements.
     The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{},
     and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit. 
-    For more details of the data status, please see the data release paper
-    (\citealt{HSCDR1}).
+    \citealt{HSCDR1} provides details on the first data release and data status.
+ .
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    The HSC survey data is currently reduced by \hscpipe{} \texttt{v4.0.5}, a
+    The HSC survey data are \susan{Style preference: data plural or singular?
+Later you use plural, and that's my preference, so I've changed the verb here.} currently reduced by \hscpipe{} \texttt{v4.0.5}, a
     version of the LSST reduction pipeline (\citealt{Ivezic2008, Axelrod2010,
@@
     Since \synpipe{} is intrinsically connected to the complex data reduction
-    processes in \hscpipe{}, here we briefly introduce the main steps along with
-    a few key HSC/LSST terminologies.
+    processes in \hscpipe{},  we briefly introduce the main steps below, along with
+    a few key HSC/LSST terms.
 
@@
         \item \textbf{Single-\texttt{Visit~}Processing}:
-            Each individual exposure is called a \term{Visit} and is assigned with
+            Each individual exposure is called a \term{Visit} and is assigned 
             an even integer.
-            After initial data screening (in background, seeing, and transparency;
+            After initial data screening (in background, seeing, and transparency
             Furusawa\etal in prep.), \hscpipe{} detrends these data (subtraction
@@
             photometric calibrations.
-            \textbf{The spatially varying PSF models, photometric zeropoints, and the
+            \textbf{\synpipe{} will use the spatially varying PSF models, photometric zeropoints, and the
             World Coordinate System (WCS; \citealt{WCS1, WCS2}) corrected for optical
-            distortion will be used by \synpipe{}}.
+            distortion.}.
 
         \item \textbf{Multi-\texttt{Visit~}Processing}:
-            Then, \hscpipe{} then warps and mosaics these reduced CCD images into
-            much deeper \texttt{coadd} images while improving the astrometric and
+            After single-\texttt{Visit~} processing, \hscpipe{}  warps and mosaics the reduced CCD images into
+            much deeper \texttt{coadded} images while improving the astrometric and
             photometric calibrations via processes similar to the \"{u}ber-calibration
-            in SDSS \citep{Padmanabhan2008}.
+            in the Sloan Digital Sky Survey (SDSS) \citep{Padmanabhan2008}.
             \textbf{\synpipe{} will use these improved calibrations.}
-            \hscpipe{} organizes these \texttt{coadd} images into equi-area
-            rectangular regions that are pre-defined as an iso-latitude tessellation
-            and are referred to as \tract{}.
+            \hscpipe{} organizes these \texttt{coadded} images into equiareal \susan{or equal-area but not equi-area}
+            rectangular regions, or \tracts{}, which are predefined as iso-latitude tessellations.
             One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of
@@
             \textbf{The \tract{} and \texttt{Patch} are basic units to deal
-            with HSC \texttt{coadd} images and \synpipe{} tests.}
+            with HSC \texttt{coadded} images and \synpipe{} tests.}
 
@@
             To achieve consistent photometry across all filters, \hscpipe{} first
-            detects and deblends objects on \texttt{coadd} images in each band
+            detects and deblends objects on \texttt{coadded} images in each band
             independently (the \unforced{} measurements).
-            The above-threshold pixels for each object is referred to as
-            \texttt{footprint}.
-            Then, \hscpipe{} merges the \texttt{footprints} and flux peaks in different
-            bands, and selects a reference band for each object based on its $S/N$ in
+            The collection of above-threshold pixels for each object is referred to as
+          a  \texttt{footprint}.
+           \hscpipe{} merges the \texttt{footprints} and flux peaks in the different
+            bands and then selects a reference band for each object based on its $S/N$ in
             each band (usually it is the $i$-band).
             With the centroids, shape, and other non-amplitude parameters fixed at the
-            reference values, \hscpipe{} perform \forced{} photometry which is
+            reference values, \hscpipe{} performs \forced{} photometry, which is
             optimized to generate accurate colors.
@@
         \item \textbf{HSC Photometry}:
-            The multiband catalogs generated by \hscpipe{} contains various photometric
+            The multi-band catalogs generated by \hscpipe{} contain a variety of photometric
             information (see \citealt{HSCDR1} for details).
@@
             colors for point sources.
-            Improved based on the SDSS version (\citealt{Lupton2001, Abazajian2004}),
-            the HSC \cmodel{}{} algorithm (described in Bosch\etal in prep.) fits the
-            flux distribution of each object using a combination of a de~Vaucouleur
-            and an exponential component taking the PSF convolution into accounts.
+            Improved over the SDSS version (\citealt{Lupton2001, Abazajian2004}),
+            the HSC \cmodel{}{} algorithm (described in Bosch\etal, in prep.) fits 
+           each object's flux distribution using a combination of the de Vaucouleur
+            profile and an exponential component that takes the PSF convolution into account.
             \cmodel{} is designed to yield accurate colors for galaxies.
@@
 
-    The quality of the DR1 data have been vetted in \citet{HSCDR1} via cross-checking
+    DR1 data quality has been vetted in \citet{HSCDR1} via cross-checking
     with the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1
-    imaging survey (\citealt{Schlafly2012, Tonry2012, Magnier2013}), examining the
+    imaging survey (\citealt{Schlafly2012, Tonry2012, Magnier2013}) to examine the
     behaviors of the stellar sequence and the shape of the PSF models.
     Generally speaking, the PSF photometry is accurate to 1--2\% level, and the
-    astrometry is accurate to ${\sim}10$ and 40 mas internally and externally.
+    astrometry is accurate to ${\sim}10$ and 40 max internally and externally.
 
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsection{Basic Design of \synpipe{}}
+\subsection{ \synpipe{} Basic Design}
     \label{ssec:design}
 
-    As summarized above and described in greater detail in Bosch\etal (in prep.),
      \hscpipe{} is a complex data reduction pipeline that still faces many challenges
     and is under active development. 
-    Unlike most photometric pipeline on the market, it involves high-level reduction
-    processes that produce not only deep \texttt{coadd} images but also a series of
+    Unlike most photometric pipelines on the market, it involves high-level reduction
+    processes that produce not only deep \texttt{coadded} images but also a series of
     science-ready catalogs.
-    To faithfully test \hscpipe{} and these data products, we make sure the
+    To faithfully test \hscpipe{} and the related data products, we have designed an approach that ensures
     \synpipe{} satisfies a few basic standards:
@@
             Instead of using the fully generative approach to simulate full HSC-like
-            images from the ground up (e.g. \citealt{Chang2015}), \synpipe{} injects
-            synthetic objects to the observed image so that all the realistic
-            features of the real data (e.g. blended objects; approximity to bright
-            object, bleeding trails, other optical artifacts \etal) can be included
+            images from the ground up (e.g., \citealt{Chang2015}), \synpipe{} injects
+            synthetic objects into the observed image so that all the realistic
+            features of the real data (e.g., blended objects; proximity to bright
+            objects, bleeding trails, other optical artifacts \susan{It's redundant to use etc. (or et al, which is incorrect here) with e.g.}) can be included
             in the test.
-            The impact of these features can be important to any topic that cares
-            about the selection function and completeness of samples
-            (e.g. WL analysis; stellar mass function of galaxies).
+            The impact of these features can be important to any topic (e.g., WL analysis; stellar mass function of galaxies) that cares
+            about the selection function and completeness of samples.
             In \synpipe{}, point source is simulated using the HSC PSF model,
-            and realistic model of galaxy is modelled by the modular galaxy image
+            and a realistic galaxy model is created by the modular galaxy image
             simulation toolkit, \galsim{} (\citealt{Rowe2015})
-            \footnote{\url{https://github.com/GalSim_developers/GalSim}}.
+            \footnote{\url{https://github.com/GalSim_developers/GalSim}} \susan{I got 404 Page Not Found when I tested the URL.
+Change underscore to hyphen: https://github.com/GalSim-developers/GalSim}.
 
         \item \textbf{Authentic Data Processing}:
-            To follow the data reduction process as close as possible, we choose to
+            To follow the data reduction process as closely as possible, we choose to
             start from the single-\visit{} images instead of directly putting
-            synthetic objects on the final \texttt{coadd} images
-            (e.g. \citealt{Suchyta2016}).
-            Through this approach, subtle effects like the seeing differences among
+            synthetic objects on the final \texttt{coadded} images
+            (e.g., \citealt{Suchyta2016}).
+            Through this approach, subtle effects like seeing differences among
             \visits{} and small errors in astrometric calibration can be taken
-            into accounts.
-            All the synthetic objects will experience all the steps for detection,
-            deblending, stacking, and measurement just like any real object.
+            into account.
+            Every synthetic object will experience all the steps we would use for any real object: detection,
+            deblending, stacking, and measurement.
             This can be important for challenging tasks like the WL measurements
@@
             The only downside of this choice is that it will certainly slow down the
-            test for \texttt{coadd} images as it needs to inject synthetic object
-            to all the \visits{} that contribute to a \tract{}.
+            test for \texttt{coadded} images because in this approach we need to inject synthetic objects
+            into all the \visits{} that contribute to a \tract{}.
 
         \item \textbf{Flexible Capabilities}:
-            To make \synpipe{} useful for HSC users with various scientific goals,
-            we make sure it is flexible enough.
-            Although we provide default catalogs to generate samples of synthetic stars
+            We must make \synpipe{} flexible enough to be useful for HSC users with various scientific goals.
+            We provide default catalogs to generate samples of synthetic stars
             and galaxies with realistic magnitude and color distributions along with
-            tools to help work on data release of HSC survey, the user is allowed to
-            be creative in term of providing input catalogs and design the tests.
-            As we are speaking, \synpipe{} is being used in a wide range of
+            tools to help the user work on HSC DR1 data; however, the user is allowed to be creative in terms of providing input catalogs and designing the tests.
+             \synpipe{} is already being used in a wide range of
             scientific applications (see Section \ref{sec:summary} for details).
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsection{Implementation of \synpipe{}}
+\subsection{\synpipe{} Implementation }
     \label{ssec:flowchart}
 
-    In this section, we will go through the implementation of \synpipe{} tests in
-    details (see Fig \ref{fig:flowchart}).
+    In this section, we describe the \synpipe{} test implementation depicted in Fig \ref{fig:flowchart}.
 
@@
 
-    To start a \synpipe{} test, the user needs to provide:
+    To start a \synpipe{} test, the user needs to provide information about the data and an input catalog, as discussed below:
 
@@
 
-        \item \textbf{Information about the data}: User needs to provide the
+        \item \textbf{Information about the data} includes the
             location of the HSC images and a list of \visits{} for the
             test.
-            For test of the \texttt{coadd} images, \synpipe{} can help user identify
-            all the \visits{} that contribute to one \tract{} in certain
+            To test the \texttt{coadded} images, \synpipe{} can help the user identify
+            all the \visits{} that contribute to one \tract{} in any given
             band.
-            It also provides tools to create optional bad-pixel mask (e.g. bright
-            object, bleeding trail, \etal) for specific \tract{} to avoid
+            \synpipe{} also provides tools to create an optional bad-pixel mask (e.g., bright
+            object, bleeding trail) for a specific \tract{} so that the user can avoid
             putting synthetic objects on problematic regions.
 
-        \item \textbf{Input catalog} in \texttt{FITS} format that contain necessary
-            information like the coordinate, magnitude, and other model parameters.
-            For certain sample of synthetic objects, \synpipe{} can help randomly
-            distribute them in a selected rectangular region with desired number
+        \item \textbf{Input catalog} in  \texttt{FITS} format contains the necessary
+            information, including the coordinate, magnitude, and other model parameters.
+susan{Define FITS at first use?
+Flexible Image Transport System (FITS); I didn't change it because I didn't want to jeopardize the LaTeX coding on FITS.}
+            For any given sample of synthetic objects, \synpipe{} can help the user randomly
+            distribute the objects in a selected rectangular region with the desired 
             density.
-            If necessary, overlaps of synthetic objects can be greatly reduced
-            via setting a minimum distance between any two of them.
+            If necessary,  \synpipe{}  can reduce overlaps of synthetic objects by setting a minimum distance between any two of them.
+\susan{Unclear: does the user set the minimum distance, or does synpipe?
+If the user, change to If necessary,  the user can reduce overlaps of synthetic objects by setting a minimum distance between any two of them.
+}
             \synpipe{} can also help put synthetic objects on an evenly separated
-            coordinate grid, which is very useful for certain test
-            (e.g. Murata\etal in prep.).
+            coordinate grid, which is very useful for certain tests
+            (e.g., Murata\etal in prep.).
 
@@
         \item \textbf{Point source}:
-            \synpipe{} simply uses the PSF model from \hscpipe{} as model for
-            point source like star or QSO.
+            \synpipe{} simply uses the PSF model from \hscpipe{} as the model for
+            a point source such as a star or a quasi-stellar object (QSO).
             \hscpipe{} uses a special version of \texttt{PSFEx}
-            (\citealt{Bertin2011, Bertin2013}) to characterize the PSF as a function
-            of the position so that a PSF model can be reconstructed for any location
+            (\citealt{Bertin2011, Bertin2013}) to characterize PSF as a function
+            of the point source's position so that a PSF model can be reconstructed for any location
             on the image.
-            User only needs to provide the integrated magnitude to simulate
+           The user only needs to provide the integrated magnitude to simulate
             point sources.
@@
             \texttt{SynPipe} uses \galsim{} \texttt{v1.4} (\citealt{Rowe2015}) to
-            simulate galaxy.
+            simulate a galaxy.
             \galsim{} is an image simulation tool that has been well tested during
-            the GRavitational lEnsing Accuracy Testing 3 (GREAT3;
-            \citealt{Mandelbaum2014}).
-            Right now, \synpipe{} allows synthetic galaxy to be modelled by single
+            the GRavitational lEnsing Accuracy Testing 3 (GREAT3) challenge 
+            (\citealt{Mandelbaum2014}).
+           Currently, \synpipe{} allows a synthetic galaxy to be modeled by single
             or double components that are described by the \citet{Sersic1963}
-            profile.
+            profile. \susan{You say "right now" (which I changed to currently); do you plan to change that capability? If not, perhaps delete currently?}
             The \ser{} profile is flexible enough to describe the overall flux
-            distributions of galaxies near and far, early-type or late-type.
-            Double-\ser{} model can further simulate galaxy with more realistic
-            structural details (e.g. bulge$+$disk).
-            For each \ser{} component, user needs to provide the magnitude,
+            distributions of galaxies near and far, both early-type or late-type.
+            A Double-\ser{} model can simulate a galaxy with even more realistic
+            structural details (e.g., bulge$+$disk).
+            For each \ser{} component, the user needs to provide the magnitude,
             effective radius ($R_{\mathrm{e}}$; in unit of arcsec), \ser{} index
@@
             angle (PA).
-            External shear can also be applied to synthetic galaxy ($g_1$ and $g_2$;
+            External shear can also be applied to a synthetic galaxy ($g_1$ and $g_2$;
             see \citealt{Rowe2015} for more details).
 
-        \item \textbf{Models or real images of galaxy from the GREAT3 challenge}:
-            In stead of providing detailed model information for each galaxy, \synpipe{}
-            also allows users to choose from the parametric models or real
-            high-resolution images of galaxies used in the GREAT3 WL challenge.
+        \item \textbf{Models or real images of a galaxy from the GREAT3 challenge}:
+            In addition to providing detailed model information for each galaxy, \synpipe{}
+            also allows users to choose from parametric models or real
+            high-resolution galaxy images used in the GREAT3 WL challenge.
             The  images are from the \hst{}/ACS F814W ($I$-band) images of the galaxies
-            in the COSMOS field (e.g. \citealt{Scoville2007}).
-            These ACS exposures are 50\% completed down to $I=26.0$ mag in aperture with
+            in the COSMOS field (e.g., \citealt{Scoville2007}).
+            These Advanced Camera for Surveys (ACS) exposures are 50\% completed down to $I=26.0$ mag in aperture with
             0.5\asec{} diameter.
-            The depth and excellent resolution (0.09\asec FWHM) make it adequate to test
-            galaxies at Wide depth in HSC survey.
-            In addition to the real cutout image, the COSMOS galaxies with
-            $I_{\mathrm{Auto}}\leq25.2$ mag are modelled via method developed by
-            \citet{Lackner2012}, and the best parametric model for each of them is
-            selected between the single-\ser{} and the \ser{} bulge$+$Exponential disk
-            ones.
-            Information for these models are stored in the
+            The depth and high resolution (0.09\asec FWHM) make the exposures adequate to test
+            galaxies at Wide depth in the HSC survey.
+            In addition to the real cutout image, \synpipe{} models the COSMOS galaxies with
+            $I_{\mathrm{Auto}}\leq25.2$ mag via a method developed by
+            \citet{Lackner2012}, and selects between the single-\ser{} and the \ser{} bulge$+$Exponential disk
+            values for the best parametric model.
+            Information for these models is stored in the
             \texttt{GalSim.COSMOSCatalog()} catalogs.
-            To use them, user can provide the ID number of the COSMOS galaxies in the
-            input catalog, or simply let \synpipe{} randomly select them for you.
+            To access them, the user can provide the ID number of the COSMOS galaxies in the
+            input catalog, or simply let \synpipe{} randomly select the galaxies.
 
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsubsection{Injection of Synthetic Objects to Single-\visit{} Image}
+\subsubsection{Injection of Synthetic Objects into Single-\visit{} Image}
     \label{sssec:addFakes}
 
-    With the input catalog and information about the test data, \synpipe{} first
-    injects synthetic objects to single exposure images (step \texttt{addFakes.py};
+    With the input catalog and test data information, \synpipe{} first
+    injects synthetic objects into single-exposure images (step \texttt{addFakes.py};
     see the middle panel of Fig \ref{fig:flowchart}).
-    For each \visit{}, \synpipe{} goes through all the individual CCD images
-    that belong to it, and decides which synthetic objects from the input catalog need
+     \synpipe{} goes through all the individual CCD images
+    that belong to each \visit{} and decides which synthetic objects from the input catalog need
     to be injected.
-    \synpipe{} makes use of the \textit{initial astrometric calibration} of each single
+    \synpipe{} uses the \textit{initial astrometric calibration} of each single
     \visit{} to convert the input coordinates into locations on the CCD image.
-    Using the available models, \synpipe{} will reconstruct the PSF at the position of
+    Using the available models, \synpipe{} reconstructs the PSF at the position of
     each injected object.
     To convert the input magnitudes of synthetic objects into fluxes on the image,
-    \synpipe{} also uses the photometric zeropoint from single-\visit{}
+    \synpipe{} also uses the photometric zero point from the single-\visit{}
     calibration.
@@
     with appropriate size and correct total flux.
-    For galaxy described by single- or double-\ser{} models, \synpipe{} passes the input
+    For a galaxy described by single- or double-\ser{} models, \synpipe{} passes the input
     \ser{} index and effective radius to the \galsim{}\texttt{.Sersic} function to
     create a \ser{} component.
-    After stretching and rotating it to expected axis ratio and position angle
-    via the \texttt{shear} and \texttt{rotate} methods, \synpipe{} assigns correct flux
+    After stretching and rotating the galaxy to the expected axis ratio and position angle
+    via the \texttt{shear} and \texttt{rotate} methods, \synpipe{} assigns the correct flux
     to this component.
-    For double-\ser{} model, \galsim{}\texttt{.Add} method is used to combine the two
-    \ser{} components together.
-    For parametric models from the GREAT3 catalog, \synpipe{} utilizes the
-    \texttt{COSMOSCatalog.makeGalaxy} method to generate corresponding model,
-    and the \galsim{}\texttt{.RealGalaxy} method is used for the case of real
-    high-resolution image.
+    For a double-\ser{} model, \synpipe{} uses the \galsim{}\texttt{.Add} method to combine the two
+    \ser{} components.
+    For parametric models from the GREAT3 catalog, \synpipe{} uses the
+    \texttt{COSMOSCatalog.makeGalaxy} method to generate a corresponding model; in the case of a real high-resolution image, \synpipe{} uses the \galsim{}\texttt{.RealGalaxy} method.
     If necessary, additional shear ($g_1$ and $g_2$) can be applied to the model at this
@@
     using \galsim{}\texttt{.Convolve}.
-    After this, \synpipe{} uses \galsim{}\texttt{.drawImage} method to create the image
+    After this, \synpipe{} uses the \galsim{}\texttt{.drawImage} method to create the image
     of the simulated galaxy.
-    Component with high \ser{} index ($n_{\mathrm{Ser}} > 4$) often requires large image
-    size to cover most of its total flux, so \synpipe{} allows user to truncate model
-    at certain radius (N$\times R_{\mathrm{e}}$).
-    It will also give warning information when component with $n_{\mathrm{Ser}} > 6$ is
-    encountered.
-    Such model takes much longer time to achieve accurate PSF convolution, and is usually
-    not realistic galaxy model.
-
-    \synpipe{} then shifts the image of synthetic object according to is location on the
-    CCD on a pixel-by-pixel basis; it also crops the images when necessary.
-    Afterwards, \synpipe{} adds appropriate noise to the image based on the pixels it
-    covers and the calibration information of the detector, and create a variance image
+    A component with a high \ser{} index ($n_{\mathrm{Ser}} > 4$) often requires a large image
+    size to cover most of its total flux, so \synpipe{} allows the user to truncate the model
+    at a given radius (N$\times R_{\mathrm{e}}$).
+    \synpipe{} will also give warning information when a component with $n_{\mathrm{Ser}} > 6$ is
+    encountered because it takes much longer to achieve accurate PSF convolution in such a model; and the result is, therefore, 
+    not a realistic galaxy model.
+
+ After \synpipe{} creates the image
+    of the simulated galaxy, it then shifts the image according to is location on the
+    CCD on a pixel-by-pixel basis; \synpipe{} also crops the images when necessary.
+    When that task is complete, \synpipe{} adds appropriate noise to the image based on the pixels it
+    covers and the calibration information of the detector, and creates a variance image
     that reflects the influence of the synthetic object.
-    Since each HSC CCD consists of four amplifiers with different characteristics,
-    \synpipe{} carefully creates corresponding gain map to provide accurate noise level.
-    Finally, \synpipe{} adds the noise-added image and the variance map to the original
+    Since each HSC CCD consists of 4 \susan{Style preference: spell out numbers?
+Earlier you've used figures, so changed four to 4 here.
+(My preference would be to spell out if fewer than 10.)} amplifiers, each with different characteristics,
+    \synpipe{} carefully creates a corresponding gain map to provide taccurate noise level.
+    In the final step, \synpipe{} adds the noise-added image and the variance map to the original
     CCD data while also adding a new \texttt{FAKE} mask bit to the mask plane.
-    On the middle panel of Fig \ref{fig:flowchart}, we demonstrate the result of the
+   The middle panel of Fig \ref{fig:flowchart} depicts the result of the
     \texttt{addFakes.py} step by showing an example CCD image before and after the
@@
 
-    These newly generated sing-\visits{} images have the same format and data
-    structure of the real HSC data, therefore \synpipe{} can directly feed them
-    to the rest steps of \hscpipe{}.
+    The newly generated single-\visit{} images have the same format and data
+    structure as the real HSC data; therefore, \synpipe{} can directly feed them
+    to the other \hscpipe{} steps.
     The \texttt{stack.py} step takes the improved astrometric and photometric
-    calibrations for each \visit{} from the original reduction and create
-    \texttt{coadd} images with synthetic objects on them.
-    Then the \texttt{multiBand.py} step will process these \texttt{coadd} images and
-    provide standard mulit-band measurements in FITS catalogs that are grouped by
+    calibrations for each \visit{} from the original reduction and creates
+    \texttt{coadded} images with synthetic objects on them.
+    Then the \texttt{multiBand.py} step processes these \texttt{coadded} images and
+    provides standard multi-band measurements in FITS catalogs that are grouped by
     \texttt{Patch} ID.
 
-    Using the infrastructures provided by \hscpipe{}, the above processes can be
-    easily parallelized, and the overall efficiency of \synpipe{} is similar to the
+    Using the infrastructures provided by \hscpipe{}, the user can easily perform the above processes in parallel, and the overall efficiency of \synpipe{} is similar to the
     real data reduction process.
-    They also generate the same amount of images and catalog data with the original
-    one.
+    The processes also generate the same amount of images and catalog data as the original
+    one \susan{Unclear what "one" refers to: original data reduction process?}.
 
@@
     radius that is specified by the user, and merge all the \unforced{} and
-    \forced{} measurements from all the \texttt{Patches} together.
-    Unmatched object from the input catalog is also passed to the result catalog with
-    special label.
-    In case of multiple matches, user can choose between only returning the nearest
-    one or returning all objects within the matching radius (the nearest one is
-    labeled).
+    \forced{} measurements from all the \texttt{Patches}.
+    Each unmatched object from the input catalog is also passed to the results catalog with a unique label.
+    In case of multiple matches, the user can choose between returning only the closest match or returning all objects within the matching radius (the nearest one is
+    labeled as such).
+    \susan{Susan stopped editing here.}
 %% ------------------------------------------------------------------------------------ %%
@@
 %% Fig: Compare with the behaviours of the Kron photometry for galaxies
-\begin{figure*}
-    \begin{center}
-        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_kron}
-    \end{center}
-    \caption{
-        Basic performance of the Kron photometry for synthetic galaxies.
-        \textbf{Left} shows the accuracy in $i$-band.
-        magnitude. The format is identical to Fig \ref{fig:galaxy_mag}.
-        \textbf{Right} shows the accuracy of the $(g-i)$ color using
-        Kron photometry.
-        Other formats are identical to Fig \ref{fig:cmodel_color}.
-        }
-    \label{fig:galaxy_kron}
-\end{figure*}
+%\begin{figure*}
+%    \begin{center}
+%        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_kron}
+%    \end{center}
+%    \caption{
+%        Basic performance of the Kron photometry for synthetic galaxies.
+%        \textbf{Left} shows the accuracy in $i$-band.
+%        magnitude. The format is identical to Fig \ref{fig:galaxy_mag}.
+%        \textbf{Right} shows the accuracy of the $(g-i)$ color using
+%        Kron photometry.
+%        Other formats are identical to Fig \ref{fig:cmodel_color}.
+%        }
+%    \label{fig:galaxy_kron}
+%\end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsection{Comparing to Kron photometry}
-
-    \plan{Uses $i$-band as example to briefly discuss Kron photometry}
-
-    \plan{Although magnitude for galaxies is Ok, the color becomes worse}
+%\subsection{Comparing to Kron photometry}
+
+%    \plan{Uses $i$-band as example to briefly discuss Kron photometry}
+
+%    \plan{Although magnitude for galaxies is Ok, the color becomes worse}
 
@@
 
-    In SDSS, the structural parameters
-
-    The CModel galaxy fitting algorithm utilizes a Bayesian prior on radius and ellipticity, largely as a way to regularize fits to low S/N and/or poorly-resolved galaxies.
-When combining this with the likelihood to form the posterior probability (which is then
-    \plan{Explain why the current \cmodel{}{} algorithm has problem with measuring
-          the size and shape of galaxies}
-
-    \plan{Briefly showcase the problem, and how small change of \hscpipe{}
-          configuration can improve the situation}
+    In SDSS, the structural parameters like size and shape from \cmodel{} are often 
+    used to study the evolution galaxies. 
+    Although the \cmodel{} in \hscpipe{} follows very similar algorithm, its primary 
+    goal now is to provide accurate and consistent magnitude and color in all five 
+    HSC filters for a vast majority of faint, small galaxies.  
+    To improve the stability of \cmodel{} for these low \s2n{} and barely-resolved 
+    galaxies, it utilizes Bayesian priors on radius and axis ratio that strongly 
+    favour these galaxies. 
+    However, the current implementation of these priors has a flaw that leads to 
+    severely underestimated size and overestimated axis ratio for most galaxies.
+
+    In Fig \ref{fig:galaxy_ba}, we demonstrate this issue using the difference between 
+    the \cmodel{} axis ratio and the input values as example.
+    Here, $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ is a combination of the 
+    axis ratios estimated by the exponential and de~Vaucouleurs models weighted by 
+    their flux ratio.
+
+    During the investigation, we notice that one of the problem relates to the 
+    \texttt{usePixelWeight} configuration of \cmodel{} that decides whether to 
+    use per-pixel variances as weights in the nonlinear fit. 
+    By default, \hscpipe{} chooses \texttt{usePixelWeight}$=$\texttt{False}. 
+    As one can see, this leads to significantly overestimated axis ratio for almost 
+    all galaxies with $i_{\mathrm{Input}}>21.5$ mag\footnote{It also leads to 
+    underestimated half-light radius for these galaxies.}.
+    At the same time, we also repeat the \synpipe{} run for galaxies with 
+    \texttt{usePixelWeight}$=$\texttt{True}, and this change clearly mitigates
+    this problem. 
+    Now $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ can provide unbiased estimation 
+    of axis ratio for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
+
+    For the current HSC data release, we warn the users against using the \cmodel{} 
+    size and shape to study galaxy with $i_{\mathrm{Input}}>21.5$. 
+    At the same time, \synpipe{} will try to help \hscpipe{} improve the details 
+    of the \cmodel{} so that it can provide more useful structural information without
+    hurting its photometric performance.
+
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %%
-
 \begin{ack}

### 2017-04-14 draft/ms_v2.tex
Minor update; change the version number
Song: Fix abstract

--- 2017-04-14 draft/ms_v1.tex
@@
 % Version 1; First draft by SH
+% Version 2; Main text is finished; with edits from Susan Foster
 
@@
 
-   The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band
-    survey using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
-      At SSP's imaging depth \susan{quantify?}, it is challenging to achieve accurate,
-    unbiased, and consistent photometry across all five bands. To improve data processing and achieve accurate photometric measurements, we have developed
-   \synpipe{}, a \texttt{Python}-based, flexible framework
-    that interfaces with the HSC data reduction pipeline (\hscpipe{}) to process data from the first public HSC--SSP data release.
-\susan{I expected to see something in the abstract that clarifies why this is Pipeline I; does this suggestion accomplish that?} We test  \synpipe{}
-    performance by injecting synthetic objects into single-\texttt{visit} HSC images.
-    We use coadded images in two Wide layer \tracts{} with representative
-    seeing conditions to demonstrate  \synpipe{} implementation and to examine  \texttt{hscpipe}'s 
-    general photometric performance.
+    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey 
+    using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
+    As SSP reaches to detection limit of $i>26.0$ mag in the Wide field, it is 
+    challenging to achieve accurate, unbiased, and consistent photometry across all 
+    five bands.
+    To improve data processing and achieve accurate photometric measurements, we have 
+    developed \synpipe{}, a \texttt{Python}-based, flexible framework that interfaces 
+    with the HSC data reduction pipeline (\hscpipe{}) to process data from the first 
+    public HSC--SSP data release. 
+    In the first paper of this series, we explain the design and implementation of 
+    \synpipe{}, and use coadd images in two Wide layer \tracts{} with representative 
+    seeing conditions to examine the photometric performance of \hscpipe{}.
     We find that uncertainties of HSC \forced{} PSF photometry for stars typically
@@
     For synthetic galaxies based on a single-\ser{} model, uncertainties of the
-    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag to
-    0.20 mag at $i{\sim} 25.2$ mag.
-    Over the color and magnitude ranges used in the  \synpipe{} tests, we find that both 
-    \forced{} PSF and \cmodel{} photometry provide unbiased color estimates that 
-    are robust in different seeing conditions.
+    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag 
+    to 0.20 mag at $i{\sim} 25.2$ mag.
+    Over the color and magnitude ranges used in these \synpipe{} tests, we find that 
+    both \forced{} PSF and \cmodel{} photometry provide unbiased color estimates 
+    that are robust in different seeing conditions.
     We also notice a few issues in the current \hscpipe{} that are worth keeping

### 2017-04-15 draft/ms_v2.tex
Song: Organize Susan's edit

@@
 \def\forced{\texttt{forced}}
+\def\coadd{\texttt{coadd}}
 \def\unforced{\texttt{unforced}}
@@
     In the first paper of this series, we explain the design and implementation of 
-    \synpipe{}, and use coadd images in two Wide layer \tracts{} with representative 
+    \synpipe{}, and use \coadd{} images in two Wide layer \tracts{} with representative 
     seeing conditions to examine the photometric performance of \hscpipe{}.
@@
     modern astrophysics and cosmology over the past decade.
-    They also have a bright future on many current and planned ambitious projects, such as the Large Synoptic Survey Telescope
+    They also have a bright future on many current and planned ambitious projects, 
+    such as the Large Synoptic Survey Telescope
     (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
@@
     uses the Hyper Suprime-Cam (HSC; \citealt{Miyazaki2012}) on the prime focus of
-    the Subaru telescope, is the most efficient in terms of etendue.
+    the Subaru telescope, is the most efficient in terms of 
+    etendue\footnote{The collecting area multiplied by the field of view.}.
     Together, these surveys will greatly help us test cosmological models, trace the
@@
     Before we can tackle any outstanding scientific questions, we must first learn
-    how to handle the huge \susan{quantify? Or is "huge" a common descriptor for data in your field?} amount of data generated by these projects as well as achieve
+    how to handle the huge amount of data\footnote{Right now, SSP has accumulated 
+    ${\sim}300$ TB of data products.} generated by these projects as well as achieve
     accurate photometric measurements of different types of objects.
     Data handling becomes increasingly challenging in the age of modern imaging
-    surveys, in part due to variations and effects related to the cameras' charge-coupled devices (CCDs).
-    The cameras are often made up of multiple
-  CCDs, each with slightly different characteristics, and have
-    large fields-of-view (FoV) over not perfectly flat focus planes.
+    surveys, in part due to variations and effects related to the cameras' 
+    charge-coupled devices (CCDs).
+    The cameras are often made up of multiple CCDs, each with slightly different 
+    characteristics, and have large fields-of-view (FoV) over not perfectly flat 
+    focus planes.
     During observation, the seeing and background conditions always show spatial
     and temporal variations across the FoV.
-    The full-depletion, thick CCDs selected for the cameras enable long exposure times
-    and excellent sensitivity in the red-end, but they often have the so-called
-    ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that bright
-    stars appear larger than they are.
+    The full-depletion, thick CCDs selected for the cameras enable long exposure 
+    times and excellent sensitivity in the red-end, but they often suffer from the 
+    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that 
+    brighter stars appear larger than they are.
     These variations and effects make accurate astrometric and photometric calibration,
@@
     difficult (e.g., \citealt{Schlafly2012}).
-    The multi-epoch, multi-band nature of the surveys also complicate
-    data reduction because the scientist must pay special attention to
-    image stacking, multi-band object detection, and measurement processes.
-     Furthermore, as ongoing surveys reach to increasingly deeper surface brightness levels,
-    the number of objects, especially faint objects, in a unit area, becomes much higher.
+    The multi-epoch, multi-band nature of the surveys also complicate data reduction 
+    because the scientist must pay special attention to image stacking, multi-band 
+    object detection, and measurement processes.
+    Furthermore, as ongoing surveys reach to increasingly deeper detection limit 
+    (e.g SSP Wide reaches to $5\ \sigma$ detection limit of point source of 
+    ${\sim}26.4$ mag), the number of objects in a unit area, especially faint objects,
+    becomes much higher. 
     In addition, it is much more common to observe objects that overlap each other at
     different levels (a phenomenon often referred to as ``blended'').
-    These modern imaging survey challenges call for photometric measurement methods that are more powerful and precise than those
-    used in previous, shallower surveys.
+    These modern imaging survey challenges call for photometric measurement methods 
+    that are more powerful and precise than those used in previous, shallower surveys.
 
@@
     following its evolution.
-    However, WL measurements critically depend on the ability to model PSF and measure the
-    shape of background galaxies with high precision (e.g., \citealt{Mandelbaum2015}).
+    However, WL measurements critically depend on the ability to model PSF and measure 
+    the shape of background galaxies with high precision 
+    (e.g., \citealt{Mandelbaum2015}).
     The photometric redshift measurement (e.g., \citealt{Benitez2000, Bolzonella2000,
@@
     (e.g., \citealt{Steidel1996}).
-    However, both of those methods are based on accurate multi-band photometric measurements.
-    There are many other examples, but these are sufficient to demonstrate that we need to develop new frameworks
-    to oversee the data reduction process of modern imaging surveys.
+    However, both of those methods are based on accurate multi-band photometric 
+    measurements.
+    There are many other examples, but these are sufficient to demonstrate that we 
+    need to develop new frameworks to oversee the data reduction process of modern 
+    imaging surveys.
     Several tools with similar goals have been developed (e.g., \citealt{Chang2015,
     Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}). 
-\susan{Clarify why you mention the DES tools; e.g., does synpipe build on these tools?
-Do they demonstrate the effectiveness of developing new frameworks?
-Why are they insufficient for the HSC survey tasks?}
+    As for the HSC--SSP (hereafter referred to as the HSC survey), the higher quality 
+    images and more complex \hscpipe{} also require more carefully designed tool to 
+    test them.
 
     %% Organization
-  To test the data reduction quality of the HSC--SSP (hereafter referred to
-    as the HSC survey) using synthetic objects, we have designed \synpipe{}, a \texttt{Python}-based
-    software that
-  is a flexible framework with many applications
-    that can help future developments of the HSC data reduction pipeline as well as HSC Synthetic Pipeline I.
-    Below, we briefly introduce the HSC survey and the current status of
-    data reduction (Section \ref{sec:ssp}),  explain  \synpipe{}  design and implementation (Section \ref{sec:synpipe}), and demonstrate \synpipe{} usage via
-    straightforward tests (Section \ref{sec:test}) that focus on the general
-    photometric quality for both synthetic stars and galaxies
-    (Section \ref{sec:result}).
+    Here, we present \synpipe{}, a \texttt{Python}-based software that is a flexible 
+    framework with many applications that can help future developments of the HSC data 
+    reduction pipeline (\hscpipe{}).
+    Below, we briefly introduce the HSC survey and the current status of data 
+    reduction (Section \ref{sec:ssp}), explain \synpipe{} design and implementation 
+    (Section \ref{sec:synpipe}), and demonstrate \synpipe{} usage via straightforward 
+    tests (Section \ref{sec:test}) that focus on the general photometric quality for 
+    both synthetic stars and galaxies (Section \ref{sec:result}).
     We then summarize the work and discuss future developments in 
@@
     The \synpipe{} code, along with basic documents and a few examples, is available
-    on GitHub at: \url{https://github.com/dr_guangtou/synpipe}.
-\susan{Is this URL correct?
-I got a 404 Page Not Found when I tried it.
-I think the underscore needs to be replaced with a hyphen: https://github.com/dr-guangtou/synpipe}
+    on GitHub at: \texttt{https://github.com/dr-guangtou/synpipe}.
 %% ------------------------------------------------------------------------------------ %%
@@
         Grey boxes indicate the required inputs at different stages.
-        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects simulated
-        images of synthetic objects onto a single-frame image. 
+        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
+        simulated images of synthetic objects onto a single-frame image. 
         We show an example CCD image with and without synthetic objects on it
@@
         using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
-        We show a small piece of coadded image with synthetic objects on it.
+        We show a small piece of \coadd{} image with synthetic objects on it.
         The figure on the right side of the middle row shows the spatial relation
         between \tract{} (outlined by the black dashed lines; each small region
-        is a \texttt{Patch}) and all the \visits{} that contribute to it. (Each \visit{} has a  unique color; each small region is the size
-        of a CCD.)
+        is a \texttt{Patch}) and all the \visits{} that contribute to it. 
+        (Each \visit{} has a  unique color; each small region is the size of a CCD.)
         }
@@
     %% Basic
-    Taking advantage of the new prime focus camera on the 8.2 m \susan{Style preference: space between value and m? Hyphenate?} Subaru telescope,
+    Taking advantage of the new prime focus camera on the 8.2--m Subaru telescope,
     the ambitious HSC survey consists of three layers: Wide, Deep, and UltraDeep.
@@
     and employ a slightly different surveying strategy.
-     Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the HSC collaborators.
-
-    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick CCDs: 112 for science and another 12 for guiding and focusing.
+    Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the 
+    HSC collaborators.
+
+    The HSC camera (\citealt{Miyazaki2012}) is made up of 124 full-depletion thick 
+    CCDs: 112 for science and another 12 for guiding and focusing.
     The camera has a circular FoV with a 1.5 deg diameter.
@@
 
-   In February 2017, the HSC collaboration  released the first 1.7 years of data to the public (DR1;
-    \citealt{HSCDR1})\footnote{\url{https://hsc_release.mtk.nao.ac.jp }}.\susan{URL is incorrect. Replace underscore with hyphen and add /doc: https://hsc-release.mtk.nao.ac.jp/doc/}
-    For our work, we  focused on data from the Wide layer and the related major scientific goals, which include
-    WL cosmology, galaxy evolution since $z{\sim}1$, and studies of galaxy clusters.
+    In February 2017, the HSC collaboration released the first 1.7 years of data to 
+    the public (DR1; 
+    \citealt{HSCDR1})\footnote{\texttt{https://hsc-release.mtk.nao.ac.jp }}.
+    For our work, we focused on data from the Wide layer as they relate to key 
+    scientific goals of HSC survey, which include WL cosmology, galaxy evolution 
+    since $z{\sim}1$, and studies of galaxy clusters.
     The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
@@
     dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
-    uniform coverage.}; for the remaining 3 bands, 20 mins of exposure time and 6 dithers are
-    used\footnote{Several 30 s exposures are taken to improve the dynamic range.}.
+    uniform coverage.}; for the remaining 3 bands, 20 mins of exposure time and 6 
+    dithers are used\footnote{Several 30 s exposures are taken to improve the 
+    dynamic range.}.
     The survey prioritizes the observations so that the $i$-band can have excellent
@@
     \citealt{HSCDR1} provides details on the first data release and data status.
- .
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    The HSC survey data are \susan{Style preference: data plural or singular?
-Later you use plural, and that's my preference, so I've changed the verb here.} currently reduced by \hscpipe{} \texttt{v4.0.5}, a
+    The HSC survey data are currently reduced by \hscpipe{} \texttt{v4.0.5}, a
     version of the LSST reduction pipeline (\citealt{Ivezic2008, Axelrod2010,
@@
             photometric calibrations.
-            \textbf{\synpipe{} will use the spatially varying PSF models, photometric zeropoints, and the
-            World Coordinate System (WCS; \citealt{WCS1, WCS2}) corrected for optical
-            distortion.}.
-
-        \item \textbf{Multi-\texttt{Visit~}Processing}:
-            After single-\texttt{Visit~} processing, \hscpipe{}  warps and mosaics the reduced CCD images into
-            much deeper \texttt{coadded} images while improving the astrometric and
-            photometric calibrations via processes similar to the \"{u}ber-calibration
-            in the Sloan Digital Sky Survey (SDSS) \citep{Padmanabhan2008}.
+            \textbf{\synpipe{} will use the spatially varying PSF models, photometric 
+            zeropoints, and the World Coordinate System (WCS; \citealt{WCS1, WCS2}) 
+            corrected for optical distortion.}.
+
+        \item \textbf{Multi-\visit{} Processing}:
+            After single-\visit{} processing, \hscpipe{} warps and mosaics the 
+            reduced CCD images into much deeper \coadd{} images while improving
+            the astrometric and photometric calibrations via processes similar to 
+            the \"{u}ber-calibration in the Sloan Digital Sky Survey (SDSS) 
+            \citep{Padmanabhan2008}.
             \textbf{\synpipe{} will use these improved calibrations.}
-            \hscpipe{} organizes these \texttt{coadded} images into equiareal \susan{or equal-area but not equi-area}
-            rectangular regions, or \tracts{}, which are predefined as iso-latitude tessellations.
-            One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of
-            sky, and adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
+            \hscpipe{} organizes these \coadd{} images into equiareal rectangular 
+            regions, or \tracts{}, which are predefined as iso-latitude tessellations.
+            One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of sky, and 
+            adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
             Each \tract{} is further divided into $9\times9$ \texttt{Patches}.
@@
             \textbf{The \tract{} and \texttt{Patch} are basic units to deal
-            with HSC \texttt{coadded} images and \synpipe{} tests.}
+            with HSC \coadd{} images and \synpipe{} tests.}
 
@@
             To achieve consistent photometry across all filters, \hscpipe{} first
-            detects and deblends objects on \texttt{coadded} images in each band
+            detects and deblends objects on \coadd{} images in each band
             independently (the \unforced{} measurements).
@@
             \hscpipe{} merges the \texttt{footprints} and flux peaks in the different
-            bands and then selects a reference band for each object based on its $S/N$ in
-            each band (usually it is the $i$-band).
+            bands and then selects a reference band for each object based on its $S/N$ 
+            in each band (usually it is the $i$-band).
             With the centroids, shape, and other non-amplitude parameters fixed at the
@@
         \item \textbf{HSC Photometry}:
-            The multi-band catalogs generated by \hscpipe{} contain a variety of photometric
-            information (see \citealt{HSCDR1} for details).
+            The multi-band catalogs generated by \hscpipe{} contain a variety of 
+            photometric information (see \citealt{HSCDR1} for details).
             \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{}
@@
             Improved over the SDSS version (\citealt{Lupton2001, Abazajian2004}),
-            the HSC \cmodel{}{} algorithm (described in Bosch\etal, in prep.) fits 
+            the HSC \cmodel{} algorithm (described in Bosch\etal, in prep.) fits 
             each object's flux distribution using a combination of the de Vaucouleur
-            profile and an exponential component that takes the PSF convolution into account.
+            profile and an exponential component that takes the PSF convolution 
+            into account.
             \cmodel{} is designed to yield accurate colors for galaxies.
-            In addition, the star--galaxy separation task is performed based on the
-            difference between the \texttt{psf} and \cmodel{}{} magnitudes.
+            In addition, the star--galaxy classification task is performed based on 
+            the difference between the \texttt{psf} and \cmodel{}{} magnitudes.
 
@@
     Unlike most photometric pipelines on the market, it involves high-level reduction
-    processes that produce not only deep \texttt{coadded} images but also a series of
+    processes that produce not only deep \coadd{} images but also a series of
     science-ready catalogs.
-    To faithfully test \hscpipe{} and the related data products, we have designed an approach that ensures
-    \synpipe{} satisfies a few basic standards:
+    To faithfully test \hscpipe{} and the related data products, we have designed an 
+    approach that ensures \synpipe{} satisfies a few basic standards:
 
@@
             features of the real data (e.g., blended objects; proximity to bright
-            objects, bleeding trails, other optical artifacts \susan{It's redundant to use etc. (or et al, which is incorrect here) with e.g.}) can be included
-            in the test.
-            The impact of these features can be important to any topic (e.g., WL analysis; stellar mass function of galaxies) that cares
-            about the selection function and completeness of samples.
+            objects, bleeding trails, other optical artifacts can be included in the 
+            test.
+            The impact of these features can be important to any topic (e.g., WL 
+            analysis; stellar mass function of galaxies) that cares about the selection 
+            function and completeness of samples.
             In \synpipe{}, point source is simulated using the HSC PSF model,
@@
             simulation toolkit, \galsim{} (\citealt{Rowe2015})
-            \footnote{\url{https://github.com/GalSim_developers/GalSim}} \susan{I got 404 Page Not Found when I tested the URL.
-Change underscore to hyphen: https://github.com/GalSim-developers/GalSim}.
+            \footnote{\texttt{https://github.com/GalSim-developers/GalSim}}.
 
         \item \textbf{Authentic Data Processing}:
-            To follow the data reduction process as closely as possible, we choose to
-            start from the single-\visit{} images instead of directly putting
-            synthetic objects on the final \texttt{coadded} images
-            (e.g., \citealt{Suchyta2016}).
+            To follow the data reduction process as realistic as possible, we choose to
+            start from the single-\visit{} images instead of directly putting synthetic 
+            objects on the final \coadd{} images (e.g., \citealt{Suchyta2016}).
             Through this approach, subtle effects like seeing differences among
@@
             into account.
-            Every synthetic object will experience all the steps we would use for any real object: detection,
-            deblending, stacking, and measurement.
+            Every synthetic object will experience all the steps we would use for any 
+            real object: detection, deblending, stacking, and measurement.
             This can be important for challenging tasks like the WL measurements
@@
             The only downside of this choice is that it will certainly slow down the
-            test for \texttt{coadded} images because in this approach we need to inject synthetic objects
-            into all the \visits{} that contribute to a \tract{}.
+            test for \coadd{} images because in this approach we need to inject 
+            synthetic objects into all the \visits{} that contribute to a \tract{}.
 
         \item \textbf{Flexible Capabilities}:
-            We must make \synpipe{} flexible enough to be useful for HSC users with various scientific goals.
+            We must make \synpipe{} flexible enough to be useful for HSC users with 
+            various scientific goals.
             We provide default catalogs to generate samples of synthetic stars
             and galaxies with realistic magnitude and color distributions along with
-            tools to help the user work on HSC DR1 data; however, the user is allowed to be creative in terms of providing input catalogs and designing the tests.
+            tools to help the user work on HSC DR1 data; however, the user is allowed 
+            to be creative in terms of providing input catalogs and designing the tests.
             \synpipe{} is already being used in a wide range of
@@
 
-    In this section, we describe the \synpipe{} test implementation depicted in Fig \ref{fig:flowchart}.
+    In this section, we describe the \synpipe{} test implementation depicted in 
+    Fig \ref{fig:flowchart}.
 
@@
 
-    To start a \synpipe{} test, the user needs to provide information about the data and an input catalog, as discussed below:
+    To start a \synpipe{} test, the user needs to provide information about the data 
+    and an input catalog, as discussed below:
 
@@
 
-        \item \textbf{Information about the data} includes the
-            location of the HSC images and a list of \visits{} for the
-            test.
-            To test the \texttt{coadded} images, \synpipe{} can help the user identify
+        \item \textbf{Information about the data}
+            includes the location of the HSC images and a list of \visits{} for 
+            the test.
+            To test the \coadd{} images, \synpipe{} can help the user identify
             all the \visits{} that contribute to one \tract{} in any given
             band.
-            \synpipe{} also provides tools to create an optional bad-pixel mask (e.g., bright
-            object, bleeding trail) for a specific \tract{} so that the user can avoid
-            putting synthetic objects on problematic regions.
-
-        \item \textbf{Input catalog} in  \texttt{FITS} format contains the necessary
-            information, including the coordinate, magnitude, and other model parameters.
-susan{Define FITS at first use?
-Flexible Image Transport System (FITS); I didn't change it because I didn't want to jeopardize the LaTeX coding on FITS.}
-            For any given sample of synthetic objects, \synpipe{} can help the user randomly
-            distribute the objects in a selected rectangular region with the desired 
-            density.
-            If necessary,  \synpipe{}  can reduce overlaps of synthetic objects by setting a minimum distance between any two of them.
-\susan{Unclear: does the user set the minimum distance, or does synpipe?
-If the user, change to If necessary,  the user can reduce overlaps of synthetic objects by setting a minimum distance between any two of them.
-}
+            \synpipe{} also provides tools to create an optional bad-pixel mask 
+            (e.g., bright object, bleeding trail) for a specific \tract{} so that 
+            the user can avoid putting synthetic objects on problematic regions.
+
+        \item \textbf{Input catalog} in \texttt{FITS} (Flexible Image Transport System)
+            format contains the necessary information, including the coordinate, 
+            magnitude, and other model parameters.  
+            For any given sample of synthetic objects, \synpipe{} can help the user 
+            randomly distribute the objects in a selected rectangular region with the
+            desired density.
+            If necessary, the user can reduce overlaps of synthetic objects by setting 
+            a minimum distance between any two of them. 
             \synpipe{} can also help put synthetic objects on an evenly separated
@@
             (\citealt{Bertin2011, Bertin2013}) to characterize PSF as a function
-            of the point source's position so that a PSF model can be reconstructed for any location
-            on the image.
+            of the point source's position so that a PSF model can be reconstructed 
+            for any location on the image.
             The user only needs to provide the integrated magnitude to simulate
@@
             or double components that are described by the \citet{Sersic1963}
-            profile. \susan{You say "right now" (which I changed to currently); do you plan to change that capability? If not, perhaps delete currently?}
+            profile\footnote{More flexible model choices will be added later.}.
             The \ser{} profile is flexible enough to describe the overall flux
@@
             angle (PA).
-            External shear can also be applied to a synthetic galaxy ($g_1$ and $g_2$;
-            see \citealt{Rowe2015} for more details).
+            External shear can also be applied to a synthetic galaxy ($g_1$ and 
+            $g_2$; see \citealt{Rowe2015} for more details).
 
         \item \textbf{Models or real images of a galaxy from the GREAT3 challenge}:
-            In addition to providing detailed model information for each galaxy, \synpipe{}
-            also allows users to choose from parametric models or real
+            In addition to providing detailed model information for each galaxy, 
+            \synpipe{} also allows users to choose from parametric models or real
             high-resolution galaxy images used in the GREAT3 WL challenge.
@@
             in the COSMOS field (e.g., \citealt{Scoville2007}).
-            These Advanced Camera for Surveys (ACS) exposures are 50\% completed down to $I=26.0$ mag in aperture with
-            0.5\asec{} diameter.
-            The depth and high resolution (0.09\asec FWHM) make the exposures adequate to test
-            galaxies at Wide depth in the HSC survey.
-            In addition to the real cutout image, \synpipe{} models the COSMOS galaxies with
-            $I_{\mathrm{Auto}}\leq25.2$ mag via a method developed by
-            \citet{Lackner2012}, and selects between the single-\ser{} and the \ser{} bulge$+$Exponential disk
-            values for the best parametric model.
+            These Advanced Camera for Surveys (ACS) exposures are 50\% completed down 
+            to $I=26.0$ mag in aperture with 0.5\asec{} diameter.
+            The depth and high resolution (0.09\asec FWHM) make the exposures adequate 
+            to test galaxies at Wide depth in the HSC survey.
+            In addition to the real cutout image, \synpipe{} models the COSMOS galaxies 
+            with $I_{\mathrm{Auto}}\leq25.2$ mag via a method developed by
+            \citet{Lackner2012}, and selects between the single-\ser{} and the \ser{} 
+            bulge$+$Exponential disk values for the best parametric model.
             Information for these models is stored in the 
             \texttt{GalSim.COSMOSCatalog()} catalogs.
-            To access them, the user can provide the ID number of the COSMOS galaxies in the
-            input catalog, or simply let \synpipe{} randomly select the galaxies.
+            To access them, the user can provide the ID number of the COSMOS galaxies 
+            in the input catalog, or simply let \synpipe{} randomly select the galaxies.
 
@@
 
-    With the input catalog and test data information, \synpipe{} first
-    injects synthetic objects into single-exposure images (step \texttt{addFakes.py};
-    see the middle panel of Fig \ref{fig:flowchart}).
-     \synpipe{} goes through all the individual CCD images
-    that belong to each \visit{} and decides which synthetic objects from the input catalog need
-    to be injected.
+    With the input catalog and test data information, \synpipe{} first injects synthetic 
+    objects into single-exposure images (step \texttt{addFakes.py}; see the middle panel 
+    of Fig \ref{fig:flowchart}).
+    \synpipe{} goes through all the individual CCD images that belong to each \visit{} 
+    and decides which synthetic objects from the input catalog need to be injected.
     \synpipe{} uses the \textit{initial astrometric calibration} of each single
@@
     with appropriate size and correct total flux.
-    For a galaxy described by single- or double-\ser{} models, \synpipe{} passes the input
-    \ser{} index and effective radius to the \galsim{}\texttt{.Sersic} function to
+    For a galaxy described by single- or double-\ser{} models, \synpipe{} passes the 
+    input \ser{} index and effective radius to the \galsim{}\texttt{.Sersic} function to
     create a \ser{} component.
-    After stretching and rotating the galaxy to the expected axis ratio and position angle
-    via the \texttt{shear} and \texttt{rotate} methods, \synpipe{} assigns the correct flux
-    to this component.
-    For a double-\ser{} model, \synpipe{} uses the \galsim{}\texttt{.Add} method to combine the two
-    \ser{} components.
+    After stretching and rotating the galaxy to the expected axis ratio and position 
+    angle via the \texttt{shear} and \texttt{rotate} methods, \synpipe{} assigns the 
+    correct flux to this component.
+    For a double-\ser{} model, \synpipe{} uses the \galsim{}\texttt{.Add} method to 
+    combine the two \ser{} components.
     For parametric models from the GREAT3 catalog, \synpipe{} uses the
-    \texttt{COSMOSCatalog.makeGalaxy} method to generate a corresponding model; in the case of a real high-resolution image, \synpipe{} uses the \galsim{}\texttt{.RealGalaxy} method.
-    If necessary, additional shear ($g_1$ and $g_2$) can be applied to the model at this
-    point.
+    \texttt{COSMOSCatalog.makeGalaxy} method to generate a corresponding model; in the 
+    case of a real high-resolution image, \synpipe{} uses the 
+    \galsim{}\texttt{.RealGalaxy} method.
+    If necessary, additional shear ($g_1$ and $g_2$) can be applied to the model at 
+    this point.
     Then, \synpipe{} passes the reconstructed PSF image into a
@@
     using \galsim{}\texttt{.Convolve}.
-    After this, \synpipe{} uses the \galsim{}\texttt{.drawImage} method to create the image
-    of the simulated galaxy.
-    A component with a high \ser{} index ($n_{\mathrm{Ser}} > 4$) often requires a large image
-    size to cover most of its total flux, so \synpipe{} allows the user to truncate the model
-    at a given radius (N$\times R_{\mathrm{e}}$).
-    \synpipe{} will also give warning information when a component with $n_{\mathrm{Ser}} > 6$ is
-    encountered because it takes much longer to achieve accurate PSF convolution in such a model; and the result is, therefore, 
+    After this, \synpipe{} uses the \galsim{}\texttt{.drawImage} method to create the 
+    image of the simulated galaxy.
+    A component with a high \ser{} index ($n_{\mathrm{Ser}} > 4$) often requires a 
+    large image size to cover all of its flux, so \synpipe{} allows the user to 
+    truncate the model at a given radius (N$\times R_{\mathrm{e}}$).
+    \synpipe{} will also give warning information when a component with $
+    n_{\mathrm{Ser}} > 6$ is encountered because it takes much longer to achieve 
+    accurate PSF convolution in such a model; and the result is, therefore,  
     not a realistic galaxy model.
 
- After \synpipe{} creates the image
-    of the simulated galaxy, it then shifts the image according to is location on the
-    CCD on a pixel-by-pixel basis; \synpipe{} also crops the images when necessary.
-    When that task is complete, \synpipe{} adds appropriate noise to the image based on the pixels it
-    covers and the calibration information of the detector, and creates a variance image
-    that reflects the influence of the synthetic object.
-    Since each HSC CCD consists of 4 \susan{Style preference: spell out numbers?
-Earlier you've used figures, so changed four to 4 here.
-(My preference would be to spell out if fewer than 10.)} amplifiers, each with different characteristics,
-    \synpipe{} carefully creates a corresponding gain map to provide taccurate noise level.
-    In the final step, \synpipe{} adds the noise-added image and the variance map to the original
-    CCD data while also adding a new \texttt{FAKE} mask bit to the mask plane.
+    After \synpipe{} creates the image of the simulated galaxy, it then shifts the 
+    image according to is location on the CCD on a pixel-by-pixel basis; 
+    \synpipe{} also crops the images when necessary.
+    When that task is complete, \synpipe{} adds appropriate noise to the image based 
+    on the pixels it covers and the calibration information of the detector, and creates 
+    a variance image that reflects the influence of the synthetic object.
+    Since each HSC CCD consists of four amplifiers, each with different characteristics,
+    \synpipe{} carefully creates a corresponding gain map to provide accurate noise 
+    level.
+    In the final step, \synpipe{} adds the noise-added image and the variance map to the
+    original CCD data while also adding a new \texttt{FAKE} mask bit to the mask plane.
     The middle panel of Fig \ref{fig:flowchart} depicts the result of the
@@
     calibrations for each \visit{} from the original reduction and creates
-    \texttt{coadded} images with synthetic objects on them.
-    Then the \texttt{multiBand.py} step processes these \texttt{coadded} images and
+    \coadd{}  images with synthetic objects on them.
+    Then the \texttt{multiBand.py} step processes these \coadd{}  images and
     provides standard multi-band measurements in FITS catalogs that are grouped by
@@
 
-    Using the infrastructures provided by \hscpipe{}, the user can easily perform the above processes in parallel, and the overall efficiency of \synpipe{} is similar to the
-    real data reduction process.
-    The processes also generate the same amount of images and catalog data as the original
-    one \susan{Unclear what "one" refers to: original data reduction process?}.
+    Using the infrastructures provided by \hscpipe{}, the user can easily perform the 
+    above processes in parallel, and the overall efficiency of \synpipe{} is similar to 
+    the real data reduction process.
+    The processes also generate the same amount of images and catalog data as the 
+    original data reduction process.
 
@@
     \forced{} measurements from all the \texttt{Patches}.
-    Each unmatched object from the input catalog is also passed to the results catalog with a unique label.
-    In case of multiple matches, the user can choose between returning only the closest match or returning all objects within the matching radius (the nearest one is
-    labeled as such).
-    \susan{Susan stopped editing here.}
+    Each unmatched object from the input catalog is also passed to the results catalog 
+    with a unique label.
+    In case of multiple matches, the user can choose between returning only the 
+    closest match or returning all objects within the matching radius (the nearest one 
+    is labeled as such).
+
+    \song{Susan's edit ends here; and Song has went through the previous sections.}
 %% ------------------------------------------------------------------------------------ %%
@@
             For the same star or galaxy, different seeing conditions affect its
-            central S/N on the \texttt{coadd} images, hence it also impacts the
+            central S/N on the \coadd{} images, hence it also impacts the
             detection and deblending processes in \hscpipe{}.
@@
     their seeing conditions in $g$ and $y$ bands are very similar.
-    For both \tracts{}, the \texttt{coadd} image in each band includes data from
+    For both \tracts{}, the \coadd{} image in each band includes data from
     20--40 \visits{}.
@@
         (\textbf{right}) via the differences in R.A and Dec between the input
-        coordinates and the ones measured on the coadd images.
+        coordinates and the ones measured on the \coadd{} images.
         Hexagonal bins (filled histogram) and contours (solid-line histogram) are for
@@
     photometric calibrations.
-    These data are then processed by \hscpipe{} to generate the coadd images and
+    These data are then processed by \hscpipe{} to generate the \coadd{} images and
     all the photometric measurements.
@@
         \item \synpipe{} now works in ``unit'' of \visit{} for single exposure
-            test, and \tract{} for test of \texttt{coadd} images.
+            test, and \tract{} for test of \coadd{} images.
             In case of tests that focus on specific regions that are much smaller than
@@
     of many topics, we will update \synpipe{} so that it can directly inject
-    synthetic objects to the coadd images and speed up these tests.
+    synthetic objects to the \coadd{} images and speed up these tests.
 

### 2017-04-19 draft/ms_susan.tex
New edits from Susan

--- 2017-04-15 draft/ms_v2.tex
@@
     Furthermore, as ongoing surveys reach to increasingly deeper detection limit 
-    (e.g SSP Wide reaches to $5\ \sigma$ detection limit of point source of 
+    (e.g., SSP Wide reaches to $5\ \sigma$ detection limit of point source of 
     ${\sim}26.4$ mag), the number of objects in a unit area, especially faint objects,
@@
         Illustration of \synpipe{} basic procedures.
-        Grey boxes indicate the required inputs at different stages.
+        Gray boxes indicate the required inputs at different stages.
         The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
@@
     ($grizy$; Kawanomoto\etal in prep.).
-    The Deep (4 separated fields; ${\sim}27$ deg$^2$) and UltraDeep (2 separated
+    The Deep (four separated fields; ${\sim}27$ deg$^2$) and UltraDeep (two separated
     fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
@@
     The camera has a circular FoV with a 1.5 deg diameter.
-    Each CCD contains 2048$\times$4096 pixels distributed in 4 amplifiers.
+    Each CCD contains 2048$\times$4096 pixels distributed in four amplifiers.
     The pixel size is equal to 0.168\asec{} on the sky.
@@
     For our work, we focused on data from the Wide layer as they relate to key 
-    scientific goals of HSC survey, which include WL cosmology, galaxy evolution 
+    scientific goals of the HSC survey, which include WL cosmology, galaxy evolution 
     since $z{\sim}1$, and studies of galaxy clusters.
     The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
-    6 different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
+   six different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
     \footnote{A small AEGIS field is also observed for calibration purposes.}.
     Except for the HECTOMAP field, the regions are all close to the equator. 
-    In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into 4
+    In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into four
     dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
-    uniform coverage.}; for the remaining 3 bands, 20 mins of exposure time and 6 
+    uniform coverage.}; for the remaining three bands, 20 mins of exposure time and six
     dithers are used\footnote{Several 30 s exposures are taken to improve the 
@@
             the HSC \cmodel{} algorithm (described in Bosch\etal, in prep.) fits 
-            each object's flux distribution using a combination of the de Vaucouleur
+            each object's flux distribution using a combination of the de Vaucouleurs
             profile and an exponential component that takes the PSF convolution 
@@
         \item \textbf{Authentic Data Processing}:
-            To follow the data reduction process as realistic as possible, we choose to
+            To follow the data reduction process as realistically as possible, we choose to
             start from the single-\visit{} images instead of directly putting synthetic 
@@
             distributions of galaxies near and far, both early-type or late-type.
-            A Double-\ser{} model can simulate a galaxy with even more realistic
+            A double-\ser{} model can simulate a galaxy with even more realistic
             structural details (e.g., bulge$+$disk).
@@
     a variance image that reflects the influence of the synthetic object.
-    Since each HSC CCD consists of four amplifiers, each with different characteristics,
+    Since each HSC CCD consists of 4 amplifiers, each with different characteristics,
     \synpipe{} carefully creates a corresponding gain map to provide accurate noise 
@@
     As the last step, \synpipe{} matches the input catalog to the results within a
-    radius that is specified by the user, and merge all the \unforced{} and
+    radius that is specified by the user, and merges all the \unforced{} and
     \forced{} measurements from all the \texttt{Patches}.
@@
     with a unique label.
-    In case of multiple matches, the user can choose between returning only the 
+    In the case of multiple matches, the user can choose between returning only the 
     closest match or returning all objects within the matching radius (the nearest one 
@@
     \song{Susan's edit ends here; and Song has went through the previous sections.}
+    \susan{Susan made some minor additional edits to the preceding text on 4/17/2017.}
 %% ------------------------------------------------------------------------------------ %%
@@
         Magnitude and color distributions of the synthetic stars.
-        \textbf{Upper panel} shows the 5-band magnitude distributions of the COSMOS
+        \textbf{Upper panel} shows the five-band magnitude distributions of the COSMOS
         stars (filled histograms) and the resampled stars (dashed lines).
@@
     \caption{
-        Distributions of 5-band magnitudes (\textbf{upper panel}) and other properties
+        Synthetic galaxy distributions of five-band magnitudes (\textbf{upper panel}) and other properties
         (\texttt{lower panel}; from left to right are the \ser{} index, axis ratio,
-        effective radius in arcsec, the $g-r$ and $r-z$ colors) of the synthetic
-        galaxies.
+        effective radius in arcsec, the $g-r$ and $r-z$ colors).
         Objects used for the \textbf{Tract} with good seeing (filled histograms) and
@@
 %% ------------------------------------------------------------------------------------ %%
+\susan{Susan started editing here on 4/17/2017.}
 \section{Generation of Synthetic Dataset}
@@
 
-    Given the design of \synpipe{} and the data volume of HSC DR1\footnote{${\sim}70$
+    Given the \synpipe{} design and the HSC DR1 data volume \footnote{${\sim}70$
     TB of images}, it is not realistic to test the whole dataset. 
@@
 
-        \item Not bothered by extremely bright ($i<12$ mag), saturated star.
-
-        \item Can represent good and bad seeing condition in the current $i$-band
-            data of HSC survey.
-            For the same star or galaxy, different seeing conditions affect its
-            central S/N on the \coadd{} images, hence it also impacts the
+        \item Not distorted by an extremely bright ($i<12$ mag), saturated star.
+
+        \item Can represent both good and bad seeing conditions in the current $i$-band
+            data of the HSC survey.
+              \end{enumerate}
+              In addition to satisfying these criteria, the selected \tracts {}  show the photometric uncertainties under both good and bad seeing conditions, since for any given star or galaxy, different seeing conditions affect its
+            central S/N on the \coadd{} images and, therefore, also impact the
             detection and deblending processes in \hscpipe{}.
-            Therefore, it is useful to show the photometric uncertainties under
-            different seeing conditions.
-
-    \end{enumerate}
-
-    \noindent These regions are:
+
+The two selected HSC Wide regions are as follows:  
     \tract{}$=9699$ in the VVDS field (median FWHM$=0.449$\asec{} in $i$-band;
-    will be referred as \texttt{goodSeeing}) and
+   in this paper referred to as \texttt{goodSeeing}) and
     \tract{}$=8764$ in the XMM-LSS field (median FWHM$=0.700$\asec{};
     \texttt{badSeeing}).
-    \tract{}$=9699$ also has better seeing in both $r$ and $z$-band;
-    their seeing conditions in $g$ and $y$ bands are very similar.
+    \tract{}$=9699$ also has better seeing in both $r$- and $z$-bands;
+    the seeing conditions in $g$- and $y$-bands are very similar for both  \tract{}$=9699$ and \tract{}$=8764$.
     For both \tracts{}, the \coadd{} image in each band includes data from
@@
 
-    In this work, we use objects from the high-resolution \hst{}/ACS observations of
-    the COSMOS field to build input catalogs of realistic synthetic stars and galaxies
-    with appropriate completeness for the Wide survey and reasonable five-band colors.
-
-    For stars, we choose to use the sample from \citet{Leauthaud2007}.
-    The authors select stars with clean photometry from the COSMOS images using not
-    only the \texttt{SExtractor} stellar classification index (\texttt{CLASS\_STAR}),
-    but also the peak surface brightness above background (\texttt{MU\_MAX}) and
-    half-light radius (\texttt{RHL}).
+    In this work, we use objects from the high-resolution \hst{}/ACS COSMOS field observations to build input catalogs of realistic synthetic stars and galaxies with appropriate completeness for the Wide survey and with reasonable five-band colors.
+We first select stars and galaxies as described below;  we then create the input catalogs via randomly distributing the selected synthetic stars and galaxies into the regions covered by the good- and bad-seeing \tracts{}.
+For stars, we use a number density of 1,000 per CCD; for galaxies, we use a number density of  500 per CCD.
+
+For star selection, we use the sample from \citet{Leauthaud2007}. 
+     We use not only the \texttt{SExtractor} stellar classification index (\texttt{CLASS\_STAR}) but also the peak surface brightness above background (\texttt{MU\_MAX}) and
+    half-light radius (\texttt{RHL}) to select stars with clean photometry. 
     The classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag.
     We match this sample of stars with the HSC UltraDeep--COSMOS data that currently
-    reaches to about ${\sim}27.2$ mag in $i$-band.
+    reach to about ${\sim}27.2$ mag in $i$-band.
     After filtering the matched sample through basic quality cuts (see \ref{app:qc}),
-    we gather 5-band HSC photometry for 14472 stars.
-    To get a larger sample for the test, we resample the their 5-band magnitudes
-    distributions using the \texttt{astroML} (\citealt{astroml}) alternative
+    we gather five-band HSC photometry for 14,472 stars.
+    To get a larger sample for the test, we resample the five-band magnitude
+    distributions using \texttt{astroML} (\citealt{astroml}) alternative
     implementation of the \texttt{extreme-deconvolution} algorithm developed by
@@
     \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
-    generate 100000 synthetic stars.
-    In Fig \ref{fig:star_sample}, we show the magnitude and color distributions of
+    generate 100,000 synthetic stars.
+    In Fig \ref{fig:star_sample}, we show that the magnitude and color distributions of
     the real COSMOS stars are nicely recovered by the resampled stars in all
-    five-band magnitude and two color-color space.
-
-    As for synthetic galaxies, we choose to use the single-\ser{} model of galaxies
+   five-band magnitude and two color-color space distributions. \susan{Later you use "2-D color-color" Should it also be 2-D here?}
+
+For synthetic galaxies, we use the single-\ser{} galaxy models 
     in the COSMOS field that have $I_{F814W} \leq 25.2$ mag.
-    These models are created via method developed by \citet{Lackner2012} on the
-    \textit{HST}/ACS images, and are included in \galsim{}.
-    Each model is described by a total of 5 parameters: magnitude, effective radius,
+    These models are created via a method developed by \citet{Lackner2012} on the
+    \textit{HST}/ACS images and are included in \galsim{}.
+    Each model is described by a total of five parameters: magnitude, effective radius,
     \ser{} index, axis ratio, and position angle.
@@
     enables it to reasonably describe the flux distribution of most galaxies.
-    Also its simplicity makes it easy to diagnose potential problems of the
+    Also, its simplicity makes it easy for us to diagnose potential problems of the
     \cmodel{} photometry.
-    We exclude a tiny fraction of ill-behaved models that have very high \ser{}
-    index ($n_{\mathrm{Ser}} > 6.0$) or very low central surface brightness
+    We exclude a tiny fraction of ill-behaved models that have a very high \ser{}
+    index ($n_{\mathrm{Ser}} > 6.0$) or a very low central surface brightness
     ($\mu_{i} < 24.0$\sb).
     We further match this COSMOS sample with the HSC UltraDeep--COSMOS data.
-    after removing the objects with problematic photometry, we obtain the a sample of
-    58210 synthetic galaxies with realistic 5-band HSC photometry.
+    After removing the objects with problematic photometry, we obtain a sample of
+    58,210 synthetic galaxies with realistic five-band HSC photometry.
     As shown in Fig \ref{fig:galaxy_sample}, the majority of these galaxies are
-    faint ($i<24.0$ mag) and barely resolved ($R_{\mathrm{e}}< 1.0$\asec) galaxies.
-    This sample is appropriate to test the general behaviours of photometry in
-    \hscpipe{}, but is lack of relative bright galaxies ($i<20.5$ mag).
-
-    We then create input catalogs via randomly distribute these synthetic stars and
-    galaxies into the regions covered by the good and bad seeing \tracts{}.
-    For stars (galaxies), we choose to use number density of 1000 (500)
-    per CCD.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-\subsection{Running \synpipe{} Test}
+    faint ($i<24.0$ mag) and barely resolved ($R_{\mathrm{e}}< 1.0$\asec).
+    This sample is appropriate to test  \hscpipe{}'s general photometric behaviors, but the sample lacks relatively bright galaxies ($i<20.5$ mag).
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+\subsection{Running the \synpipe{} Tests}
     \label{ssec:running}
 
-    We conduct these tests on the cluster (\texttt{Master}) at Kavli-IPMU using
-    the HSC DR1 data stored there.
+    We use HSC DR1 data stored at Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU) to conduct the \synpipe{} tests on the cluster (\texttt{Master}).
     The \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in each
-    band; same process takes longer for the test of galaxies (${\sim}3.0$ hours per
-    \tract{} in each band) as the \galsim{} simulation is more time consuming.
-    The \texttt{stack.py} and \texttt{multiBand.py} together take ${\sim}3.5$ hours
+    band; the same process takes longer for the galaxy tests (${\sim}3.0$ hours per
+    \tract{} in each band) because the \galsim{} simulation is more time consuming.
+    The \texttt{stack.py} step and \texttt{multiBand.py} step together take ${\sim}3.5$ hours
     per \tract{}.
 
-    We match the results with the input catalogs using a 2 pixels matching radius
+    We match the results with the input catalogs using a 2--pixel matching radius
     to generate output catalogs for \forced{} and \unforced{} photometry
@@
     object.
-    These objects are useful in the WL-related statistical tests (see Murata et al.
-    in prep. for more details), but will not help test photometry, hence they will
-    be excluded later
-
-    The detailed log of the entire tests can be found here:
+\susan{Is ambiguously blended well-understood by your reader?
+Or is the definition that they are objects that are right on top of the flux peak of a real object?
+If so, change sentence to the following: We also match the input catalogs with the original HSC catalogs to identify the  ``ambiguously blended'' objects, which are defined as those objects that are right on top of the flux peak of a real
+    object.}
+    The ambiguously blended objects are useful in the WL-related statistical tests (see Murata et al.
+    in prep. for more details); but since they will not help test photometry, they will be excluded later.
+
+    The detailed log of the entire tests can be found at 
     \url{goo.gl/VINOVP}.
-    User should be able to reproduce the results presented in this work using this
-    information.
-    It can also serve as a brief manual for running \synpipe{} test.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-\section{Results on Photometric Performance}
+    The user should be able to reproduce the results presented in this work using this information. It can also serve as a brief manual for running a \synpipe{} test.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+\section{Photometric Performance Results}
     \label{sec:result}
 
-    Here we show the general performance of \hscpipe{} for stars (galaxies)
-    mainly through the \forced{} PSF (\cmodel{}) photometry.
-    Although \hscpipe{} provides more options (e.g. aperture and Kron photometry),
-    these two are the most appropriate and relevant ones for magnitude and colors of
-    star and galaxy as they consider the effects of PSF in different bands,
-    and are consistent across all bands in terms of position and shape.
+    Here we discuss \hscpipe{}'s general performance, assessed mainly through  \forced{} PSF photometry (for stars) and (\cmodel{}) photometry (for galaxies).
+ Although  \hscpipe{} does provide other options (e.g., aperture and Kron photometry), 
+these two are the only options that consider the effects of PSF in different bands and are consistent across all bands in terms of position and shape.
+Therefore, they are the most appropriate and relevant to star and galaxy magnitudes and colors.
 
@@
     \caption{
-        Relations between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
+        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
         $g$-band) of synthetic stars and the $log(S/N)$ measured by \hscpipe{} PSF
@@
         Hexagonal binned density plots and contours show the distributions for
-        stars in the \tract{} with good and bad seeing.
+        stars in both the good- and bad-seeing \tracts{}.
         The highly blended stars are highlighted using scatter plots. 
-        A grey dashed line marks $S/N = 5$.
+        The gray dashed line marks $S/N = 5$. \susan{"grey" is an acceptable spelling; however, gray is more commonly used in the United States.}
         }
@@
     \caption{
-        Accuracies of the \texttt{hscpipe} PSF photometry for synthetic stars measured
+        Accuracy of the \texttt{hscpipe} PSF photometry for synthetic stars measured
         by the difference between input and output \forced{} PSF magnitudes.
-        Plot [a, b, c, d, e] shows the results for [$g$, $r$, $i$, $z$, $y$]-band.
-        In each plot, left panel shows the relation between input magnitude and
+        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-band, respectively.
+        The left panel in each plot shows the relation between input magnitude and
         magnitude difference.
-        Hexagonal binned density plot and contour are for the synthetic galaxies from
+        Hexagonal binned density plots and contours are for the synthetic galaxies from
         good and bad seeing \tracts{}.
-        Highly blended objects are highlighted using scattered plot.
-        The long-dashed line marks zero magnitude difference, while the pair of
+        Highly blended objects are highlighted using scattered plots.
+        The long-dashed lines mark zero magnitude difference, while the pairs of
         dashed lines outline the running-median of PSF magnitude errors
         (including the uncertainties in aperture correction).
-        Right panel shows the distributions of the magnitude differences for objects
+        The right panel in each plot shows the distributions of the magnitude differences for objects
         in good (filled) and bad (solid line) seeing \tracts{}.
-        The dashed line is for the distribution of highly blended objects.
+        The dashed lines identify the distribution of highly blended objects.
         }
@@
         (\textbf{right}).
-        Other formats are identical to the plots in Fig \ref{fig:psf_mag}.
+        The lines and contours legend is identical to the plots in Fig \ref{fig:psf_mag}.
         }
@@
     \caption{
-        Accuracies of the color measurements for synthetic stars via the differences
+        Accuracy of the color measurements for synthetic stars via the differences
         between input and \forced{} PSF colors.
-        The \textbf{Upper panels} and \textbf{lower panels} are for $g-i$ and $i-y$
+        The \textbf{upper panels} and \textbf{lower panels} are for $g-i$ and $i-y$
         colors separately.
         The \textbf{left} column shows the relation between input magnitude and
-        the color difference, and the \textbf{right} one uses the input colors as
+        the color difference, and the \textbf{right} column uses the input colors as
         x--axis instead.
-        Other formats are identical to the plot in Fig \ref{fig:psf_mag}.
+        The lines and contours legend is identical to the plot in Fig \ref{fig:psf_mag}.
         }
@@
     \caption{
-        Evaluations of the accuracy of color measurements for synthetic stars using
+        Evaluations of color measurement accuracy for synthetic stars using
         the color-color distributions.
-        \textbf{Left} uses $(g-r)$ v.s. $(r-i)$ colors, and the \textbf{right} one
+       The plot on the \textbf{left} (a) uses $(g-r)$ v.s. $(r-i)$ colors, and the plot on the \textbf{right} (b) 
         uses $(i-z)$ and $(z-y)$ colors.
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsection{PSF photometry of Stars}
+\subsection{PSF photometry of stars}
     \label{ssec:psf}
 
-    In \hscpipe{}, the PSF magnitude is derived using matched-filter method that
+    In \hscpipe{}, the PSF magnitude is derived using a matched-filter method that
     depends on the best-fit PSF model and uses the Lanczos interpolation to shift
-    PSF model.
-    The error of PSF magnitude from \hscpipe{} only considers the per-pixel noise,
-    not the uncertainty of the centroid.
+    the PSF model.
+    The error of the PSF magnitude from \hscpipe{} only considers the per-pixel noise,
+    and does not include centroid uncertainty.
     \hscpipe{} also estimates aperture correction for PSF photometry.
-    For more details please see Section 4.9.5 of Bosch\etal (in prep.).
-
-    In our tests, we randomly inject ${\sim}100000$ stars to each \tract{} in all
-    five-bands.
-    Among these stars, ${\sim}3$--$4$\% of them locate within 2 pixels to the centroids
-    of real objects.
-    We remove them from the sample to avoid confusion in the comparisons.
-    After this step, there are still ${\sim}1$--$3$\% of the remaining synthetic stars
-    have no match in the \synpipe{} outputs.
-    They could be either below the detection threshold or ambiguously blended with real
-    objects.
+    For more details please see Bosch\etal (in prep.). \susan{Suggest you not include a section number for a document in preparation; section numbers can change before a text is published. }
+
+    In our tests, we randomly inject ${\sim}100,000$ stars into each \tract{} in all
+    five bands. Approximately \susan{Spell out approximately and delete approximate sign before 3-4.}
+ ${\sim}3$--$4$\% of the stars are located within 2 pixels of the centroids
+    of real objects; we remove those stars from the sample to avoid confusion in the comparisons.
+    After this step, ${\sim}1$--$3$\% of the remaining synthetic stars still have no match in the \synpipe{} outputs.
+    They could either be below the detection threshold or ambiguously blended with real objects.
     The input $i$-band magnitudes of these unmatched stars are on average ${\sim}0.9$
     mag fainter than the matched ones.
-    The fraction of unmatched stars is slightly higher in the bad seeing \tract{},
-    which is consistent with the expectation of seeing-dependent limit magnitude,
-    although the difference in not very significant.
+    The fraction of unmatched stars is slightly higher in the bad seeing \tract{}; this result is consistent with our expectation that magnitude depends on seeing conditions,
+    although the difference is not very significant.
     For the matched stars, we select the primary detections
@@
     (see Appendix \ref{app:qc} for details).
-    This gives us ${\sim}83000$ stars in each \tract{}.
+    This gives us ${\sim}83,000$ stars in each \tract{}.
 
@@
     The misclassified stars are on average ${\sim}1$ mag fainter than the others.
-    We exclude them from the photometric comparison below, and will further discuss
+    We exclude them from the photometric comparison below, and further discuss
     the star--galaxy separation issue in Section \ref{ssec:sg}.
 
-    In the following comparisons, we will always show the results from the
-    \textbf{good seeing} and \textbf{bad seeing} \tracts{} separately, because it
-    is important to understand the impact of seeing on photometric accuracies,
-    and to test whether \hscpipe{} can deliver unbiased photometry under different
-    seeing conditions.
+    In the following comparisons, we show the results from the
+    \textbf{good-seeing} and \textbf{bad-seeing} \tracts{} separately because it
+    is important to understand how the seeing condition affects photometric accuracy as well as to test whether \hscpipe{} can deliver unbiased photometry under different  seeing conditions.
+\susan{Later you use "slightly worse" and "better" seeing; if you want to use those terms, perhaps define here where you make the distinction?
+For example, can you quantify slightly worse and better?}
 
@@
     for details) is another factor that influences the photometric accuracy.
-    We therefore separate the samples into relative isolated and highly blended
+    Therefore, we separate the samples into relatively isolated and highly blended
     groups based on the $b$ values. 
     Assuming zero pixel noise, $b$ of object $A$ reflects the fraction of flux
-    within the \texttt{Footprint} of $A$ that comes from other objects.
-    Ideally, $b=0$ means perfect isolation, and $b{\sim}1$ means completely
-    confused with other object.
-    Here we use $b>0.05$ to define blended stars (${\sim}4$--$9$\%).
-    Fraction of highly blended stars slightly increases in the bad seeing \tract{}.
+    within the  $A$ \texttt{Footprint} that comes from other objects.
+    Ideally, $b=0$, which means perfect isolation; $b{\sim}1$ means completely
+    confused with another object.
+    Here we use $b>0.05$ to define highly \susan{Later you say that $b>0.05$ is "highly blended"; it needs to be consistent.
+If inserting "highly" is incorrect here, please define b for highly blended stars since you use highly blended throughout the text.} blended stars (${\sim}4$--$9$\% are blended).
+    The fraction of highly blended stars slightly increases in the bad seeing \tract{}.
     We highlight these stars separately as well, and will discuss more about the
@@
 
-\subsubsection{Input magnitude and the \s2n{} of PSF photometry}
-
-    We first briefly discuss the relationship between input magnitude and the
-    signal-to-noise ratio of the output PSF photometry.
-    Here, we simply define the \s2n{} as
+\subsubsection{PSF photometry input magnitude and \s2n{} }
+
+    In discussing the relation between the input magnitude and the
+    signal-to-noise ratio of the output PSF photometry, we define \s2n{} simply as
     $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band
     without considering the aperture correction.
-    This will help us visualize
+    This helps us visualize
     1) the detection limit for point sources,
     2) the impact of seeing condition on PSF photometric,
-    3) and the scatter of photometric accuracies at fixed input magnitude given all
-       the realistic features of HSC images (e.g. background subtraction, nearby
-       object, optical artefacts).
-    We show the results for $g$- and $i$-band in Fig \ref{fig:star_sn}, and find tight
+    3) and the scatter of photometric accuracies at a fixed input magnitude given all
+       the realistic features of HSC images (e.g., background subtraction, nearby
+       objects, optical artifacts).
+    We show the results for $g$- and $i$-bands in Fig \ref{fig:star_sn}, and find close
     relations in both bands.
@@
     sources at fixed input magnitude.
-    In $i$-band, the \tract{} with slightly worse seeing (0.7\asec{}) shows systematically
-    lower \s2n{} comparing to the one with better seeing (0.5\asec{}).
-    As for the $g$-band, since the two \tracts{} share similar seeings now, they also
-    follow similar relations.
-    We also see that the blendedness can also affect accuracies of PSF photometry.
+    In  $i$-band, the bad-seeing (0.7\asec{}) \tract{}  shows systematically
+    lower \s2n{} than the good-seeing (0.5\asec{}) \tract{}. 
+     \s2n{} is similar for the two $g$-band \tracts{} because they share similar seeing conditions.
+    Our results show that blendedness can also affect the accuracy of PSF photometry.
     In $i$-band, the highly blended synthetic stars scatter toward lower \s2n{} at
@@
 
-    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ and
-    $i$-band at average seeing condition, which is consistent with the values found
-    in \citet{HSCDR1}.
-    At the same time, it is worth reminding the users of HSC data that the detection
+    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$- and
+    $i$-bands at average seeing conditions, which is consistent with the values found
+    in \citet{HSCDR1}. \susan{Is there a value for "average seeing conditions"?}
+    At the same time, it is worth reminding HSC data users that the detection
     limit will show spatial variations due to the seeing conditions.
@@
 
-    Now, we will look into the accuracies of PSF magnitudes in all five bands
+    Now, we look into PSF magnitude accuracy in each of the five bands
     independently.
-    In Fig \ref{fig:psf_mag}, we show the relations between the input magnitude and the
+    Fig \ref{fig:psf_mag} shows the relation between the input magnitude and the
     magnitude difference from the \hscpipe{} \forced{} PSF photometry.
@@
     In $i$-band, the median magnitude difference for \tract{} with 0.45\asec{} seeing is
-    around ${\sim}0.015$ mag (${\sim}1.5$\% accuracy) at
+     ${\sim}0.015$ mag (${\sim}1.5$\% accuracy) at
     $i_{\mathrm{Input}}{\sim}19.0$ mag.
     At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of PSF
-    magnitude keeps at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
-    Down to $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
+    magnitude holds at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
+    At $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
     ${\sim}7$\% level with an average ${\sim}0.072$ mag difference.
-    The \tract{} with worse seeing shows similar accuracy of PSF photometry at
+    The bad-seeing \tract{} shows similar accuracy of PSF photometry at
     $i_{\mathrm{Input}}<23.5$ mag.
-    At faint end, the accuracy becomes slightly worse: ${\sim}5$\% accuracy around
-    $i_{\mathrm{Input}}{\sim}24.0$ mag; and ${\sim}11$\% accuracy around
+    At the faint end, the accuracy becomes slightly worse: ${\sim}5$\% accuracy around
+    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% accuracy around
     $i_{\mathrm{Input}}{\sim}25.2$ mag.
     \citet{HSCDR1} evaluates the accuracy of PSF photometry via external comparisons
-    with the PS1 PV2 and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
+    with the PS1, PV2, and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
     which is consistent with our results.
     At fainter magnitude, external comparisons become difficult due to the lack of deep
-    imaging data at HSC level and the impact of the color-term when comparing photometry
+    imaging data at HSC level and also due to the impact of the color-term when comparing photometry
     using different filters.
@@
     detection limit\footnote{Strictly speaking, the uncertainties here should be
-    considered as lower limit as the \synpipe{} now does not consider the uncertainties
+    considered as the lower limit because \synpipe{} currently does not consider the uncertainties
     in PSF modeling.}.
@@
     We also see that the accuracy of PSF photometry does not strongly depend on filters.
-    The forced PSF magnitude in $r$ and $z$-band have very similar accuracy with
-    $i$-band (1.5-4.0\% at $19.0 < r_{\mathrm{Input}} < 24.0$ mag, ${\sim}8$\% down to
+    The accuracy of the forced PSF magnitude in $r$- and $z$-bands is similar to 
+    $i$-band observations (1.5-4.0\% at $19.0 < r_{\mathrm{Input}} < 24.0$ mag, ${\sim}8$\% down to
     $r_{\mathrm{Input}}{\sim}25.2$ mag;
@@
     $z_{\mathrm{Input}}{\sim}25.2$ mag).
-    The accuracies in $g$- and $y$-band become slightly worse (
-    1.5-7.0\% at $19.0 < g_{\mathrm{Input}} < 24.0$ mag, ${\sim}13$\% down to
+    The accuracies in $g$- and $y$-bands become slightly worse (1.5-7.0\% at $19.0 < g_{\mathrm{Input}} < 24.0$ mag, ${\sim}13$\% down to
     $g_{\mathrm{Input}}{\sim}25.2$ mag;
     1.5-5.0\% at $19.0 < y_{\mathrm{Input}} < 23.0$ mag, ${\sim}12$\% down to
-    $y_{\mathrm{Input}}{\sim}24.0$ mag;), but the differences can be attributed to the
+    $y_{\mathrm{Input}}{\sim}24.0$ mag;); however, the differences can be attributed to the
     differences in seeing conditions.
 
-    For relative isolated stars, \hscpipe{} provides unbiased PSF photometry down to
-    very faint magnitude in $i$- and $z$-band.
-    For $g$-, $r$-, and $y$-band, we find small offsets in the distributions of magnitude
+    For relatively isolated stars, \hscpipe{} provides unbiased PSF photometry down to a
+    very faint magnitude in $i$- and $z$-bands.
+    For $g$-, $r$-, and $y$-bands, we find small offsets in the distributions of magnitude
     differences, which indicates \hscpipe{} tends to underestimate the fluxes of stars
     in these bands by ${\sim}0.01-0.02$ mag.
-    Although the exact cause of this offset is unclear (could still be related to
-    differences in seeing), it will not affect the accuracies of magnitudes of colors.
+    Although the exact cause of this offset is unclear (it could be related to
+    differences in seeing), it will not affect the accuracies of magnitudes of \susan{should "of" be "or"?} colors.
 
     At the same time, the story for highly blended stars is very different.
-    \hscpipe{} on average systematically underestimates the total fluxes of them by
-    $0.05$--$0.10$ mag at fixed input magnitude.
+    \hscpipe{} on average systematically underestimates their total fluxes by
+    $0.05$--$0.10$ mag at a fixed input magnitude.
     We see the same effect in all bands, and the impact of blendedness becomes
     increasingly significant at fainter magnitude.
-    It is therefore important to keep this in mind when using PSF photometry for point
+    It is important to keep this in mind when using PSF photometry for point
     sources in HSC data.
@@
     accuracies.
-    During the measurement of \forced{} PSF photometry, \hscpipe{} fixes the centroid
-    of the PSF model across all five band.
-    Therefore, the magnitude difference between \forced{} and \unforced{} PSF magnitudes
-    indicates the photometric uncertainties induced by differences in the accuracies of
+    While measuring \forced{} PSF photometry, \hscpipe{} fixes the centroid
+    of the PSF model across all five bands.
+    Therefore, the  difference between \forced{} and \unforced{} PSF magnitudes
+    indicates the photometric uncertainties induced by the differences in the accuracies of
     astrometric calibrations and PSF modeling among different bands.
     We highlight the differences between \forced{} and \unforced{} PSF photometry of
-    $g$- and $y$-band in Fig \ref{fig:psf_diff}.
-    The overall difference is very small ($<0.01$ mag), but it also suggest that
+    $g$- and $y$-bands in Fig \ref{fig:psf_diff}.
+    The overall difference is very small ($<0.01$ mag), but it also suggests that
     \hscpipe{} \unforced{} PSF photometry systematically recovers slightly more fluxes
-    at very faint end.
+    at the very faint end.
 
@@
 
-    Color measurement based on PSF photometry is the most appropriate one for point
-    sources, and is therefore important to many scientific goals of the HSC survey
-    (e.g. study of the Milky Way structure, selection of unique stellar objects or
-    high-redshift quasars, and the accurate star--galaxy separation).
+    PSF photometry is the most appropriate way to measure colors for point
+    sources; therefore, the accuracy of the PSF color estimates is important to many scientific goals of the HSC survey
+    (e.g., study of the Milky Way structure, selection of unique stellar objects or
+    high-redshift quasars, and accurate star--galaxy separation).
 
@@
     These results suggest that \hscpipe{} provides accurate and unbiased PSF color
-    estimates for synthetic stars with realistic color distributions down to very faint
+    estimates for synthetic stars with realistic color distributions down to a very faint
     magnitude.
@@
     the synthetic stars or the seeing conditions.
-    For instance, the accuracy of $(g-i)$ color for \tract{} with bad seeing only becomes
+    For instance, the accuracy of $(g-i)$ color for a bad-seeing \tract{} is only 
     slightly worse in the very faint end (${\sim}0.14$ mag at
-    $i_{\mathrm{Input}}{\sim}24.0$ mag) comparing to the results for good seeing \tract{}.
+    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the results for a good-seeing \tract{}.
 
     We further illustrate the accuracies of PSF colors via comparing the distributions
-    of colors for the input synthetic stars and the ones recovered by \hscpipe{}
+    of colors for the input synthetic stars and the stars recovered by \hscpipe{}
     (see Fig \ref{fig:psf_cdist}).
-    Using four different colors and two color--color planes, we show that the \forced{}
+    Using four different colors and two \susan{2-D?} color--color planes, we show that the \forced{}
     PSF colors can accurately reproduce the distributions of all four colors and the
-    2-D color-color distributions.
+    2-D \susan{or two?} color-color distributions.
 
     As for the highly blended stars, on Fig \ref{fig:psf_color}, we see that on average
-    they still have larger uncertainties in colors comparing to the relative isolated
+    they still have larger uncertainties in colors compared to the relatively isolated
     ones.
     For $(g-i)$ color, the average color uncertainty is ${\sim}0.1$ mag larger for the
-    highly blended stars at fixed input magnitude.
+    highly blended stars at a fixed input magnitude.
     However, the biases in color measurements for these stars are less severe than
     the magnitude measurements.
-    Although the blended stars still show slightly bluer (redder) $(g-i)$ ($(i-y)$)
-    colors comparing to the isolated ones and the input values, the differences in the
+    Although the blended stars still show slightly bluer color for $(g-i)$ and slightly redder color for $(i-y)$ 
+    compared to the isolated stars and the input values, the differences in the
     distributions of color uncertainties of blended and isolated stars are less striking
-    than the ones for magnitude differences.
+    than the distribution differences for magnitude.
 
@@
     \caption{
-        Relations between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
+        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
         $g$-band) of synthetic galaxies and the $log(S/N)$ measured by \hscpipe{}
         \cmodel{} photometry.
-        Other formats are very similar to Fig \ref{fig:star_sn}
+        The lines and contours legend is similar to Fig \ref{fig:star_sn}
         }
@@
         \cmodel{} magnitudes.
-        Plot [a, b, c, d, e] shows the results for [$g$, $r$, $i$, $z$, $y$]-band.
-        Other formats are identical to Fig \ref{fig:psf_mag}.
+        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-bands, respectively.
+       The lines and contours legend is identical to Fig \ref{fig:psf_mag}.
         }
@@
         $y$-band (\textbf{right}).
-        Other formats are identical to the plots in Fig \ref{fig:psf_diff}.
+        The lines and contours legend is identical to the plots in Fig \ref{fig:psf_diff}.
         }
@@
         differences between input and \forced{} \cmodel{} colors.
-        The \textbf{Upper panels} and \textbf{lower panels} are for $g-i$ and $i-y$
+        The \textbf{upper panels} and \textbf{lower panels} are for $g-i$ and $i-y$
         colors separately.
-        The \textbf{left} column shows the relation between input magnitude and
-        the color difference, and the \textbf{right} one uses the input colors as
-        x--axis instead.
-        Other formats are identical to the plot in Fig \ref{fig:psf_color}.
+        The \textbf{left} column shows the relation between input magnitude (x-axis) and
+        the color difference, and the \textbf{right} column uses the input colors as
+       the  x--axis.
+       The lines and contours legend is identical to the plot in Fig \ref{fig:psf_color}.
         }
@@
     \caption{
-        Evaluations of the accuracy of color measurements for synthetic galaxies
+        Evaluations of color measurement accuracy for synthetic galaxies
         using the color-color distributions.
-        \textbf{Left} uses $(g-r)$ v.s. $(r-i)$ colors, and the \textbf{right} one
+        The \textbf{left} panel (a) uses $(g-r)$ vs. $(r-i)$ colors, and the \textbf{right} panel (b)
         uses $(i-z)$ and $(z-y)$ colors.
@@
 
-    \cmodel{} algorithm is the primary photometric method for galaxies in
-    \hscpipe{} that can be seen as an improved version of the SDSS \cmodel{}
+  For galaxies, \hscpipe{} uses a \cmodel{} photometry algorithm 
+     that is an improved version of the SDSS \cmodel{}
     photometry.
-    For more details, please see Section 4.9.8 of Bosch\etal (in prep.).
-    In short, \cmodel{} tries to fit each object using a combination of de Vaucouleur
+    For more details, please see Bosch\etal (in prep.).\susan{Suggest you not include a section number for a document in preparation; section numbers can change before a text is published. }
+    In short, \cmodel{} tries to fit each object using a combination of de Vaucouleurs
     and exponential profiles that are approximated by multiple Gaussian profiles.
-    Despite the limitation of the \cmodel{} method (e.g. sensitive to background
+    Despite the limitation of the \cmodel{} method (e.g., sensitive to background
     subtraction and deblender failure), it can deliver robust PSF-corrected fluxes and
@@
 
-    In our tests, we randomly inject ${\sim}40000$ synthetic galaxies into each 
-    \tract{}, and select samples for photometric comparisons in a similar way to the
-    stars. 
+    In our tests, we randomly inject ${\sim}40,000$ synthetic galaxies into each 
+    \tract{}; and, using an approach similar to that for star selection, we then select galaxy samples for photometric comparisons. 
     First, ${\sim}2$--$3$\% of the synthetic galaxies are ambiguously blended with 
@@
     \synpipe{} results in different \tracts{} and filters. 
-    The fraction of unmatched objects is slightly higher for the $g$- and $y$-band. 
-    For the same filter, the fraction is always higher for the bad seeing \tract{}.
+    The fraction of unmatched objects is slightly higher for the $g$- and $y$-bands. 
+    For the same filter, the fraction is always higher for the bad-seeing \tract{}.
     The magnitudes of the unmatched galaxies are systematically fainter than the 
@@
     In $i$-band, the median input magnitudes for matched and unmatched galaxies are 
-    $24.0$ mag and $24.6$ mag.
+    $24.0$ mag and $24.6$ mag, respectively.
 
     After selecting the matched synthetic galaxies with primary detection and 
-    clean photometry (see Appendix \ref{app:qc} for details), we have ${\sim}30000$
+    clean photometry (see Appendix \ref{app:qc} for details), we have ${\sim}30,000$
     galaxies in each \tract{} for comparison.  
-    Among these objects, only $<1$\% is misclassified as point sources by \hscpipe{}
-    in the good seeing \tract{}.  
-    However, for the bad seeing one, the fraction increases to $4$\%.  
+   \hscpipe{} misclassifies less than $1$\% of these objects as point sources 
+    in the good-seeing \tract{}.  
+    However,   \hscpipe{} misclassifies more objects ($4$\%) in the bad-seeing \tract{}.
     The median input magnitude for these misclassified sources is ${\sim}24.9$ mag 
-    in $i$-band, significantly fainter than the median of others.  
-    We will further discuss this in Section \ref{ssec:sg}.
+    in $i$-band, significantly fainter than the median of other sources.  
+    We further discuss this in Section \ref{ssec:sg}.
 
     We also use $b>0.1$ to define samples of highly blended galaxies.
-    Due to the extended nature, the distributions of $b$ for synthetic galaxies are 
-    very different from stars, and skew toward higher values (especially for the 
+    Due to the extended nature of the galaxies, the $b$ distributions for synthetic galaxies are 
+    very different from the  $b$ distributions for synthetic stars, and they also skew toward higher values (especially for the 
     bad-seeing \tract{}). 
-    About ${\sim}7$--$9$\% of synthetic galaxies are highly blended by this standard.
+    About ${\sim}7$--$9$\% \susan{Delete the approximately symbol when you use "About"; it's redundant.} of synthetic galaxies are highly blended by this standard.
     The fraction is only slightly higher in the bad-seeing \tract{}, and the 
     $g$-band has the highest fraction of highly blended galaxies. 
-    We highlight the highly blended ones in comparisons, and there are more relevant 
+    We highlight the highly blended ones in comparisons, and there are other relevant 
     discussions in Section \ref{ssec:blendedness}.
@@
     ($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec). 
-    The photometric quality of these galaxies is very challenging, and also crucial
-    to several key scientific goals of the HSC survey. 
-    At the same time, these samples are unable to provide enough amounts of 
-    bright or large galaxies to test. 
-    We will supplement results for these galaxies using better samples for them 
+    It is very challenging to obtain good photometric quality of these galaxies, which is crucial
+    to achieving several key scientific goals of the HSC survey. 
+    The selected samples do not provide enough bright or large galaxies to test. 
+    Therefore, we will supplement results for these galaxies using better samples 
     in the future.
@@
 
-    In Fig \ref{fig:cmodel_sn}, we first show the relations between the input 
+    In Fig \ref{fig:cmodel_sn}, we first show the relation between the input 
     magnitudes and the \s2n{} of the synthetic galaxies estimated by the ratio 
@@
     Since these galaxies are extended objects, the \s2n{} here should be treated 
-    as the average \s2n{} which is different from the \s2n{} of stars using PSF 
+    as the average \s2n{}, which is different from the \s2n{} of stars using PSF 
     photometry.
 
-    We still use $i$- and $g$-band as examples. 
-    Comparing to the similar figure for stars, the most obvious difference is that
-    at fixed input magnitude, the \s2n{} distribution of galaxies show much larger
-    scatter than stars.  
-    At the same total flux, galaxy can have different size and shape, and 
-    naturally leads to differences in their peak and average \s2n{}.  
+    As we did for stars, we use $i$- and $g$-bands as examples for galaxies. 
+    The most obvious difference between the  \s2n{} distribution for stars and the  \s2n{} distribution for galaxies is that
+    at fixed input magnitude, the galaxy \s2n{} distribution shows much larger
+    scatter.  
+    At the same total flux, a galaxy can have a different size and shape, which 
+    naturally leads to differences in the galaxy's peak and average \s2n{}.  
     This also makes it difficult to have a clear definition of ``detection limit'' 
@@
     For $i$-band, the typical \s2n{} for synthetic galaxies at the magnitude limit 
-    of our sample ($25.2$ mag) is ${\sim}20$, but the low-\s2n{} tail has already 
-    reached to the \s2n{}$=5$ boundary.  
+    of our sample ($25.2$ mag) is ${\sim}20$, but at that limit the low-\s2n{} tail has  
+    reached the \s2n{}$=5$ boundary.  
     This suggests that, although HSC Wide can detect galaxies as faint as 
-    $i{\sim}26.0$ mag, the sample will become highly incomplete. 
-    Furthermore, it can also introduce bias into the selection as galaxies with 
-    certain structural properties are harder to detect than others. 
-    Users of HSC survey data who want to select flux-limited samples of galaxies,
-    or intend to study the population of faint (e.g. high-$z$) galaxies should
+    $i{\sim}26.0$ mag, the sample at that magnitude will be significantly incomplete. 
+    Furthermore, the magnitude limit can also introduce selection bias because galaxies with certain structural properties are harder to detect than others. 
+    HSC survey data users who want to select flux-limited samples of galaxies,
+    or intend to study the population of faint (e.g., high-$z$) galaxies should
     keep this in mind.
 
-    Similar to the synthetic stars, worse seeing condition can also lead to 
-    noticeable decrease of \s2n{} at the same magnitude (see the figure for
+    Similar to the synthetic stars, the worse the seeing condition, the more 
+    we noticed a decrease in \s2n{} at the same magnitude (see the figure \susan{cite actual figure number.} for
     $i$-band). 
@@
     In Fig \ref{fig:cmodel_mag}, we illustrate the photometric uncertainties of the 
-    \cmodel{} magnitudes in each band using the same format with 
+    \cmodel{} magnitudes in each band using the same format as 
     Fig \ref{fig:psf_mag}.
@@
     down to $i_{\mathrm{Input}}=25.2$ mag. 
-    Comparing to the qualities of PSF photometry for stars, the magnitude differences
-    of \cmodel{} show much larger scatter. 
+    Compared to the qualities of PSF photometry for stars, the magnitude differences
+    of \cmodel{} show much larger scatter for galaxies. 
     Given the diversity of properties of these galaxies and the complexities in the 
@@
 
-    In $i$-band, the median flux uncertainties of \forced{} \cmodel{} is ${\sim}7$\% 
+    In $i$-band, the median flux uncertainty of the \forced{} \cmodel{} is ${\sim}7$\% 
     in the good-seeing \tract{} at $i_{\mathrm{Input}}{\sim}20.0$ mag, 
@@
     at ${\sim}11$\% level. 
-    For the bad-seeing \tract{}, the performance is very similar in $i$-band. 
+    For the bad-seeing \tract{} in $i$-band, the performance is very similar. 
     From $i_{\mathrm{Input}}{\sim}20.0$ to $25.0$ mag, the median magnitude difference
@@
     \minus{}$0.005$ mag, which suggests that \forced{} \cmodel{} photometry is 
-    unbiased down to very faint end. 
+    unbiased down to the very faint end. 
     It is worth noting that the photometric uncertainties estimated by \synpipe{}
-    are significantly larger than the fiducial error from \hscpipe{} that does not 
-    take into account the systematically uncertainties involved in the modeling 
+    are significantly larger than the fiducial error from \hscpipe{}, which does not 
+    take into account the systematic uncertainties involved in the modeling 
     fitting process. 
-    Although the synthetic galaxies here are described by the simple single-\ser{} 
-    model, \cmodel{} algorithm can only approximate them to certain accuracy, 
+    Although the synthetic galaxies in our sample are described by the simple single-\ser{} 
+    model, the\cmodel{} algorithm can only approximate them to a certain accuracy, 
     especially when the noise level, deblending uncertainty, and priors of model 
     parameters are considered. 
-    Given that the real galaxies are more complex in structural details, these 
+    Given that real galaxies are more complex in structural details, these 
     uncertainties should be treated as lower limits.
@@
     filters. 
-    For $g$, $r$, and $z$-band, the photometric uncertainties are very similar to 
-    the ones for $i$-band between $20.0$ to $25.0$ mag. 
-    The \forced{} \cmodel{} magnitudes are also unbiased for these 3 filters 
+    For $g$-, $r$-, and $z$-bands, the photometric uncertainties are very similar to 
+    the ones for $i$-band between $20.0$ and $25.0$ mag. 
+    The \forced{} \cmodel{} magnitudes are also unbiased for these three filters 
     across the entire input magnitude range. 
-    The uncertainties for $y$-band are slightly large, range from 9-17\% in the 
+    The uncertainties for $y$-band are slightly larger, ranging from 9\% to 17\% in the 
     same magnitude bins. 
-    In addition, \forced{} \cmodel{} tends to overestimate the total flux in $y$-band
+    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in $y$-band
     at $y_{\mathrm{Input}}>24.0$ mag. 
@@
     mag at 25.0 mag.  
-    Both worse seeing condition and higher background noise level can make it more 
-    difficult to detect faint object on $y$-band image.
+    Both a worse seeing condition and a higher background noise level can make it more 
+    difficult to detect a faint object on a $y$-band image.
     At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} in $y$-band
@@
 
-    As mentioned, the statistics for brighter galaxies are very uncertain due to 
+    As mentioned, the statistics for brighter galaxies are very uncertain due to the
     small sample size. 
@@
     This problem is confirmed via comparing with more carefully derived total fluxes 
-    for bright galaxies (e.g. \citealt{HSCDR1}, Huang\etal in prep.). 
-    It relates to the known issues of \hscpipe{} (e.g. over-deblend around bright 
-    objects; inappropriate weighting of priors in \cmodel{}), but it may also suggest
+    for bright galaxies (e.g., \citealt{HSCDR1}, Huang\etal in prep.). 
+    It relates to the known issues of \hscpipe{} (e.g., \hscpipe{}over-deblends around bright objects; inappropriately weights priors in \cmodel{}); but it may also suggest
     that, at the imaging depth of HSC, assumptions in \cmodel{} are no longer the 
-    best choice in modeling these galaxies (e.g. for massive elliptical galaxies; 
+    best choice in modeling these galaxies (e.g., for massive elliptical galaxies; 
     see Huang\etal in prep.~for more details).
@@
     of photometric uncertainty in all five bands.  
-    Meanwhile, the contrast between relative isolated and highly blended galaxies 
-    in photometric performance is no longer as staggering as the one for synthetic
+    Meanwhile, the contrast between relatively isolated and highly blended galaxies 
+    in photometric performance is not as staggering as the one for synthetic
     stars (Fig \ref{fig:psf_mag}).
@@
     We highlight the differences between \forced{} and \unforced{} \cmodel{} 
-    photometry in $g$- and $y$-band in Fig \ref{fig:cmodel_diff}.
+    photometry in $g$- and $y$-bands in Fig \ref{fig:cmodel_diff}.
     The only noticeable difference is for galaxies brighter than $24.0$ mag in 
-    $g$-band, their \forced{} \cmodel{} magnitudes are systematically brighter than 
+    $g$-band; their \forced{} \cmodel{} magnitudes are systematically brighter than 
     the \unforced{} ones.
@@
     In Fig \ref{fig:cmodel_color}, we demonstrate the accuracies of \forced{} $(g-i)$
-    and $(i-y)$ \cmodel{} colors in the same format for synthetic stars 
+    and $(i-y)$ \cmodel{} colors in the same format used for synthetic stars 
     (Fig \ref{fig:psf_color}).
@@
     synthetic galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag. 
-    For $(g-i)$ colors, average uncertainty around $i_{\mathrm{Input}}{\sim}21.0$ mag 
+    For $(g-i)$ colors, the average uncertainty around $i_{\mathrm{Input}}{\sim}21.0$ mag 
     is ${\sim}0.04$ mag.
@@
     The performance of \forced{} \cmodel{} color does not show dependence on seeing
-    condition, and is unbiased across the ranges for input total magnitude and color.
+    condition, and it is unbiased across the ranges for input total magnitude and color.
     The only noticeable feature is that the $(i-y)$ color at 
     $i_{\mathrm{Input}}>24.0$ is slightly overestimated. 
-    As mentioned above, this is not surprise given the shallower imaging depth of 
+    As mentioned above, this is not surprising given the shallower imaging depth of  the
     $y$-band.    
     At the same time, high blendedness of synthetic galaxies can still increase the 
-    uncertainties of the color and bias the color measurements.
-    The highly blended galaxies on average show slightly bluer $(g-i)$ 
-    colors and redder $(i-y)$ colors than the input values.
-
-    Similar to Fig \ref{fig:psf_cdist}, we also compare the color--color distributions 
+   color uncertainties and bias the color measurements.
+    The highly blended galaxies on average show slightly bluer  $(g-i)$ colors
+     and redder  $(i-y)$ colors  than the input values.
+
+    Similar to the star comparison in Fig \ref{fig:psf_cdist}, we also compare the color--color distributions 
     of the input and output \forced{} \cmodel{} values in Fig \ref{fig:cmodel_cdist}. 
-    The general distributions of colors are well recovered despite the accuracy is 
-    not as good as the one for stars, especially on the $(i-z)$ v.s. $(z-y)$ plane. 
-    It is expected given the narrow dynamical ranges of these colors among red filters.
+    The general color distributions are well recovered despite the fact that the galaxy accuracy is 
+    not as good as the accuracy for stars, especially on the $(i-z)$ vs. $(z-y)$ plane. 
+    That result is expected given the narrow dynamical ranges of these colors among red filters.
     The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$ 
-    colors at the very ``blue'' end, while overestimate the $(i-y)$ color at very 
+    colors at the very ``blue'' end, while overestimating the $(i-y)$ color at the very 
     red end.
 
-    In the end, we should point out that we assume constant color for the entire galaxy.  
-    In reality, different colors for individual components and smooth color gradient 
-    can really complicated the situation, hence the uncertainties of \cmodel{} colors 
+   We should point out that we assume constant color for the entire galaxy.  
+    In reality, different colors for individual components and a smooth color gradient 
+    can complicate the situation; hence, the uncertainties of \cmodel{} colors 
     here should be considered as lower limits.
@@
     \caption{
-        Astrometric accuracy for synthetic star (\textbf{left}) and galaxy
+        Astrometric accuracy for a synthetic star (\textbf{left}) and a galaxy
         (\textbf{right}) via the differences in R.A and Dec between the input
@@
         Hexagonal bins (filled histogram) and contours (solid-line histogram) are for
-        the synthetic objects from \tracts{} with good and bad seeing conditions.
+        the synthetic objects from \tracts{} with good and bad seeing conditions, respectively.
         $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.
@@
     \caption{
-        Illustrates the problems with current star--galaxy separation method in
-        \hscpipe{} which is based on the magnitude difference between the PSF and
+        Problems with the current  \hscpipe{}star--galaxy separation method, which is based on the magnitude difference between the PSF and
         \cmodel{} photometry.
-        \textbf{Left} plot is for the synthetic stars.
+       The plot on the \textbf{left} (a) illustrates distributions for the synthetic stars.
         Hexagonal bins and filled histogram show distributions of correctly classified
-        synthetic stars in the good seeing \tract{}.
+        synthetic stars in the good-seeing \tract{}.
         The scatter plot (dashed-line histogram) and contour (solid-line histogram)
         show distributions of synthetic stars that are misclassified as extended
-        objects in \tracts{} with bad and good seeing conditions.
-        \textbf{Right} one is for synthetic galaxies.
-        Here the hexagonal bins (filled histogram) and contours (solid-line histogram)
-        are for galaxies from good and bad seeing \tracts{}.
+        objects in \tracts{} with bad and good seeing conditions, respectively.
+        The plot on the \textbf{right} (b) illustrates distributions for synthetic galaxies.
+        Hexagonal bins (filled histogram) and contours (solid-line histogram)
+        are for galaxies from good- and bad-seeing \tracts{}, respectively.
         The scatter plot and dashed-line histogram are for synthetic galaxies that are
@@
     \caption{
-        Shows the relationships between the $\log(\mathrm{Blendedness})$ parameter
-        and the photometric accuracies for synthetic stars (\textbf{upper row}) and
-        galaxies (\textbf{lower row}).
-        \textbf{Left} column is for uncertainties of PSF or \cmodel{} magnitude,
-        and the \textbf{right} one is for uncertainties of $(g-i)$ color.
-        Hexagonal bins and contours show results for good and bad seeing
-        \tracts{}.
-        $\log(\mathrm{Blendedness}) = -1.0$ is marked using vertical dashed line.
+        The relation between the $\log(\mathrm{Blendedness})$ parameter
+        and the photometric accuracies for synthetic stars (\textbf{upper row}, a and b) and
+        galaxies (\textbf{lower row}, c and d) .
+       The \textbf{left} column (a and c) is for uncertainties of PSF or \cmodel{} magnitude,
+        and the \textbf{right} column (b and d) is for uncertainties of $(g-i)$ color.
+        Hexagonal bins and contours show results for good- and bad-seeing
+        \tracts{}, respectively.
+        $\log(\mathrm{Blendedness}) = -1.0$ is marked using a vertical dashed line.
         }
@@
     \caption{
-        Shows the accuracy of the weighted axis ratio measurements for synthetic
+        Accuracy of the weighted axis ratio measurements for synthetic
         galaxies using \cmodel{} photometry.
-        \textbf{Left} shows the relation between the input $(b/a)$ and the
+      The  \textbf{left} (a) plot shows the relation between the input $(b/a)$ and the
         uncertainties of $(b/a)$ estimates.
-        \textbf{Right} shows the relation between input magnitude of synthetic galaxy
+        The \textbf{right} (b) plot shows the relation between input magnitude of a synthetic galaxy
         and the $(b/a)$ uncertainties.
@@
 
-    In this section, we briefly discuss a few other issues of \hscpipe{} that relates 
-    to astrometric calibration, star-galaxy separation, and measurements of galaxy 
-    shape to demonstrate the ranges of topics can be tested by \synpipe{}
+    In this section, we briefly discuss a few other  \hscpipe{} aspects that relate 
+    to astrometric calibration, star-galaxy separation, blendedness and photometric errors, and galaxy shape measurements to demonstrate the range of topics that can be tested with \synpipe{}.
 
@@
 
-    For \synpipe{} test, we inject synthetic objects to single \visit{} images using 
-    the less accurate, initial astrometric calibration. 
-    During the image stacking step, the joint calibration process will improve the 
+    For a \synpipe{} test, we inject synthetic objects to single-\visit{} images using 
+    the less accurate initial astrometric calibration. 
+    During the image stacking step, the joint calibration process  improves the 
     astrometric solutions. 
-    Therefore the differences between the input and output coordinates from \synpipe{}
-    can help understand the systematic effect of this step.
+    Therefore, the differences between the input and output coordinates from \synpipe{}
+    can help us understand the systematic effect of the image stacking step.
 
@@
 
-    As we already mentioned, star--galaxy separation is important for cosmology survey,
-    and becomes increasingly difficult at very faint magnitude ($i<24.0$ mag). 
+    Star--galaxy separation is an important aspect of a cosmology survey,
+    and it becomes increasingly difficult at very faint magnitude ($i<24.0$ mag). 
     In \hscpipe{}, the star--galaxy classification primarily depends on the extendedness 
-    value that is measured by the magnitude difference between PSF and \cmodel{} 
+    value, which is measured by the magnitude difference between PSF and \cmodel{} 
     photometry in $i$-band. 
-    For more details about this algorithm, please see Section 4.9.9 in Bosch\etal 
-    (in prep.).
+    For more details about this algorithm, please see Bosch\etal 
+    (in prep.). \susan{Suggest you not include a section number for a document in preparation; section numbers can change before a text is published. }
 
@@
     via comparing the input magnitude with the difference between PSF and \cmodel{} 
-    magnitudes for both synthetic stars and galaxies, and highlight the distributions 
+    magnitudes for both synthetic stars and galaxies, and we highlight the distributions 
     for misclassified objects. 
-    As described in earlier sections, $>20$\% of synthetic stars at 
-    $i_{\mathrm{Input}}>23.0$ mag is misclassified as extended objects, while only a 
+    As described above, more than $20$\% of synthetic stars at 
+    $i_{\mathrm{Input}}>23.0$ mag are misclassified as extended objects, while only a 
     tiny fraction of faint synthetic galaxies ($i_{\mathrm{Input}}>24.0$) are 
@@
     This confirms that the current star--galaxy classification strategy in \hscpipe{}
-    results in galaxy sample with \textbf{high completeness} and star sample 
+    results in a galaxy sample with \textbf{high completeness} and star sample 
     with \textbf{high purity}.
 
-    It it also easy to notice that seeing condition strongly modify the distributions 
-    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$, where worse seeing clearly make it 
+    It is also clear that seeing condition strongly modifies the distributions 
+    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$, where worse seeing conditions clearly make it 
     more difficult to separate star and galaxy.  
-    This implies that the completeness/purity of star and galaxy sample at faint end
-    may depend on seeing, which deserve the attention of HSC users who care about 
-    these properties.
-
-    In the next data release, \hscpipe{} will include a better star--galaxy classifier
-    that is based on Machine Learning method takes the shape and color information 
-    into account. 
+    This implies that the completeness or purity of the galaxy or star sample at the faint end may depend on seeing; therefore, seeing condition deserves the attention of HSC users who care about these properties.
+
+    In the next data release, \hscpipe{} will include a better star--galaxy classifier, which will be based on a machine learning method that takes shape and color information into account.
 We will test its improvement using \synpipe{} in the future.
@@
 
-    For both PSF and \cmodel{} magnitude, we can see clear trends that high-blendeness
-    ($b>0.05$ or $0.1$) objects have systematically underestimated total fluxes. 
+    For both PSF and \cmodel{} magnitude distributions, we can see clear trends that total fluxes are systematically underestimated for highly blended
+    ($b>0.05$ for stars or $0.1$ for galaxies) objects. 
     This effect is particularly strong for stars. 
-    As for colors, higher blendedness still result in higher uncertainties for both 
-    stars and galaxies, but the trends are different. 
-    For stars, highly blended ones have clearly overestimated $(g-i)$ colors, and the 
-    highly blended galaxies seem to have bluer $(g-i)$ colors than the true values.
-
-    These blendedness-related uncertainties are not included in the photometric errors
-    released by \hscpipe{}.  
-    We therefore remind the HSC users of treating the highly blended object with 
+    As for colors, higher blendedness still results in higher uncertainties for both 
+    stars and galaxies, but the trends are different for each. 
+    Highly blended stars have clearly overestimated $(g-i)$ colors, and the 
+    highly blended galaxies seem to have  $(g-i)$ colors that are bluer than the true values.
+
+    These blendedness-related uncertainties are not included in the photometric errors released by \hscpipe{}.  
+    We therefore remind the HSC users to treat the highly blended object with 
     greater caution.
@@
 
-    In SDSS, the structural parameters like size and shape from \cmodel{} are often 
+    In SDSS,  structural parameters like size and shape from \cmodel{} are often 
     used to study the evolution galaxies. 
-    Although the \cmodel{} in \hscpipe{} follows very similar algorithm, its primary 
+    Although the \cmodel{} in \hscpipe{} follows a very similar algorithm, its primary 
     goal now is to provide accurate and consistent magnitude and color in all five 
     HSC filters for a vast majority of faint, small galaxies.  
-    To improve the stability of \cmodel{} for these low \s2n{} and barely-resolved 
-    galaxies, it utilizes Bayesian priors on radius and axis ratio that strongly 
-    favour these galaxies. 
+    To improve the stability of \cmodel{} for these low-\s2n{} and barely resolved 
+    galaxies, \hscpipe{} uses Bayesian priors on a radius and axis ratio that strongly 
+    favors these galaxies. 
     However, the current implementation of these priors has a flaw that leads to 
@@
     In Fig \ref{fig:galaxy_ba}, we demonstrate this issue using the difference between 
-    the \cmodel{} axis ratio and the input values as example.
+    the \cmodel{} axis ratio and the input values as an example.
     Here, $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ is a combination of the 
-    axis ratios estimated by the exponential and de~Vaucouleurs models weighted by 
-    their flux ratio.
-
-    During the investigation, we notice that one of the problem relates to the 
-    \texttt{usePixelWeight} configuration of \cmodel{} that decides whether to 
+    axis ratios estimated by the exponential and de Vaucouleurs models weighted by their flux ratio.
+
+    During the investigation, we noticed that one of the problems relates to the \cmodel{} \texttt{usePixelWeight} configuration, which decides whether to 
     use per-pixel variances as weights in the nonlinear fit. 
     By default, \hscpipe{} chooses \texttt{usePixelWeight}$=$\texttt{False}. 
-    As one can see, this leads to significantly overestimated axis ratio for almost 
-    all galaxies with $i_{\mathrm{Input}}>21.5$ mag\footnote{It also leads to 
+    As one can see, this leads to a significantly overestimated axis ratio for almost 
+    all galaxies with $i_{\mathrm{Input}}>21.5$ mag\footnote{It also leads to an
     underestimated half-light radius for these galaxies.}.
@@
     \texttt{usePixelWeight}$=$\texttt{True}, and this change clearly mitigates
-    this problem. 
-    Now $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ can provide unbiased estimation 
-    of axis ratio for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
-
-    For the current HSC data release, we warn the users against using the \cmodel{} 
-    size and shape to study galaxy with $i_{\mathrm{Input}}>21.5$. 
+    the problem. When we use \texttt{usePixelWeight}$=$\texttt{True},
+     $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ can provide an unbiased axis ratio estimation 
+    for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
+
+    For the current HSC data release, we warn users against using the \cmodel{} 
+    size and shape to study a galaxy with $i_{\mathrm{Input}}>21.5$. 
     At the same time, \synpipe{} will try to help \hscpipe{} improve the details 
-    of the \cmodel{} so that it can provide more useful structural information without
-    hurting its photometric performance.
+    of the \cmodel{} so that it can provide more useful structural information without hurting its photometric performance.
 
@@
     %% Short summary
-    The on-going HSC survey just had its first public data release, and is still
-    producing increasingly larger amount of high-quality imaging data.
+    In February 2017, the HSC survey made its first public data release, and the survey continues to
+    produce increasingly larger amounts of high-quality imaging data.
     To help achieve the designed goals of the survey and facilitate scientific
-    outputs, we develop \synpipe{}, a flexible framework that is based on the
-    \hscpipe{} to exam the data reduction process and check the accuracy of all the
-    pipeline outputs.
-    \synpipe{} injects synthetic stars and galaxies to the desired locations on the
+    outputs, we developed \synpipe{}, a flexible framework that is based on 
+    \hscpipe{}, to examine the data reduction process and check the accuracy of all the HSC pipeline outputs.
+    \synpipe{} injects synthetic stars and galaxies into the desired locations on the
     single-\visit{} images with the help of the original astrometric and
@@
     to an extent that many subtle systematical effects can be taken into
-    consideration, which is helpful for the outstanding scientific goals of the HSC
+    consideration, which is helpful for achieving the outstanding scientific goals of the HSC
     survey.
-    In this work, we choose two \tracts{} in the HSC/Wide layer with
-    representative seeing conditions (good/bad) to test the general behaviors of HSC
+    In this work, we choose two \tracts{} in the HSC Wide layer with
+    representative seeing conditions (good and bad) to test the general behaviors of HSC
     photometry for both stars and galaxies.
 
-    From these tests, we find:
+    From these tests, we find the following:
 
@@
         \item The \forced{} PSF and \cmodel{} photometry are robust against different
-            seeing conditions, despite that worse seeing leads to lower
+            seeing conditions, despite the fact that worse seeing leads to a lower
             $\mathrm{S}/\mathrm{N}$ at fixed input magnitude.
 
-        \item High blendedness ($b>0.1$) impacts the accuracy of both PSF and \cmodel{}
+        \item High blendedness ($b>0.1$) \susan{This is the value you've given for highly blended galaxies; should the text in the parentheses read ($b>0.1$ for galaxies and $b>0.05$ for stars)}impacts the accuracy of both PSF and \cmodel{}
             photometry, especially for stars.
             For highly blended stars, the \forced{} PSF photometry on average
-            overestimate the magnitudes of stars by 0.1–-0.2 mag.
+            overestimates the magnitudes of stars by 0.1–-0.2 mag.
             For galaxies, high-blendedness typically adds an additional 0.05 mag
@@
 
-    Meanwhile, we also notice a few issues in the current \hscpipe{}:
+    We also notice a few issues in the current \hscpipe{}:
 
@@
 
-        \item The performance of current star--galaxy separation algorithm in \hscpipe{}
-            is not perfect, especially at faint magnitude end and under poor seeing
-            condition.
+        \item The performance of the current star--galaxy separation algorithm in \hscpipe{}
+            is not perfect, especially at the faint magnitude end and under poor seeing
+            conditions.
             The fraction of stars that are misclassified as extended objects is still
@@
 
-        \item The \cmodel{} setting right now (\texttt{usePixelWeights=True}) results
+        \item The nominal \cmodel{} setting  (\texttt{usePixelWeights=True}) results
             in very biased estimates of shape and size for galaxies, especially for the
-            relative faint ones.
-            The axis ratio of galaxy using \cmodel{} is highly overestiamted while
+            relatively faint ones.
+            The axis ratio of a galaxy using \cmodel{} is highly overestimated, while
             the effective radius is underestimated.
-            We show that, using \texttt{usePixelWeights=True} instead and significantly
-            improve this situation.
-            However, it may impact the accuracy of deblender, which we will test in the
-            future.
+            We show that we can significantly improve the result if we use \texttt{usePixelWeights=True} instead.
+            However, that choice may impact the accuracy of the deblender, which we will test in the future.
 
@@
     The HSC collaboration is working on improving these issues in the future version
-    of \hscpipe{} and the following data release.
-    Meanwhile, we suggest the users of HSC data to keep these caveats in mind.
+    of \hscpipe{} and the subsequent data release.
+    Meanwhile, we suggest that HSC data users keep these caveats in mind.
 %% ------------------------------------------------------------------------------------ %%
@@
     %% Other applications
-    Although we mainly focus on the general behaviors of photometric measurements here,
-    \synpipe{} is quite flexible and has plenty of other applications for any HSC
+    Although we mainly focus on the general behaviors of photometric measurements in this study,
+    \synpipe{} is quite flexible and has many other applications for any HSC
     dataset.
-    For instance, in a following paper, Murata\etal (in prep.) uses \synpipe{} to test
-    the impacts of extremely blended objects on the WL measurements.
-    Also, \citep{Niikura2017} applies \synpipe{} to the high-cadence HSC observations
-    of M31 to help the search of interesting microlensing events.
-    At this moment, it is also being used to estimate the completeness of the selections 
-    for high-$z$ Lyman-break galaxies (LBG) and Lyman- $\alpha$ emitters 
-    (Ono\etal in prep.; Konno\etal in prep), check the dependence of the detection and 
+    For instance,  Murata\etal (in prep.) uses \synpipe{} to test
+    the impacts of extremely blended \susan{Quantify? Is "extremely blended" more blended than "highly blended"?} objects on the WL measurements.
+    Also, \citep{Niikura2017} applies \synpipe{} to the high-cadence M31 HSC observations
+    to help users search for interesting microlensing events.
+  \synpipe{} is also currently being used to estimate the completeness of the selections 
+    for high-$z$ LBG and Lyman- $\alpha$ emitters 
+    (Ono\etal in prep.; Konno\etal in prep.), check the dependence of the detection and 
     completeness of high-$z$ LBG pairs on the pair separation (Harikane\etal in prep.),
-    identify low surface brightness dwarf galaxies (Greco\etal in prep),
-    and test photometric and WL measurements around nearby clusters (Chiu\etal in prep).
+    identify low surface--brightness dwarf galaxies (Greco\etal in prep.),
+    and test photometric and WL measurements around nearby clusters (Chiu\etal in prep.).
 
     %% Caveats
-    In the end, it is worth brief discussing the limitations of the current \synpipe{}:
+    The limitations of the current \synpipe{} include the following:
 
@@
             Unfortunately, \synpipe{} now takes the original background subtraction on
-            the single-\visit{} image for granted, hence lacks the capability to
+            the single-\visit{} image for granted; hence, it lacks the capability to
             test or help improve this problem.
 
-        \item Right now, \synpipe{} simply adopts the PSF measured by \hscpipe{} and
-            use it for model of point source and PSF convolution for galaxy.
-            Hence it can not be used to test how the uncertainty of the PSF modeling
+        \item  \synpipe{} simply adopts the PSF measured by \hscpipe{} and
+            uses it as a model of point source and PSF convolution for a galaxy.
+            Hence, it cannot be used to test how the uncertainty of the PSF modeling
             affects the photometry and shape measurements.
-            This could be important for regions with exquisite seeing that makes the
+            This could be important for regions with exquisite seeing \susan{Quantify "exquisite"? Is it better than "good" or "better" seeing? Suggest using consistent adjectives.}  that makes the
             PSF modeling difficult, and for accurate WL measurements.
 
-        \item \synpipe{} now works in ``unit'' of \visit{} for single exposure
-            test, and \tract{} for test of \coadd{} images.
-            In case of tests that focus on specific regions that are much smaller than
-            the size of \visit{} or \tract{} (e.g. quality of photometry
-            around rich galaxy clusters), the usage of \synpipe{} often leads to
+        \item \synpipe{} works in a ``unit'' of \visit{} for a single-exposure
+            test, and uses a \tract{} to test \coadd{} images.
+            In the case of tests that focus on specific regions that are much smaller than
+            the size of a \visit{} or a \tract{} (e.g., quality of photometry
+            around rich galaxy clusters), using \synpipe{} often leads to
             low efficiency.
@@
     %% Future developments
-    Right now, both \hscpipe{} and \synpipe{} still undergo active development,
-    and \synpipe{} will update accordingly to provide photometric benchmark for
-    each data release of HSC survey, and help \hscpipe{} improve.
+    Both \hscpipe{} and \synpipe{} are currently undergoing active development. The plan is to update \synpipe{} to provide a photometric benchmark for
+    each HSC survey data release, which will help \hscpipe{} improve.
     At the same time, we are also working on improving the efficiency of \synpipe{}.
-    Since subtle effects involved in the image stacking process are not the concerns
-    of many topics, we will update \synpipe{} so that it can directly inject
-    synthetic objects to the \coadd{} images and speed up these tests.
+    Since many survey data users are not concerned with the subtle effects involved in the image stacking process, we will update \synpipe{} so that it can directly inject synthetic objects to the \coadd{} images and speed up these tests.
 
@@
     Japan and Taiwan, and Princeton University.
-    The HSC instrumentation and software were developed by the National Astronomical
-    Observatory of Japan (NAOJ), the Kavli Institute for the Physics and Mathematics of
-    the Universe (Kavli IPMU), the University of Tokyo, the High Energy Accelerator
-    Research Organization (KEK), the Academia Sinica Institute for Astronomy and
-    Astrophysics in Taiwan (ASIAA), and Princeton University.
-    Funding was contributed by the FIRST program from Japanese Cabinet Office, the
-    Ministry of Education, Culture, Sports, Science and Technology (MEXT), the Japan
-    Society for the Promotion of Science (JSPS), Japan Science and Technology Agency
-    (JST), the Toray Science  Foundation, NAOJ, Kavli IPMU, KEK, ASIAA, and Princeton
-    University.
+    The HSC instrumentation and software were developed by National Astronomical
+    Observatory of Japan (NAOJ), Kavli Institute for the Physics and Mathematics of
+    the Universe (Kavli IPMU), University of Tokyo, High Energy Accelerator
+    Research Organization (KEK) in Japan,  Academia Sinica Institute for Astronomy and
+    Astrophysics  (ASIAA) in Taiwan, and Princeton University in the United States.
+    Funding was contributed by the FIRST program from Japanese Cabinet Office; Ministry of Education, Culture, Sports, Science and Technology (MEXT); Japan
+    Society for the Promotion of Science (JSPS); Japan Science and Technology Agency
+    (JST); Toray Science  Foundation; NAOJ; Kavli IPMU; KEK; ASIAA; and Princeton University.
 
@@
     % Pan-STARRS1 part
-    The Pan-STARRS1 Surveys (PS1) have been made possible through contributions of the
-    Institute for Astronomy, the University of Hawaii, the Pan-STARRS Project Office,
-    the Max-Planck Society and its participating institutes, the Max Planck Institute
-    for Astronomy, Heidelberg and the Max Planck Institute for Extraterrestrial Physics,
-    Garching, The Johns Hopkins University, Durham University, the University of
-    Edinburgh, Queen's University Belfast, the Harvard-Smithsonian Center for Astrophysics,
-    the Las Cumbres Observatory Global Telescope Network Incorporated, the National
-    Central University of Taiwan, the Space Telescope Science Institute, the National
+    Pan-STARRS1 Surveys (PS1) have been made possible through contributions of 
+    Institute for Astronomy, University of Hawaii, Pan-STARRS Project Office,
+    Max-Planck Society and its participating institutes (Max Planck Institute
+    for Astronomy, Heidelberg, and Max Planck Institute for Extraterrestrial Physics,
+    Garching), Johns Hopkins University, Durham University, University of
+    Edinburgh, Queen's University Belfast, Harvard-Smithsonian Center for Astrophysics,
+    Las Cumbres Observatory Global Telescope Network Incorporated,  National
+    Central University of Taiwan, Space Telescope Science Institute,  National
     Aeronautics and Space Administration under Grant No.
-    NNX08AR22G issued through the Planetary Science Division of the NASA Science
-    Mission Directorate, the National Science Foundation under Grant No. AST-1238877,
-    the University of Maryland, and Eotvos Lorand University (ELTE) and the Los Alamos
+    NNX08AR22G issued through Planetary Science Division of NASA Science
+    Mission Directorate, National Science Foundation under Grant No. AST-1238877,
+    University of Maryland, Eötvös Loránd University (ELTE), and Los Alamos
     National Laboratory.
@@
     {\texttt{SciPy}},
-        an open source scientific tools for Python (\citealt{SciPy};
+        an open source scientific tool for Python (\citealt{SciPy};
         \url{http://www.scipy.org/});
@@
         a 2-D plotting library for Python (\citealt{Matplotlib};
-        \url{http://matplotlib.org/});
+        \url{http://matplotlib.org/}); and
     {\texttt{scikit-learn}},
-        a machine-learning library in Python (\citealt{scikit-learn};
-        \url{http://scikit_learn.org/}).
+        a machine learning library in Python (\citealt{scikit-learn};
+        \url{http://scikit_learn.org/} \susan{I think correct URL is http://scikit-learn.org/ (hyphen, not underscore.}).
 
@@
 %% ------------------------------------------------------------------------------------ %%
+\susan{Susan did not review bibliographic citations.}
 \begin{thebibliography}{}
@@
 
-    To select synthetic stars and galaxies from the results to test the photometry,
-    we apply some basic quality control cuts here.
+    To select synthetic stars and galaxies from the HSC survey data in order to test the photometry,
+    we apply some basic quality control cuts.
 
     The HSC survey defines the full--depth \& full--color regions (\texttt{FDFC}) to
-    make sure the data used for science reach the expected number of exposures in each
+  ensure the data used for science reach the expected number of exposures in each
     band
     ($\mathtt{(\#gri\ \geq\ 4)\ and\ (\#yz\ \geq\ 6)\ and\ (Limiting\ imag> 25.6)}$).
-    And, the two \tracts{} we used in this work are almost entirely covered in
-    the \texttt{FDFC} region so we do not apply this cut.
-    We apply the following cuts to the matched synthetic objects"
+    Since the two \tracts{} we used in this work are almost entirely covered in
+    the \texttt{FDFC} region, we did not apply this cut.
+    We did apply the following cuts to the matched synthetic objects.
 
@@
 
-    To evaluate at what degree an object is blended with others, \hscpipe{} introduces
+    To evaluate the degree to which an object is blended with others, \hscpipe{} introduces
     the blendedness parameter: $b$ (\texttt{[grizy]blendedness\_abs\_flux}).
-    Please refer to Bosch\etal (in prep.) and Murata\etal (in prep.) for more details,
-    here we briefly explain the definition.
+    We briefly define  $b$ below; please refer to Bosch\etal (in prep.) and Murata\etal (in prep.) for more details.
 
@@
     ${\rm A}$ (no PSF correction).
-    $F_{\mathrm{total}}({\bf x })$ and $F_{\rm{A}}({\bf x })$ are pixels values of
-    ${\rm A}$ before and after \hscpipe{} deblending process.
+    $F_{\mathrm{total}}({\bf x })$ and $F_{\rm{A}}({\bf x })$ are pixel values of
+    ${\rm A}$ before and after \hscpipe{} deblending process, respectively.
 

### 2017-04-19 draft/ms_v3.tex
Start the final edits

--- 2017-04-19 draft/ms_susan.tex
@@
-% Version 0; Only rough outline by SH
+% Version 0; Rough outline by SH
 % Version 1; First draft by SH
-% Version 2; Main text is finished; with edits from Susan Foster
+% Version 2; Finish main text; with edits from Susan Foster
+% Version 3; More edits from Susan
 
@@
 
-% Package Settings
-%\usepackage{hyperref}
-%\hypersetup{colorlinks=true,
-%            citecolor=cyan,
-%            linkcolor=cyan,
-%            filecolor=magenta,
-%            urlcolor=cyan}
-%\urlstyle{same}
 %% ------------------------------------------------------------------------------------ %%
@@
     the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan}
+
 \altaffiltext{2}{Department of Astronomy and Astrophysics, University of California,
     Santa Cruz, 1156 High Street, Santa Cruz, CA 95064 USA}
+
 \altaffiltext{3}{Department of Astrophysical Sciences, Princeton University,
     4 Ivy Lane, Princeton, NJ 08544}
+
 \altaffiltext{4}{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
+
 \altaffiltext{5}{McWilliams Center for Cosmology, Department of Physics,
     Carnegie Mellon University, Pittsburgh, PA 15213, USA}
+
 \altaffiltext{6}{SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
     Tokyo, 181--8588, Japan}
+
 \altaffiltext{7}{Other affiliations}
@@
     is labeled as such).
-
-    \song{Susan's edit ends here; and Song has went through the previous sections.}
-    \susan{Susan made some minor additional edits to the preceding text on 4/17/2017.}
 %% ------------------------------------------------------------------------------------ %%
@@
     \caption{
-        Synthetic galaxy distributions of five-band magnitudes (\textbf{upper panel}) and other properties
+        Synthetic galaxy distributions of five-band magnitudes (\textbf{upper panel})
+        and other properties
         (\texttt{lower panel}; from left to right are the \ser{} index, axis ratio,
@@
 %% ------------------------------------------------------------------------------------ %%
-\susan{Susan started editing here on 4/17/2017.}
 \section{Generation of Synthetic Dataset}
@@
             data of the HSC survey.
-              \end{enumerate}
-              In addition to satisfying these criteria, the selected \tracts {}  show the photometric uncertainties under both good and bad seeing conditions, since for any given star or galaxy, different seeing conditions affect its
+            Since for any given star or galaxy, different seeing conditions affect its
             central S/N on the \coadd{} images and, therefore, also impact the
             detection and deblending processes in \hscpipe{}.
+
+    \end{enumerate}
 
@@
     \tract{}$=9699$ also has better seeing in both $r$- and $z$-bands;
-    the seeing conditions in $g$- and $y$-bands are very similar for both  \tract{}$=9699$ and \tract{}$=8764$.
+    the seeing conditions in $g$- and $y$-bands are very similar for both
+    \tract{}$=9699$ and \tract{}$=8764$.
     For both \tracts{}, the \coadd{} image in each band includes data from
@@
 
-    In this work, we use objects from the high-resolution \hst{}/ACS COSMOS field observations to build input catalogs of realistic synthetic stars and galaxies with appropriate completeness for the Wide survey and with reasonable five-band colors.
-We first select stars and galaxies as described below;  we then create the input catalogs via randomly distributing the selected synthetic stars and galaxies into the regions covered by the good- and bad-seeing \tracts{}.
-For stars, we use a number density of 1,000 per CCD; for galaxies, we use a number density of  500 per CCD.
-
+    In this work, we use objects from the high-resolution \hst{}/ACS COSMOS field
+    observations to build input catalogs of realistic synthetic stars and galaxies with
+    appropriate completeness for the Wide survey and with reasonable five-band colors.
+    We first select stars and galaxies as described below;
+    we then create the input catalogs via randomly distributing the selected synthetic
+    stars and galaxies into the regions covered by the good- and bad-seeing \tracts{}.
+    For stars, we use a number density of 1,000 per CCD; for galaxies, we use a number
+    density of 500 per CCD.
+
+    \song{Song Huang's edit}
     For star selection, we use the sample from \citet{Leauthaud2007}.
-     We use not only the \texttt{SExtractor} stellar classification index (\texttt{CLASS\_STAR}) but also the peak surface brightness above background (\texttt{MU\_MAX}) and
-    half-light radius (\texttt{RHL}) to select stars with clean photometry. 
+    We use not only the \texttt{SExtractor} stellar classification index
+    (\texttt{CLASS\_STAR}) but also the peak surface brightness above background
+    (\texttt{MU\_MAX}) and half-light radius (\texttt{RHL}) to select stars with clean
+    photometry.
     The classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag.
@@
     the real COSMOS stars are nicely recovered by the resampled stars in all
-   five-band magnitude and two color-color space distributions. \susan{Later you use "2-D color-color" Should it also be 2-D here?}
+    five-band magnitude and two color-color space distributions.
 
@@
     faint ($i<24.0$ mag) and barely resolved ($R_{\mathrm{e}}< 1.0$\asec).
-    This sample is appropriate to test  \hscpipe{}'s general photometric behaviors, but the sample lacks relatively bright galaxies ($i<20.5$ mag).
-
-%% ------------------------------------------------------------------------------------ %%
+    This sample is appropriate to test \hscpipe{}'s general photometric behaviors, but
+    the sample lacks relatively bright galaxies ($i<20.5$ mag).
 

### 2017-04-20 draft/ms_v3.tex
Quickly go through Susan's edits

@@
 
-    \song{Song Huang's edit}
     For star selection, we use the sample from \citet{Leauthaud2007}.
@@
 
-    We use HSC DR1 data stored at Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU) to conduct the \synpipe{} tests on the cluster (\texttt{Master}).
+    We use HSC DR1 data stored at Kavli Institute for the Physics and Mathematics of 
+    the Universe (Kavli IPMU) to conduct the \synpipe{} tests on the cluster 
+    (\texttt{Master}).
     The \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in each
@@
     \tract{} in each band) because the \galsim{} simulation is more time consuming.
-    The \texttt{stack.py} step and \texttt{multiBand.py} step together take ${\sim}3.5$ hours
-    per \tract{}.
+    The \texttt{stack.py} step and \texttt{multiBand.py} step together take 
+    ${\sim}3.5$ hours per \tract{}.
 
@@
     We also match the input catalogs with the original HSC catalogs to identify the
-    ``ambiguously blended'' objects that are right on top of the flux peak of a real
-    object.
-\susan{Is ambiguously blended well-understood by your reader?
-Or is the definition that they are objects that are right on top of the flux peak of a real object?
-If so, change sentence to the following: We also match the input catalogs with the original HSC catalogs to identify the  ``ambiguously blended'' objects, which are defined as those objects that are right on top of the flux peak of a real
-    object.}
-    The ambiguously blended objects are useful in the WL-related statistical tests (see Murata et al.
-    in prep. for more details); but since they will not help test photometry, they will be excluded later.
-
-    The detailed log of the entire tests can be found at
-    \url{goo.gl/VINOVP}.
-    The user should be able to reproduce the results presented in this work using this information. It can also serve as a brief manual for running a \synpipe{} test.
+    ``ambiguously blended'' objects, which are defined as so extreme blends that 
+    some objects are detected as a single object.
+    The ambiguously blended objects are useful in the WL-related statistical tests 
+    (see Murata et al. in prep. for more details); but since they will not help test 
+    photometry, they will be excluded later.
+
+    The detailed log of the entire tests can be found at \url{goo.gl/VINOVP}.
+    The user should be able to reproduce the results presented in this work using 
+    this information. It can also serve as a brief manual for running a \synpipe{} 
+    test.
 
@@
 
-    Here we discuss \hscpipe{}'s general performance, assessed mainly through  \forced{} PSF photometry (for stars) and (\cmodel{}) photometry (for galaxies).
+    Here we discuss \hscpipe{}'s general performance, assessed mainly through \forced{} 
+    PSF photometry (for stars) and (\cmodel{}) photometry (for galaxies).
     Although \hscpipe{} does provide other options (e.g., aperture and Kron photometry),
-these two are the only options that consider the effects of PSF in different bands and are consistent across all bands in terms of position and shape.
-Therefore, they are the most appropriate and relevant to star and galaxy magnitudes and colors.
-
+    these two are the only options that consider the effects of PSF in different bands 
+    and are consistent across all bands in terms of position and shape. T
+    Therefore, they are the most appropriate and relevant methods for star and galaxy.
+    \song{Edit stops here}
 %% ------------------------------------------------------------------------------------ %%
@@
         The highly blended stars are highlighted using scatter plots.
-        The gray dashed line marks $S/N = 5$. \susan{"grey" is an acceptable spelling; however, gray is more commonly used in the United States.}
+        The gray dashed line marks $S/N = 5$.
         }
@@
     \hscpipe{} also estimates aperture correction for PSF photometry.
-    For more details please see Bosch\etal (in prep.). \susan{Suggest you not include a section number for a document in preparation; section numbers can change before a text is published. }
+    For more details please see Bosch\etal (in prep.).
 
     In our tests, we randomly inject ${\sim}100,000$ stars into each \tract{} in all
-    five bands. Approximately \susan{Spell out approximately and delete approximate sign before 3-4.}
- ${\sim}3$--$4$\% of the stars are located within 2 pixels of the centroids
+    five bands. Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the centroids
     of real objects; we remove those stars from the sample to avoid confusion in the comparisons.
@@
     is important to understand how the seeing condition affects photometric accuracy as well as to test whether \hscpipe{} can deliver unbiased photometry under different  seeing conditions.
-\susan{Later you use "slightly worse" and "better" seeing; if you want to use those terms, perhaps define here where you make the distinction?
-For example, can you quantify slightly worse and better?}
 
@@
     confused with another object.
-    Here we use $b>0.05$ to define highly \susan{Later you say that $b>0.05$ is "highly blended"; it needs to be consistent.
-If inserting "highly" is incorrect here, please define b for highly blended stars since you use highly blended throughout the text.} blended stars (${\sim}4$--$9$\% are blended).
+    Here we use $b>0.05$ to define highly blended stars (${\sim}4$--$9$\% are blended).
     The fraction of highly blended stars slightly increases in the bad seeing \tract{}.
@@
     At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$- and
-    $i$-bands at average seeing conditions, which is consistent with the values found
-    in \citet{HSCDR1}. \susan{Is there a value for "average seeing conditions"?}
+    $i$-bands, which is consistent with the values found
+    in \citet{HSCDR1} for average seeing conditions.
     At the same time, it is worth reminding HSC data users that the detection
@@
     Although the exact cause of this offset is unclear (it could be related to
-    differences in seeing), it will not affect the accuracies of magnitudes of \susan{should "of" be "or"?} colors.
+    differences in seeing), it will not affect the accuracies of magnitudes or colors.
 
@@
     (see Fig \ref{fig:psf_cdist}).
-    Using four different colors and two \susan{2-D?} color--color planes, we show that the \forced{}
+    Using four different colors and two 2--D color--color planes, we show that the \forced{}
     PSF colors can accurately reproduce the distributions of all four colors and the
-    2-D \susan{or two?} color-color distributions.
+    2-D color-color distributions.
 
@@
     photometry.
-    For more details, please see Bosch\etal (in prep.).\susan{Suggest you not include a section number for a document in preparation; section numbers can change before a text is published. }
+    For more details, please see Bosch\etal (in prep.).
     In short, \cmodel{} tries to fit each object using a combination of de Vaucouleurs
@@
     bad-seeing \tract{}).
-    About ${\sim}7$--$9$\% \susan{Delete the approximately symbol when you use "About"; it's redundant.} of synthetic galaxies are highly blended by this standard.
+    About $7$--$9$\% of synthetic galaxies are highly blended by this standard.
     The fraction is only slightly higher in the bad-seeing \tract{}, and the
@@
     Similar to the synthetic stars, the worse the seeing condition, the more
-    we noticed a decrease in \s2n{} at the same magnitude (see the figure \susan{cite actual figure number.} for
-    $i$-band).
+    we noticed a decrease in \s2n{} at the same magnitude (see Fig \ref{fig:psf_s2n}) 
+    for $i$-band).
     Meanwhile, the highly blended synthetic galaxies do not show significantly
@@
     For more details about this algorithm, please see Bosch\etal
-    (in prep.). \susan{Suggest you not include a section number for a document in preparation; section numbers can change before a text is published. }
+    (in prep.).
 
@@
 
-        \item High blendedness ($b>0.1$) \susan{This is the value you've given for highly blended galaxies; should the text in the parentheses read ($b>0.1$ for galaxies and $b>0.05$ for stars)}impacts the accuracy of both PSF and \cmodel{}
+        \item High blendedness ($b>0.1$) impacts the accuracy of both PSF and \cmodel{}
             photometry, especially for stars.
@@
     For instance,  Murata\etal (in prep.) uses \synpipe{} to test
-    the impacts of extremely blended \susan{Quantify? Is "extremely blended" more blended than "highly blended"?} objects on the WL measurements.
+    the impacts of the ambiguously blended objects on the WL measurements.
     Also, \citep{Niikura2017} applies \synpipe{} to the high-cadence M31 HSC observations
@@
             affects the photometry and shape measurements.
-            This could be important for regions with exquisite seeing \susan{Quantify "exquisite"? Is it better than "good" or "better" seeing? Suggest using consistent adjectives.}  that makes the
+            This could be important for regions with exquisite seeing 
+            (e.g. FWHM${\sim}0.4$\asec{}) that makes the
             PSF modeling difficult, and for accurate WL measurements.
@@
         a machine learning library in Python (\citealt{scikit-learn};
-        \url{http://scikit_learn.org/} \susan{I think correct URL is http://scikit-learn.org/ (hyphen, not underscore.}).
+        \texttt{http://scikit-learn.org/}.
 
@@
 %% ------------------------------------------------------------------------------------ %%
-\susan{Susan did not review bibliographic citations.}
 \begin{thebibliography}{}

### 2017-04-21 draft/ms_v4.tex
Alexie's edits and Add Jean Coupon to author list

--- 2017-04-20 draft/ms_v3.tex
@@
 % Version 3; More edits from Susan
+% Version 4; Edits from Alexie
 
@@
 
+\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
+
 \def\redm{\texttt{redMaPPer}}
@@
 %% ------------------------------------------------------------------------------------ %%
-\title{HSC Synthetic Pipeline I: Basic Design and Characterization of HSC
-       Photometric Performance}
+\title{Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.}
 
@@
         Alexie Leauthaud \altaffilmark{1,2},
-        Ryoma Murata \altaffilmark{1, 4},
+        Ryoma Murata \altaffilmark{2, 4},
         Jim Bosch \altaffilmark{3},
@@
         Rachel Mandelbaum \altaffilmark{5},
-        Claire Lackner \altaffilmark{1},
-        Steven Bickerton \altaffilmark{1},
-        Satoshi Miyazaki \altaffilmark{6}
-        HSC Collaboration \altaffilmark{7}}
-%% ------------------------------------------------------------------------------------ %%
-
-\altaffiltext{1}{Kavli Institute for the Physics and Mathematics of the
+        Claire Lackner \altaffilmark{2},
+        Steven Bickerton \altaffilmark{2},
+        Satoshi Miyazaki \altaffilmark{6}, 
+        Jean Coupon \altaffilmark{7},
+        HSC Collaboration \altaffilmark{8}}
+%% ------------------------------------------------------------------------------------ %%
+
+\altaffiltext{1}{Department of Astronomy and Astrophysics, University of California,
+    Santa Cruz, 1156 High Street, Santa Cruz, CA 95064 USA}
+
+\altaffiltext{2}{Kavli Institute for the Physics and Mathematics of the
     Universe, The University of Tokyo Institutes for Advanced Study,
@@
 
-\altaffiltext{2}{Department of Astronomy and Astrophysics, University of California,
-    Santa Cruz, 1156 High Street, Santa Cruz, CA 95064 USA}
-
 \altaffiltext{3}{Department of Astrophysical Sciences, Princeton University,
@@
 
-\altaffiltext{7}{Other affiliations}
+\altaffiltext{7}{Department of Astronomy, University of Geneva, ch. d'\'Ecogia 16, 
+    1290 Versoix, Switzerland}
+
+\altaffiltext{8}{Other affiliations}
 
@@
     using the Hyper Suprime-Cam (HSC) on the Subaru telescope.
-    As SSP reaches to detection limit of $i>26.0$ mag in the Wide field, it is
-    challenging to achieve accurate, unbiased, and consistent photometry across all
+The  Wide layer of the SSP is both wide and deep, reaching a detection limit of $i>26.0$ mag.
+At these depths, it is challenging to achieve accurate, unbiased, and consistent photometry across all
     five bands.
-    To improve data processing and achieve accurate photometric measurements, we have
-    developed \synpipe{}, a \texttt{Python}-based, flexible framework that interfaces
-    with the HSC data reduction pipeline (\hscpipe{}) to process data from the first
-    public HSC--SSP data release.
-    In the first paper of this series, we explain the design and implementation of
-    \synpipe{}, and use \coadd{} images in two Wide layer \tracts{} with representative
-    seeing conditions to examine the photometric performance of \hscpipe{}.
-    We find that uncertainties of HSC \forced{} PSF photometry for stars typically
-    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
-    mag (1\%-7\% accuracy in the $i$-band).
-    For synthetic galaxies based on a single-\ser{} model, uncertainties of the
-    forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag
-    to 0.20 mag at $i{\sim} 25.2$ mag.
-    Over the color and magnitude ranges used in these \synpipe{} tests, we find that
-    both \forced{} PSF and \cmodel{} photometry provide unbiased color estimates
-    that are robust in different seeing conditions.
-    We also notice a few issues in the current \hscpipe{} that are worth keeping
-    in mind when using HSC data:
-    1) The degree to which an object is blended with others impacts the photometric
-    accuracy, especially for point sources.
-    Highly blended objects tend to have larger photometric uncertainty, systematically
-    underestimated flux, and slightly biased color.
-    2) A relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
-    misclassified as extended objects.
-    3) The shape and size estimates for galaxies using \cmodel{} suffer from strong
-    biases.
+The HSC data are reduced using a pipeline that builds on the prototype pipeline being designed by the Large Synoptic Survey Telescope’s Data Management system.
+We have developed a \texttt{Python}-based, flexible framework to inject synthetic galaxies into real HSC images called \synpipe{}.
+In this paper, we explain the design and implementation of \synpipe{} and we generate a sample of synthetic galaxies to examine the photometric performance of the HSC pipeline.
+For stars, we achieve 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and ${\sim}0.06$ mag respectively).
+\alexie{Put numbers in here using this phrase format} For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry achieves 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and ${\sim}0.06$ mag respectively).
+    %For synthetic galaxies based on a single-\ser{} model, uncertainties of the
+    %forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag
+    %to 0.20 mag at $i{\sim} 25.2$ mag.
+    we show that
+    both \forced{} PSF and \cmodel{} photometry yield unbiased color estimates
+    that are robust to seeing conditions.
+We identify several caveats that apply to version xxx of the  HSC pipeline and than need to be considered when using data from the first public HSC data release.
+First, the degree to which an object is blended with other objects impacts the overall photometric performance.
+This is especially true for point sources \alexie{quanityf here}.
+Highly blended objects tend to have larger photometric uncertainties, systematically underestimated fluxes \alexie{Should be overestimated here no?}, and slightly biased colors.
+Second, a relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
+    misclassified as extended objects \alexie{need to quantify here}. Third, the shape and size estimates for galaxies using \cmodel{} suffer from strong
+    biases \alexie{quantify here}.
 
@@
     Wide-field, multi-band imaging surveys have stepped onto the central stage of
-    modern astrophysics and cosmology over the past decade.
-    They also have a bright future on many current and planned ambitious projects,
-    such as the Large Synoptic Survey Telescope
+    modern astrophysics and cosmology over the past decade.  These efforts will soon be replaced with even more ambitious programs such as the Large Synoptic Survey Telescope
     (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
@@
     and the \textit{Euclid} project
-    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}.
-    Among many ongoing efforts, the Subaru Strategic Program
+    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}. Among many ongoing efforts, the Subaru Strategic Program
     (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
@@
     etendue\footnote{The collecting area multiplied by the field of view.}.
-    Together, these surveys will greatly help us test cosmological models, trace the
-    evolution of galaxies, study the stellar structure of our Milky Way, and discover
-    a large number of interesting transient objects.
+Surveys such as HSC, and other to follow, will  provide stringent constraints on  the cosmological model,  characterize the evolution of galaxies, map out the stellar structure of our Milky Way, and are poised to discover a large number of interesting transient objects.
 
     %% Challenges
-    Before we can tackle any outstanding scientific questions, we must first learn
-    how to handle the huge amount of data\footnote{Right now, SSP has accumulated
-    ${\sim}300$ TB of data products.} generated by these projects as well as achieve
-    accurate photometric measurements of different types of objects.
+    Before we can tackle outstanding scientific questions, we must first learn
+    how to handle the the large amounts of data\footnote{Right now, SSP has accumulated
+    ${\sim}300$ TB of data products.} generated by these projects while satisfying  strict requirements for  high quality image processing with accurate measurement for the magnitudes and shapes of stars and galaxies.
 Data handling becomes increasingly challenging in the age of modern imaging
-    surveys, in part due to variations and effects related to the cameras'
-    charge-coupled devices (CCDs).
-    The cameras are often made up of multiple CCDs, each with slightly different
-    characteristics, and have large fields-of-view (FoV) over not perfectly flat
-    focus planes.
-    During observation, the seeing and background conditions always show spatial
-    and temporal variations across the FoV.
-    The full-depletion, thick CCDs selected for the cameras enable long exposure
-    times and excellent sensitivity in the red-end, but they often suffer from the
+    surveys am we aim to characterize and account for subtle effects related to charge-coupled devices (CCDs). Cameras are made up of multiple CCDs, each with slightly different
+    characteristics, and have large fields-of-views (FoV) over focal planes that are not perfectly flat.
+During observations, the seeing and background conditions display spatial and temporal variations across the FoV.
+The full-depletion, thick CCDs selected for HSC enable long exposure
+    times and have excellent red-sensitivity, but they also suffer from the
     so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that
-    brighter stars appear larger than they are.
-    These variations and effects make accurate astrometric and photometric calibration,
+    brighter stars have larger Point Spread Functions (PSFs) than fainter stars. These variations and effects make accurate astrometric and photometric calibration,
     background subtraction, and point spread function (PSF) modeling intrinsically
-    difficult (e.g., \citealt{Schlafly2012}).
-    The multi-epoch, multi-band nature of the surveys also complicate data reduction
-    because the scientist must pay special attention to image stacking, multi-band
-    object detection, and measurement processes.
-    Furthermore, as ongoing surveys reach to increasingly deeper detection limit
-    (e.g., SSP Wide reaches to $5\ \sigma$ detection limit of point source of
-    ${\sim}26.4$ mag), the number of objects in a unit area, especially faint objects,
-    becomes much higher.
-    In addition, it is much more common to observe objects that overlap each other at
-    different levels (a phenomenon often referred to as ``blended'').
-    These modern imaging survey challenges call for photometric measurement methods
+    difficult (e.g., \citealt{Schlafly2012}). Furthermore, as surveys reach to increasingly deeper detection limits
+    (e.g., the SSP Wide layer reaches a $5\ \sigma$ point source detection limit of
+    ${\sim}26.4$ mag), the number of objects per unit area increases.
+Hence, deep surveys become  more sensitive and subject to the effects of blending.
+The challenge of modern imaging surveys call for  photometric measurement methods
     that are more powerful and precise than those used in previous, shallower surveys.
 
-%% ------------------------------------------------------------------------------------ %%
-    %% Reason
-    The challenges are not merely technical details; their resolution is crucial
-    to achieving the surveys' key scientific goals.
+    %
+
+    These challenges are not merely technical details; their resolution is crucial
+    to achieving key scientific goals.
     For instance, weak gravitational lensing (WL; \citealt{Kaiser1993, Bartelmann2001})
-    is a powerful tool for measuring the large-scale distribution of dark matter and
-    following its evolution.
-    However, WL measurements critically depend on the ability to model PSF and measure
-    the shape of background galaxies with high precision
-    (e.g., \citealt{Mandelbaum2015}).
-    The photometric redshift measurement (e.g., \citealt{Benitez2000, Bolzonella2000,
-    Ilbert2009}) is fundamentally important for studying the evolution of galaxies,
-    and the ``drop-out'' method is very useful in selecting high-redshift galaxies
+    is a powerful tool for measuring the large-scale distribution of dark matter.
+    However, WL measurements critically depend on our ability to measure the shape and photometric redshifts of background galaxies with high precision.
+Photometric redshifts (e.g., \citealt{Benitez2000, Bolzonella2000,
+    Ilbert2009}) are fundamentally important for studying the evolution of galaxies,
+    and the ``drop-out'' method is critical for selecting high-redshift galaxies
     (e.g., \citealt{Steidel1996}).
-    However, both of those methods are based on accurate multi-band photometric
-    measurements.
-    There are many other examples, but these are sufficient to demonstrate that we
-    need to develop new frameworks to oversee the data reduction process of modern
-    imaging surveys.
+    However, both of those methods reply on the availability of accurate multi-band photometric
+    measurements. With increasingly large surveys,  and with more stringent requirements on data quality,  quality control also becomes a pressing issue.
+
+   In this paper, we present a \texttt{Python}-based software package called  \synpipe{} that  injects synthetic objects into  HSC images  and  which interfaces with the HSC data reduction pipeline (\hscpipe{}).
+Among other applications, \synpipe{} can be used to perform quality control and to characterize the performance and limitations of  \hscpipe{}.
 Several tools with similar goals have been developed (e.g., \citealt{Chang2015,
     Suchyta2016}) for the Dark Energy Survey (DES; \citealt{DES2005}).
-    As for the HSC--SSP (hereafter referred to as the HSC survey), the higher quality
-    images and more complex \hscpipe{} also require more carefully designed tool to
-    test them.
-
-    %% Organization
-    Here, we present \synpipe{}, a \texttt{Python}-based software that is a flexible
-    framework with many applications that can help future developments of the HSC data
-    reduction pipeline (\hscpipe{}).
+
+ \alexie{Edit here following this format}. In Section 1 we ... in section 2 we ....
+
     Below, we briefly introduce the HSC survey and the current status of data
@@
 
-    The \synpipe{} code, along with basic documents and a few examples, is available
+    The code for \synpipe{}, along with documentation and examples, is made available
     on GitHub at: \texttt{https://github.com/dr-guangtou/synpipe}.
+
 %% ------------------------------------------------------------------------------------ %%
@@
     \caption{
-        Illustration of \synpipe{} basic procedures.
-        Gray boxes indicate the required inputs at different stages.
-        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects
-        simulated images of synthetic objects onto a single-frame image.
-        We show an example CCD image with and without synthetic objects on it
-        (highlighted by green circles).
-        Red boxes depict the subsequent image coadding and multiband measurement steps
-        using \texttt{stack.py} and \texttt{multiBand.py} from \hscpipe{}.
-        We show a small piece of \coadd{} image with synthetic objects on it.
-        The figure on the right side of the middle row shows the spatial relation
-        between \tract{} (outlined by the black dashed lines; each small region
-        is a \texttt{Patch}) and all the \visits{} that contribute to it.
-        (Each \visit{} has a  unique color; each small region is the size of a CCD.)
-        }
+        Illustration of the main steps involved in using \synpipe{}.
+        Gray boxes indicate required inputs at different stages.
+        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects synthetic objects into single-frame images.
+Below the blue box, we show an HSC image before and after the insertion of synthetic galaxies.
+The positions of synthetic  objects are highlighted with green circles.
+Red boxes depict the image coadding and multi-band measurement steps
+        using \texttt{stack.py} and \texttt{multiBand.py}. At the bottom left, we show a \coadd{} image which contains synthetic galaxies. On the right hand side, we show the spatial relation
+        between \texttt{Tracts}, \texttt{Patches}, and \texttt{Visits}.
+The xxxxxxx colored box corresponds to one \texttt{Tract} which has an area of about xx deg$^2$.
+Large colored circles are \texttt{Visits} (also commonly known as "pointings") with small rectangles representing CCDs.
+\texttt{Patches} are represented by black dashed lines.
+One \texttt{Tract} typically contains xx  \texttt{Patches}.}
     \label{fig:flowchart}
@@
     The Deep (four separated fields; ${\sim}27$ deg$^2$) and UltraDeep (two separated
-    fields; ${\sim}3.5$ deg$^2$) layers will use a few additional narrow-band filters
+    fields; ${\sim}3.5$ deg$^2$) layers use a few additional narrow-band filters
     and employ a slightly different surveying strategy.
@@
     The camera has a circular FoV with a 1.5 deg diameter.
-    Each CCD contains 2048$\times$4096 pixels distributed in four amplifiers.
-    The pixel size is equal to 0.168\asec{} on the sky.
+    Each CCD contains 2048$\times$4096 pixels and the sizes of pixels are 0.168\asec{}.
 
@@
     For our work, we focused on data from the Wide layer as they relate to key
-    scientific goals of the HSC survey, which include WL cosmology, galaxy evolution
-    since $z{\sim}1$, and studies of galaxy clusters.
-    The current Wide layer includes ${\sim}108$ deg$^2$ of sky isolated in
-   six different regions (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
+    scientific goals of the HSC survey, which include weak lensing cosmology, galaxy evolution, and studies of galaxy clusters.
+The Wide layer data in DR1 corresponds to ${\sim}108$ deg$^2$ spread over
+   six fields (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
     \footnote{A small AEGIS field is also observed for calibration purposes.}.
     Except for the HECTOMAP field, the regions are all close to the equator.
-    In the Wide layer, the $g$ and $r$ bands have 10 mins of exposure broken into four
-    dithers\footnote{Large, ${\sim}1/3$ of the FoV dither pattern is used to ensure
-    uniform coverage.}; for the remaining three bands, 20 mins of exposure time and six
-    dithers are used\footnote{Several 30 s exposures are taken to improve the
-    dynamic range.}.
-    The survey prioritizes the observations so that the $i$-band can have excellent
-    seeing conditions to help make accurate WL shape measurements.
-    The current Wide layer has impressive median seeing with FWHM${\sim}0.6$\asec{},
-    and has a $i{\sim} 26.4$ mag $5\sigma$ point source detection limit.
+    In the Wide layer, the $g$ and $r$ bands have 10 minute exposures broken into four
+    dithers.
+The  $i$, $z$, and $y$ bands have 20 minute exposures broken into six dithers.
+The survey prioritizes the observations so that the $i$-band has the best seeing conditions to improve galaxy shape measurements for weak lensing science.
+The  $i$ band data in the Wide layer reach a $5\sigma$ point source limiting magnitude of  $i{\sim} 26.4$ mag  and have a median seeing with FWHM${\sim}0.6$\asec{}.
 \citealt{HSCDR1} provides details on the first data release and data status.
@@
 
-    The HSC survey data are currently reduced by \hscpipe{} \texttt{v4.0.5}, a
-    version of the LSST reduction pipeline (\citealt{Ivezic2008, Axelrod2010,
-    Juric2015}), which is described in detail in Bosch\etal (in prep.).
-    Since \synpipe{} is intrinsically connected to the complex data reduction
-    processes in \hscpipe{}, we briefly introduce the main steps below, along with
-    a few key HSC/LSST terms.
+The HSC data are reduced using a pipeline that builds on the prototype pipeline being designed by the Large Synoptic Survey Telescope’s Data Management system (\citealt{Ivezic2008, Axelrod2010,
+    Juric2015}) and is described in Bosch\etal (in prep.). DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. Because\synpipe{} is intrinsically connected to the complex data reduction
+    processes in \hscpipe{}, we briefly introduce the main steps below, and we introduce a few key HSC/LSST terms.
 
@@
             an even integer.
-            After initial data screening (in background, seeing, and transparency
+            After initial data screening (considering the background level, seeing, and transparency
             Furusawa\etal in prep.), \hscpipe{} detrends these data (subtraction
-            of overscan, bias, and dark; flatfielding), generates variance and mask
-            images, subtracts background, and provides initial astrometric and
-            photometric calibrations.
-            \textbf{\synpipe{} will use the spatially varying PSF models, photometric
-            zeropoints, and the World Coordinate System (WCS; \citealt{WCS1, WCS2})
-            corrected for optical distortion.}.
-
+            of overscan, bias, and dark; flatfielding), \alexie{xxxxx} generates variance and mask
+            images, subtracts the background, and provides initial astrometric and
+            photometric calibrations. \synpipe{} uses the spatially varying PSF models, photometric zeropoints, and the World Coordinate System (WCS; \citealt{WCS1, WCS2})
+            corrected for optical distortion provided by \hscpipe{}.
         \item \textbf{Multi-\visit{} Processing}:
@@
             regions, or \tracts{}, which are predefined as iso-latitude tessellations.
-            One \tract{} covers approximately $1.7\times 1.7$ deg$^2$ of sky, and
+            One \tract{} covers approximately $1.7\times 1.7$ degrees$^2$ and
             adjacent \tracts{} overlap each other by ${\sim}1$\amin{}.
@@
             adjacent \texttt{Patches} overlap each other by 100 pixels.   
-            \textbf{The \tract{} and \texttt{Patch} are basic units to deal
-            with HSC \coadd{} images and \synpipe{} tests.}
-
         \item \textbf{Multi-band Measurements}:
@@
             \hscpipe{} merges the \texttt{footprints} and flux peaks in the different
-            bands and then selects a reference band for each object based on its $S/N$
-            in each band (usually it is the $i$-band).
-            With the centroids, shape, and other non-amplitude parameters fixed at the
-            reference values, \hscpipe{} performs \forced{} photometry, which is
-            optimized to generate accurate colors.
-
+            bands and then selects a reference band for each object based on its $S/N$ in each band (usually this corresponds to the $i$-band).
+Centroids, shapes, and other non-amplitude parameters are then fixed to  the values from the reference band.
+\hscpipe{} then performs \forced{} photometry using these fixed quantities.
+The goal of the  \forced{} photometry step is to generate accurate colors.
         \item \textbf{HSC Photometry}:
-            The multi-band catalogs generated by \hscpipe{} contain a variety of
-            photometric information (see \citealt{HSCDR1} for details).
-            \textbf{Here, we focus on the \forced{} \texttt{psf} and \cmodel{}
-            photometry.}
+            The multi-band catalogs generated by \hscpipe{} contain various types of photometry measurements (see \citealt{HSCDR1} for details).
+Here, we focus on characterizing the the \forced{} \texttt{psf} and \cmodel{}
+            photometry. The
             \texttt{psf} photometry should provide the most appropriate magnitudes and
             colors for point sources.
-            Improved over the SDSS version (\citealt{Lupton2001, Abazajian2004}),
-            the HSC \cmodel{} algorithm (described in Bosch\etal, in prep.) fits
-            each object's flux distribution using a combination of the de Vaucouleurs
-            profile and an exponential component that takes the PSF convolution
-            into account.
-            \cmodel{} is designed to yield accurate colors for galaxies.
-            In addition, the star--galaxy classification task is performed based on
-            the difference between the \texttt{psf} and \cmodel{}{} magnitudes.
-
+The  \cmodel{} should be used for galaxies.
+The HSC  \cmodel{} algorithm is described in Bosch\etal, in prep.
+and is an  improved version of the SDSS \cmodel{} magnitude (\citealt{Lupton2001, Abazajian2004}).
+The HSC  \cmodel{} fits objects using both a de Vaucouleurs and an exponential profiles taking into account the smearing by the PSF.
+\cmodel{} then linearly combines the two results to find the best fit to the galaxy image.
+\cmodel{} magnitudes are designed to yield accurate fluxes and colors for galaxies.
+Star--galaxy separation is performed based on
+            the difference between \texttt{psf} and \cmodel{}{} magnitudes.
     \end{enumerate}
 
-    DR1 data quality has been vetted in \citet{HSCDR1} via cross-checking
+    DR1 data quality has been vetted in \citet{HSCDR1} by cross-checking
     with the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1
     imaging survey (\citealt{Schlafly2012, Tonry2012, Magnier2013}) to examine the
-    behaviors of the stellar sequence and the shape of the PSF models.
-    Generally speaking, the PSF photometry is accurate to 1--2\% level, and the
+    behavior of the stellar sequence.
+    Generally speaking, the PSF photometry is accurate at the 1--2\% level \alexie{only for bright stars}, and the
     astrometry is accurate to ${\sim}10$ and 40 max internally and externally.
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsection{ \synpipe{} Basic Design}
+\subsection{Design}
     \label{ssec:design}
@@
     processes that produce not only deep \coadd{} images but also a series of
-    science-ready catalogs.
-    To faithfully test \hscpipe{} and the related data products, we have designed an
-    approach that ensures \synpipe{} satisfies a few basic standards:
+    science-ready catalogs. To perform tests of the  data products that result from \hscpipe{},  \synpipe{} is designed to satisfies a few basic standards:
 
@@
         \item \textbf{Realistic Images}:
-            Instead of using the fully generative approach to simulate full HSC-like
+            Instead of using a fully generative approach to simulate full HSC-like
             images from the ground up (e.g., \citealt{Chang2015}), \synpipe{} injects
-            synthetic objects into the observed image so that all the realistic
+            synthetic objects into real HSC images so that all the realistic
             features of the real data (e.g., blended objects; proximity to bright
@@
             test.
-            The impact of these features can be important to any topic (e.g., WL
-            analysis; stellar mass function of galaxies) that cares about the selection
-            function and completeness of samples.
-            In \synpipe{}, point source is simulated using the HSC PSF model,
+            The impact of these features can be important for studies that care about completeness and the selection
+            function.
+            In \synpipe{}, point sources are simulated using the HSC PSF model,
             and a realistic galaxy model is created by the modular galaxy image
@@
             into account.
-            Every synthetic object will experience all the steps we would use for any
-            real object: detection, deblending, stacking, and measurement.
-            This can be important for challenging tasks like the WL measurements
+            Every synthetic object will experience all the steps we would use for a real object: detection, deblending, stacking, and measurement.
+            This can be important for challenging tasks like WL measurements
             or the detection of high-$z$ galaxies.
-            The only downside of this choice is that it will certainly slow down the
-            test for \coadd{} images because in this approach we need to inject
-            synthetic objects into all the \visits{} that contribute to a \tract{}.
-
-        \item \textbf{Flexible Capabilities}:
-            We must make \synpipe{} flexible enough to be useful for HSC users with
-            various scientific goals.
+            The downside of this choice is that it slows down the overall run-time because we need to inject synthetic objects into all the \visits{} that contribute to a \tract{}.
+        \item \textbf{Flexible Capabilities}: \synpipe{} is designed to be flexible enough to be useful for HSC users with a range of scientific goals.
             We provide default catalogs to generate samples of synthetic stars
-            and galaxies with realistic magnitude and color distributions along with
-            tools to help the user work on HSC DR1 data; however, the user is allowed
-            to be creative in terms of providing input catalogs and designing the tests.
+            and galaxies with realistic magnitudes and color distributions along with
+            tools to help the user work on HSC DR1 data. However, \synpipe{} also easily allows users to  design and use their own custom made input catalogs.
             \synpipe{} is already being used in a wide range of
@@
 
-    In this section, we describe the \synpipe{} test implementation depicted in
-    Fig \ref{fig:flowchart}.
+    In this section, we describe the \synpipe{} test implementation illustrated in Fig \ref{fig:flowchart}.
 
@@
 
-    To start a \synpipe{} test, the user needs to provide information about the data
-    and an input catalog, as discussed below:
+    To create a catalog of synthetic objects, the user first needs to select which HSC data and which input synthetic galaxy catalog to use.
 
@@
 
-        \item \textbf{Information about the data}
-            includes the location of the HSC images and a list of \visits{} for
-            the test.
-            To test the \coadd{} images, \synpipe{} can help the user identify
+        \item \textbf{Information about the data}. This  corresponds to the location of HSC images and a list of \visits{} to be used. \synpipe{} can also help the user identify
             all the \visits{} that contribute to one \tract{} in any given
@@
             \synpipe{} also provides tools to create an optional bad-pixel mask
-            (e.g., bright object, bleeding trail) for a specific \tract{} so that
+            (e.g., bright object, bleeding trails) for a specific \tract{} so that
             the user can avoid putting synthetic objects on problematic regions.
 
-        \item \textbf{Input catalog} in \texttt{FITS} (Flexible Image Transport System)
-            format contains the necessary information, including the coordinate,
-            magnitude, and other model parameters.
-            For any given sample of synthetic objects, \synpipe{} can help the user
-            randomly distribute the objects in a selected rectangular region with the
-            desired density.
-            If necessary, the user can reduce overlaps of synthetic objects by setting
-            a minimum distance between any two of them.
-            \synpipe{} can also help put synthetic objects on an evenly separated
-            coordinate grid, which is very useful for certain tests
-            (e.g., Murata\etal in prep.).
-
+        \item \textbf{Input catalog}. This is a catalog in \texttt{FITS} (Flexible Image Transport System)
+            format that contains the  coordinates, magnitudes, and model parameters of synthetic  galaxies.
+The positions of synthetic galaxies can be specified  via the input catalog, they can be distributed randomly over a given region, or on a grid (the grid option is useful in that it avoids blends between Synthetic objects, Murata\etal in prep.).
     \end{itemize}
 
-    For the synthetic object, \synpipe{} provides the following choices:
+Synthetic objects can be one of the following:
 
@@
 
-        \item \textbf{Point source}:
-            \synpipe{} simply uses the PSF model from \hscpipe{} as the model for
-            a point source such as a star or a quasi-stellar object (QSO).
+        \item \textbf{Point source}: \synpipe{} simply uses the PSF model from \hscpipe{} as the model for
+            a point source (stars and/or quasi-stellar objects).
             \hscpipe{} uses a special version of \texttt{PSFEx}
             (\citealt{Bertin2011, Bertin2013}) to characterize PSF as a function
-            of the point source's position so that a PSF model can be reconstructed
-            for any location on the image.
-            The user only needs to provide the integrated magnitude to simulate
-            point sources.
-
-        \item \textbf{Single- or Double-\ser{} model for galaxy}:
+            of position and the PSF model can be reconstructed
+            for any location on the image. To inject point sources, the user only needs to specify a catalog of coordinates and magnitudes.
+        \item \textbf{\ser{}models}:
             \texttt{SynPipe} uses \galsim{} \texttt{v1.4} (\citealt{Rowe2015}) to
-            simulate a galaxy.
-            \galsim{} is an image simulation tool that has been well tested during
-            the GRavitational lEnsing Accuracy Testing 3 (GREAT3) challenge
-            (\citealt{Mandelbaum2014}).
-            Currently, \synpipe{} allows a synthetic galaxy to be modeled by single
-            or double components that are described by the \citet{Sersic1963}
-            profile\footnote{More flexible model choices will be added later.}.
-            The \ser{} profile is flexible enough to describe the overall flux
+            simulate galaxies.
+            \galsim{} is an image simulation tool that was designed for the GRavitational lEnsing Accuracy Testing 3 (GREAT3) challenge
+            (\citealt{Mandelbaum2014}). Currently, \synpipe{} allows synthetic galaxies to be modeled by a single
+            or a double \citet{Sersic1963}
+            profile\footnote{More flexible model choices will be added later.}. The \ser{} profile is flexible enough to describe the overall flux
             distributions of galaxies near and far, both early-type or late-type.
@@
             For each \ser{} component, the user needs to provide the magnitude,
-            effective radius ($R_{\mathrm{e}}$; in unit of arcsec), \ser{} index
+            effective radius ($R_{\mathrm{e}}$, in unit of arcsec), \ser{} index
             ($n_{\mathrm{Ser}}$), axis ratio ($\mathrm{b}/\mathrm{a}$), and position
@@
             External shear can also be applied to a synthetic galaxy ($g_1$ and
-            $g_2$; see \citealt{Rowe2015} for more details).
-
-        \item \textbf{Models or real images of a galaxy from the GREAT3 challenge}:
-            In addition to providing detailed model information for each galaxy,
-            \synpipe{} also allows users to choose from parametric models or real
-            high-resolution galaxy images used in the GREAT3 WL challenge.
-            The images are from the \hst{}/ACS F814W ($I$-band) images of the galaxies
-            in the COSMOS field (e.g., \citealt{Scoville2007}).
-            These Advanced Camera for Surveys (ACS) exposures are 50\% completed down
-            to $I=26.0$ mag in aperture with 0.5\asec{} diameter.
-            The depth and high resolution (0.09\asec FWHM) make the exposures adequate
-            to test galaxies at Wide depth in the HSC survey.
-            In addition to the real cutout image, \synpipe{} models the COSMOS galaxies
-            with $I_{\mathrm{Auto}}\leq25.2$ mag via a method developed by
-            \citet{Lackner2012}, and selects between the single-\ser{} and the \ser{}
-            bulge$+$Exponential disk values for the best parametric model.
-            Information for these models is stored in the
-            \texttt{GalSim.COSMOSCatalog()} catalogs.
-            To access them, the user can provide the ID number of the COSMOS galaxies
-            in the input catalog, or simply let \synpipe{} randomly select the galaxies.
-
+            $g_2$, see \citealt{Rowe2015} for more details).
+        \item \textbf{Galaxies from the GREAT3 challenge}: \synpipe{} also allows users to choose from parametric models or real
+            high-resolution galaxy images used in the GREAT3 WL challenge. Real galaxy images are drawn from the \hst{}/ACS F814W ($I$-band) images of galaxies
+            in the COSMOS field (e.g., \citealt{Scoville2007,Leauthaud2007}).
+Instead of using real galaxy images, the users may also use models of  COSMOS galaxies to $I_{\mathrm{Auto}}\leq25.2$ mag via a method developed by
+            \citet{Lackner2012}.  Parametric models of COSMOS galaxies include a single-\ser{} and the \ser{}
+            bulge$+$Exponential disk model. The parameter values for these models are stored in the
+            \texttt{GalSim.COSMOSCatalog()} catalog.
+            To access them, the user can provide the ID number of COSMOS galaxies
+            in the input catalog, or can simply opt to let \synpipe{} randomly select galaxies from the COSMOS input catalog.
     \end{itemize}
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsubsection{Injection of Synthetic Objects into Single-\visit{} Image}
+\subsubsection{Injection of Synthetic Objects into Single-\visit{} Images}
     \label{sssec:addFakes}
 
-    With the input catalog and test data information, \synpipe{} first injects synthetic
+    \alexie{Can we use bullet points to highlight the different steps? This paragraph is really hard to read.}
+
+    With the input catalog and test data information in hand, \synpipe{}injects synthetic
     objects into single-exposure images (step \texttt{addFakes.py}; see the middle panel
@@
     \visit{} to convert the input coordinates into locations on the CCD image.
-    Using the available models, \synpipe{} reconstructs the PSF at the position of
-    each injected object.
-    To convert the input magnitudes of synthetic objects into fluxes on the image,
-    \synpipe{} also uses the photometric zero point from the single-\visit{}
-    calibration.
-
+For each synthetic object, \synpipe{} uses the  reconstructed PSF for each exposure.
+The photometric zero point from the single-\visit{} calibration is used to convert input magnitudes of synthetic objects into fluxes.
 For point sources, \synpipe{} generates a rectangular cutout image of the PSF model
-    with appropriate size and correct total flux.
-    For a galaxy described by single- or double-\ser{} models, \synpipe{} passes the
+    with appropriate size and correct total flux. For galaxies described by single- or double-\ser{} models, \synpipe{} passes the
     input \ser{} index and effective radius to the \galsim{}\texttt{.Sersic} function to
@@
     For a double-\ser{} model, \synpipe{} uses the \galsim{}\texttt{.Add} method to
-    combine the two \ser{} components.
-    For parametric models from the GREAT3 catalog, \synpipe{} uses the
-    \texttt{COSMOSCatalog.makeGalaxy} method to generate a corresponding model; in the
-    case of a real high-resolution image, \synpipe{} uses the
-    \galsim{}\texttt{.RealGalaxy} method.
-    If necessary, additional shear ($g_1$ and $g_2$) can be applied to the model at
+    combine two \ser{} components. For  parametric models from the GREAT3 catalog, \synpipe{} uses the
+    \texttt{COSMOSCatalog.makeGalaxy} method to generate models.  To inject  real HST galaxy images,  \synpipe{} calls the \galsim{}\texttt{.RealGalaxy} method.
+    If necessary, an additional shear ($g_1$ and $g_2$) can be applied to the model at
     this point.
@@
     The newly generated single-\visit{} images have the same format and data
-    structure as the real HSC data; therefore, \synpipe{} can directly feed them
-    to the other \hscpipe{} steps.
+    structure as real HSC data. To perform stacking and measurements, \synpipe{} calls standard \hscpipe{} routines.
+
     The \texttt{stack.py} step takes the improved astrometric and photometric
     calibrations for each \visit{} from the original reduction and creates
-    \coadd{}  images with synthetic objects on them.
-    Then the \texttt{multiBand.py} step processes these \coadd{}  images and
+    \coadd{}  images that contain synthetic objects.
+    The \texttt{multiBand.py} step then processes these \coadd{}  images and
     provides standard multi-band measurements in FITS catalogs that are grouped by
@@
 
-    Using the infrastructures provided by \hscpipe{}, the user can easily perform the
-    above processes in parallel, and the overall efficiency of \synpipe{} is similar to
-    the real data reduction process.
-    The processes also generate the same amount of images and catalog data as the
-    original data reduction process.
-
-    As the last step, \synpipe{} matches the input catalog to the results within a
-    radius that is specified by the user, and merges all the \unforced{} and
-    \forced{} measurements from all the \texttt{Patches}.
+    Using the infrastructures provided by \hscpipe{}, the user can easily perform these steps in parallel, and the overall efficiency of \synpipe{} is similar to
+    the real data reduction process. The data and catalog volumes is also similar to the original data reduction process.
+
+ The final step is to identify Synthetic galaxies in the output catalogs.
+\synpipe{} can match the input catalog to the output catalog (this contains a mix of real and synthetic galaxies) using a matching radius that is specified by the user.
     Each unmatched object from the input catalog is also passed to the results catalog
@@
     \caption{
-        Magnitude and color distributions of the synthetic stars.
-        \textbf{Upper panel} shows the five-band magnitude distributions of the COSMOS
-        stars (filled histograms) and the resampled stars (dashed lines).
-        \textbf{Lower panel} shows their color-color distributions
-        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$).
-        We show the number density distribution of the COSMOS stars in hexagonal bins,
-        and use contours for the resampled stars.
-        }
+        Magnitude and color distributions of synthetic stars.
+        \textbf{Upper panel}: five-band magnitude distributions of the COSMOS
+        stars (filled histograms) and  resampled stars (dashed lines).
+        \textbf{Lower panel}: color-color distributions
+        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$). Hexagonal bins indicate COSMOS stars and contours indicate resampled stars.}
     \label{fig:star_sample}
@@
     \end{center}
-    \caption{
-        Synthetic galaxy distributions of five-band magnitudes (\textbf{upper panel})
-        and other properties
-        (\texttt{lower panel}; from left to right are the \ser{} index, axis ratio,
-        effective radius in arcsec, the $g-r$ and $r-z$ colors).
-        Objects used for the \textbf{Tract} with good seeing (filled histograms) and
-        the one with bad seeing (dashed line) have almost identical distributions.
-        }
+    \caption{ textbf{Upper panel}: five-band magnitude distributions of synthetic galaxies. (\texttt{lower panel}; from left to right are the \ser{} index, axis ratio,
+        effective radius in arcsec, the $g-r$ and $r-z$ colors).}
     \label{fig:galaxy_sample}
@@
 
-    Here we demonstrate the application of \synpipe{} via testing the basic performance
-    of HSC photometry for both stars and galaxies.
-
-%% ------------------------------------------------------------------------------------ %%
-\subsection{Test Data}
-
-    Given the \synpipe{} design and the HSC DR1 data volume \footnote{${\sim}70$
-    TB of images}, it is not realistic to test the whole dataset.
-    For this work, we select two \tracts{} in HSC Wide regions
-    that fit the following criteria:
-
-    \begin{enumerate}
-
-        \item Not at the edge of any Wide region, so the full \tract{} is
-            useful for test.
-
-        \item Not distorted by an extremely bright ($i<12$ mag), saturated star.
-
-        \item Can represent both good and bad seeing conditions in the current $i$-band
-            data of the HSC survey.
-            Since for any given star or galaxy, different seeing conditions affect its
-            central S/N on the \coadd{} images and, therefore, also impact the
-            detection and deblending processes in \hscpipe{}.
-
-    \end{enumerate}
-
-    The two selected HSC Wide regions are as follows:
-    \tract{}$=9699$ in the VVDS field (median FWHM$=0.449$\asec{} in $i$-band;
+    We now describe the  generation of the synthetic data set that we use to characterize the performance of \hscpipe{}.
+
+%% ------------------------------------------------------------------------------------ %%
+\subsection{Data}
+    We use \tract{}$=9699$ in the VVDS field (median FWHM$=0.449$\asec{} in $i$-band;
     in this paper referred to as \texttt{goodSeeing}) and
@@
     20--40 \visits{}.
+These  two \tract{} are selected  because they are not at the edge of a field, do not contain any  extremely bright ($i<12$ mag) saturated stars, and  are representative of both "good" and "bad" seeing conditions in the $i$-band.
 
@@
 
-    In this work, we use objects from the high-resolution \hst{}/ACS COSMOS field
-    observations to build input catalogs of realistic synthetic stars and galaxies with
-    appropriate completeness for the Wide survey and with reasonable five-band colors.
-    We first select stars and galaxies as described below;
-    we then create the input catalogs via randomly distributing the selected synthetic
-    stars and galaxies into the regions covered by the good- and bad-seeing \tracts{}.
-    For stars, we use a number density of 1,000 per CCD; for galaxies, we use a number
-    density of 500 per CCD.
-
-    For star selection, we use the sample from \citet{Leauthaud2007}.
-    We use not only the \texttt{SExtractor} stellar classification index
-    (\texttt{CLASS\_STAR}) but also the peak surface brightness above background
-    (\texttt{MU\_MAX}) and half-light radius (\texttt{RHL}) to select stars with clean
-    photometry.
-    The classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag.
-    We match this sample of stars with the HSC UltraDeep--COSMOS data that currently
-    reach to about ${\sim}27.2$ mag in $i$-band.
-    After filtering the matched sample through basic quality cuts (see \ref{app:qc}),
-    we gather five-band HSC photometry for 14,472 stars.
-    To get a larger sample for the test, we resample the five-band magnitude
-    distributions using \texttt{astroML} (\citealt{astroml}) alternative
-    implementation of the \texttt{extreme-deconvolution} algorithm developed by
+We use a synthetic star sample built using data from  the HST/ACS catalog of \citet{Leauthaud2007}.
+We first select stars from the  \citet{Leauthaud2007} catalog (this classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag).
+We then match this sample against our HSC UltraDeep--COSMOS data (which reaches ${\sim}27.2$ mag in $i$-band).
+After applying basic quality cuts (see \ref{app:qc}), this procedure  provides us with five-band HSC photometry for 14,472 stars.
+To increase the sample size, we re-sample the five-band magnitude distributions using the \texttt{astroML} (\citealt{astroml}) implementation of the \texttt{extreme-deconvolution} algorithm developed by
     \citet{Bovy2011}
     \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
-    generate 100,000 synthetic stars.
-    In Fig \ref{fig:star_sample}, we show that the magnitude and color distributions of
-    the real COSMOS stars are nicely recovered by the resampled stars in all
-    five-band magnitude and two color-color space distributions.
-
-    For synthetic galaxies, we use the single-\ser{} galaxy models
-    in the COSMOS field that have $I_{F814W} \leq 25.2$ mag.
-    These models are created via a method developed by \citet{Lackner2012} on the
-    \textit{HST}/ACS images and are included in \galsim{}.
+    generate 100,000 synthetic stars. Fig \ref{fig:star_sample} shows the magnitude and color distributions of real COSMOS stars compared to the resampled distributions in all
+    five-bands and in color-color space.
+
+    For synthetic galaxies, we use single-\ser{} galaxy models of COSMOS galaxies with $I_{F814W} \leq 25.2$ mag.
+These are models from \citet{Lackner2012} applied to \textit{HST}/ACS images and are included in \galsim{}.
 Each model is described by a total of five parameters: magnitude, effective radius,
     \ser{} index, axis ratio, and position angle.
-    Although the single-\ser{} model is not always the best choice, its flexibility
+    Although the single-\ser{} model is not always the best choice for describing galaxies, its flexibility
     enables it to reasonably describe the flux distribution of most galaxies.
-    Also, its simplicity makes it easy for us to diagnose potential problems of the
-    \cmodel{} photometry.
+    Also, its simplicity makes it easy for us to diagnose potential problems with the \cmodel{} photometry.
     We exclude a tiny fraction of ill-behaved models that have a very high \ser{}
@@
     We further match this COSMOS sample with the HSC UltraDeep--COSMOS data.
-    After removing the objects with problematic photometry, we obtain a sample of
+    After removing objects with problematic photometry, we obtain a sample of
     58,210 synthetic galaxies with realistic five-band HSC photometry.
@@
 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-\subsection{Running the \synpipe{} Tests}
+    We spatially distribute synthetic stars and galaxies randomly in our two selected \tracts{}. For stars, we use a number density of 1,000 per CCD. For galaxies, we use a number
+    density of 500 per CCD.
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+\subsection{Generating \synpipe{} Data}
     \label{ssec:running}
@@
     We use HSC DR1 data stored at Kavli Institute for the Physics and Mathematics of 
-    the Universe (Kavli IPMU) to conduct the \synpipe{} tests on the cluster 
-    (\texttt{Master}).
-    The \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in each
-    band; the same process takes longer for the galaxy tests (${\sim}3.0$ hours per
+    the Universe (Kavli IPMU). For stars the \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in each
+    band. The same process takes longer for galaxy tests (${\sim}3.0$ hours per
     \tract{} in each band) because the \galsim{} simulation is more time consuming.
@@
     to generate output catalogs for \forced{} and \unforced{} photometry
-    in each band.
-    We also match the input catalogs with the original HSC catalogs to identify the
-    ``ambiguously blended'' objects, which are defined as so extreme blends that 
-    some objects are detected as a single object.
-    The ambiguously blended objects are useful in the WL-related statistical tests 
-    (see Murata et al. in prep. for more details); but since they will not help test 
-    photometry, they will be excluded later.
-
-    The detailed log of the entire tests can be found at \url{goo.gl/VINOVP}.
+    in each band. For our tests, we reject  synthetic objects  locate within 2 pixels of a real HSC object.
+
+    The detailed log of our runs can be found at \url{goo.gl/VINOVP}.
     The user should be able to reproduce the results presented in this work using 
-    this information. It can also serve as a brief manual for running a \synpipe{} 
-    test.
+    this information. It can also serve as a brief manual for generating \synpipe{} data.
 
@@
     these two are the only options that consider the effects of PSF in different bands 
-    and are consistent across all bands in terms of position and shape. T
-    Therefore, they are the most appropriate and relevant methods for star and galaxy.
-    \song{Edit stops here}
+    and are consistent across all bands in terms of position and shape.
+
 %% ------------------------------------------------------------------------------------ %%
@@
         Hexagonal binned density plots and contours show the distributions for
-        stars in both the good- and bad-seeing \tracts{}.
-        The highly blended stars are highlighted using scatter plots.
-        The gray dashed line marks $S/N = 5$.
+        stars in both the good- and bad-seeing \tracts{}. Highly blended stars are highlighted using scatter plots.
+        The gray dashed line marks $S/N = 5$ which is the detection threshold used by \hscpipe{}.
+Our 5$\sigma$  point source detection limit  is \alexie{xxxx} however we do not reach these magnitudes with our current synthetic stellar input catalog.
         }
@@
     The error of the PSF magnitude from \hscpipe{} only considers the per-pixel noise,
-    and does not include centroid uncertainty.
+    and does not include centroid uncertainties.
     \hscpipe{} also estimates aperture correction for PSF photometry.
@@
 
-    In our tests, we randomly inject ${\sim}100,000$ stars into each \tract{} in all
+    We randomly inject ${\sim}100,000$ stars into each \tract{} in all
     five bands. Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the centroids
-    of real objects; we remove those stars from the sample to avoid confusion in the comparisons.
-    After this step, ${\sim}1$--$3$\% of the remaining synthetic stars still have no match in the \synpipe{} outputs.
-    They could either be below the detection threshold or ambiguously blended with real objects.
-    The input $i$-band magnitudes of these unmatched stars are on average ${\sim}0.9$
-    mag fainter than the matched ones.
-    The fraction of unmatched stars is slightly higher in the bad seeing \tract{}; this result is consistent with our expectation that magnitude depends on seeing conditions,
-    although the difference is not very significant.
-    For the matched stars, we select the primary detections
+    of real objects; we remove those stars from the sample to avoid confusion in the comparisons. \alexie{xxxxxx}
+ %   After this step, ${\sim}1$--$3$\% of the remaining synthetic stars still have no match in the \synpipe{} outputs.
+ %   They could either be below the detection threshold or ambiguously blended with real objects \alexie{said you identified those}.
+ %   The input $i$-band magnitudes of these unmatched stars are on average ${\sim}0.9$
+ %   mag fainter than the matched ones.
+ %   The fraction of unmatched stars is slightly higher in the bad seeing \tract{}; this result is consistent with our expectation that magnitude depends on seeing conditions,
+ %   although the difference is not very significant \alexie{cut?}.
+    For matched stars, we select the primary detections
     (\texttt{detect.is-primary=True}) that have good photometric quality
@@
 
-    Next, we isolate the stars that are misidentified by \hscpipe{} as extended
+    Next, we identify stars that are misidentified by \hscpipe{} as extended
     objects using the \texttt{classification.extendedness} parameter in each band.
@@
     while $i$-band is recommended for selecting point sources.
-    The misclassified stars are on average ${\sim}1$ mag fainter than the others.
+    The misclassified stars are on average ${\sim}1$ mag fainter than the others \alexie{xx}.
     We exclude them from the photometric comparison below, and further discuss
@@
 
-    Besides seeing, ``blendedness'' ($b$; parameter that describes on what level
-    the flux distribution of one object is affected by others; please see
-    Appendix \ref{app:defineb} for precise definition, and see Murata\etal in prep.
-    for details) is another factor that influences the photometric accuracy.
-    Therefore, we separate the samples into relatively isolated and highly blended
-    groups based on the $b$ values.
-    Assuming zero pixel noise, $b$ of object $A$ reflects the fraction of flux
-    within the  $A$ \texttt{Footprint} that comes from other objects.
-    Ideally, $b=0$, which means perfect isolation; $b{\sim}1$ means completely
-    confused with another object.
+    Besides seeing, the degree to which an object is blended with other objects  is another factor that influences photometric accuracy.
+To quantify the impact of blending effects, we use the ``blendedness'' parameter, $b$.
+This parameter describes how  much any given object overlaps with neighboring objects (see Appendix \ref{app:defineb} and Murata\etal in prep.).
+We divide our sample  according to the  blendedness parameter.
+A value of $b=0$ corresponds to isolated objects whereas  objects with $b=1$ complete overlap with other objects.
 Here we use $b>0.05$ to define highly blended stars (${\sim}4$--$9$\% are blended).
-    The fraction of highly blended stars slightly increases in the bad seeing \tract{}.
-    We highlight these stars separately as well, and will discuss more about the
-    impact of blendedness in Section \ref{ssec:blendedness}.
-
-\subsubsection{PSF photometry input magnitude and \s2n{} }
-
-    In discussing the relation between the input magnitude and the
-    signal-to-noise ratio of the output PSF photometry, we define \s2n{} simply as
+    The fraction of highly blended stars slightly increases in the bad seeing \tract{}. The
+    impact of blendedness will be discussed more in Section \ref{ssec:blendedness}.
+
+\subsubsection{Relationship between stellar magnitude and \s2n{}}
+
+\alexie{TO HERE}
+
+We define the  \s2n{} for PSF photometry as
     $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band
-    without considering the aperture correction.
+    without considering aperture corrections.
     This helps us visualize

### 2017-04-21 draft/ms_v4.tex
Update abstract

@@
 %% ------------------------------------------------------------------------------------ %%
-\title{Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.}
+\title{Characterization and Photometric Performance of the Hyper Suprime-Cam 
+       Software Pipeline.}
 
@@
     using the Hyper Suprime-Cam (HSC) on the Subaru telescope. 
-The  Wide layer of the SSP is both wide and deep, reaching a detection limit of $i>26.0$ mag.
-At these depths, it is challenging to achieve accurate, unbiased, and consistent photometry across all
-    five bands.
-The HSC data are reduced using a pipeline that builds on the prototype pipeline being designed by the Large Synoptic Survey Telescope’s Data Management system.
-We have developed a \texttt{Python}-based, flexible framework to inject synthetic galaxies into real HSC images called \synpipe{}.
-In this paper, we explain the design and implementation of \synpipe{} and we generate a sample of synthetic galaxies to examine the photometric performance of the HSC pipeline.
-For stars, we achieve 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and ${\sim}0.06$ mag respectively).
-\alexie{Put numbers in here using this phrase format} For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry achieves 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and ${\sim}0.06$ mag respectively).
-    %For synthetic galaxies based on a single-\ser{} model, uncertainties of the
-    %forced \cmodel{} photometry typically range from 0.14 mag at $i{\sim}20.0$ mag
-    %to 0.20 mag at $i{\sim} 25.2$ mag.
-    we show that
-    both \forced{} PSF and \cmodel{} photometry yield unbiased color estimates
-    that are robust to seeing conditions.
-We identify several caveats that apply to version xxx of the  HSC pipeline and than need to be considered when using data from the first public HSC data release.
-First, the degree to which an object is blended with other objects impacts the overall photometric performance.
-This is especially true for point sources \alexie{quanityf here}.
-Highly blended objects tend to have larger photometric uncertainties, systematically underestimated fluxes \alexie{Should be overestimated here no?}, and slightly biased colors.
-Second, a relatively high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
-    misclassified as extended objects \alexie{need to quantify here}. Third, the shape and size estimates for galaxies using \cmodel{} suffer from strong
-    biases \alexie{quantify here}.
+    The Wide layer of the SSP is both wide and deep, reaching a detection limit of 
+    $i>26.0$ mag. 
+    At these depths, it is challenging to achieve accurate, unbiased, and consistent
+    photometry across all five bands. 
+    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
+    being designed by the Large Synoptic Survey Telescope’s Data Management system. 
+    We have developed a \texttt{Python}-based, flexible framework to inject synthetic
+    galaxies into real HSC images called \synpipe{}. 
+    In this paper, we explain the design and implementation of \synpipe{} and generate 
+    a sample of synthetic galaxies to examine the photometric performance of the HSC
+    pipeline. 
+    For stars, we achieve 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at
+    $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and 
+    ${\sim}0.06$ mag respectively).  
+    For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
+    achieves 7\% photometry at $i{\sim}20.0$ mag and 11\% photometry at $i{\sim}25.0$ 
+    in the $i$-band (corresponding to uncertainties of ${\sim}0.14$ and ${\sim}0.20$ 
+    mag respectively). 
+    We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
+    estimates that are robust to seeing conditions. 
+    We identify several caveats that apply to version \texttt{4.0.2} of the HSC 
+    pipeline and they need to be considered when using data from the first public 
+    HSC data release. 
+    First, the degree to which an object is blended with other objects impacts the 
+    overall photometric performance.  
+    This is especially true for point sources. 
+    Highly blended objects tend to have larger photometric uncertainties, 
+    systematically underestimated fluxes and slightly biased colors. 
+    Second, $>20$\% of stars at $22.5< i < 25.0$ mag can be misclassified as 
+    extended objects.
+    Third, the current \cmodel{} algorithm tends to strongly underestimate the 
+    half-light radius and ellipticity of galaxies with $i>21.5$ mag.
 

### 2017-04-22 draft/ms_v4.tex
Update until Section 6.1

@@
     Wide-field, multi-band imaging surveys have stepped onto the central stage of
-    modern astrophysics and cosmology over the past decade.  These efforts will soon be replaced with even more ambitious programs such as the Large Synoptic Survey Telescope
+    modern astrophysics and cosmology over the past decade.  
+    These efforts will soon be replaced with even more ambitious programs such as the 
+    Large Synoptic Survey Telescope
     (LSST)\footnote{\url{https://www.lsst.org/}}, the Wide-Field Infrared Survey
@@
     and the \textit{Euclid} project
-    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}. Among many ongoing efforts, the Subaru Strategic Program
+    (\citealt{Laureijs2012})\footnote{\url{http://sci.esa.int/euclid/}}. 
+    Among many ongoing efforts, the Subaru Strategic Program
     (SSP; \citealt{HSCDR1})\footnote{\url{http://hsc.mtk.nao.ac.jp/ssp/}}, which
@@
     etendue\footnote{The collecting area multiplied by the field of view.}. 
-Surveys such as HSC, and other to follow, will  provide stringent constraints on  the cosmological model,  characterize the evolution of galaxies, map out the stellar structure of our Milky Way, and are poised to discover a large number of interesting transient objects.
+    Surveys such as HSC, and other to follow, will provide stringent constraints on 
+    the cosmological model, characterize the evolution of galaxies, map out the 
+    stellar structure of our Milky Way, and are poised to discover a large number of
+    interesting transient objects.
 
@@
     how to handle the the large amounts of data\footnote{Right now, SSP has accumulated
-    ${\sim}300$ TB of data products.} generated by these projects while satisfying  strict requirements for  high quality image processing with accurate measurement for the magnitudes and shapes of stars and galaxies.
+    ${\sim}300$ TB of data products.} generated by these projects while satisfying  
+    strict requirements for high quality image processing with accurate measurement 
+    for the magnitudes and shapes of stars and galaxies. 
     Data handling becomes increasingly challenging in the age of modern imaging
@@
     %
-
     These challenges are not merely technical details; their resolution is crucial
@@
 
- \alexie{Edit here following this format}. In Section 1 we ... in section 2 we ....
-
-    Below, we briefly introduce the HSC survey and the current status of data
-    reduction (Section \ref{sec:ssp}), explain \synpipe{} design and implementation
-    (Section \ref{sec:synpipe}), and demonstrate \synpipe{} usage via straightforward
-    tests (Section \ref{sec:test}) that focus on the general photometric quality for
-    both synthetic stars and galaxies (Section \ref{sec:result}).
-    We then summarize the work and discuss future developments in
-    Section \ref{sec:summary}.
+    In Section \ref{sec:ssp}, we briefly introduce the HSC survey and the current status
+    of data reductionin. 
+    In Section \ref{sec:synpipe}, we explain \synpipe{} design and implementation.
+    In Section \ref{sec:test}, we demonstrate \synpipe{} usage via straightforward
+    tests, we show the main results for the general photometric quality of synthetic 
+    stars and galaxies in Section \ref{sec:result}.
+    We then summarize the work and discuss future developments in Section 
+    \ref{sec:summary}.
 
@@
         between \texttt{Tracts}, \texttt{Patches}, and \texttt{Visits}. 
-The xxxxxxx colored box corresponds to one \texttt{Tract} which has an area of about xx deg$^2$.
-Large colored circles are \texttt{Visits} (also commonly known as "pointings") with small rectangles representing CCDs.
+        The red colored box corresponds to one \texttt{Tract} which has an area of 
+        about 1.5 deg$^2$. 
+        Large colored circles are \texttt{Visits} (also commonly known as "pointings") 
+        with small rectangles representing CCDs. 
         \texttt{Patches} are represented by black dashed lines. 
-One \texttt{Tract} typically contains xx  \texttt{Patches}.}
+        One \texttt{Tract} typically contains 81 \texttt{Patches}.}
     \label{fig:flowchart}
@@
             an even integer.
-            After initial data screening (considering the background level, seeing, and transparency
-            Furusawa\etal in prep.), \hscpipe{} detrends these data (subtraction
-            of overscan, bias, and dark; flatfielding), \alexie{xxxxx} generates variance and mask
-            images, subtracts the background, and provides initial astrometric and
-            photometric calibrations. \synpipe{} uses the spatially varying PSF models, photometric zeropoints, and the World Coordinate System (WCS; \citealt{WCS1, WCS2})
+            After initial data screening (considering the background level, seeing, 
+            and transparency Furusawa\etal in prep.), \hscpipe{} subtracts overscan, 
+            bias, and dark frames, and performs flatfielding to the single CCD images.
+            During this step, \hscpipe{} also generates variance and mask images, 
+            subtracts the background, and provides initial astrometric and photometric
+            calibrations. 
+            \synpipe{} uses the spatially varying PSF models, photometric zeropoints, 
+            and the World Coordinate System (WCS; \citealt{WCS1, WCS2})
             corrected for optical distortion provided by \hscpipe{}.
+
         \item \textbf{Multi-\visit{} Processing}:
@@
             adjacent \texttt{Patches} overlap each other by 100 pixels.
+
         \item \textbf{Multi-band Measurements}:
@@
 The goal of the  \forced{} photometry step is to generate accurate colors.
+
         \item \textbf{HSC Photometry}:
@@
             the difference between \texttt{psf} and \cmodel{}{} magnitudes.
+
     \end{enumerate}
+%% ------------------------------------------------------------------------------------ %%
 
@@
     behavior of the stellar sequence.
-    Generally speaking, the PSF photometry is accurate at the 1--2\% level \alexie{only for bright stars}, and the
-    astrometry is accurate to ${\sim}10$ and 40 max internally and externally.
+    Generally speaking, the PSF photometry is accurate at the 1--2\% level for bright 
+    stars, and the astrometry is accurate to ${\sim}10$ and 40 max internally and 
+    externally.
 
@@
 
-    \alexie{Can we use bullet points to highlight the different steps? This paragraph is really hard to read.}
-
-    With the input catalog and test data information in hand, \synpipe{}injects synthetic
-    objects into single-exposure images (step \texttt{addFakes.py}; see the middle panel
-    of Fig \ref{fig:flowchart}).
-    \synpipe{} goes through all the individual CCD images that belong to each \visit{}
-    and decides which synthetic objects from the input catalog need to be injected.
-    \synpipe{} uses the \textit{initial astrometric calibration} of each single
-    \visit{} to convert the input coordinates into locations on the CCD image.
-For each synthetic object, \synpipe{} uses the  reconstructed PSF for each exposure.
-The photometric zero point from the single-\visit{} calibration is used to convert input magnitudes of synthetic objects into fluxes.
-For point sources, \synpipe{} generates a rectangular cutout image of the PSF model
-    with appropriate size and correct total flux. For galaxies described by single- or double-\ser{} models, \synpipe{} passes the
-    input \ser{} index and effective radius to the \galsim{}\texttt{.Sersic} function to
-    create a \ser{} component.
-    After stretching and rotating the galaxy to the expected axis ratio and position
-    angle via the \texttt{shear} and \texttt{rotate} methods, \synpipe{} assigns the
-    correct flux to this component.
-    For a double-\ser{} model, \synpipe{} uses the \galsim{}\texttt{.Add} method to
-    combine two \ser{} components. For  parametric models from the GREAT3 catalog, \synpipe{} uses the
-    \texttt{COSMOSCatalog.makeGalaxy} method to generate models.  To inject  real HST galaxy images,  \synpipe{} calls the \galsim{}\texttt{.RealGalaxy} method.
-    If necessary, an additional shear ($g_1$ and $g_2$) can be applied to the model at
-    this point.
+    \begin{itemize}
+
+        \item With the input catalog and test data information in hand, \synpipe{} 
+            injects synthetic objects into single-exposure images (step
+            \texttt{addFakes.py}; see the middle panel of Fig \ref{fig:flowchart}).
+            \synpipe{} goes through all the individual CCD images that belong to 
+            each \visit{} and decides which synthetic objects from the input catalog 
+            need to be injected. 
+            \synpipe{} uses the \textit{initial astrometric calibration} of each 
+            single \visit{} to convert the input coordinates into locations on the 
+            CCD image. 
+            For each synthetic object, \synpipe{} uses the reconstructed PSF for each 
+            exposure.  
+            The photometric zero point from the single-\visit{} calibration is used
+            to convert input magnitudes of synthetic objects into fluxes.
+
+        \item With the help of \galsim{} module, \synpipe{} simulate the images of
+            synthetic objects.
+            \begin{itemize}
+
+            \item For point sources, \synpipe{} generates a rectangular cutout image 
+                of the PSF model with appropriate size and correct total flux.
+
+            \item For galaxies described by single- or double-\ser{} models, 
+                \synpipe{} passes the input \ser{} index and effective radius to 
+                the \galsim{}\texttt{.Sersic} function to create a \ser{} component.
+                After stretching and rotating the galaxy to the expected axis ratio 
+                and position angle via the \texttt{shear} and \texttt{rotate} methods,
+                \synpipe{} assigns the correct flux to this component.
+
+            \item For a double-\ser{} model, \synpipe{} uses the \galsim{}\texttt{.Add}
+                method to combine two \ser{} components.
+
+            \item For parametric models from the GREAT3 catalog, \synpipe{} uses the
+                \texttt{COSMOSCatalog.makeGalaxy} method to generate models.
+
+            \item To inject real HST galaxy images, \synpipe{} calls the \galsim{}    
+                \texttt{.RealGalaxy} method.
+
+            \end{itemize}
+
+        If necessary, an additional shear ($g_1$ and $g_2$) can be applied to the 
+        model at this point.
         Then, \synpipe{} passes the reconstructed PSF image into a
-    \galsim{}\texttt{InterpolatedImage} object and convolves it with the galaxy model
-    using \galsim{}\texttt{.Convolve}.
-    After this, \synpipe{} uses the \galsim{}\texttt{.drawImage} method to create the
-    image of the simulated galaxy.
-    A component with a high \ser{} index ($n_{\mathrm{Ser}} > 4$) often requires a
-    large image size to cover all of its flux, so \synpipe{} allows the user to
-    truncate the model at a given radius (N$\times R_{\mathrm{e}}$).
+        \galsim{}\texttt{InterpolatedImage} object and convolves it with the galaxy 
+        model using \galsim{}\texttt{.Convolve}.
+        After this, \synpipe{} uses the \galsim{}\texttt{.drawImage} method to create 
+        the image of the simulated galaxy.
+        A component with a high \ser{} index ($n_{\mathrm{Ser}} > 4$) often requires 
+        a large image size to cover all of its flux, so \synpipe{} allows the user 
+        to truncate the model at a given radius (N$\times R_{\mathrm{e}}$).
         \synpipe{} will also give warning information when a component with $
@@
 
-    After \synpipe{} creates the image of the simulated galaxy, it then shifts the
-    image according to is location on the CCD on a pixel-by-pixel basis;
-    \synpipe{} also crops the images when necessary.
-    When that task is complete, \synpipe{} adds appropriate noise to the image based
-    on the pixels it covers and the calibration information of the detector, and creates
-    a variance image that reflects the influence of the synthetic object.
-    Since each HSC CCD consists of 4 amplifiers, each with different characteristics,
-    \synpipe{} carefully creates a corresponding gain map to provide accurate noise
-    level.
-    In the final step, \synpipe{} adds the noise-added image and the variance map to the
-    original CCD data while also adding a new \texttt{FAKE} mask bit to the mask plane.
+        \item After \synpipe{} creates the image of the simulated galaxy, it then 
+            shifts the image according to is location on the CCD on a pixel-by-pixel 
+            basis; \synpipe{} also crops the images when necessary.
+            When that task is complete, \synpipe{} adds appropriate noise to the 
+            image based on the pixels it covers and the calibration information of 
+            the detector, and creates a variance image that reflects the influence 
+            of the synthetic object.
+            Since each HSC CCD consists of 4 amplifiers, each with different 
+            characteristics, \synpipe{} carefully creates a corresponding gain map 
+            to provide accurate noise level.
+
+        \item In the final step, \synpipe{} adds the noise-added image and the 
+            variance map to the original CCD data while also adding a new 
+            \texttt{FAKE} mask bit to the mask plane.
             The middle panel of Fig \ref{fig:flowchart} depicts the result of the
-    \texttt{addFakes.py} step by showing an example CCD image before and after the
-    synthetic objects are injected.
+            \texttt{addFakes.py} step by showing an example CCD image before and 
+            after the synthetic objects are injected.
+
+    \end{itemize}
 %% ------------------------------------------------------------------------------------ %%
@@
         Hexagonal binned density plots and contours show the distributions for
-        stars in both the good- and bad-seeing \tracts{}. Highly blended stars are highlighted using scatter plots.
-        The gray dashed line marks $S/N = 5$ which is the detection threshold used by \hscpipe{}.
-Our 5$\sigma$  point source detection limit  is \alexie{xxxx} however we do not reach these magnitudes with our current synthetic stellar input catalog.
+        stars in both the good- and bad-seeing \tracts{}. 
+        Highly blended stars are highlighted using scatter plots.
+        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
+        by \hscpipe{}.  
+        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
+        however we do not reach these magnitudes with our current synthetic stellar 
+        input catalog.
         }
@@
     five bands. Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the centroids
-    of real objects; we remove those stars from the sample to avoid confusion in the comparisons. \alexie{xxxxxx}
+    of real objects; we remove those stars from the sample to avoid confusion in the comparisons.
      %   After this step, ${\sim}1$--$3$\% of the remaining synthetic stars still have no match in the \synpipe{} outputs.

### 2017-04-22 draft/ms_v4.tex
More edits from Alexie

@@
 
-    Next, we identify stars that are misidentified by \hscpipe{} as extended
+    Next, we exclude stars that are misidentified by \hscpipe{} as extended
     objects using the \texttt{classification.extendedness} parameter in each band.
-    The fraction of misclassification is ${\sim}8$--$15$\%, and clearly depends on
+    The fraction of misclassification is ${\sim}10$--$20$\%, and clearly depends on
     seeing conditions.
@@
     while $i$-band is recommended for selecting point sources.
-    The misclassified stars are on average ${\sim}1$ mag fainter than the others \alexie{xx}.
-    We exclude them from the photometric comparison below, and further discuss
-    the star--galaxy separation issue in Section \ref{ssec:sg}.
+    The star--galaxy separation issue is discussed more in Section \ref{ssec:sg}.
 
@@
 
-\alexie{TO HERE}
-
-We define the  \s2n{} for PSF photometry as
-    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band
-    without considering aperture corrections.
-    This helps us visualize
-    1) the detection limit for point sources,
-    2) the impact of seeing condition on PSF photometric,
-    3) and the scatter of photometric accuracies at a fixed input magnitude given all
-       the realistic features of HSC images (e.g., background subtraction, nearby
-       objects, optical artifacts).
-    We show the results for $g$- and $i$-bands in Fig \ref{fig:star_sn}, and find close
-    relations in both bands.
-
-    As expected, we clearly see that the seeing condition impacts the \s2n{} of point
+The \s2n{} for PSF photometry is defined as
+    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band (no aperture corrections) \alexie{have you defined aperture correction?}.
+Figure  \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} in the $g$- and $i$-bands.
+This Figure  shows the expected  \s2n{} of stars as a function of magnitude for the Wide layer.
+
+%    This helps us visualize
+%    1) the detection limit for point sources,
+%    2) the impact of seeing condition on PSF photometric,
+%    3) and the scatter of photometric accuracies at a fixed input magnitude given all
+%       the realistic features of HSC images (e.g., background subtraction, nearby
+%       objects, optical artifacts). \alexie{Why is this relevant in this figure? I wouldn't use SN to quantofy this?}
+
+    Figure \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
     sources at fixed input magnitude.
@@
     lower \s2n{} than the good-seeing (0.5\asec{}) \tract{}.
-     \s2n{} is similar for the two $g$-band \tracts{} because they share similar seeing conditions.
-    Our results show that blendedness can also affect the accuracy of PSF photometry.
-    In $i$-band, the highly blended synthetic stars scatter toward lower \s2n{} at
-    fixed magnitude.
-    Interestingly, the effect is not obvious in $g$-band, suggesting the deblending
-    process and photometric quality of blended objects also depend on seeing condition.
+     The \s2n{} is similar for the two $g$-band \tracts{} because they share similar seeing conditions. 
+    %Our results show that blendedness can also affect the accuracy of PSF photometry.\alexie{why use SN here?}
+    %In $i$-band, the highly blended synthetic stars scatter toward lower \s2n{} at
+    %fixed magnitude.
+    %Interestingly, the effect is not obvious in $g$-band, suggesting the deblending
+    %process and photometric quality of blended objects also depend on seeing condition.
 
@@
 
-\subsubsection{Accuracy of PSF magnitude}
-
-    Now, we look into PSF magnitude accuracy in each of the five bands
-    independently.
-    Fig \ref{fig:psf_mag} shows the relation between the input magnitude and the
-    magnitude difference from the \hscpipe{} \forced{} PSF photometry.
-
-    The overall performance of PSF photometry is excellent.
-    In $i$-band, the median magnitude difference for \tract{} with 0.45\asec{} seeing is
-     ${\sim}0.015$ mag (${\sim}1.5$\% accuracy) at
-    $i_{\mathrm{Input}}{\sim}19.0$ mag.
-    At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of PSF
-    magnitude holds at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
+%% ------------------------------------------------------------------------------------ %%
+\subsubsection{Accuracy of PSF magnitudes}
+
+    We now investigate the accuracy of the PSF magnitude in each of the five bands
+    independently. Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the  \hscpipe{} \forced{} PSF magnitude as a function of input magnitude.
+
+    The overall performance of the \hscpipe{} \forced{} PSF magnitude is excellent. The median $i$-band magnitude difference for the \tract{} with 0.45\asec{} seeing is
+     ${\sim}0.015$ mag (${\sim}1.5$\%) at
+    $i_{\mathrm{Input}}{\sim}19.0$ mag. At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of the PSF
+    magnitude is ${\sim}3$\% level (${\sim}0.036$ mag average difference).
     At $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
-    ${\sim}7$\% level with an average ${\sim}0.072$ mag difference.
-    The bad-seeing \tract{} shows similar accuracy of PSF photometry at
-    $i_{\mathrm{Input}}<23.5$ mag.
-    At the faint end, the accuracy becomes slightly worse: ${\sim}5$\% accuracy around
-    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% accuracy around
+    ${\sim}7$\% with an average ${\sim}0.072$ mag difference.
+
+    The accuracy of the PSF photometry for the bad-seeing \tract{} shows a similar performance at  $i_{\mathrm{Input}}<23.5$ mag.
+At fainter magnitudes, the accuracy slightly degrades.
+The bad-seeing \tract{} displays a performance of ${\sim}5$\% accuracy at
+    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% accuracy at
     $i_{\mathrm{Input}}{\sim}25.2$ mag.
@@
     with the PS1, PV2, and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
-    which is consistent with our results.
-    At fainter magnitude, external comparisons become difficult due to the lack of deep
-    imaging data at HSC level and also due to the impact of the color-term when comparing photometry
-    using different filters.
-    The results from \synpipe{} hence provide more useful evaluations down to the
-    detection limit\footnote{Strictly speaking, the uncertainties here should be
-    considered as the lower limit because \synpipe{} currently does not consider the uncertainties
-    in PSF modeling.}.
-
-    We also see that the accuracy of PSF photometry does not strongly depend on filters.
-    The accuracy of the forced PSF magnitude in $r$- and $z$-bands is similar to
-    $i$-band observations (1.5-4.0\% at $19.0 < r_{\mathrm{Input}} < 24.0$ mag, ${\sim}8$\% down to
-    $r_{\mathrm{Input}}{\sim}25.2$ mag;
+    which is consistent with our results. At fainter magnitudes however, external comparisons become difficult due to the  lack of imaging matched to HSC depths.
+    The results from \synpipe{} hence provide  useful evaluations of  the accuracy of the HSC photometry  down to our detection limit\footnote{Strictly speaking, the uncertainties reported here should be
+    considered as the lower limit because \synpipe{} currently does not consider PSF modeling uncertainties}.
+
+Figure \ref{fig:psf_mag} also shows that the accuracy of the PSF photometry is not filter dependent.
+The accuracy of forced PSF magnitudes in $r$ and $z$ is similar to the $i$-band.
+For $r$ band we find  1.5-4.0\% at $r_{\mathrm{Input}} < 24.0$ and ${\sim}8$\% at $r_{\mathrm{Input}}{\sim}25.2$.
+For $z$-band we find  \alexie{xxxxx reformat}
+
  1.0-5.0\% at $19.0 < z_{\mathrm{Input}} < 24.0$ mag, ${\sim}10$\% down to
     $z_{\mathrm{Input}}{\sim}25.2$ mag).
-    The accuracies in $g$- and $y$-bands become slightly worse (1.5-7.0\% at $19.0 < g_{\mathrm{Input}} < 24.0$ mag, ${\sim}13$\% down to
+
+    The accuracy in the $g$ and $y$-bands becomes slightly worse (1.5-7.0\% at $19.0 < g_{\mathrm{Input}} < 24.0$ mag, ${\sim}13$\% down to
     $g_{\mathrm{Input}}{\sim}25.2$ mag;
     1.5-5.0\% at $19.0 < y_{\mathrm{Input}} < 23.0$ mag, ${\sim}12$\% down to
-    $y_{\mathrm{Input}}{\sim}24.0$ mag;); however, the differences can be attributed to the
-    differences in seeing conditions.
-
-    For relatively isolated stars, \hscpipe{} provides unbiased PSF photometry down to a
-    very faint magnitude in $i$- and $z$-bands.
-    For $g$-, $r$-, and $y$-bands, we find small offsets in the distributions of magnitude
-    differences, which indicates \hscpipe{} tends to underestimate the fluxes of stars
-    in these bands by ${\sim}0.01-0.02$ mag.
-    Although the exact cause of this offset is unclear (it could be related to
-    differences in seeing), it will not affect the accuracies of magnitudes or colors.
-
-    At the same time, the story for highly blended stars is very different.
-    \hscpipe{} on average systematically underestimates their total fluxes by
-    $0.05$--$0.10$ mag at a fixed input magnitude.
+    $y_{\mathrm{Input}}{\sim}24.0$ mag;). These differences are however consistent with the differences in the seeing conditions between the filters
+
+The PSF photometry for relatively isolated stars is unbiased in the $i$- and $z$-bands down to faint magnitudes .
+For the $g$, $r$, and $y$-bands, we find small offsets between the  input and recovered magnitude.
+\hscpipe{} tends to underestimate the fluxes of stars
+    in these bands by ${\sim}0.01-0.02$ mag. The exact cause of this offset is unclear but the levels of bias is quite small and not a major concern.
+
+	However, Figure \ref{fig:psf_mag} also shows that blending has a strong impact on photometry estimation.
+On average, \hscpipe{} on average systematically underestimates the total fluxes of stars that are subject to blending effects by $0.05$--$0.10$ mag at a fixed input magnitude.
     We see the same effect in all bands, and the impact of blendedness becomes
-    increasingly significant at fainter magnitude.
-    It is important to keep this in mind when using PSF photometry for point
+    increasingly significant at fainter magnitudes.
+    It is important to bear this caveat in mind when using PSF photometry for point
     sources in HSC data.
 
-    We also test the \unforced{} PSF photometry in all five bands, and find very similar
-    accuracies.
-    While measuring \forced{} PSF photometry, \hscpipe{} fixes the centroid
+	Finally, we also perform similar tests for the \unforced{} PSF photometry in all five bands, and find similar results.  To measure the \forced{} PSF photometry, \hscpipe{} fixes the centroid
     of the PSF model across all five bands.
-    Therefore, the  difference between \forced{} and \unforced{} PSF magnitudes
-    indicates the photometric uncertainties induced by the differences in the accuracies of
-    astrometric calibrations and PSF modeling among different bands.
-    We highlight the differences between \forced{} and \unforced{} PSF photometry of
-    $g$- and $y$-bands in Fig \ref{fig:psf_diff}.
-    The overall difference is very small ($<0.01$ mag), but it also suggests that
-    \hscpipe{} \unforced{} PSF photometry systematically recovers slightly more fluxes
-    at the very faint end.
-
-\subsubsection{Accuracy of the PSF colors}
+A difference between \forced{} and \unforced{} PSF magnitudes would therefore be an indication of  photometric uncertainties  arising from  inaccurate astrometric calibrations and PSF modeling across different bands.
+Figure  \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} PSF photometry for the $g$ and the $y$ band.
+The overall differences are small ($<0.01$ mag) .
+
+%% ------------------------------------------------------------------------------------ %%
+\subsubsection{Accuracy of PSF colors}
+
+\alexie{ALEXIE EDITED TO HERE}
 

### 2017-04-24 draft/ms_v4.tex
New figure1 and some edits

@@
     Before we can tackle outstanding scientific questions, we must first learn
-    how to handle the the large amounts of data\footnote{Right now, SSP has accumulated
-    ${\sim}300$ TB of data products.} generated by these projects while satisfying  
-    strict requirements for high quality image processing with accurate measurement 
-    for the magnitudes and shapes of stars and galaxies. 
+    how to handle the the large amounts of data\footnote{Right now, SSP has 
+    accumulated ${\sim}300$ TB of data products.} generated by these projects while 
+    satisfying strict requirements for high quality image processing with accurate 
+    measurement for the magnitudes and shapes of stars and galaxies. 
     Data handling becomes increasingly challenging in the age of modern imaging
-    surveys am we aim to characterize and account for subtle effects related to charge-coupled devices (CCDs). Cameras are made up of multiple CCDs, each with slightly different
-    characteristics, and have large fields-of-views (FoV) over focal planes that are not perfectly flat.
-During observations, the seeing and background conditions display spatial and temporal variations across the FoV.
+    surveys am we aim to characterize and account for subtle effects related to 
+    charge-coupled devices (CCDs). 
+    Cameras are made up of multiple CCDs, each with slightly different
+    characteristics, and have large fields-of-views (FoV) over focal planes that 
+    are not perfectly flat. 
+    During observations, the seeing and background conditions display spatial and 
+    temporal variations across the FoV. 
     The full-depletion, thick CCDs selected for HSC enable long exposure
@@
     so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that
-    brighter stars have larger Point Spread Functions (PSFs) than fainter stars. These variations and effects make accurate astrometric and photometric calibration,
+    brighter stars have larger Point Spread Functions (PSFs) than fainter stars. 
+    These variations and effects make accurate astrometric and photometric calibration,
     background subtraction, and point spread function (PSF) modeling intrinsically
-    difficult (e.g., \citealt{Schlafly2012}). Furthermore, as surveys reach to increasingly deeper detection limits
+    difficult (e.g., \citealt{Schlafly2012}). 
+    Furthermore, as surveys reach to increasingly deeper detection limits
     (e.g., the SSP Wide layer reaches a $5\ \sigma$ point source detection limit of
@@
 
-    %
+%% ------------------------------------------------------------------------------------ %%
     These challenges are not merely technical details; their resolution is crucial
@@
     is a powerful tool for measuring the large-scale distribution of dark matter.
-    However, WL measurements critically depend on our ability to measure the shape and photometric redshifts of background galaxies with high precision.
-Photometric redshifts (e.g., \citealt{Benitez2000, Bolzonella2000,
-    Ilbert2009}) are fundamentally important for studying the evolution of galaxies,
-    and the ``drop-out'' method is critical for selecting high-redshift galaxies
+    However, WL measurements critically depend on our ability to measure the shape and 
+    photometric redshifts of background galaxies with high precision. 
+    Photometric redshifts (e.g., \citealt{Benitez2000, Bolzonella2000, Ilbert2009}) are 
+    fundamentally important for studying the evolution of galaxies, and the ``drop-out'' 
+    method is critical for selecting high-redshift galaxies 
     (e.g., \citealt{Steidel1996}).
-    However, both of those methods reply on the availability of accurate multi-band photometric
-    measurements. With increasingly large surveys,  and with more stringent requirements on data quality,  quality control also becomes a pressing issue.
-
-   In this paper, we present a \texttt{Python}-based software package called  \synpipe{} that  injects synthetic objects into  HSC images  and  which interfaces with the HSC data reduction pipeline (\hscpipe{}).
-Among other applications, \synpipe{} can be used to perform quality control and to characterize the performance and limitations of  \hscpipe{}.
+    However, both of those methods rely on the availability of accurate multi-band 
+    photometric measurements. 
+    With increasingly large surveys, and with more stringent requirements on data 
+    quality, quality control also becomes a pressing issue.
+
+    In this paper, we present a \texttt{Python}-based software package called 
+    \synpipe{} that injects synthetic objects into HSC images and which interfaces with 
+    the HSC data reduction pipeline (\hscpipe{}). 
+    Among other applications, \synpipe{} can be used to perform quality control and 
+    to characterize the performance and limitations of \hscpipe{}. 
     Several tools with similar goals have been developed (e.g., \citealt{Chang2015,
@@
         Gray boxes indicate required inputs at different stages.
-        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects synthetic objects into single-frame images.
-Below the blue box, we show an HSC image before and after the insertion of synthetic galaxies.
+        The blue box identifies the \texttt{addFakes.py} step, when \synpipe{} injects 
+        synthetic objects into single-frame images. 
+        Below the blue box, we show an HSC image before and after the insertion of 
+        synthetic galaxies. 
         The positions of synthetic objects are highlighted with green circles. 
         Red boxes depict the image coadding and multi-band measurement steps
-        using \texttt{stack.py} and \texttt{multiBand.py}. At the bottom left, we show a \coadd{} image which contains synthetic galaxies. On the right hand side, we show the spatial relation
-        between \texttt{Tracts}, \texttt{Patches}, and \texttt{Visits}. 
+        using \texttt{stack.py} and \texttt{multiBand.py}. 
+        At the bottom left, we show a \coadd{} image which contains synthetic galaxies. 
+        On the right hand side, we show the spatial relation between \texttt{Tracts},
+        \texttt{Patches}, and \texttt{Visits}. 
         The red colored box corresponds to one \texttt{Tract} which has an area of 
@@
         \texttt{Patches} are represented by black dashed lines. 
-        One \texttt{Tract} typically contains 81 \texttt{Patches}.}
+        One \texttt{Tract} typically contains 81 \texttt{Patches}.
+        }
     \label{fig:flowchart}

### 2017-04-24 draft/ms_v4.tex
More minor adjustments

@@
     For our work, we focused on data from the Wide layer as they relate to key
-    scientific goals of the HSC survey, which include weak lensing cosmology, galaxy evolution, and studies of galaxy clusters.
-The Wide layer data in DR1 corresponds to ${\sim}108$ deg$^2$ spread over
+    scientific goals of the HSC survey, which include weak lensing cosmology, galaxy 
+    evolution, and studies of galaxy clusters. 
+    The Wide layer data in DR1 correspond to ${\sim}108$ deg$^2$ spread over 
     six fields (XMM--LSS, GAMA09H, WIDE12H, GAMA15H, HECTOMAP, and VVDS)
@@
     Except for the HECTOMAP field, the regions are all close to the equator.
-    In the Wide layer, the $g$ and $r$ bands have 10 minute exposures broken into four
-    dithers.
+    In the Wide layer, the $g$ and $r$ bands have 10 minute exposures broken into 
+    four dithers.  
     The $i$, $z$, and $y$ bands have 20 minute exposures broken into six dithers. 
-The survey prioritizes the observations so that the $i$-band has the best seeing conditions to improve galaxy shape measurements for weak lensing science.
-The  $i$ band data in the Wide layer reach a $5\sigma$ point source limiting magnitude of  $i{\sim} 26.4$ mag  and have a median seeing with FWHM${\sim}0.6$\asec{}.
+    The survey prioritizes the observations so that the $i$-band has the best seeing 
+    conditions to improve galaxy shape measurements for weak lensing science. 
+    The $i$ band data in the Wide layer reach a $5\sigma$ point source limiting 
+    magnitude of $i{\sim} 26.4$ mag and have a median seeing with 
+    FWHM${\sim}0.6$\asec{}. 
     \citealt{HSCDR1} provides details on the first data release and data status.
@@
 
-The HSC data are reduced using a pipeline that builds on the prototype pipeline being designed by the Large Synoptic Survey Telescope’s Data Management system (\citealt{Ivezic2008, Axelrod2010,
-    Juric2015}) and is described in Bosch\etal (in prep.). DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. Because\synpipe{} is intrinsically connected to the complex data reduction
-    processes in \hscpipe{}, we briefly introduce the main steps below, and we introduce a few key HSC/LSST terms.
+    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
+    being designed for the Large Synoptic Survey Telescope’s Data Management system
+    (\citealt{Ivezic2008, Axelrod2010, Juric2015}) and is described in 
+    Bosch\etal (in prep.). 
+    DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. 
+    Because\synpipe{} is intrinsically connected to the complex data reduction
+    processes in \hscpipe{}, we briefly introduce the main steps below along with a 
+    few key HSC/LSST terms.
 
@@
             \hscpipe{} merges the \texttt{footprints} and flux peaks in the different
-            bands and then selects a reference band for each object based on its $S/N$ in each band (usually this corresponds to the $i$-band).
-Centroids, shapes, and other non-amplitude parameters are then fixed to  the values from the reference band.
+            bands and then selects a reference band for each object based on its $S/N$ 
+            in each band (usually this corresponds to the $i$-band).  
+            Centroids, shapes, and other non-amplitude parameters are then fixed to  
+            the values from the reference band. 
             \hscpipe{} then performs \forced{} photometry using these fixed quantities. 
@@
         \item \textbf{HSC Photometry}:
-            The multi-band catalogs generated by \hscpipe{} contain various types of photometry measurements (see \citealt{HSCDR1} for details).
-Here, we focus on characterizing the the \forced{} \texttt{psf} and \cmodel{}
-            photometry. The
-            \texttt{psf} photometry should provide the most appropriate magnitudes and
-            colors for point sources.
-The  \cmodel{} should be used for galaxies.
-The HSC  \cmodel{} algorithm is described in Bosch\etal, in prep.
-and is an  improved version of the SDSS \cmodel{} magnitude (\citealt{Lupton2001, Abazajian2004}).
-The HSC  \cmodel{} fits objects using both a de Vaucouleurs and an exponential profiles taking into account the smearing by the PSF.
-\cmodel{} then linearly combines the two results to find the best fit to the galaxy image.
-\cmodel{} magnitudes are designed to yield accurate fluxes and colors for galaxies.
-Star--galaxy separation is performed based on
-            the difference between \texttt{psf} and \cmodel{}{} magnitudes.
+            The multi-band catalogs generated by \hscpipe{} contain various types of 
+            photometric measurements (see \citealt{HSCDR1} for details). 
+            Here, we focus on characterizing the the \forced{} \texttt{psf} and 
+            \cmodel{} photometry. 
+            The \texttt{psf} photometry should provide the most appropriate magnitudes 
+            and colors for point sources, while the \cmodel{} should be used for 
+            galaxies. 
+            The HSC \cmodel{} algorithm is described in Bosch\etal, in prep. and is an
+            improved version of the SDSS \cmodel{} magnitude (\citealt{Lupton2001, 
+            Abazajian2004}). 
+            The HSC \cmodel{} fits objects using both a de~Vaucouleurs and an 
+            exponential profiles taking into account the smearing by the PSF.  
+            \cmodel{} then linearly combines the two results to find the best fit to 
+            the galaxy image. 
+            \cmodel{} magnitudes are designed to yield accurate fluxes and colors for 
+            galaxies. 
+            Star--galaxy separation is performed based on the difference between 
+            \texttt{psf} and \cmodel{}{} magnitudes.
 
@@
 
-    DR1 data quality has been vetted in \citet{HSCDR1} by cross-checking
-    with the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1
-    imaging survey (\citealt{Schlafly2012, Tonry2012, Magnier2013}) to examine the
-    behavior of the stellar sequence.
+    DR1 data quality has been vetted in \citet{HSCDR1} by cross-checking with the 
+    Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey
+    (\citealt{Schlafly2012, Tonry2012, Magnier2013}) to examine the behavior of the 
+    stellar sequence.
     Generally speaking, the PSF photometry is accurate at the 1--2\% level for bright 
@@
     processes that produce not only deep \coadd{} images but also a series of
-    science-ready catalogs. To perform tests of the  data products that result from \hscpipe{},  \synpipe{} is designed to satisfies a few basic standards:
+    science-ready catalogs. 
+    To perform tests of the data products that result from \hscpipe{}, \synpipe{} is 
+    designed to satisfies a few basic standards:
 
@@
             test.
-            The impact of these features can be important for studies that care about completeness and the selection
-            function.
+            The impact of these features can be important for studies that care about 
+            completeness and the selection function.
             In \synpipe{}, point sources are simulated using the HSC PSF model,
@@
         \item \textbf{Authentic Data Processing}:
-            To follow the data reduction process as realistically as possible, we choose to
-            start from the single-\visit{} images instead of directly putting synthetic
-            objects on the final \coadd{} images (e.g., \citealt{Suchyta2016}).
+            To follow the data reduction process as realistically as possible, we 
+            choose to start from the single-\visit{} images instead of directly putting 
+            synthetic objects on the final \coadd{} images 
+            (e.g., \citealt{Suchyta2016}).
             Through this approach, subtle effects like seeing differences among
@@
             into account.
-            Every synthetic object will experience all the steps we would use for a real object: detection, deblending, stacking, and measurement.
-            This can be important for challenging tasks like WL measurements
-            or the detection of high-$z$ galaxies.
-            The downside of this choice is that it slows down the overall run-time because we need to inject synthetic objects into all the \visits{} that contribute to a \tract{}.
-        \item \textbf{Flexible Capabilities}: \synpipe{} is designed to be flexible enough to be useful for HSC users with a range of scientific goals.
+            Every synthetic object will experience all the steps we would use for a 
+            real object: detection, deblending, stacking, and measurement.
+            This can be important for challenging tasks like WL measurements or the 
+            detection of high-$z$ galaxies.
+            The downside of this choice is that it slows down the overall run-time
+            because we need to inject synthetic objects into all the \visits{} that 
+            contribute to a \tract{}.
+
+        \item \textbf{Flexible Capabilities}: 
+            \synpipe{} is designed to be flexible enough to be useful for HSC users 
+            with a range of scientific goals.
             We provide default catalogs to generate samples of synthetic stars
             and galaxies with realistic magnitudes and color distributions along with
-            tools to help the user work on HSC DR1 data. However, \synpipe{} also easily allows users to  design and use their own custom made input catalogs.
+            tools to help the user work on HSC DR1 data. 
+            However, \synpipe{} also easily allows users to design and use their own 
+            custom made input catalogs.
             \synpipe{} is already being used in a wide range of
@@
 
-    In this section, we describe the \synpipe{} test implementation illustrated in Fig \ref{fig:flowchart}.
+    In this section, we describe the \synpipe{} test implementation illustrated in 
+    Fig \ref{fig:flowchart}.
 
@@
 
-    To create a catalog of synthetic objects, the user first needs to select which HSC data and which input synthetic galaxy catalog to use.
+    To create a catalog of synthetic objects, the user first needs to select which HSC 
+    data and which input synthetic galaxy catalog to use.
 
@@
 
-        \item \textbf{Information about the data}. This  corresponds to the location of HSC images and a list of \visits{} to be used. \synpipe{} can also help the user identify
-            all the \visits{} that contribute to one \tract{} in any given
-            band.
+        \item \textbf{Information about the data}. 
+            This  corresponds to the location of HSC images and a list of \visits{} to 
+            be used. 
+            \synpipe{} can also help the user identify all the \visits{} that contribute 
+            to one \tract{} in any given band.
             \synpipe{} also provides tools to create an optional bad-pixel mask
@@
 
-        \item \textbf{Input catalog}. This is a catalog in \texttt{FITS} (Flexible Image Transport System)
-            format that contains the  coordinates, magnitudes, and model parameters of synthetic  galaxies.
-The positions of synthetic galaxies can be specified  via the input catalog, they can be distributed randomly over a given region, or on a grid (the grid option is useful in that it avoids blends between Synthetic objects, Murata\etal in prep.).
+        \item \textbf{Input catalog}. 
+            This is a catalog in \texttt{FITS} (Flexible Image Transport System)
+            format that contains the coordinates, magnitudes, and model parameters of 
+            synthetic objects.  
+            The positions of synthetic galaxies can be specified via the input catalog, 
+            they can be distributed randomly over a given region, or on a grid 
+            (the grid option is useful in that it avoids blends between Synthetic 
+            objects, e.g. see Murata\etal in prep.).
+
     \end{itemize}
 
-Synthetic objects can be one of the following:
+    \noindent Synthetic objects can be one of the following:
 
@@
 
-        \item \textbf{Point source}: \synpipe{} simply uses the PSF model from \hscpipe{} as the model for
+        \item \textbf{Point source}: 
+            \synpipe{} simply uses the PSF model from \hscpipe{} as the model for
             a point source (stars and/or quasi-stellar objects).
@@
             (\citealt{Bertin2011, Bertin2013}) to characterize PSF as a function
-            of position and the PSF model can be reconstructed
-            for any location on the image. To inject point sources, the user only needs to specify a catalog of coordinates and magnitudes.
+            of position and the PSF model can be reconstructed for any location on 
+            the image. 
+            To inject point sources, the user only needs to specify a catalog of 
+            coordinates and magnitudes.
+
         \item \textbf{\ser{}models}:
@@
             simulate galaxies.
-            \galsim{} is an image simulation tool that was designed for the GRavitational lEnsing Accuracy Testing 3 (GREAT3) challenge
-            (\citealt{Mandelbaum2014}). Currently, \synpipe{} allows synthetic galaxies to be modeled by a single
-            or a double \citet{Sersic1963}
-            profile\footnote{More flexible model choices will be added later.}. The \ser{} profile is flexible enough to describe the overall flux
+            \galsim{} is an image simulation tool that was designed for the 
+            GRavitational lEnsing Accuracy Testing 3 (GREAT3) challenge
+            (\citealt{Mandelbaum2014}). 
+            Currently, \synpipe{} allows synthetic galaxies to be modeled by a
+            single or a double \citet{Sersic1963}
+            profile\footnote{More flexible model choices will be added later.}. 
+            The \ser{} profile is flexible enough to describe the overall flux
             distributions of galaxies near and far, both early-type or late-type.
@@
             $g_2$, see \citealt{Rowe2015} for more details).
-        \item \textbf{Galaxies from the GREAT3 challenge}: \synpipe{} also allows users to choose from parametric models or real
-            high-resolution galaxy images used in the GREAT3 WL challenge. Real galaxy images are drawn from the \hst{}/ACS F814W ($I$-band) images of galaxies
-            in the COSMOS field (e.g., \citealt{Scoville2007,Leauthaud2007}).
-Instead of using real galaxy images, the users may also use models of  COSMOS galaxies to $I_{\mathrm{Auto}}\leq25.2$ mag via a method developed by
-            \citet{Lackner2012}.  Parametric models of COSMOS galaxies include a single-\ser{} and the \ser{}
-            bulge$+$Exponential disk model. The parameter values for these models are stored in the
+
+        \item \textbf{Galaxies from the GREAT3 challenge}: 
+            \synpipe{} also allows users to choose from parametric models or real
+            high-resolution galaxy images used in the GREAT3 WL challenge. 
+            Real galaxy images are drawn from the \hst{}/ACS F814W ($I$-band) images 
+            of galaxies in the COSMOS field (e.g., \citealt{Scoville2007,Leauthaud2007}). 
+            Instead of using real galaxy images, the users may also use models of COSMOS 
+            galaxies to $I_{\mathrm{Auto}}\leq25.2$ mag via a method developed by
+            \citet{Lackner2012}.  
+            Parametric models of COSMOS galaxies include a single-\ser{} and the \ser{}
+            bulge$+$Exponential disk model. 
+            The parameter values for these models are stored in the
             \texttt{GalSim.COSMOSCatalog()} catalog.
             To access them, the user can provide the ID number of COSMOS galaxies
-            in the input catalog, or can simply opt to let \synpipe{} randomly select galaxies from the COSMOS input catalog.
+            in the input catalog, or can simply opt to let \synpipe{} randomly select 
+            galaxies from the COSMOS input catalog.
+
     \end{itemize}
@@
 
+%% ------------------------------------------------------------------------------------ %%            
         If necessary, an additional shear ($g_1$ and $g_2$) can be applied to the 
@@
 
-    \todo{Details for stars and galaxies}
-
 %% ------------------------------------------------------------------------------------ %%
@@
 
-    To evaluate the degree to which an object is blended with others, \hscpipe{} introduces
-    the blendedness parameter: $b$ (\texttt{[grizy]blendedness\_abs\_flux}).
-    We briefly define  $b$ below; please refer to Bosch\etal (in prep.) and Murata\etal (in prep.) for more details.
+    To evaluate the degree to which an object is blended with others, \hscpipe{} 
+    introduces the blendedness parameter: $b$ (\texttt{[grizy]blendedness\_abs\_flux}).
+    We briefly define  $b$ below; please refer to Bosch\etal (in prep.) and Murata\etal 
+    (in prep.) for more details.
 

### 2017-04-24 draft/ms_v4.tex
Catch up with Alexie's edits

@@
     The newly generated single-\visit{} images have the same format and data
-    structure as real HSC data. To perform stacking and measurements, \synpipe{} calls standard \hscpipe{} routines.
+    structure as real HSC data. To perform stacking and measurements, \synpipe{} calls 
+    standard \hscpipe{} routines.
 
@@
 
-    Using the infrastructures provided by \hscpipe{}, the user can easily perform these steps in parallel, and the overall efficiency of \synpipe{} is similar to
-    the real data reduction process. The data and catalog volumes is also similar to the original data reduction process.
+    Using the infrastructures provided by \hscpipe{}, the user can easily perform these 
+    steps in parallel, and the overall efficiency of \synpipe{} is similar to
+    the real data reduction process. 
+    The data and catalog volumes is also similar to the original data reduction process.
 
     The final step is to identify Synthetic galaxies in the output catalogs. 
-\synpipe{} can match the input catalog to the output catalog (this contains a mix of real and synthetic galaxies) using a matching radius that is specified by the user.
+    \synpipe{} can match the input catalog to the output catalog (this contains a mix 
+    of real and synthetic galaxies) using a matching radius that is specified by the 
+    user.
     Each unmatched object from the input catalog is also passed to the results catalog
@@
         \textbf{Lower panel}: color-color distributions
-        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$). Hexagonal bins indicate COSMOS stars and contours indicate resampled stars.}
+        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$). 
+        Hexagonal bins indicate COSMOS stars and contours indicate resampled stars.
+        }
     \label{fig:star_sample}
@@
     \end{center}
-    \caption{ textbf{Upper panel}: five-band magnitude distributions of synthetic galaxies. (\texttt{lower panel}; from left to right are the \ser{} index, axis ratio,
-        effective radius in arcsec, the $g-r$ and $r-z$ colors).}
+    \caption{
+         \textbf{Upper panel}: five-band magnitude distributions of synthetic
+         galaxies. (\texttt{lower panel}; from left to right are the \ser{} index, 
+         axis ratio, effective radius in arcsec, the $g-r$ and $r-z$ colors).
+         }
     \label{fig:galaxy_sample}
@@
 
-    We now describe the  generation of the synthetic data set that we use to characterize the performance of \hscpipe{}.
+    We now describe the generation of the synthetic data set that we use to 
+    characterize the performance of \hscpipe{}.
 
@@
     20--40 \visits{}.  
-These  two \tract{} are selected  because they are not at the edge of a field, do not contain any  extremely bright ($i<12$ mag) saturated stars, and  are representative of both "good" and "bad" seeing conditions in the $i$-band.
-
+    These two \tract{} are selected because they are not at the edge of a field, do 
+    not contain any extremely bright ($i<12$ mag) saturated stars, and are 
+    representative of both "good" and "bad" seeing conditions in the $i$-band.
 %% ------------------------------------------------------------------------------------ %%
@@
 
-We use a synthetic star sample built using data from  the HST/ACS catalog of \citet{Leauthaud2007}.
-We first select stars from the  \citet{Leauthaud2007} catalog (this classification is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag).
-We then match this sample against our HSC UltraDeep--COSMOS data (which reaches ${\sim}27.2$ mag in $i$-band).
-After applying basic quality cuts (see \ref{app:qc}), this procedure  provides us with five-band HSC photometry for 14,472 stars.
-To increase the sample size, we re-sample the five-band magnitude distributions using the \texttt{astroML} (\citealt{astroml}) implementation of the \texttt{extreme-deconvolution} algorithm developed by
-    \citet{Bovy2011}
+    We use a synthetic star sample built using data from the HST/ACS catalog of 
+    \citet{Leauthaud2007}.  
+    We first select stars from the \citet{Leauthaud2007} catalog (this classification 
+    is reliable down to $I_{\mathrm{F814W}}{\sim}25.2$ mag). 
+    We then match this sample against our HSC UltraDeep--COSMOS data (which reaches 
+    ${\sim}27.2$ mag in $i$-band). 
+    After applying basic quality cuts (see \ref{app:qc}), this procedure provides us 
+    with five-band HSC photometry for 14,472 stars.
+    To increase the sample size, we re-sample the five-band magnitude distributions 
+    using the \texttt{astroML} (\citealt{astroml}) implementation of the 
+    \texttt{extreme-deconvolution} algorithm developed by \citet{Bovy2011}
     \footnote{\texttt{https://github.com/jobovy/extreme-deconvolution/}} to
-    generate 100,000 synthetic stars. Fig \ref{fig:star_sample} shows the magnitude and color distributions of real COSMOS stars compared to the resampled distributions in all
-    five-bands and in color-color space.
-
-    For synthetic galaxies, we use single-\ser{} galaxy models of COSMOS galaxies with $I_{F814W} \leq 25.2$ mag.
-These are models from \citet{Lackner2012} applied to \textit{HST}/ACS images and are included in \galsim{}.
+    generate 100,000 synthetic stars. 
+    Fig \ref{fig:star_sample} shows the magnitude and color distributions of real 
+    COSMOS stars compared to the resampled distributions in all five-bands and in 
+    color-color space.
+
+    For synthetic galaxies, we use single-\ser{} galaxy models of COSMOS galaxies with 
+    $I_{F814W} \leq 25.2$ mag. 
+    These are models from \citet{Lackner2012} applied to \textit{HST}/ACS images and 
+    are included in \galsim{}. 
     Each model is described by a total of five parameters: magnitude, effective radius,
     \ser{} index, axis ratio, and position angle.
-    Although the single-\ser{} model is not always the best choice for describing galaxies, its flexibility
-    enables it to reasonably describe the flux distribution of most galaxies.
-    Also, its simplicity makes it easy for us to diagnose potential problems with the \cmodel{} photometry.
-    We exclude a tiny fraction of ill-behaved models that have a very high \ser{}
-    index ($n_{\mathrm{Ser}} > 6.0$) or a very low central surface brightness
-    ($\mu_{i} < 24.0$\sb).
+    Although the single-\ser{} model is not always the best choice for describing 
+    galaxies, its flexibility enables it to reasonably describe the flux distribution 
+    of most galaxies.
+    Also, its simplicity makes it easy for us to diagnose potential problems with the 
+    \cmodel{} photometry.
+    We exclude a tiny fraction (${\sim}4$\%) of ill-behaved models that have a very 
+    high \ser{} index ($n_{\mathrm{Ser}} > 6.0$) or a very low central surface 
+    brightness ($\mu_{i} < 24.0$\sb).
     We further match this COSMOS sample with the HSC UltraDeep--COSMOS data.
@@
     faint ($i<24.0$ mag) and barely resolved ($R_{\mathrm{e}}< 1.0$\asec).
-    This sample is appropriate to test \hscpipe{}'s general photometric behaviors, but
-    the sample lacks relatively bright galaxies ($i<20.5$ mag).
-
-    We spatially distribute synthetic stars and galaxies randomly in our two selected \tracts{}. For stars, we use a number density of 1,000 per CCD. For galaxies, we use a number
-    density of 500 per CCD.
+    This sample is appropriate to test \hscpipe{}'s general photometric behaviors, 
+    but the sample lacks relatively bright galaxies ($i<20.5$ mag).
+
+    We spatially distribute synthetic stars and galaxies randomly in our two selected 
+    \tracts{}. 
+    For stars, we use a number density of 1,000 per CCD. 
+    For galaxies, we use a number density of 500 per CCD.
 
@@
     We use HSC DR1 data stored at Kavli Institute for the Physics and Mathematics of 
-    the Universe (Kavli IPMU). For stars the \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in each
-    band. The same process takes longer for galaxy tests (${\sim}3.0$ hours per
+    the Universe (Kavli IPMU). 
+    For stars the \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in 
+    each band. 
+    The same process takes longer for galaxy tests (${\sim}3.0$ hours per
     \tract{} in each band) because the \galsim{} simulation is more time consuming.
@@
     to generate output catalogs for \forced{} and \unforced{} photometry
-    in each band. For our tests, we reject  synthetic objects  locate within 2 pixels of a real HSC object.
+    in each band. For our tests, we reject  synthetic objects  locate within 2 pixels 
+    of a real HSC object.
 
@@
     The user should be able to reproduce the results presented in this work using 
-    this information. It can also serve as a brief manual for generating \synpipe{} data.
+    this information. It can also serve as a brief manual for generating \synpipe{} 
+    data.
 
@@
         by the difference between input and output \forced{} PSF magnitudes.
-        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-band, respectively.
+        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-band, 
+        respectively.
         The left panel in each plot shows the relation between input magnitude and
         magnitude difference.
-        Hexagonal binned density plots and contours are for the synthetic galaxies from
-        good and bad seeing \tracts{}.
+        Hexagonal binned density plots and contours are for the synthetic galaxies 
+        from good and bad seeing \tracts{}.
         Highly blended objects are highlighted using scattered plots.
@@
         (including the uncertainties in aperture correction).
-        The right panel in each plot shows the distributions of the magnitude differences for objects
-        in good (filled) and bad (solid line) seeing \tracts{}.
+        The right panel in each plot shows the distributions of the magnitude 
+        differences for objects in good (filled) and bad (solid line) seeing \tracts{}.
         The dashed lines identify the distribution of highly blended objects.
@@
         the color-color distributions.
-       The plot on the \textbf{left} (a) uses $(g-r)$ v.s. $(r-i)$ colors, and the plot on the \textbf{right} (b)
-        uses $(i-z)$ and $(z-y)$ colors.
+        The plot on the \textbf{left} (a) uses $(g-r)$ v.s. $(r-i)$ colors, and the plot 
+        on the \textbf{right} (b) uses $(i-z)$ and $(z-y)$ colors.
         The filled contours and shaded histograms reflect the distributions for input
@@
 
-    We randomly inject ${\sim}100,000$ stars into each \tract{} in all
-    five bands. Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the centroids
-    of real objects; we remove those stars from the sample to avoid confusion in the comparisons.
-     %   After this step, ${\sim}1$--$3$\% of the remaining synthetic stars still have no match in the \synpipe{} outputs.
- %   They could either be below the detection threshold or ambiguously blended with real objects \alexie{said you identified those}.
- %   The input $i$-band magnitudes of these unmatched stars are on average ${\sim}0.9$
- %   mag fainter than the matched ones.
- %   The fraction of unmatched stars is slightly higher in the bad seeing \tract{}; this result is consistent with our expectation that magnitude depends on seeing conditions,
- %   although the difference is not very significant \alexie{cut?}.
+    We randomly inject ${\sim}100,000$ stars into each \tract{} in all five bands. 
+    Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the 
+    centroids of real objects; we remove those stars from the sample to avoid confusion 
+    in the comparisons.
     For matched stars, we select the primary detections 
@@
     \textbf{good-seeing} and \textbf{bad-seeing} \tracts{} separately because it
-    is important to understand how the seeing condition affects photometric accuracy as well as to test whether \hscpipe{} can deliver unbiased photometry under different  seeing conditions.
-
-    Besides seeing, the degree to which an object is blended with other objects  is another factor that influences photometric accuracy.
-To quantify the impact of blending effects, we use the ``blendedness'' parameter, $b$.
-This parameter describes how  much any given object overlaps with neighboring objects (see Appendix \ref{app:defineb} and Murata\etal in prep.).
+    is important to understand how the seeing condition affects photometric accuracy 
+    as well as to test whether \hscpipe{} can deliver unbiased photometry under 
+    different seeing conditions.
+
+    Besides seeing, the degree to which an object is blended with other objects 
+    is another factor that influences photometric accuracy. 
+    To quantify the impact of blending effects, we use the ``blendedness'' 
+    parameter, $b$. 
+    This parameter describes how much any given object overlaps with neighboring 
+    objects (see Appendix \ref{app:defineb} and Murata\etal in prep.). 
     We divide our sample according to the blendedness parameter. 
-A value of $b=0$ corresponds to isolated objects whereas  objects with $b=1$ complete overlap with other objects.
+    A value of $b=0$ corresponds to isolated objects whereas objects with $b=1$ 
+    complete overlap with other objects. 
     Here we use $b>0.05$ to define highly blended stars (${\sim}4$--$9$\% are blended).
-    The fraction of highly blended stars slightly increases in the bad seeing \tract{}. The
-    impact of blendedness will be discussed more in Section \ref{ssec:blendedness}.
-
+    The fraction of highly blended stars slightly increases in the bad seeing \tract{}. 
+    The impact of blendedness will be discussed more in Section \ref{ssec:blendedness}.
+
+%% ------------------------------------------------------------------------------------ %%
 \subsubsection{Relationship between stellar magnitude and \s2n{}}
@@
     The \s2n{} for PSF photometry is defined as
-    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band (no aperture corrections) \alexie{have you defined aperture correction?}.
-Figure  \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} in the $g$- and $i$-bands.
-This Figure  shows the expected  \s2n{} of stars as a function of magnitude for the Wide layer.
-
-%    This helps us visualize
-%    1) the detection limit for point sources,
-%    2) the impact of seeing condition on PSF photometric,
-%    3) and the scatter of photometric accuracies at a fixed input magnitude given all
-%       the realistic features of HSC images (e.g., background subtraction, nearby
-%       objects, optical artifacts). \alexie{Why is this relevant in this figure? I wouldn't use SN to quantofy this?}
+    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
+    Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
+    in the $g$- and $i$-bands. 
+    This Figure shows the expected \s2n{} of stars as a function of magnitude in the 
+    Wide layer.
 
@@
     lower \s2n{} than the good-seeing (0.5\asec{}) \tract{}.
-     The \s2n{} is similar for the two $g$-band \tracts{} because they share similar seeing conditions. 
-    %Our results show that blendedness can also affect the accuracy of PSF photometry.\alexie{why use SN here?}
-    %In $i$-band, the highly blended synthetic stars scatter toward lower \s2n{} at
-    %fixed magnitude.
-    %Interestingly, the effect is not obvious in $g$-band, suggesting the deblending
-    %process and photometric quality of blended objects also depend on seeing condition.
-
-    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$- and
-    $i$-bands, which is consistent with the values found
-    in \citet{HSCDR1} for average seeing conditions.
+    The \s2n{} is similar for the two $g$-band \tracts{} because they share similar 
+    seeing conditions.
+
+    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ 
+    and $i$ bands, which is consistent with the values found in \citet{HSCDR1} for 
+    average seeing conditions.
     At the same time, it is worth reminding HSC data users that the detection
@@
     We now investigate the accuracy of the PSF magnitude in each of the five bands
-    independently. Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the  \hscpipe{} \forced{} PSF magnitude as a function of input magnitude.
-
-    The overall performance of the \hscpipe{} \forced{} PSF magnitude is excellent. The median $i$-band magnitude difference for the \tract{} with 0.45\asec{} seeing is
-     ${\sim}0.015$ mag (${\sim}1.5$\%) at
-    $i_{\mathrm{Input}}{\sim}19.0$ mag. At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of the PSF
-    magnitude is ${\sim}3$\% level (${\sim}0.036$ mag average difference).
+    independently. 
+    Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the
+    \hscpipe{} \forced{} PSF magnitude as a function of input magnitude.
+
+    The overall performance of the \hscpipe{} \forced{} PSF magnitude is excellent. 
+    The median $i$-band magnitude difference for the \tract{} with 0.45\asec{} seeing 
+    is ${\sim}0.015$ mag (${\sim}1.5$\%) at $i_{\mathrm{Input}}{\sim}19.0$ mag. 
+    At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of the PSF magnitude is 
+    ${\sim}3$\% level (${\sim}0.036$ mag average difference).
     At $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
@@
 
-    The accuracy of the PSF photometry for the bad-seeing \tract{} shows a similar performance at  $i_{\mathrm{Input}}<23.5$ mag.
+    The accuracy of the PSF photometry for the bad-seeing \tract{} shows a similar 
+    performance at $i_{\mathrm{Input}}<23.5$ mag. 
     At fainter magnitudes, the accuracy slightly degrades. 
@@
     with the PS1, PV2, and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
-    which is consistent with our results. At fainter magnitudes however, external comparisons become difficult due to the  lack of imaging matched to HSC depths.
-    The results from \synpipe{} hence provide  useful evaluations of  the accuracy of the HSC photometry  down to our detection limit\footnote{Strictly speaking, the uncertainties reported here should be
-    considered as the lower limit because \synpipe{} currently does not consider PSF modeling uncertainties}.
-
-Figure \ref{fig:psf_mag} also shows that the accuracy of the PSF photometry is not filter dependent.
+    which is consistent with our results. 
+    However, at fainter magnitudes, external comparisons become difficult due to the 
+    lack of imaging matched to HSC depths.
+    The results from \synpipe{} hence provide useful evaluations of the accuracy of 
+    the HSC photometry down to our detection limit\footnote{Strictly speaking, the 
+    uncertainties reported here should be considered as the lower limit because 
+    \synpipe{} currently does not consider PSF modeling uncertainties}.
+
+    Figure \ref{fig:psf_mag} also shows that the accuracy of the PSF photometry is 
+    not filter dependent. 
     The accuracy of forced PSF magnitudes in $r$ and $z$ is similar to the $i$-band. 
-For $r$ band we find  1.5-4.0\% at $r_{\mathrm{Input}} < 24.0$ and ${\sim}8$\% at $r_{\mathrm{Input}}{\sim}25.2$.
-For $z$-band we find  \alexie{xxxxx reformat}
-
- 1.0-5.0\% at $19.0 < z_{\mathrm{Input}} < 24.0$ mag, ${\sim}10$\% down to
-    $z_{\mathrm{Input}}{\sim}25.2$ mag).
-
-    The accuracy in the $g$ and $y$-bands becomes slightly worse (1.5-7.0\% at $19.0 < g_{\mathrm{Input}} < 24.0$ mag, ${\sim}13$\% down to
-    $g_{\mathrm{Input}}{\sim}25.2$ mag;
-    1.5-5.0\% at $19.0 < y_{\mathrm{Input}} < 23.0$ mag, ${\sim}12$\% down to
-    $y_{\mathrm{Input}}{\sim}24.0$ mag;). These differences are however consistent with the differences in the seeing conditions between the filters
-
-The PSF photometry for relatively isolated stars is unbiased in the $i$- and $z$-bands down to faint magnitudes .
-For the $g$, $r$, and $y$-bands, we find small offsets between the  input and recovered magnitude.
-\hscpipe{} tends to underestimate the fluxes of stars
-    in these bands by ${\sim}0.01-0.02$ mag. The exact cause of this offset is unclear but the levels of bias is quite small and not a major concern.
-
-	However, Figure \ref{fig:psf_mag} also shows that blending has a strong impact on photometry estimation.
-On average, \hscpipe{} on average systematically underestimates the total fluxes of stars that are subject to blending effects by $0.05$--$0.10$ mag at a fixed input magnitude.
+    For $r$ band we find 1.5-4.0\% at $r_{\mathrm{Input}} < 24.0$ mag and ${\sim}8$\% 
+    at $r_{\mathrm{Input}}{\sim}25.2$. 
+    For $z$-band we find 1.0-5.0\% at $z_{\mathrm{Input}} < 24.0$ mag and ${\sim}10$\% 
+    down to $z_{\mathrm{Input}}{\sim}25.2$ mag).
+
+    The accuracy in the $g$ and $y$ bands becomes slightly worse at the very faint end. 
+    For $g$ band, the accuracy is 1.5-7.0\% at $g_{\mathrm{Input}} < 24.0$ mag and is
+    ${\sim}13$\% down to $25.2$ mag.
+    For $y$ band, we find 1.5-5.0\% accuracy at $y_{\mathrm{Input}} < 23.0$ mag and
+    ${\sim}12$\% down to $24.0$ mag. 
+    These differences are however consistent with the differences in the seeing 
+    conditions between the filters
+
+    The PSF photometry for relatively isolated stars is unbiased in the $i$ and $z$ 
+    bands down to faint magnitudes. 
+    For the $g$, $r$, and $y$ bands, we find small offsets between the input and 
+    recovered magnitude. 
+    \hscpipe{} tends to underestimate the fluxes of stars in these bands by 
+    ${\sim}0.01-0.02$ mag. 
+    The exact cause of this offset is unclear but the levels of bias is quite small 
+    and not a major concern.
+
+	However, Figure \ref{fig:psf_mag} also shows that blending has a strong impact on 
+	photometry.  
+	On average, \hscpipe{} systematically underestimates the total fluxes of stars 
+	that are subject to blending effects by $0.05$--$0.10$ mag at a fixed input magnitude.
     We see the same effect in all bands, and the impact of blendedness becomes
@@
 
-	Finally, we also perform similar tests for the \unforced{} PSF photometry in all five bands, and find similar results.  To measure the \forced{} PSF photometry, \hscpipe{} fixes the centroid
-    of the PSF model across all five bands.
-A difference between \forced{} and \unforced{} PSF magnitudes would therefore be an indication of  photometric uncertainties  arising from  inaccurate astrometric calibrations and PSF modeling across different bands.
-Figure  \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} PSF photometry for the $g$ and the $y$ band.
+	Finally, we also perform similar tests for the \unforced{} PSF photometry in all 
+	five bands, and find similar results. 
+	To measure the \forced{} PSF photometry, \hscpipe{} fixes the centroid of the PSF 
+	model across all five bands. 
+	A difference between \forced{} and \unforced{} PSF magnitudes would therefore be 
+	an indication of photometric uncertainties arising from  inaccurate astrometric 
+	calibrations and PSF modeling across different bands. 
+	Figure \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} 
+	PSF photometry for the $g$ and the $y$ band. 
 	The overall differences are small ($<0.01$ mag) .

### 2017-04-24 draft/ms_v4.tex
PSF color

@@
     PSF photometry is the most appropriate way to measure colors for point
-    sources; therefore, the accuracy of the PSF color estimates is important to many scientific goals of the HSC survey
+    sources; therefore, the accuracy of the PSF color estimates is important to many 
+    scientific goals of the HSC survey
     (e.g., study of the Milky Way structure, selection of unique stellar objects or
@@
     These results suggest that \hscpipe{} provides accurate and unbiased PSF color
-    estimates for synthetic stars with realistic color distributions down to a very faint
-    magnitude.
-    For $(g-i)$ color, the average uncertainty around $i_{\mathrm{Input}}{\sim}19.0$ mag
-    is ${\sim}0.025$ mag, and increases to ${\sim}0.11$ mag at
+    estimates for synthetic stars with realistic color distributions down to very 
+    faint magnitude.
+    For $(g-i)$ color, the average uncertainty around $i_{\mathrm{Input}}{\sim}19.0$ 
+    mag is ${\sim}0.025$ mag, and it increases to ${\sim}0.11$ mag at
     $i_{\mathrm{Input}}{\sim}24.0$ mag.
-    The results are very similar for the $(i-y)$ color.
-    We also find that the accuracies of PSF colors do not depend on the input colors of
-    the synthetic stars or the seeing conditions.
-    For instance, the accuracy of $(g-i)$ color for a bad-seeing \tract{} is only
+    The $(i-y)$ color shows very similar results.
+    We also find that the accuracies of PSF colors do not depend on the input colors 
+    of the synthetic stars or the seeing conditions.
+    For instance, the accuracy of $(g-i)$ color for the bad-seeing \tract{} is only
     slightly worse in the very faint end (${\sim}0.14$ mag at
-    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the results for a good-seeing \tract{}.
+    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the results for the 
+    good-seeing \tract{}.
 
@@
     (see Fig \ref{fig:psf_cdist}).
-    Using four different colors and two 2--D color--color planes, we show that the \forced{}
-    PSF colors can accurately reproduce the distributions of all four colors and the
-    2-D color-color distributions.
+    Using four different colors and two color--color planes, we show that the 
+    \forced{} PSF colors can accurately reproduce the distributions of all four colors 
+    and the color-color distributions.
 
@@
     highly blended stars at a fixed input magnitude.
-    However, the biases in color measurements for these stars are less severe than
-    the magnitude measurements.
-    Although the blended stars still show slightly bluer color for $(g-i)$ and slightly redder color for $(i-y)$
-    compared to the isolated stars and the input values, the differences in the
-    distributions of color uncertainties of blended and isolated stars are less striking
-    than the distribution differences for magnitude.
-
+    Also, for blended stars, the $(g-i)$ color biases toward bluer end while the 
+    $(i-y)$ color biases toward redder end.
+    However, the biases in color measurements for highly blended stars are less severe 
+    than their magnitude measurements.
 %% ------------------------------------------------------------------------------------ %%
@@
         \cmodel{} magnitudes.
-        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-bands, respectively.
+        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-bands, 
+        respectively.
         The lines and contours legend is identical to Fig \ref{fig:psf_mag}.
@@
         the x--axis.
-       The lines and contours legend is identical to the plot in Fig \ref{fig:psf_color}.
+        The lines and contours legend is identical to the plot in 
+        Fig \ref{fig:psf_color}.
         }
@@
         using the color-color distributions.
-        The \textbf{left} panel (a) uses $(g-r)$ vs. $(r-i)$ colors, and the \textbf{right} panel (b)
-        uses $(i-z)$ and $(z-y)$ colors.
+        The \textbf{left} panel (a) uses $(g-r)$ vs. $(r-i)$ colors, and the 
+        \textbf{right} panel (b) uses $(i-z)$ and $(z-y)$ colors.
         The filled contours and shaded histograms reflect the distributions for input
@@
 
-  For galaxies, \hscpipe{} uses a \cmodel{} photometry algorithm
-     that is an improved version of the SDSS \cmodel{}
-    photometry.
+    For galaxies, \hscpipe{} uses a \cmodel{} photometry algorithm that is an improved 
+    version of the SDSS \cmodel{} photometry.
     For more details, please see Bosch\etal (in prep.).

### 2017-04-24 draft/ms_v4.tex
cModel S2N

@@
     For more details, please see Bosch\etal (in prep.).
-    In short, \cmodel{} tries to fit each object using a combination of de Vaucouleurs
-    and exponential profiles that are approximated by multiple Gaussian profiles.
+    In short, \cmodel{} tries to fit each object using the combination of a
+    de~Vaucouleurs and an exponential profiles that are approximated by multiple 
+    Gaussian profiles.
     Despite the limitation of the \cmodel{} method (e.g., sensitive to background
@@
     In our tests, we randomly inject ${\sim}40,000$ synthetic galaxies into each
-    \tract{}; and, using an approach similar to that for star selection, we then select galaxy samples for photometric comparisons.
-    First, ${\sim}2$--$3$\% of the synthetic galaxies are ambiguously blended with
-    real objects, and are hence removed from the sample.
-    Among the rest of the sample, ${\sim}2$--$7$\% do not have any match in the
-    \synpipe{} results in different \tracts{} and filters.
-    The fraction of unmatched objects is slightly higher for the $g$- and $y$-bands.
-    For the same filter, the fraction is always higher for the bad-seeing \tract{}.
-    The magnitudes of the unmatched galaxies are systematically fainter than the
-    matched ones.
-    In $i$-band, the median input magnitudes for matched and unmatched galaxies are
-    $24.0$ mag and $24.6$ mag, respectively.
+    \tract{}; and, using an approach similar to that for synthetic stars, we select 
+    galaxy samples for photometric comparisons.
+    First, ${\sim}3$--$7$\% of the synthetic galaxies are located within 2 pixels 
+    of the centroids of real objects or do not show any match in the \synpipe{} 
+    results, they are hence removed from the sample.
+    The fraction of unmatched objects slightly increases with worse seeing condition.
 
@@
     in the good-seeing \tract{}.
-    However,   \hscpipe{} misclassifies more objects ($4$\%) in the bad-seeing \tract{}.
+    But the fraction of misclassified galaxies increases to $4$\% in the
+    bad-seeing \tract{}.
     The median input magnitude for these misclassified sources is ${\sim}24.9$ mag
@@
 
-    We also use $b>0.1$ to define samples of highly blended galaxies.
-    Due to the extended nature of the galaxies, the $b$ distributions for synthetic galaxies are
-    very different from the  $b$ distributions for synthetic stars, and they also skew toward higher values (especially for the
-    bad-seeing \tract{}).
+    We also use $b>0.05$ to define samples of highly blended galaxies.
+    Due to the extended nature of the galaxies, the $b$ distributions for synthetic 
+    galaxies skew toward higher values (especially for the bad-seeing \tract{}) than
+    the ones for stars.
     About $7$--$9$\% of synthetic galaxies are highly blended by this standard.
@@
     ($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec).
-    It is very challenging to obtain good photometric quality of these galaxies, which is crucial
-    to achieving several key scientific goals of the HSC survey.
+    It is very challenging to obtain good photometric quality of these galaxies, which 
+    is crucial to key scientific goals of the HSC survey.
     The selected samples do not provide enough bright or large galaxies to test.
@@
     magnitudes and the \s2n{} of the synthetic galaxies estimated by the ratio
-    between \cmodel{} flux and its uncertainties from \hscpipe{}.
-    Since these galaxies are extended objects, the \s2n{} here should be treated
-    as the average \s2n{}, which is different from the \s2n{} of stars using PSF
-    photometry.
-
-    As we did for stars, we use $i$- and $g$-bands as examples for galaxies.
-    The most obvious difference between the  \s2n{} distribution for stars and the  \s2n{} distribution for galaxies is that
-    at fixed input magnitude, the galaxy \s2n{} distribution shows much larger
-    scatter.
-    At the same total flux, a galaxy can have a different size and shape, which
-    naturally leads to differences in the galaxy's peak and average \s2n{}.
-    This also makes it difficult to have a clear definition of ``detection limit''
-    for galaxies.
-    For $i$-band, the typical \s2n{} for synthetic galaxies at the magnitude limit
-    of our sample ($25.2$ mag) is ${\sim}20$, but at that limit the low-\s2n{} tail has
-    reached the \s2n{}$=5$ boundary.
-    This suggests that, although HSC Wide can detect galaxies as faint as
-    $i{\sim}26.0$ mag, the sample at that magnitude will be significantly incomplete.
-    Furthermore, the magnitude limit can also introduce selection bias because galaxies with certain structural properties are harder to detect than others.
-    HSC survey data users who want to select flux-limited samples of galaxies,
+    between \cmodel{} flux and its uncertainty.
+    The \s2n{} used here is the average one for extended object.
+
+    We still use $i$ and $g$ bands as examples.
+    As PSF magnitude for stars, \cmodel{} photometry establishes well-behaved relation 
+    between input magnitude and output \s2n{}. 
+    Comparing to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows larger
+    scatter at fixed input magnitude, which is likely due to differences in size and 
+    shape of the galaxies.
+    This makes it difficult to define ``detection limit'' for galaxies clearly.
+
+    In $i$ band, typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but 
+    there are already galaxies at the same magnitude have \s2n{} below 5.
+    Although HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag, the 
+    sample will be incomplete at this faint magnitude.
+    It also introduces selection bias if galaxies with certain structural properties 
+    are harder to detect than others.
+    HSC survey data users who want to select flux-limited galaxy sample,
     or intend to study the population of faint (e.g., high-$z$) galaxies should
     keep this in mind.
-
-    Similar to the synthetic stars, the worse the seeing condition, the more
-    we noticed a decrease in \s2n{} at the same magnitude (see Fig \ref{fig:psf_s2n}) 
-    for $i$-band).
-    Meanwhile, the highly blended synthetic galaxies do not show significantly
-    different \s2n{} distributions here.
+    Similar to stars, worse seeing also leads to lower \s2n{} at fixed magnitude 
+    (see Fig \ref{fig:psf_s2n} for $i$-band).
 

### 2017-04-24 draft/ms_v4.tex
cModel mag

@@
     In Fig \ref{fig:cmodel_mag}, we illustrate the photometric uncertainties of the
-    \cmodel{} magnitudes in each band using the same format as
-    Fig \ref{fig:psf_mag}.
-
-    The overall performance of \cmodel{} photometry is very reasonable all the way
-    down to $i_{\mathrm{Input}}=25.2$ mag.
-    Compared to the qualities of PSF photometry for stars, the magnitude differences
-    of \cmodel{} show much larger scatter for galaxies.
-    Given the diversity of properties of these galaxies and the complexities in the
-    model-fitting process, this difference is expected.
-    At the same time, we can see that the \cmodel{} algorithm in \hscpipe{} can
-    provide unbiased and consistent photometry for galaxies in different bands and
-    seeing conditions.
-
-    In $i$-band, the median flux uncertainty of the \forced{} \cmodel{} is ${\sim}7$\%
-    in the good-seeing \tract{} at $i_{\mathrm{Input}}{\sim}20.0$ mag,
+    \cmodel{} magnitudes in each band using the same format for Fig \ref{fig:psf_mag}.
+
+    The overall performance of \cmodel{} photometry is reasonable down to 
+    $i_{\mathrm{Input}}=25.2$ mag.
+    Compared to PSF photometry for stars, the uncertainties of \cmodel{} show larger 
+    scatter for galaxies, which is expected given the diversity of structural 
+    properties and complexities in the model-fitting process.
+    At the same time, \cmodel{} algorithm in \hscpipe{} provides unbiased and consistent 
+    photometry for galaxies in different bands and seeing conditions.
+
+    In $i$-band, the typical flux accuracy for \forced{} \cmodel{} is ${\sim}7-9$\%
+    in the good-seeing \tract{} at $i_{\mathrm{Input}}<24.0$ mag, and moderately 
+    decreases to ${\sim}11$\% at $25.0$ mag.
     and ${\sim}9$\% at $i_{\mathrm{Input}}{\sim}24.0$ mag.
-    Down to $i_{\mathrm{Input}}{\sim}25.0$ mag, the median uncertainty maintains
-    at ${\sim}11$\% level.
     For the bad-seeing \tract{} in $i$-band, the performance is very similar.
-    From $i_{\mathrm{Input}}{\sim}20.0$ to $25.0$ mag, the median magnitude difference
+    At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the median magnitude offset
     between output and input values changes from \plus{}$0.041$ mag to
@@
     unbiased down to the very faint end.
-    It is worth noting that the photometric uncertainties estimated by \synpipe{}
-    are significantly larger than the fiducial error from \hscpipe{}, which does not
-    take into account the systematic uncertainties involved in the modeling
-    fitting process.
-    Although the synthetic galaxies in our sample are described by the simple single-\ser{}
-    model, the\cmodel{} algorithm can only approximate them to a certain accuracy,
-    especially when the noise level, deblending uncertainty, and priors of model
-    parameters are considered.
-    Given that real galaxies are more complex in structural details, these
-    uncertainties should be treated as lower limits.
-
-    The performance of \forced{} \cmodel{} photometry is very consistent across all
-    filters.
-    For $g$-, $r$-, and $z$-bands, the photometric uncertainties are very similar to
-    the ones for $i$-band between $20.0$ and $25.0$ mag.
+
+    It is worth noting that the flux uncertainty from \synpipe{} is significantly 
+    larger than the flux error from \hscpipe{}, which does not take into account the 
+    systematic uncertainties involved in the modeling fitting process.
+    Although the synthetic galaxies here are described by simple single-\ser{} model, 
+    \cmodel{} algorithm can only approximate them to certain accuracy, especially when 
+    background noise, deblending uncertainty, and priors of model parameters are 
+    considered.
+    Given that real galaxies are more complex in structure, these uncertainties should 
+    be treated as lower limits.
+
+%% ------------------------------------------------------------------------------------ %%
+
+    The accuracy of \forced{} \cmodel{} photometry is consistent across all filters.
+    For $g$, $r$, and $z$ bands, the photometric uncertainties are very similar to
+    $i$-band results between $20.0$ and $25.0$ mag.
     The \forced{} \cmodel{} magnitudes are also unbiased for these three filters
     across the entire input magnitude range.
-    The uncertainties for $y$-band are slightly larger, ranging from 9\% to 17\% in the
+    The uncertainties for $y$ band are slightly worse, ranging from 9\% to 17\% in the
     same magnitude bins.
-    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in $y$-band
-    at $y_{\mathrm{Input}}>24.0$ mag.
-    Mean magnitude differences change from \minus{}0.06 at 24.0 mag to \minus{}0.22
+    In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
+    $y$ band at $>24.0$ mag.
+    Average magnitude offsets change from \minus{}0.06 at $24.0$ mag to \minus{}0.22
     mag at 25.0 mag.
     Both a worse seeing condition and a higher background noise level can make it more
-    difficult to detect a faint object on a $y$-band image.
-    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} in $y$-band
-    is already close to the detection threshold.
-
-    As mentioned, the statistics for brighter galaxies are very uncertain due to the
-    small sample size.
-    However, we do notice that, at $i_{\mathrm{Input}}<20.0$, the \forced{}
-    \cmodel{} photometry shows larger uncertainty and starts to systematically
-    underestimate the total flux.
-    This problem is confirmed via comparing with more carefully derived total fluxes
-    for bright galaxies (e.g., \citealt{HSCDR1}, Huang\etal in prep.).
-    It relates to the known issues of \hscpipe{} (e.g., \hscpipe{}over-deblends around bright objects; inappropriately weights priors in \cmodel{}); but it may also suggest
-    that, at the imaging depth of HSC, assumptions in \cmodel{} are no longer the
-    best choice in modeling these galaxies (e.g., for massive elliptical galaxies;
-    see Huang\etal in prep.~for more details).
-
-    For the highly blended synthetic galaxies, we also see systematically
-    underestimated total flux (average offset ${\sim}0.1$ mag) and larger scatter
-    of photometric uncertainty in all five bands.
+    difficult to detect faint object in $y$ band.
+    At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
+    around the detection threshold.
+
+    As mentioned, the statistics for brighter galaxies are uncertain due to small 
+    sample size.
+    We do notice that, at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry 
+    shows larger uncertainty and starts to systematically underestimate the total flux.
+    Based on external comparisons, the behavior of \cmodel{} for bright galaxies may 
+    depend on the galaxy type (e.g., \citealt{HSCDR1}). 
+    Known issues of current \hscpipe{} (e.g., \hscpipe{} over-deblends around bright 
+    objects; inappropriately weights priors in \cmodel{}) could lead to poorer 
+    photometric quality for bright galaxies. 
+    Meanwhile, at the imaging depth of HSC ($>29.0$\sb{} in $i$ band for Wide layer), 
+    assumptions in \cmodel{} may no longer be the best choice for modeling bright 
+    galaxies (e.g., for massive elliptical galaxies; see Huang\etal in prep.~for 
+    more details).
+    We will look into these issues more carefully in the future.
+
+    For the highly blended galaxies, we also see systematically underestimated total 
+    flux (average offset ${\sim}0.1$ mag) and larger scatter of photometric 
+    uncertainty in all five bands.
     Meanwhile, the contrast between relatively isolated and highly blended galaxies
@@
     We highlight the differences between \forced{} and \unforced{} \cmodel{}
-    photometry in $g$- and $y$-bands in Fig \ref{fig:cmodel_diff}.
-    The only noticeable difference is for galaxies brighter than $24.0$ mag in
-    $g$-band; their \forced{} \cmodel{} magnitudes are systematically brighter than
-    the \unforced{} ones.
+    photometry in $g$ and $y$ bands in Fig \ref{fig:cmodel_diff}.
+    The only noticeable feature is for galaxies brighter than $24.0$ mag in
+    $g$ band, the \forced{} \cmodel{} magnitudes are systematically brighter than
+    the \unforced{} ones, suggesting \forced{} \cmodel{} shows better accuracy in 
+    $g$ band.
 

### 2017-04-25 draft/ms_v4.tex
cModel color

@@
     In Fig \ref{fig:cmodel_color}, we demonstrate the accuracies of \forced{} $(g-i)$
-    and $(i-y)$ \cmodel{} colors in the same format used for synthetic stars
+    and $(i-y)$ \cmodel{} colors in the same format for synthetic stars
     (Fig \ref{fig:psf_color}).
-    These plots show that \hscpipe{} can provide reliable \cmodel{} colors for
-    synthetic galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
-    For $(g-i)$ colors, the average uncertainty around $i_{\mathrm{Input}}{\sim}21.0$ mag
+    They confirm that \hscpipe{} can provide reliable \cmodel{} colors for synthetic 
+    galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
+    For $(g-i)$ colors, the average uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ mag
     is ${\sim}0.04$ mag.
     The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
-    Results for $(i-y)$ colors are similar.
-
-    The performance of \forced{} \cmodel{} color does not show dependence on seeing
-    condition, and it is unbiased across the ranges for input total magnitude and color.
-    The only noticeable feature is that the $(i-y)$ color at
-    $i_{\mathrm{Input}}>24.0$ is slightly overestimated.
-    As mentioned above, this is not surprising given the shallower imaging depth of  the
-    $y$-band.
-    At the same time, high blendedness of synthetic galaxies can still increase the
-   color uncertainties and bias the color measurements.
-    The highly blended galaxies on average show slightly bluer  $(g-i)$ colors
-     and redder  $(i-y)$ colors  than the input values.
-
-    Similar to the star comparison in Fig \ref{fig:psf_cdist}, we also compare the color--color distributions
+    $(i-y)$ colors show similar results.
+
+    The performance of \forced{} \cmodel{} color does not depend on seeing and is 
+    unbiased for entire ranges of input magnitudes and colors.
+    The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
+    is slightly overestimated.
+    As mentioned above, this is not surprising given the shallower imaging depth in
+    $y$ band.
+    Meanwhile, high blendedness also increases the color uncertainties and biases the 
+    color measurements.
+    The highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
+    $(i-y)$ colors than the input ones.
+
+    Similar to Fig \ref{fig:psf_cdist}, we also compare the color--color distributions
     of the input and output \forced{} \cmodel{} values in Fig \ref{fig:cmodel_cdist}.
-    The general color distributions are well recovered despite the fact that the galaxy accuracy is
-    not as good as the accuracy for stars, especially on the $(i-z)$ vs. $(z-y)$ plane.
-    That result is expected given the narrow dynamical ranges of these colors among red filters.
+    The general 2--D distributions are well recovered but the accuracy is not as good as 
+    the one for stars, especially on the $(i-z)$ vs. $(z-y)$ plane.
+    This is expected given the narrow dynamical ranges of these colors among red filters.
     The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
@@
     We should point out that we assume constant color for the entire galaxy.
-    In reality, different colors for individual components and a smooth color gradient
-    can complicate the situation; hence, the uncertainties of \cmodel{} colors
-    here should be considered as lower limits.
+    In reality, different colors for individual component or color gradient can 
+    complicate the situation.
+    The uncertainties of \cmodel{} colors here should be considered as lower limits.
 %% ------------------------------------------------------------------------------------ %%

### 2017-04-25 draft/ms_v4.tex
More edits

@@
 
+    \vspace{0.5cm}
     \noindent Synthetic objects can be one of the following:
@@
         Hexagonal bins (filled histogram) and contours (solid-line histogram) are for
-        the synthetic objects from \tracts{} with good and bad seeing conditions, respectively.
+        the synthetic objects from \tracts{} with good and bad seeing conditions, 
+        respectively.
         $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.
@@
     \caption{
-        Problems with the current  \hscpipe{}star--galaxy separation method, which is based on the magnitude difference between the PSF and
-        \cmodel{} photometry.
-       The plot on the \textbf{left} (a) illustrates distributions for the synthetic stars.
+        Problems with the current  \hscpipe{}star--galaxy separation method, which is 
+        based on the magnitude difference between the PSF and \cmodel{} photometry.
+        The plot on the \textbf{left} (a) illustrates distributions for the synthetic 
+        stars.
         Hexagonal bins and filled histogram show distributions of correctly classified
@@
         objects in \tracts{} with bad and good seeing conditions, respectively.
-        The plot on the \textbf{right} (b) illustrates distributions for synthetic galaxies.
+        The plot on the \textbf{right} (b) illustrates distributions for synthetic 
+        galaxies.
         Hexagonal bins (filled histogram) and contours (solid-line histogram)
@@
         The relation between the $\log(\mathrm{Blendedness})$ parameter
-        and the photometric accuracies for synthetic stars (\textbf{upper row}, a and b) and
-        galaxies (\textbf{lower row}, c and d) .
-       The \textbf{left} column (a and c) is for uncertainties of PSF or \cmodel{} magnitude,
-        and the \textbf{right} column (b and d) is for uncertainties of $(g-i)$ color.
+        and the photometric accuracies for synthetic stars (\textbf{upper row}, a and 
+        b) and galaxies (\textbf{lower row}, c and d) .
+        The \textbf{left} column (a and c) is for uncertainties of PSF or \cmodel{} 
+        magnitude, and the \textbf{right} column (b and d) is for uncertainties of 
+        $(g-i)$ color.
         Hexagonal bins and contours show results for good- and bad-seeing
@@
 \end{figure*}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-%% Fig: Compare with the behaviours of the Kron photometry for galaxies
-%\begin{figure*}
-%    \begin{center}
-%        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_kron}
-%    \end{center}
-%    \caption{
-%        Basic performance of the Kron photometry for synthetic galaxies.
-%        \textbf{Left} shows the accuracy in $i$-band.
-%        magnitude. The format is identical to Fig \ref{fig:galaxy_mag}.
-%        \textbf{Right} shows the accuracy of the $(g-i)$ color using
-%        Kron photometry.
-%        Other formats are identical to Fig \ref{fig:cmodel_color}.
-%        }
-%    \label{fig:galaxy_kron}
-%\end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
         uncertainties of $(b/a)$ estimates.
-        The \textbf{right} (b) plot shows the relation between input magnitude of a synthetic galaxy
-        and the $(b/a)$ uncertainties.
+        The \textbf{right} (b) plot shows the relation between input magnitude of a 
+        synthetic galaxy and the $(b/a)$ uncertainties.
         Contours are for the default test with \texttt{usePixelWeights=False}, and the
@@
     In this section, we briefly discuss a few other \hscpipe{} aspects that relate
-    to astrometric calibration, star-galaxy separation, blendedness and photometric errors, and galaxy shape measurements to demonstrate the range of topics that can be tested with \synpipe{}.
+    to astrometric calibration, star-galaxy separation, blendedness and photometric 
+    errors, and galaxy shape measurements to demonstrate the range of topics \synpipe{}
+    can test.
 
@@
 
-    For a \synpipe{} test, we inject synthetic objects to single-\visit{} images using
+    For \synpipe{} test, we inject synthetic objects to single-\visit{} images using
     the less accurate initial astrometric calibration.
@@
     and it becomes increasingly difficult at very faint magnitude ($i<24.0$ mag).
-    In \hscpipe{}, the star--galaxy classification primarily depends on the extendedness
-    value, which is measured by the magnitude difference between PSF and \cmodel{}
-    photometry in $i$-band.
-    For more details about this algorithm, please see Bosch\etal
-    (in prep.).
+    In \hscpipe{}, the star--galaxy classification primarily depends on the 
+    extendedness value, which is measured by the magnitude difference between PSF and 
+    \cmodel{} photometry in $i$-band.
+    For more details about this algorithm, please see Bosch\etal (in prep.).
 
@@
     via comparing the input magnitude with the difference between PSF and \cmodel{}
-    magnitudes for both synthetic stars and galaxies, and we highlight the distributions
-    for misclassified objects.
+    magnitudes for both synthetic stars and galaxies, and we highlight the 
+    distributions for misclassified objects.
     As described above, more than $20$\% of synthetic stars at
@@
     It is also clear that seeing condition strongly modifies the distributions
-    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$, where worse seeing conditions clearly make it
-    more difficult to separate star and galaxy.
-    This implies that the completeness or purity of the galaxy or star sample at the faint end may depend on seeing; therefore, seeing condition deserves the attention of HSC users who care about these properties.
-
-    In the next data release, \hscpipe{} will include a better star--galaxy classifier, which will be based on a machine learning method that takes shape and color information into account.
+    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$, where worse seeing conditions clearly 
+    make it more difficult to separate star and galaxy.
+    This implies that the completeness or purity of the galaxy or star sample at the 
+    faint end may depend on seeing; therefore, seeing condition deserves the attention 
+    of HSC users who care about these properties.
+
+    In the next data release, \hscpipe{} will include a better star--galaxy classifier, 
+    which will be based on a machine learning method that takes shape and color 
+    information into account. 
     We will test its improvement using \synpipe{} in the future.
@@
 
-    For both PSF and \cmodel{} magnitude distributions, we can see clear trends that total fluxes are systematically underestimated for highly blended
-    ($b>0.05$ for stars or $0.1$ for galaxies) objects.
+    For both PSF and \cmodel{} magnitude distributions, we can see clear trends that 
+    total fluxes are systematically underestimated for highly blended ($b>0.05$ for 
+    stars or $0.1$ for galaxies) objects.
     This effect is particularly strong for stars.
@@
     Highly blended stars have clearly overestimated $(g-i)$ colors, and the
-    highly blended galaxies seem to have  $(g-i)$ colors that are bluer than the true values.
-
-    These blendedness-related uncertainties are not included in the photometric errors released by \hscpipe{}.
+    highly blended galaxies seem to have  $(g-i)$ colors that are bluer than the 
+    true values.
+
+    These blendedness-related uncertainties are not included in the photometric errors 
+    released by \hscpipe{}.
     We therefore remind the HSC users to treat the highly blended object with
     greater caution.
-
-%% ------------------------------------------------------------------------------------ %%
-%\subsection{Comparing to Kron photometry}
-
-%    \plan{Uses $i$-band as example to briefly discuss Kron photometry}
-
-%    \plan{Although magnitude for galaxies is Ok, the color becomes worse}
 
@@
     Here, $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ is a combination of the
-    axis ratios estimated by the exponential and de Vaucouleurs models weighted by their flux ratio.
-
-    During the investigation, we noticed that one of the problems relates to the \cmodel{} \texttt{usePixelWeight} configuration, which decides whether to
+    axis ratios estimated by the exponential and de Vaucouleurs models weighted by 
+    their flux ratio.
+
+    During the investigation, we noticed that one of the problems relates to the 
+    \cmodel{} \texttt{usePixelWeight} configuration, which decides whether to
     use per-pixel variances as weights in the nonlinear fit.
@@
     the problem. When we use \texttt{usePixelWeight}$=$\texttt{True},
-     $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ can provide an unbiased axis ratio estimation
-    for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
+    $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ can provide an unbiased axis ratio 
+    estimation for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
 
@@
     At the same time, \synpipe{} will try to help \hscpipe{} improve the details
-    of the \cmodel{} so that it can provide more useful structural information without hurting its photometric performance.
+    of the \cmodel{} so that it can provide more useful structural information 
+    without hurting its photometric performance.
 
@@
     %% Short summary
-    In February 2017, the HSC survey made its first public data release, and the survey continues to
-    produce increasingly larger amounts of high-quality imaging data.
+    In February 2017, the HSC survey made its first public data release, and the survey 
+    continues to produce increasingly larger amounts of high-quality imaging data.
     To help achieve the designed goals of the survey and facilitate scientific
     outputs, we developed \synpipe{}, a flexible framework that is based on
-    \hscpipe{}, to examine the data reduction process and check the accuracy of all the HSC pipeline outputs.
+    \hscpipe{}, to examine the data reduction process and check the accuracy of all the 
+    HSC pipeline outputs.
     \synpipe{} injects synthetic stars and galaxies into the desired locations on the
@@
     to an extent that many subtle systematical effects can be taken into
-    consideration, which is helpful for achieving the outstanding scientific goals of the HSC
-    survey.
+    consideration, which is helpful for achieving the outstanding scientific goals of the
+    HSC survey.
     In this work, we choose two \tracts{} in the HSC Wide layer with
@@
 
-    We also notice a few issues in the current \hscpipe{}:
+    \vspace{0.5cm}
+    \noindent We also notice a few issues in the current \hscpipe{}:
 
@@
             the effective radius is underestimated.
-            We show that we can significantly improve the result if we use \texttt{usePixelWeights=True} instead.
-            However, that choice may impact the accuracy of the deblender, which we will test in the future.
+            We show that we can significantly improve the result if we use
+            \texttt{usePixelWeights=True} instead.
+            However, that choice may impact the accuracy of the deblender, which we 
+            will test in the future.
 
@@
     %% Other applications
-    Although we mainly focus on the general behaviors of photometric measurements in this study,
-    \synpipe{} is quite flexible and has many other applications for any HSC
-    dataset.
+    Although we mainly focus on the general behaviors of photometric measurements in 
+    this study, \synpipe{} is quite flexible and has many other applications for any 
+    HSC dataset.
     For instance,  Murata\etal (in prep.) uses \synpipe{} to test
     the impacts of the ambiguously blended objects on the WL measurements.
-    Also, \citep{Niikura2017} applies \synpipe{} to the high-cadence M31 HSC observations
-    to help users search for interesting microlensing events.
-  \synpipe{} is also currently being used to estimate the completeness of the selections
-    for high-$z$ LBG and Lyman- $\alpha$ emitters
+    Also, \citep{Niikura2017} applies \synpipe{} to the high-cadence M31 HSC 
+    observations to help users search for interesting microlensing events.
+    \synpipe{} is also currently being used to estimate the completeness of the 
+    selections for high-$z$ LBG and Lyman- $\alpha$ emitters
     (Ono\etal in prep.; Konno\etal in prep.), check the dependence of the detection and
@@
     identify low surface--brightness dwarf galaxies (Greco\etal in prep.),
-    and test photometric and WL measurements around nearby clusters (Chiu\etal in prep.).
+    and test photometric and WL measurements around nearby clusters 
+    (Chiu\etal in prep.).
 
@@
             test, and uses a \tract{} to test \coadd{} images.
-            In the case of tests that focus on specific regions that are much smaller than
-            the size of a \visit{} or a \tract{} (e.g., quality of photometry
+            In the case of tests that focus on specific regions that are much smaller 
+            than the size of a \visit{} or a \tract{} (e.g., quality of photometry
             around rich galaxy clusters), using \synpipe{} often leads to
@@
     %% Future developments
-    Both \hscpipe{} and \synpipe{} are currently undergoing active development. The plan is to update \synpipe{} to provide a photometric benchmark for
+    Both \hscpipe{} and \synpipe{} are undergoing active development. 
+    Our plan is to update \synpipe{} to provide a photometric benchmark for
     each HSC survey data release, which will help \hscpipe{} improve.
     At the same time, we are also working on improving the efficiency of \synpipe{}.
-    Since many survey data users are not concerned with the subtle effects involved in the image stacking process, we will update \synpipe{} so that it can directly inject synthetic objects to the \coadd{} images and speed up these tests.
+    Since many survey data users are not concerned with the subtle effects involved in 
+    the image stacking process, we will update \synpipe{} so that it can directly 
+    inject synthetic objects to the \coadd{} images and speed up these tests.
 
@@
     Astrophysics  (ASIAA) in Taiwan, and Princeton University in the United States.
-    Funding was contributed by the FIRST program from Japanese Cabinet Office; Ministry of Education, Culture, Sports, Science and Technology (MEXT); Japan
+    Funding was contributed by the FIRST program from Japanese Cabinet Office; Ministry 
+    of Education, Culture, Sports, Science and Technology (MEXT); Japan
     Society for the Promotion of Science (JSPS); Japan Science and Technology Agency
-    (JST); Toray Science  Foundation; NAOJ; Kavli IPMU; KEK; ASIAA; and Princeton University.
+    (JST); Toray Science  Foundation; NAOJ; Kavli IPMU; KEK; ASIAA; and Princeton
+    University.
 

### 2017-04-27 draft/ms_alexie.tex
More edits from Alexie

--- 2017-04-25 draft/ms_v4.tex
@@
     We identify several caveats that apply to version \texttt{4.0.2} of the HSC 
-    pipeline and they need to be considered when using data from the first public 
+    pipeline that need to be taking into consideration when using data from the first public 
     HSC data release. 
@@
     Third, the current \cmodel{} algorithm tends to strongly underestimate the 
-    half-light radius and ellipticity of galaxies with $i>21.5$ mag.
+    half-light radius and ellipticities of galaxies with $i>21.5$ mag.
 
@@
 
-\alexie{ALEXIE EDITED TO HERE}
-
     PSF photometry is the most appropriate way to measure colors for point
@@
 
-    In Fig \ref{fig:psf_color}, we evaluate the accuracies of the \forced{} $(g-i)$
-    and $(i-y)$ PSF colors via comparing the error in color measurements with both
-    input magnitudes and input colors.
-    These results suggest that \hscpipe{} provides accurate and unbiased PSF color
+    In Fig \ref{fig:psf_color}, we evaluate the accuracy of the \forced{} $(g-i)$
+    and $(i-y)$ PSF colors by comparing the error in color measurements with the input magnitudes colors. Figure  \ref{fig:psf_color} shows that \hscpipe{} provides accurate and unbiased PSF color
     estimates for synthetic stars with realistic color distributions down to very 
-    faint magnitude.
-    For $(g-i)$ color, the average uncertainty around $i_{\mathrm{Input}}{\sim}19.0$ 
-    mag is ${\sim}0.025$ mag, and it increases to ${\sim}0.11$ mag at
+    faint magnitudes. The average uncertainty for $(g-i)$ is  ${\sim}0.025$ mag for $i_{\mathrm{Input}}{\sim}19.0$. This uncertainty increases to ${\sim}0.11$ mag at
     $i_{\mathrm{Input}}{\sim}24.0$ mag.
-    The $(i-y)$ color shows very similar results.
-    We also find that the accuracies of PSF colors do not depend on the input colors 
-    of the synthetic stars or the seeing conditions.
-    For instance, the accuracy of $(g-i)$ color for the bad-seeing \tract{} is only
+The $(i-y)$ color displays similar uncertainties.
+Figure \ref{fig:psf_color} also shows that the accuracy of the PSF colors do not depend on the input colors of the synthetic stars or the seeing conditions.
+For instance, the accuracy of $(g-i)$ for the bad-seeing \tract{} is only
     slightly worse in the very faint end (${\sim}0.14$ mag at
-    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the results for the 
+    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the 
     good-seeing \tract{}.
 
-    We further illustrate the accuracies of PSF colors via comparing the distributions
-    of colors for the input synthetic stars and the stars recovered by \hscpipe{}
-    (see Fig \ref{fig:psf_cdist}).
+Figure \ref{fig:psf_cdist} displays the uncertainties in PSF colors  by comparing the color distributions of the input synthetic star sample to the recovered color distributions.
 Using four different colors and two color--color planes, we show that the
-    \forced{} PSF colors can accurately reproduce the distributions of all four colors 
+    \forced{} PSF colors accurately recover the distributions of all four colors 
     and the color-color distributions.
 
-    As for the highly blended stars, on Fig \ref{fig:psf_color}, we see that on average
-    they still have larger uncertainties in colors compared to the relatively isolated
-    ones.
-    For $(g-i)$ color, the average color uncertainty is ${\sim}0.1$ mag larger for the
-    highly blended stars at a fixed input magnitude.
-    Also, for blended stars, the $(g-i)$ color biases toward bluer end while the 
-    $(i-y)$ color biases toward redder end.
-    However, the biases in color measurements for highly blended stars are less severe 
-    than their magnitude measurements.
+    As for highly blended stars, Fig \ref{fig:psf_color} also shows that highly blended stars have larger uncertainties in their colors compared to isolated stars.
+At fixed input magnitude, the  uncertainty in $(g-i)$ is ${\sim}0.1$ mag larger for highly blened stars, Also, for blended stars, $(g-i)$ shows a bias towards bluer colors, while $(i-y)$ shows a bias towards redder colors.
+However, such biases appear to be less severe in terms of colors than in terms of magnitudes.
+
 %% ------------------------------------------------------------------------------------ %%
@@
         Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
-        $g$-band) of synthetic galaxies and the $log(S/N)$ measured by \hscpipe{}
-        \cmodel{} photometry.
-        The lines and contours legend is similar to Fig \ref{fig:star_sn}
+        $g$-band) of synthetic galaxies $log(S/N)$ as measured by \hscpipe{} \cmodel{} photometry. Lines and contours are similar to Fig \ref{fig:star_sn}
         }
@@
     \end{center}
-    \caption{
-        Evaluations of color measurement accuracy for synthetic galaxies
-        using the color-color distributions.
+    \caption{Color-color distributions of synthetic  galaxies.
         The \textbf{left} panel (a) uses $(g-r)$ vs. $(r-i)$ colors, and the 
         \textbf{right} panel (b) uses $(i-z)$ and $(z-y)$ colors.
-        The filled contours and shaded histograms reflect the distributions for input
-        colors.
-        The empty contours and solid-line histograms show the distributions recovered
+Filled contours and shaded histograms  correspond to the input colors.
+Empty contours and solid-line histograms show the distributions recovered
         by \hscpipe{} \cmodel{} photometry.
@@
     For more details, please see Bosch\etal (in prep.).
-    In short, \cmodel{} tries to fit each object using the combination of a
-    de~Vaucouleurs and an exponential profiles that are approximated by multiple 
-    Gaussian profiles.
-    Despite the limitation of the \cmodel{} method (e.g., sensitive to background
-    subtraction and deblender failure), it can deliver robust PSF-corrected fluxes and
+    In short, \cmodel{} tries fits object using both a de~Vaucouleurs and an exponential profile.
+The \cmodel{} algorithm then fits a linear combination of these two best fit models.
+Despite the limitations of the \cmodel{} method (e.g., sensitivity to the background
+    subtraction and to deblending failures), it can deliver robust PSF-corrected fluxes and
     colors for galaxies.
 
-    In our tests, we randomly inject ${\sim}40,000$ synthetic galaxies into each
+    We randomly inject ${\sim}40,000$ synthetic galaxies into each
     \tract{}; and, using an approach similar to that for synthetic stars, we select 
-    galaxy samples for photometric comparisons.
-    First, ${\sim}3$--$7$\% of the synthetic galaxies are located within 2 pixels 
-    of the centroids of real objects or do not show any match in the \synpipe{} 
-    results, they are hence removed from the sample.
-    The fraction of unmatched objects slightly increases with worse seeing condition.
-
-    After selecting the matched synthetic galaxies with primary detection and
-    clean photometry (see Appendix \ref{app:qc} for details), we have ${\sim}30,000$
-    galaxies in each \tract{} for comparison.
-    \hscpipe{} misclassifies less than $1$\% of these objects as point sources
+    galaxy samples for photometric comparisons. Synthetic galaxies that are located within 2 pixels 
+    of the centroids of real objects are removed from the sample  (these represent ${\sim}3$--$7$\% of the input sample).
+After imposing quality cuts on the  recovered synthetic galaxy sample (see Appendix \ref{app:qc} for details), we have ${\sim}30,000$
+    galaxies in each \tract{}.
+
+    We find that \hscpipe{} mis-classifies less than $1$\% of these objects as point sources
     in the good-seeing \tract{}.
     But the fraction of misclassified galaxies increases to $4$\% in the
-    bad-seeing \tract{}.
-    The median input magnitude for these misclassified sources is ${\sim}24.9$ mag
-    in $i$-band, significantly fainter than the median of other sources.
-    We further discuss this in Section \ref{ssec:sg}.
-
-    We also use $b>0.05$ to define samples of highly blended galaxies.
-    Due to the extended nature of the galaxies, the $b$ distributions for synthetic 
-    galaxies skew toward higher values (especially for the bad-seeing \tract{}) than
-    the ones for stars.
-    About $7$--$9$\% of synthetic galaxies are highly blended by this standard.
+    bad-seeing \tract{}. We will discuss star/galaxy separation further in Section \ref{ssec:sg}.
+
+    We define a sample of highly blended galaxies  by imposing the cut $b>0.05$.
+    Due to the extended nature of galaxies, the $b$ distribution of synthetic 
+    galaxies is more skewed toward high values (especially for the bad-seeing \tract{}) compared to the b distribution of stars.
+    About $7$--$9$\% of synthetic galaxies are highly blended with $b>0.05$.
     The fraction is only slightly higher in the bad-seeing \tract{}, and the
-    $g$-band has the highest fraction of highly blended galaxies.
-    We highlight the highly blended ones in comparisons, and there are other relevant
-    discussions in Section \ref{ssec:blendedness}.
-
-    Although these galaxies span in very wide large ranges of magnitude and
-    structural parameters, the majority of them are faint
-    ($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec).
-    It is very challenging to obtain good photometric quality of these galaxies, which 
-    is crucial to key scientific goals of the HSC survey.
-    The selected samples do not provide enough bright or large galaxies to test.
-    Therefore, we will supplement results for these galaxies using better samples
-    in the future.
+    $g$-band has the highest fraction of highly blended galaxies \alexie{I don't understand here.
+Is this just a question of seeing?
+Is thid because the g-band has worse seeing.
+It seems in contradiction with the previous phrase.}.
+In our plots, we will highlight highly blended galaxies and we will discuss blending effects further in Section \ref{ssec:blendedness}.
+
+% ALEXIE: not necessary
+    %The majority of the galaxies in our synthetic galaxy samples are  are faint
+    %($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec).
+    %It is very challenging to obtain accurate photometry good photometric quality of these galaxies, which 
+    %is crucial to key scientific goals of the HSC survey.
+    %The selected samples do not provide enough bright or large galaxies to test.
+    %Therefore, we will supplement results for these galaxies using better samples
+    %in the future.
 
@@
 
-    In Fig \ref{fig:cmodel_sn}, we first show the relation between the input
-    magnitudes and the \s2n{} of the synthetic galaxies estimated by the ratio
-    between \cmodel{} flux and its uncertainty.
+    Figure \ref{fig:cmodel_sn} shows the relation between the input
+    magnitudes and the \s2n{} of synthetic galaxies.
+The  \s2n{} is the ratio  of the \cmodel{} flux and its uncertainty.
 The \s2n{} used here is the average one for extended object.
-
-    We still use $i$ and $g$ bands as examples.
-    As PSF magnitude for stars, \cmodel{} photometry establishes well-behaved relation 
-    between input magnitude and output \s2n{}. 
-    Comparing to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows larger
-    scatter at fixed input magnitude, which is likely due to differences in size and 
-    shape of the galaxies.
-    This makes it difficult to define ``detection limit'' for galaxies clearly.
-
-    In $i$ band, typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but 
-    there are already galaxies at the same magnitude have \s2n{} below 5.
-    Although HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag, the 
-    sample will be incomplete at this faint magnitude.
-    It also introduces selection bias if galaxies with certain structural properties 
+\alexie{What do you mean here?
+You have a clound of points for each object, not a mean value of SN per mag bin.
+Needs to be calrified.}
+
+ Figure  \ref{fig:cmodel_sn} shows  that the \cmodel{} photometry displays a well-behaved relation between input magnitude and output \s2n{}.
+Compared to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows a larger
+    scatter at fixed input magnitude.
+This is likely due to the fact that galaxies have a wider range in sizes and shapes than point sources.
+In $i$ band, a typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but
+    there are also galaxies at the same magnitude which have \s2n{} below 5. The HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag but the 
+    sample becomes incomplete at these faint magnitudes.
+    It also introduces a selection bias if galaxies with certain structural properties  (e.g., more extended and lower surface brightness)
     are harder to detect than others.
-    HSC survey data users who want to select flux-limited galaxy sample,
-    or intend to study the population of faint (e.g., high-$z$) galaxies should
-    keep this in mind.
-    Similar to stars, worse seeing also leads to lower \s2n{} at fixed magnitude 
+    HSC survey data users who want to select flux-limited galaxy samples,
+    or who intend to study the population of faint (e.g., high-$z$) galaxies should
+    keep this in mind.  Finally, we also find that  a worse seeing leads to a lower \s2n{} at fixed magnitude 
     (see Fig \ref{fig:psf_s2n} for $i$-band).
@@
 
-    In Fig \ref{fig:cmodel_mag}, we illustrate the photometric uncertainties of the
-    \cmodel{} magnitudes in each band using the same format for Fig \ref{fig:psf_mag}.
+    Fig \ref{fig:cmodel_mag} shows the photometric uncertainties of the
+    \cmodel{} magnitudes in each band using the same format as Fig \ref{fig:psf_mag}.
 
@@
     $i_{\mathrm{Input}}=25.2$ mag.
-    Compared to PSF photometry for stars, the uncertainties of \cmodel{} show larger 
-    scatter for galaxies, which is expected given the diversity of structural 
-    properties and complexities in the model-fitting process.
-    At the same time, \cmodel{} algorithm in \hscpipe{} provides unbiased and consistent 
-    photometry for galaxies in different bands and seeing conditions.
-
-    In $i$-band, the typical flux accuracy for \forced{} \cmodel{} is ${\sim}7-9$\%
-    in the good-seeing \tract{} at $i_{\mathrm{Input}}<24.0$ mag, and moderately 
-    decreases to ${\sim}11$\% at $25.0$ mag.
-    and ${\sim}9$\% at $i_{\mathrm{Input}}{\sim}24.0$ mag.
-    For the bad-seeing \tract{} in $i$-band, the performance is very similar.
+    Compared to the PSF photometry for stars, the uncertainties of \cmodel{} show larger 
+    scatter for galaxies, which is expected given the diversity of galaxy shapes and sizes which adds complexity to the model-fitting process.
+    At the same time, Figure \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in \hscpipe{} provides unbiased and consistent 
+    photometry for galaxies across different bands and seeing conditions.
+
+The typical $i$-band flux accuracy for \forced{} \cmodel{} is ${\sim}7-9$\% in the good-seeing \tract{} at $i_{\mathrm{Input}}<24.0$ mag.
+This moderately degrades to ${\sim}11$\% at $25.0$ mag.
+The performance is similar in the $i$-band bad-seeing \tract{}.
 At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the median magnitude offset
@@
 
-    It is worth noting that the flux uncertainty from \synpipe{} is significantly 
-    larger than the flux error from \hscpipe{}, which does not take into account the 
-    systematic uncertainties involved in the modeling fitting process.
-    Although the synthetic galaxies here are described by simple single-\ser{} model, 
-    \cmodel{} algorithm can only approximate them to certain accuracy, especially when 
-    background noise, deblending uncertainty, and priors of model parameters are 
-    considered.
-    Given that real galaxies are more complex in structure, these uncertainties should 
-    be treated as lower limits.
+    It is worth noting that the flux uncertainty from \synpipe{} are significantly 
+    larger than the flux errors from \hscpipe{}, which does not take into account the 
+    systematic uncertainties involved in the modeling fitting process. Even though our synthetic galaxy sample is  comprised of objects with simple single-\ser{} models, 
+    \cmodel{} algorithm can only approximate them to a certain accuracy because of the background noise, deblending uncertainties, and priors imposed on model parameters.
+Given that real galaxies are more complex in structure, the uncertainties derived from our \synpipe{} tests should be treated as lower limits.
+
+\alexie{What does this say about the values of SN from CMODEL then? If the unceratinties are underestimated, then the SN is overestimated? By how much? WOrth commenting on here?}
 
@@
     The accuracy of \forced{} \cmodel{} photometry is consistent across all filters.
-    For $g$, $r$, and $z$ bands, the photometric uncertainties are very similar to
+    For the$g$, $r$, and $z$ bands, the photometric uncertainties are very similar to
     $i$-band results between $20.0$ and $25.0$ mag.
@@
     across the entire input magnitude range.
-    The uncertainties for $y$ band are slightly worse, ranging from 9\% to 17\% in the
+    The uncertainties for the $y$ band are slightly worse, ranging from 9\% to 17\% in the
     same magnitude bins.
     In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
-    $y$ band at $>24.0$ mag.
-    Average magnitude offsets change from \minus{}0.06 at $24.0$ mag to \minus{}0.22
-    mag at 25.0 mag.
-    Both a worse seeing condition and a higher background noise level can make it more
-    difficult to detect faint object in $y$ band.
+    the $y$ band at $>24.0$ mag. This bias in the $y$ band flux is equal to  \minus{}0.06 at $24.0$ mag to \minus{}0.22
+    mag at 25.0 mag. Worse seeing conditions and a  higher background noise level mean that it is more
+    difficult to detect faint objects in the $y$ band.
     At $y_{\mathrm{Input}}{\sim}24.0$, the average \s2n{} for \cmodel{} is already
@@
 
-    As mentioned, the statistics for brighter galaxies are uncertain due to small 
-    sample size.
-    We do notice that, at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry 
-    shows larger uncertainty and starts to systematically underestimate the total flux.
+Our synthetic galaxy sample is dominated by faint galaxies.
+Hence, we have poor statistics for bright galaxies.
+However, we do find that at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry starts to systematically underestimate total fluxes.
 Based on external comparisons, the behavior of \cmodel{} for bright galaxies may
-    depend on the galaxy type (e.g., \citealt{HSCDR1}). 
-    Known issues of current \hscpipe{} (e.g., \hscpipe{} over-deblends around bright 
-    objects; inappropriately weights priors in \cmodel{}) could lead to poorer 
-    photometric quality for bright galaxies. 
-    Meanwhile, at the imaging depth of HSC ($>29.0$\sb{} in $i$ band for Wide layer), 
-    assumptions in \cmodel{} may no longer be the best choice for modeling bright 
+    depend on galaxy types (e.g., \citealt{HSCDR1}).  Also, at bright magnitudes, another known issue is that the current \hscpipe{} (e.g., \hscpipe{} over-deblends around bright 
+    objects.
+Inappropriately weight priors in \cmodel{}) may also lead to poorer photometric quality for bright galaxies.
+Finally, at the imaging depth of HSC ($>29.0$\sb{} in the Wide Layer $i$ band),  \cmodel{} may simply not be a good choice for modeling bright
     galaxies (e.g., for massive elliptical galaxies; see Huang\etal in prep.~for 
     more details).
-    We will look into these issues more carefully in the future.
-
-    For the highly blended galaxies, we also see systematically underestimated total 
-    flux (average offset ${\sim}0.1$ mag) and larger scatter of photometric 
-    uncertainty in all five bands.
-    Meanwhile, the contrast between relatively isolated and highly blended galaxies
-    in photometric performance is not as staggering as the one for synthetic
+
+We also find that highly blended galaxies tend to have systematically underestimated total 
+    fluxes (with an average offset ${\sim}0.1$ mag) and larger photometric uncertainties in all five bands. However,  the contrast between relatively isolated and highly blended galaxies
+    in photometric performance is not as stark as for synthetic
     stars (Fig \ref{fig:psf_mag}).
@@
     results suggest similar accuracies.
-    We highlight the differences between \forced{} and \unforced{} \cmodel{}
-    photometry in $g$ and $y$ bands in Fig \ref{fig:cmodel_diff}.
-    The only noticeable feature is for galaxies brighter than $24.0$ mag in
-    $g$ band, the \forced{} \cmodel{} magnitudes are systematically brighter than
-    the \unforced{} ones, suggesting \forced{} \cmodel{} shows better accuracy in 
-    $g$ band.
+
+    Fig \ref{fig:cmodel_diff} compared the difference between  \forced{} and \unforced{} \cmodel{} in $g$ and $y$.
+We find that  \forced{} and \unforced{} \cmodel{} shows similar trends.
+The main  noticeable trend is that galaxies brighter than $24.0$ mag in $g$ band, have systematically brighter \forced{} \cmodel{} magnitudes.
+This suggests that the \forced{} \cmodel{} is more accurate in the $g$ band.
 
@@
 
-    The consistent and accurate five-band \cmodel{} colors from \hscpipe{} are crucial
-    to the photometric redshift and spectral energy distribution (SED) fitting results.
-    They are also key to the selection of high-$z$ Lyman-break galaxies (LBG) and
-    and many other interesting objects.
-
-    In Fig \ref{fig:cmodel_color}, we demonstrate the accuracies of \forced{} $(g-i)$
-    and $(i-y)$ \cmodel{} colors in the same format for synthetic stars
-    (Fig \ref{fig:psf_color}).
-    They confirm that \hscpipe{} can provide reliable \cmodel{} colors for synthetic 
+    Consistent and accurate five-band \cmodel{} colors from \hscpipe{} are crucial  for photometric redshift and spectral energy distribution (SED) estimates.
+They are also key, for example, to the selection of high-$z$ Lyman-break galaxies (LBG) .
+
+    Fig \ref{fig:cmodel_color} evaluates the  accuracy of \forced{} $(g-i)$ and $(i-y)$ \cmodel{} colors using the same format as Figure Fig \ref{fig:psf_color}.
+We find that \hscpipe{} provides reliable \cmodel{} colors for synthetic
     galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
@@
     The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
-    $(i-y)$ colors show similar results.
+    The $(i-y)$ colors show similar results.
 
     The performance of \forced{} \cmodel{} color does not depend on seeing and is 
-    unbiased for entire ranges of input magnitudes and colors.
+    unbiased for the entire range of magnitudes and colors that we have tested.
     The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
     is slightly overestimated.
-    As mentioned above, this is not surprising given the shallower imaging depth in
-    $y$ band.
-    Meanwhile, high blendedness also increases the color uncertainties and biases the 
-    color measurements.
-    The highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
-    $(i-y)$ colors than the input ones.
-
-    Similar to Fig \ref{fig:psf_cdist}, we also compare the color--color distributions
-    of the input and output \forced{} \cmodel{} values in Fig \ref{fig:cmodel_cdist}.
-    The general 2--D distributions are well recovered but the accuracy is not as good as 
-    the one for stars, especially on the $(i-z)$ vs. $(z-y)$ plane.
-    This is expected given the narrow dynamical ranges of these colors among red filters.
+    As mentioned above, this is not surprising given the shallower $y$ band imaging depth.
+Highly blended galaxies have larger uncertainties in their colors compared to isolated galaxies.
+Highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder
+    $(i-y)$ colors compared to their input colors.
+
+Figure  \ref{fig:cmodel_cdist} compare the input color--color distributions with the recovered color distributions.
+The general 2--D distributions are well recovered but the accuracy is not as good as for stars, especially in the $(i-z)$ vs.
+$(z-y)$ plane.
+    This is expected given the narrow dynamical ranges of these colors in the redder filters.
     The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
@@
 
-    We should point out that we assume constant color for the entire galaxy.
-    In reality, different colors for individual component or color gradient can 
-    complicate the situation.
-    The uncertainties of \cmodel{} colors here should be considered as lower limits.
+We note that  our synthetic galaxies do not have color gradients.
+In reality, color gradients will complicate the situation and hence the uncertainties shown here should be considered as lower limits.
+
 %% ------------------------------------------------------------------------------------ %%
@@
     \caption{
-        Astrometric accuracy for a synthetic star (\textbf{left}) and a galaxy
-        (\textbf{right}) via the differences in R.A and Dec between the input
-        coordinates and the ones measured on the \coadd{} images.
-        Hexagonal bins (filled histogram) and contours (solid-line histogram) are for
-        the synthetic objects from \tracts{} with good and bad seeing conditions, 
+        Astrometric accuracy for synthetic stars (\textbf{left}) and galaxies
+        (\textbf{right}).
+We show the differences between the input R.A and Dec and the coordinates measured on the \coadd{} images.
+Hexagonal bins (filled histogram) and contours (solid-line histogram) are for synthetic objects from \tracts{} with good and bad seeing conditions,
         respectively.
-        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.
+        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines. \alexie{Need one phrase here. Always give the take home message in the caption. We find that xxxxxx .}
         }
@@
     \end{center}
-    \caption{
-        Problems with the current  \hscpipe{}star--galaxy separation method, which is 
-        based on the magnitude difference between the PSF and \cmodel{} photometry.
-        The plot on the \textbf{left} (a) illustrates distributions for the synthetic 
-        stars.
+    \caption{Evaluation of the \hscpipe{} star--galaxy separation scheme.
+Star--galaxy separation is based on the the magnitude difference between the PSF and \cmodel{} photometry.
+The plot on the \textbf{left} (a) corresponds to synthetic stars.
 Hexagonal bins and filled histogram show distributions of correctly classified
@@
         objects in \tracts{} with bad and good seeing conditions, respectively.
-        The plot on the \textbf{right} (b) illustrates distributions for synthetic 
+        The plot on the \textbf{right} (b) corresponds to synthetic 
         galaxies.
@@
         are for galaxies from good- and bad-seeing \tracts{}, respectively.
-        The scatter plot and dashed-line histogram are for synthetic galaxies that are
-        misclassified as point sources.
-        Zero magnitude difference is highlighted using dashed lines on both plots.
-        }
+        The scatter plot and dashed-line histogram highlight synthetic galaxies that are
+        misclassified as point sources.}
     \label{fig:sg}
@@
     \caption{
-        The relation between the $\log(\mathrm{Blendedness})$ parameter
-        and the photometric accuracies for synthetic stars (\textbf{upper row}, a and 
-        b) and galaxies (\textbf{lower row}, c and d) .
-        The \textbf{left} column (a and c) is for uncertainties of PSF or \cmodel{} 
-        magnitude, and the \textbf{right} column (b and d) is for uncertainties of 
-        $(g-i)$ color.
+        Relation between the $\log(\mathrm{Blendedness})$ parameter
+        and the photometric accuracy f synthetic stars (\textbf{upper row}, a and 
+        b) and galaxies (\textbf{lower row}, c and d).
+        \textbf{Left} columns (a and c) show the uncertainties in PSF and/or \cmodel{} 
+        magnitudes. \textbf{Right} columns (b and d) show the uncertainties in 
+        $(g-i)$ colors.
         Hexagonal bins and contours show results for good- and bad-seeing
@@
     \caption{
-        Accuracy of the weighted axis ratio measurements for synthetic
+        Accuracy of weighted axis ratio estimates for synthetic
         galaxies using \cmodel{} photometry.
         The \textbf{left} (a) plot shows the relation between the input $(b/a)$ and the
-        uncertainties of $(b/a)$ estimates.
-        The \textbf{right} (b) plot shows the relation between input magnitude of a 
-        synthetic galaxy and the $(b/a)$ uncertainties.
-        Contours are for the default test with \texttt{usePixelWeights=False}, and the
-        hexagonal bins are used for same tests with \texttt{usePixelWeights=True}.
+        uncertainty in $(b/a)$.
+        The \textbf{right} (b) plot shows the relation between input magnitude and the undertainty in $(b/a)$.
+        Contours are for the default test with \texttt{usePixelWeights=False}, and hexagonal bins correspond to \texttt{usePixelWeights=True}.
         }
@@
 
-\section{Results on Other Aspects of \hscpipe{}}
+\section{Other Performace Tests}
     \label{sec:others}
 
-    In this section, we briefly discuss a few other \hscpipe{} aspects that relate
-    to astrometric calibration, star-galaxy separation, blendedness and photometric 
-    errors, and galaxy shape measurements to demonstrate the range of topics \synpipe{}
-    can test.
+    In this section, we turn our attention to astrometric calibration, star-galaxy separation, blending effects, and galaxy shape measurements.
+
+    %to demonstrate the range of topics \synpipe{}
+    %can test.
 
@@
 
-    For \synpipe{} test, we inject synthetic objects to single-\visit{} images using
-    the less accurate initial astrometric calibration.
+    We inject synthetic objects into single-\visit{} images using the initial (and less accurate) astrometric calibration.
     During the image stacking step, the joint calibration process improves the
     astrometric solutions.
-    Therefore, the differences between the input and output coordinates from \synpipe{}
-    can help us understand the systematic effect of the image stacking step.
-
-    In Fig \ref{fig:astrometry}, we plot the distributions of astrometric offsets for
-    both synthetic stars and galaxies in good- and bad-seeing \tracts{}.
-    Small systematic offsets at ${\sim}10$--20 mas can be noticed in either direction.
-    The two \tracts{} apparently show different systematic offsets.
-    In the same \tracts{}, synthetic stars and galaxies show very similar offsets,
-    although the scatter for galaxies is slightly larger due to their extended nature.
+    Therefore, differences between the input and output coordinates from \synpipe{}
+    can help us understand systematic effects related to the image stacking step.
+\alexie{Not clear what we are testing here exactly?
+Is this an absolute astrometric calibratio for HSC....?
+Or is this showing how much change there is in the refined astrometric solution??}
+
+    Fig \ref{fig:astrometry} shows the distribution of astrometric offsets for synthetic stars and galaxies in good- and bad-seeing \tracts{}.
+    We find small systematic offsets at the ${\sim}10$--20 mas level.
+    The two \tracts{} show different systematic offsets.
+    In the same \tracts{}, synthetic stars and galaxies show similar offsets, but the scatter for galaxies is slightly larger than stars due to their extended nature.
+\alexie{Need a final take home message here.
+What have we learned?}
 
@@
 
-    Star--galaxy separation is an important aspect of a cosmology survey,
-    and it becomes increasingly difficult at very faint magnitude ($i<24.0$ mag).
+    Star--galaxy separation becomes increasingly difficult at faint magnitudes ($i<24.0$ mag).
     In \hscpipe{}, the star--galaxy classification primarily depends on the 
@@
 
-    In Fig \ref{fig:sg}, we show the current status of star--galaxy classification
-    via comparing the input magnitude with the difference between PSF and \cmodel{}
-    magnitudes for both synthetic stars and galaxies, and we highlight the 
-    distributions for misclassified objects.
-    As described above, more than $20$\% of synthetic stars at
-    $i_{\mathrm{Input}}>23.0$ mag are misclassified as extended objects, while only a
-    tiny fraction of faint synthetic galaxies ($i_{\mathrm{Input}}>24.0$) are
-    misclassified.
-    This confirms that the current star--galaxy classification strategy in \hscpipe{}
-    results in a galaxy sample with \textbf{high completeness} and star sample
+    Fig \ref{fig:sg} shows the current status of our star--galaxy classification scheme.  Figure  \ref{fig:sg} shows the difference between PSF and \cmodel{}
+    magnitudes as a function of  input magnitude.
+We find that $20$\% of synthetic stars at $i_{\mathrm{Input}}>23.0$ mag are misclassified as extended objects, while only a tiny fraction of faint synthetic galaxies ($i_{\mathrm{Input}}>24.0$) are
+    misclassified as stars. This confirms that the current star--galaxy classification strategy in \hscpipe{}
+    results in a galaxy sample with \textbf{high completeness} and at star sample
     with \textbf{high purity}.
@@
     It is also clear that seeing condition strongly modifies the distributions
-    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$, where worse seeing conditions clearly 
-    make it more difficult to separate star and galaxy.
-    This implies that the completeness or purity of the galaxy or star sample at the 
-    faint end may depend on seeing; therefore, seeing condition deserves the attention 
-    of HSC users who care about these properties.
-
-    In the next data release, \hscpipe{} will include a better star--galaxy classifier, 
-    which will be based on a machine learning method that takes shape and color 
+    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$.
+Worse seeing conditions make star-galaxy separation more challenging.
+The completeness and purity of galaxy and star samples at the faint end will depend on seeing conditions.
+
+    In the next data release, \hscpipe{} will include an improved star--galaxy classifier which will be based on a machine learning method that takes both shape \alexie{size?} and color 
     information into account.
-    We will test its improvement using \synpipe{} in the future.
-
-%% ------------------------------------------------------------------------------------ %%
-\subsection{Blendedness and Photometric Errors}
+
+%% ------------------------------------------------------------------------------------ %%
+\subsection{Blending Effects}
     \label{ssec:blendedness}
 
-    In the above sections, we have pointed out the impact of high blendedness on
-    photometry through a small sample of highly blended objects.
-    Here, in Fig \ref{fig:blend}, we further explore the effect of blendedness via
-    directly plotting it against the uncertainties of magnitudes and colors.
-
-    For both PSF and \cmodel{} magnitude distributions, we can see clear trends that 
+ Fig \ref{fig:blend} shows the $b$ parameter versus uncertainties in magnitudes and colors. For both PSF and \cmodel{} magnitude distributions, we can see clear trends that 
     total fluxes are systematically underestimated for highly blended ($b>0.05$ for 
@@
     This effect is particularly strong for stars.
-    As for colors, higher blendedness still results in higher uncertainties for both
+    As for colors, higher values of $b$ results in higher uncertainties for both
     stars and galaxies, but the trends are different for each.
-    Highly blended stars have clearly overestimated $(g-i)$ colors, and the
-    highly blended galaxies seem to have  $(g-i)$ colors that are bluer than the 
+    Highly blended stars have clearly overestimated \alexie{redder? bluer? what does overestimated mean} $(g-i)$ colors. Highly blended galaxies seem to have  $(g-i)$ colors that are bluer than the 
     true values.
 
-    These blendedness-related uncertainties are not included in the photometric errors 
+    Blendedness-related uncertainties are not included in the photometric errors 
     released by \hscpipe{}.
-    We therefore remind the HSC users to treat the highly blended object with
+    We therefore caution HSC users to treat the highly blended object with
     greater caution.
@@
     To improve the stability of \cmodel{} for these low-\s2n{} and barely resolved
-    galaxies, \hscpipe{} uses Bayesian priors on a radius and axis ratio that strongly
-    favors these galaxies.
-    However, the current implementation of these priors has a flaw that leads to
-    severely underestimated size and overestimated axis ratio for most galaxies.
-
-    In Fig \ref{fig:galaxy_ba}, we demonstrate this issue using the difference between
-    the \cmodel{} axis ratio and the input values as an example.
-    Here, $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ is a combination of the
+    galaxies, \hscpipe{} uses Bayesian priors on galaxy sizes and axis ratios.
+However, the current implementation of these priors has a flaw \alexie{Is this just that the prior is wrong?
+Can we just say that the prior is wrong?} that leads to a severe  underesaimte in the sizes and axis ratios of galaxies.
+
+    Figure \ref{fig:galaxy_ba} demonstrates this issue and compares the  input and measured values of the  \cmodel{} axis ratio.
+Here, $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ is a \alexie{the weighted sum?
+The eighted mean?} combination of the
     axis ratios estimated by the exponential and de Vaucouleurs models weighted by 
@@
 
-    During the investigation, we noticed that one of the problems relates to the 
-    \cmodel{} \texttt{usePixelWeight} configuration, which decides whether to
-    use per-pixel variances as weights in the nonlinear fit.
-    By default, \hscpipe{} chooses \texttt{usePixelWeight}$=$\texttt{False}.
+    Using our \synpipe{} tests, we discovered that one issue is related to the  \cmodel{} \texttt{usePixelWeight} configuration. This option which decides whether to
+    use a per-pixel variances as weights in the nonlinear fit. By default, \hscpipe{} chooses \texttt{usePixelWeight}$=$\texttt{False}.
     As one can see, this leads to a significantly overestimated axis ratio for almost
@@
     the problem. When we use \texttt{usePixelWeight}$=$\texttt{True},
-    $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ can provide an unbiased axis ratio 
+    $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ provides an unbiased axis ratio 
     estimation for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
-
-    For the current HSC data release, we warn users against using the \cmodel{}
-    size and shape to study a galaxy with $i_{\mathrm{Input}}>21.5$.
-    At the same time, \synpipe{} will try to help \hscpipe{} improve the details
-    of the \cmodel{} so that it can provide more useful structural information 
-    without hurting its photometric performance.
+This  is a good example  that  demonstrates how the \synpipe{} framework is a valuable tool  for quality control and that can be used to improve \hscpipe{}.
+
+    For the current HSC data release, we warn users against using the sizes and shapes from \cmodel{} to study the structural properties of galaxies with $i_{\mathrm{Input}}>21.5$.
+
+%    At the same time, \synpipe{} will try to help \hscpipe{} improve the details
+%    of the \cmodel{} so that it can provide more useful structural information 
+%    without hurting its photometric performance.
 
@@
     continues to produce increasingly larger amounts of high-quality imaging data.
-    To help achieve the designed goals of the survey and facilitate scientific
-    outputs, we developed \synpipe{}, a flexible framework that is based on
-    \hscpipe{}, to examine the data reduction process and check the accuracy of all the 
-    HSC pipeline outputs.
-    \synpipe{} injects synthetic stars and galaxies into the desired locations on the
-    single-\visit{} images with the help of the original astrometric and
-    photometric calibrations.
-    These data are then processed by \hscpipe{} to generate the \coadd{} images and
-    all the photometric measurements.
-    In this way, \synpipe{} can simulate the realistic data reduction process
-    to an extent that many subtle systematical effects can be taken into
-    consideration, which is helpful for achieving the outstanding scientific goals of the
-    HSC survey.
-    In this work, we choose two \tracts{} in the HSC Wide layer with
-    representative seeing conditions (good and bad) to test the general behaviors of HSC
+    To help achieve the designed goals of the survey and to facilitate scientific investigations, we have developed \synpipe{}, a flexible framework based on
+    \hscpipe{} and that can be used to perform quality control on the 
+    HSC pipeline outputs. \synpipe{} operates by injecting synthetic stars and galaxies into single-\visit{} images. 
+    These data are then processed by \hscpipe{} to generate a \coadd{} images and to perform photometry measurements.
+With this  approach,  \synpipe{} can be used as an end-to-end and realistic test of the full  data reduction process.
+In this paper, we  use  two \tracts{} in the HSC Wide layer with
+    representative seeing conditions (good and bad \alexie{repeat the numbers here}) to test the general behaviors of HSC
     photometry for both stars and galaxies.
 
-    From these tests, we find the following:
+    Our main findings are the following:
 
@@
 
-        \item The \forced{} PSF photometry provides excellent magnitude and color
-            measurements for isolated stars at $18.0 < i < 25.0$.
-            The typical uncertainties of HSC forced PSF photometry for stars range
-            from around 0.01 mag at $i{\sim}18.0$ mag to 0.08 mag at $i{\sim}25.0$
+        \item The \forced{} PSF photometry provides excellent \alexie{isn't really a god word. Unbiased? Accurate?} measurements of magnitude and color for isolated stars at $18.0 < i < 25.0$.
+            The typical uncertainty of HSC forced PSF photometry for stars ranges
+            from 0.01 mag at $i{\sim}18.0$ mag to 0.08 mag at $i{\sim}25.0$
             mag (1\%-7\% accuracy in the $i$-band).
             The \forced{} PSF photometry can accurately recover the color--color
-            sequences for stars.
+            sequences of stars.
 
@@
             The \forced{} \cmodel{} colors for galaxies are accurate and unbiased.
-            The accuracies of colors do not show dependence on input magnitude and
+            The accuracy of galaxy colors do not dependence on input magnitude \alexie{What does this mean? They become more inaccurate at fainter magnitue, right? So it does depend on color.} or
             color.
 
-        \item The \forced{} PSF and \cmodel{} photometry are robust against different
-            seeing conditions, despite the fact that worse seeing leads to a lower
+        \item The \forced{} PSF and \cmodel{} photometry are robust against moderate changes in the seeing conditions, despite the fact that worse seeing leads to a lower
             $\mathrm{S}/\mathrm{N}$ at fixed input magnitude.
 
-        \item High blendedness ($b>0.1$) impacts the accuracy of both PSF and \cmodel{}
+        \item Blending ($b>0.1$) has an impact on the accuracy of both PSF and \cmodel{}
             photometry, especially for stars.
-            For highly blended stars, the \forced{} PSF photometry on average
-            overestimates the magnitudes of stars by 0.1–-0.2 mag.
-            For galaxies, high-blendedness typically adds an additional 0.05 mag
+            For highly blended stars, the \forced{} PSF photometry overestimates the magnitudes of stars on average by 0.1–-0.2 mag.
+            For galaxies, blending effects typically add an additional 0.05 mag
             uncertainty in both magnitude and color estimates.
-
     \end{enumerate}
@@
     \vspace{0.5cm}
-    \noindent We also notice a few issues in the current \hscpipe{}:
+    \noindent We also high-light several known issues with the  current version of \hscpipe{}:
 
@@
         \item The performance of the current star--galaxy separation algorithm in \hscpipe{}
-            is not perfect, especially at the faint magnitude end and under poor seeing
+            is not perfect,  and degrades at fainter magnitudes and with poor seeing
             conditions.
@@
         \item The nominal \cmodel{} setting  (\texttt{usePixelWeights=True}) results
-            in very biased estimates of shape and size for galaxies, especially for the
-            relatively faint ones.
-            The axis ratio of a galaxy using \cmodel{} is highly overestimated, while
-            the effective radius is underestimated.
-            We show that we can significantly improve the result if we use
-            \texttt{usePixelWeights=True} instead.
+            in very biased estimates of the shapes and sizes for galaxies.
+The axis ratio of a galaxy using \cmodel{} is highly overestimated and the effective radius is typically underestimated.
+Galaxy shapes and sizes can be more well measured with the \texttt{usePixelWeights=True} option.
             However, that choice may impact the accuracy of the deblender, which we 
             will test in the future.
-
     \end{enumerate}
 
-    The HSC collaboration is working on improving these issues in the future version
-    of \hscpipe{} and the subsequent data release.
-    Meanwhile, we suggest that HSC data users keep these caveats in mind.
+    The HSC collaboration is working on improving these issues for future versions of \hscpipe{} and for subsequent data releases.
+
 %% ------------------------------------------------------------------------------------ %%
@@
     %% Other applications
-    Although we mainly focus on the general behaviors of photometric measurements in 
-    this study, \synpipe{} is quite flexible and has many other applications for any 
-    HSC dataset.
-    For instance,  Murata\etal (in prep.) uses \synpipe{} to test
-    the impacts of the ambiguously blended objects on the WL measurements.
-    Also, \citep{Niikura2017} applies \synpipe{} to the high-cadence M31 HSC 
-    observations to help users search for interesting microlensing events.
-    \synpipe{} is also currently being used to estimate the completeness of the 
-    selections for high-$z$ LBG and Lyman- $\alpha$ emitters
-    (Ono\etal in prep.; Konno\etal in prep.), check the dependence of the detection and
-    completeness of high-$z$ LBG pairs on the pair separation (Harikane\etal in prep.),
-    identify low surface--brightness dwarf galaxies (Greco\etal in prep.),
-    and test photometric and WL measurements around nearby clusters 
-    (Chiu\etal in prep.).
+    Here we  focused on characterizing the  photometric performance of  \hscpipe{}.
+However,  \synpipe{} is a flexible tool and is being used for a range of other applications.
+For instance,  Murata\etal (in prep.) use \synpipe{} to characterize the level of blending in the HSC Wide Layer.
+\citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of  M31 HSC to search for microlensing events.
+\synpipe{} is also currently being used to estimate the completeness of  high-$z$ LBG and Lyman- $\alpha$ emitters (Ono\etal in prep.; Konno\etal in prep.),  to check the completeness of  high-$z$ LBG pairs as a function of pair separation (Harikane\etal in prep.), to test the completeness of low surface--brightness dwarf galaxies selections (Greco\etal in prep.),and to test magnifications effects around nearby clusters (Chiu\etal in prep.).
 
     %% Caveats
+
+    \alexie{The stuff below should not go here. Move it into the bulk of the draft in Section 4}.
+
     The limitations of the current \synpipe{} include the following:
@@
     Our plan is to update \synpipe{} to provide a photometric benchmark for
-    each HSC survey data release, which will help \hscpipe{} improve.
+    each HSC survey data release, which will help improve \hscpipe{}.
     At the same time, we are also working on improving the efficiency of \synpipe{}.
-    Since many survey data users are not concerned with the subtle effects involved in 
-    the image stacking process, we will update \synpipe{} so that it can directly 
-    inject synthetic objects to the \coadd{} images and speed up these tests.
+    Many users are not necessarily concerned with the subtle effects involved in 
+    the image stacking process.
+Hence, a future implementation of \synpipe{} will include the option of injecting objects directly into  \coadd{} images which will speed up the generation of synthetic data sets.
+The results shown in this paper demonstrate the  utility of the \synpipe{} framework in order to perform end-to-end quality control on pipeline products to the level of accuracy needed by large panchromatic surveys.
 

### 2017-04-27 draft/ms_v5.tex
Final version; Jim-->James

--- 2017-04-27 draft/ms_alexie.tex
@@
 % Version 4; Edits from Alexie
+% Version 5; Edits from Alexie; Comments by Jim
 
@@
         Ryoma Murata \altaffilmark{2, 4},
-        Jim Bosch \altaffilmark{3},
+        James Bosch \altaffilmark{3},
         Paul Price \altaffilmark{3},

### 2017-04-27 draft/ms_v5.tex
Not capitalize tract and visit
Abstract

@@
 \def\unforced{\texttt{unforced}}
-\def\tract{\texttt{Tract}}
-\def\visit{\texttt{Visit}}
-\def\tracts{\texttt{Tracts}}
-\def\visits{\texttt{Visits}}
+\def\tract{\texttt{tract}}
+\def\visit{\texttt{visit}}
+\def\tracts{\texttt{tracts}}
+\def\visits{\texttt{visits}}
 \def\galsim{\texttt{G}{\scriptsize \texttt{AL}}\texttt{S}{\scriptsize \texttt{IM}}}
@@
     The Wide layer of the SSP is both wide and deep, reaching a detection limit of 
-    $i>26.0$ mag. 
+    $i{\sim}26.0$ mag. 
     At these depths, it is challenging to achieve accurate, unbiased, and consistent
@@
     For stars, we achieve 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at
-    $i{\sim}25.5$ in the $i$-band (corresponding to uncertainties of ${\sim}0.01$ and 
-    ${\sim}0.06$ mag respectively).  
+    $i{\sim}25.5$ in the $i$-band (corresponding to statistical accuracies of 
+    ${\sim}0.01$ and ${\sim}0.06$ mag respectively).  
     For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
     achieves 7\% photometry at $i{\sim}20.0$ mag and 11\% photometry at $i{\sim}25.0$ 
-    in the $i$-band (corresponding to uncertainties of ${\sim}0.14$ and ${\sim}0.20$ 
-    mag respectively). 
+    in the $i$-band (corresponding to statistical accuracies of ${\sim}0.14$ and 
+    ${\sim}0.20$ mag respectively). 
     We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
     estimates that are robust to seeing conditions. 
-    We identify several caveats that apply to version \texttt{4.0.2} of the HSC 
-    pipeline that need to be taking into consideration when using data from the first public 
-    HSC data release. 
+    We identify several caveats that apply to the version of HSC pipeline used for 
+    the first public HSC data release (DR1) that need to be taking into consideration. 
     First, the degree to which an object is blended with other objects impacts the 

### 2017-04-27 draft/ms_v5.tex
Introduction

@@
     Telescope
-    (WFIRST; \citealt{Dressler2012})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
+    (WFIRST; \citealt{Dressler2012, 
+    Spergel2015})\footnote{\url{https://wfirst.gsfc.nasa.gov/}},
     and the \textit{Euclid} project
@@
     Before we can tackle outstanding scientific questions, we must first learn
-    how to handle the the large amounts of data\footnote{Right now, SSP has 
+    how to handle the the large amounts of data\footnote{Until Feb 2017, SSP has 
     accumulated ${\sim}300$ TB of data products.} generated by these projects while 
@@
     times and have excellent red-sensitivity, but they also suffer from the
-    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014}), which means that
-    brighter stars have larger Point Spread Functions (PSFs) than fainter stars. 
+    so-called ``brighter-fatter'' effect (\citealt{Antilogus2014, Guyonnet2015}), 
+    which means that brighter stars have larger Point Spread Functions (PSFs) than 
+    fainter stars. 
     These variations and effects make accurate astrometric and photometric calibration,
@@
     (e.g., the SSP Wide layer reaches a $5\ \sigma$ point source detection limit of
-    ${\sim}26.4$ mag), the number of objects per unit area increases.  
+    ${\sim}26.4$ mag in $i$-band), the number of objects per unit area increases.  
     Hence, deep surveys become more sensitive and subject to the effects of blending.  
@@
     \caption{
-        Illustration of the main steps involved in using \synpipe{}.
+        Illustration of the workflow of \synpipe{}.
         Gray boxes indicate required inputs at different stages.
@@
         At the bottom left, we show a \coadd{} image which contains synthetic galaxies. 
-        On the right hand side, we show the spatial relation between \texttt{Tracts},
-        \texttt{Patches}, and \texttt{Visits}. 
-        The red colored box corresponds to one \texttt{Tract} which has an area of 
+        On the right hand side, we show the spatial relation between \texttt{tracts},
+        \texttt{patches}, and \texttt{visits}. 
+        The red colored box corresponds to one \texttt{tract} which has an area of 
         about 1.5 deg$^2$. 
-        Large colored circles are \texttt{Visits} (also commonly known as "pointings") 
+        Large colored circles are \texttt{visits} (also commonly known as "pointings") 
         with small rectangles representing CCDs. 
-        \texttt{Patches} are represented by black dashed lines. 
-        One \texttt{Tract} typically contains 81 \texttt{Patches}.
+        \texttt{patches} are represented by black dashed lines. 
+        One \texttt{tract} typically contains 81 \texttt{patches}.
         }
@@
 
-    \bibitem[Antilogus et al.(2014)]{2014JInst...9C3048A} Antilogus, P., Astier, P.,
+    \bibitem[Antilogus et al.(2014)]{Antilogus2014} Antilogus, P., Astier, P.,
              Doherty, P., Guyonnet, A., \& Regnault, N.\ 2014, Journal of
@@
              2002, \aap, 395, 1077
+
+    \bibitem[Guyonnet et al.(2015)]{Guyonnet2015} Guyonnet, A., Astier, P., Antilogus, 
+             P., Regnault, N., \& Doherty, P.\ 2015, \aap, 575, A41
 
@@
 
+    \bibitem[Spergel et al.(2015)]{Spergel2015} Spergel, D., Gehrels, N., Baltay, 
+             C., et al.\ 2015, arXiv:1503.03757
+
+    \bibitem[Steidel et al.(1996)]{Steidel1996} Steidel, C.~C., Giavalisco, M.,
+             Pettini, M., Dickinson, M., \& Adelberger, K.~L.\ 1996, \apjl, 462, L17
+
     \bibitem[Suchyta et al.(2016)]{Suchyta2016} Suchyta, E., Huff, E.~M., Aleksi{\'c},
              J., et al.\ 2016, \mnras, 457, 786
-
-    \bibitem[Steidel et al.(1996)]{Steidel1996} Steidel, C.~C., Giavalisco, M.,
-             Pettini, M., Dickinson, M., \& Adelberger, K.~L.\ 1996, \apjl, 462, L17
 

### 2017-04-27 draft/ms_v5.tex
HSC overview

@@
 
+%% ------------------------------------------------------------------------------------ %%
+\subsection{Status of the Survey}
+    \label{ssec:ssp}
+
     %% Basic
@@
     and employ a slightly different surveying strategy.
-    Strauss\etal (in prep.) describes the HSC survey in more detail, and identifies the
+    \citet{HSCOverview} describes the HSC survey in more detail, and identifies the
     HSC collaborators.
@@
     The camera has a circular FoV with a 1.5 deg diameter.
-    Each CCD contains 2048$\times$4096 pixels and the sizes of pixels are 0.168\asec{}.
+    Each CCD contains 2048$\times$4096 pixels and the sizes of pixels are 
+    0.168\asec{}.
+    For more details about the HSC camera, please see Miyazaki\etal (in prep.).
 
@@
     magnitude of $i{\sim} 26.4$ mag and have a median seeing with 
-    FWHM${\sim}0.6$\asec{}. 
+    FWHM${\sim}0.6$\asec{} in the $i$ band. 
     \citealt{HSCDR1} provides details on the first data release and data status.
@@
 %% ------------------------------------------------------------------------------------ %%
-\section{The HSC Data Reduction Pipeline}
+\subsection{The HSC Data Reduction Pipeline}
     \label{ssec:hscpipe}
@@
             calibrations. 
+            The photometric calibration is based on data from the Panoramic Survey 
+            Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey 
+            (\citealt{Schlafly2012, Tonry2012, Magnier2013}).
             \synpipe{} uses the spatially varying PSF models, photometric zeropoints, 
@@
             \citep{Padmanabhan2008}.
-            \textbf{\synpipe{} will use these improved calibrations.}
+            \synpipe{} will use these improved calibrations.
             \hscpipe{} organizes these \coadd{} images into equiareal rectangular
@@
             galaxies.
-            The HSC \cmodel{} algorithm is described in Bosch\etal, in prep. and is an
-            improved version of the SDSS \cmodel{} magnitude (\citealt{Lupton2001, 
-            Abazajian2004}). 
-            The HSC \cmodel{} fits objects using both a de~Vaucouleurs and an 
-            exponential profiles taking into account the smearing by the PSF.  
-            \cmodel{} then linearly combines the two results to find the best fit to 
-            the galaxy image. 
-            \cmodel{} magnitudes are designed to yield accurate fluxes and colors for 
-            galaxies. 
-            Star--galaxy separation is performed based on the difference between 
-            \texttt{psf} and \cmodel{}{} magnitudes.
+
+            \begin{itemize}
+
+                \item \hscpipe{} uses matched-filter method to derive PSF magnitude 
+                    with the centroid fixed. 
+                    The algorithm matches the image of a star with the PSF model 
+                    multiplied by an amplitude. 
+                    This amplitude parameter is estimated via the inner product of 
+                    the image and PSF model after shifting the model to the centroid 
+                    of the star, then divide by the effective area of the PSF model.
+
+                \item The HSC \cmodel{} algorithm is described in Bosch\etal (in prep), 
+                    and is based on the version for the SDSS \cmodel{} magnitude 
+                    (\citealt{Lupton2001, Abazajian2004}). 
+                    It fits objects using both a de~Vaucouleurs and an exponential 
+                    profiles convolved with the PSF model.  
+                    \cmodel{} then linearly combines the two results to find the best 
+                    fit to the galaxy image. 
+                    \cmodel{} magnitudes are designed to yield accurate fluxes and 
+                    colors for galaxies. 
+                    Star--galaxy classification is also performed based on the 
+                    difference between \texttt{psf} and \cmodel{}{} magnitudes.
+
+            \end{itemize}
 
@@
     DR1 data quality has been vetted in \citet{HSCDR1} by cross-checking with the 
-    Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) 1 imaging survey
-    (\citealt{Schlafly2012, Tonry2012, Magnier2013}) to examine the behavior of the 
-    stellar sequence.
+    Pan-STARRS 1 imaging survey to examine the behavior of the stellar sequence.
     Generally speaking, the PSF photometry is accurate at the 1--2\% level for bright 
@@
             features of the real data (e.g., blended objects; proximity to bright
-            objects, bleeding trails, other optical artifacts can be included in the
+            objects, bleeding trails, other optical artifacts) can be included in the
             test.
@@
 
-    \bibitem[Aihara et al.(2017)]{HSCDR1} Aihara, H., Armstrong, R., Bickerton, S.,
+    \bibitem[Aihara et al.(2017a)]{HSCDR1} Aihara, H., Armstrong, R., Bickerton, S.,
              et al.\ 2017, arXiv:1702.08449
+
+    \bibitem[Aihara et al.(2017b)]{HSCOverview} Aihara, H., Armstrong, R., 
+             Bickerton, S., et al.\ 2017, arXiv:1702.08449
 

### 2017-04-27 draft/ms_v5.tex
Synthetic data

@@
     and is under active development.
-    Unlike most photometric pipelines on the market, it involves high-level reduction
-    processes that produce not only deep \coadd{} images but also a series of
-    science-ready catalogs. 
+    Unlike most publicly available photometric pipelines, it involves high-level 
+    reduction processes that produce not only deep \coadd{} images but also a series 
+    of science-ready catalogs. 
     To perform tests of the data products that result from \hscpipe{}, \synpipe{} is 
@@
             tools to help the user work on HSC DR1 data. 
-            However, \synpipe{} also easily allows users to design and use their own 
-            custom made input catalogs.
+            However, the users can also supply their own input catalogs best suited 
+            for their applications.
             \synpipe{} is already being used in a wide range of
-            scientific applications (see Section \ref{sec:summary} for details).
+            scientific topics (see Section \ref{sec:summary} for details).
 
@@
             The positions of synthetic galaxies can be specified via the input catalog, 
-            they can be distributed randomly over a given region, or on a grid 
-            (the grid option is useful in that it avoids blends between Synthetic 
-            objects, e.g. see Murata\etal in prep.).
+            they can be distributed randomly over a given region, or on an 
+            evenly-spaced grid (the grid option is useful in that it avoids blends 
+            between Synthetic objects, e.g. see Murata\etal in prep.).
 
@@
             \texttt{addFakes.py}; see the middle panel of Fig \ref{fig:flowchart}).
-            \synpipe{} goes through all the individual CCD images that belong to 
+            \synpipe{} goes through individual CCD images that belong to 
             each \visit{} and decides which synthetic objects from the input catalog 
@@
         model using \galsim{}\texttt{.Convolve}.
-        After this, \synpipe{} uses the \galsim{}\texttt{.drawImage} method to create 
+        After this, \synpipe{} uses the \galsim{}\texttt{.drawImage} method to redner 
         the image of the simulated galaxy.
@@
             to provide accurate noise level.
+            The added noise only accounts for the additional flux in the synthetic 
+            object, and will thus be subdominant compared to the noise already in 
+            the image for faint objects.
 
@@
 
-    Using the infrastructures provided by \hscpipe{}, the user can easily perform these 
+    Using the infrastructure provided by \hscpipe{}, the user can easily perform these 
     steps in parallel, and the overall efficiency of \synpipe{} is similar to
@@
     \synpipe{} can match the input catalog to the output catalog (this contains a mix 
-    of real and synthetic galaxies) using a matching radius that is specified by the 
-    user.
+    of real and synthetic galaxies) using a matching radius specified by the user.
     Each unmatched object from the input catalog is also passed to the results catalog
@@
 \subsection{Data}
-    We use \tract{}$=9699$ in the VVDS field (median FWHM$=0.449$\asec{} in $i$-band;
+    We use \tract{}$=9699$ in the VVDS field (median FWHM$=0.449$\asec{} in $i$ band;
     in this paper referred to as \texttt{goodSeeing}) and
@@
     \texttt{badSeeing}).
-    \tract{}$=9699$ also has better seeing in both $r$- and $z$-bands;
-    the seeing conditions in $g$- and $y$-bands are very similar for both
+    \tract{}$=9699$ also has better seeing in both $r$ and $z$ bands than the median 
+    conditions in those bands.
+    The seeing conditions in $g$ and $y$ bands are very similar for both
     \tract{}$=9699$ and \tract{}$=8764$.
     For both \tracts{}, the \coadd{} image in each band includes data from
-    20--40 \visits{}.  
+    20--40 \visits{}\footnote{The large number of \visits{} here is due to large 
+    dither pattern. Please see Fig \ref{fig:flowchart}.}.  
     These two \tract{} are selected because they are not at the edge of a field, do 
     not contain any extremely bright ($i<12$ mag) saturated stars, and are 
-    representative of both "good" and "bad" seeing conditions in the $i$-band.
+    representative of both "good" and "bad" seeing\footnote{Here, ``bad'' seeing only 
+    suggests that it is worse than the median seeing condition by HSC standard.} 
+    conditions in the $i$ band.
 %% ------------------------------------------------------------------------------------ %%
@@
     We then match this sample against our HSC UltraDeep--COSMOS data (which reaches 
-    ${\sim}27.2$ mag in $i$-band). 
+    ${\sim}27.2$ mag in $i$ band). 
     After applying basic quality cuts (see \ref{app:qc}), this procedure provides us 
-    with five-band HSC photometry for 14,472 stars.
+    with five-band HSC PSF photometry for 14,472 stars.
     To increase the sample size, we re-sample the five-band magnitude distributions 
@@
     We further match this COSMOS sample with the HSC UltraDeep--COSMOS data.
-    After removing objects with problematic photometry, we obtain a sample of
-    58,210 synthetic galaxies with realistic five-band HSC photometry.
+    After removing objects with problematic photometry (see Appendix \ref{app:qc} for 
+    details), we obtain a sample of 58,210 synthetic galaxies with realistic 
+    five-band HSC \cmodel{} photometry.
     As shown in Fig \ref{fig:galaxy_sample}, the majority of these galaxies are
@@
     For galaxies, we use a number density of 500 per CCD. 
+    Given the magnitude distributions of these objects, these numbers are high enough 
+    to ensure large sample of useful synthetic objects for the test, and will also not
+    create unrealistic crowded images.
 
@@
     We use HSC DR1 data stored at Kavli Institute for the Physics and Mathematics of 
-    the Universe (Kavli IPMU). 
-    For stars the \texttt{addFakes.py} step takes ${\sim}1.5$ hours per \tract{} in 
-    each band. 
+    the Universe (Kavli IPMU) for these tests. 
+    Using 108 cores, the \texttt{addFakes.py} step takes ${\sim}1.5$ hours per 
+    \tract{} in each band for stars. 
     The same process takes longer for galaxy tests (${\sim}3.0$ hours per
@@
     to generate output catalogs for \forced{} and \unforced{} photometry
-    in each band. For our tests, we reject  synthetic objects  locate within 2 pixels 
+    in each band. 
+    For our tests, we reject synthetic objects locate within 2 pixels 
     of a real HSC object. 
+    These ``ambiguously blended'' (e.g. \citealt{Dawson2016}) objects are extreme 
+    blends in which multiple objects are detected as a single object, and are not 
+    useful for photometric tests.
 
@@
     Although \hscpipe{} does provide other options (e.g., aperture and Kron photometry),
-    these two are the only options that consider the effects of PSF in different bands 
-    and are consistent across all bands in terms of position and shape.
+    these two are the only options that consider the effects of the PSF in different 
+    bands and are consistent across all bands in terms of position and shape.
 
@@
     In \hscpipe{}, the PSF magnitude is derived using a matched-filter method that
-    depends on the best-fit PSF model and uses the Lanczos interpolation to shift
-    the PSF model.
+    depends on the best-fit PSF model and uses third-order Lanczos interpolation to 
+    shift the PSF model.
     The error of the PSF magnitude from \hscpipe{} only considers the per-pixel noise,
@@
     seeing conditions.
-    For the same reason, $g$-band has the highest fraction of misclassification,
+    For the same reason, the $g$-band has the highest fraction of misclassification,
     while $i$-band is recommended for selecting point sources.
@@
     In the following comparisons, we show the results from the
-    \textbf{good-seeing} and \textbf{bad-seeing} \tracts{} separately because it
+    \texttt{goodSeeing} and \texttt{badSeeing} \tracts{} separately because it
     is important to understand how the seeing condition affects photometric accuracy 
@@
     complete overlap with other objects. 
-    Here we use $b>0.05$ to define highly blended stars (${\sim}4$--$9$\% are blended).
+    Here we use $b>0.05$ to define highly blended stars (${\sim}4$--$9$\% are blended
+    according to this criterion).
     The fraction of highly blended stars slightly increases in the bad seeing \tract{}. 
@@
     %% C %%
+    \bibitem[Calabretta \& Greisen(2002b)]{WCS2} Calabretta, M.~R., \& Greisen, E.~W.\
+             2002, \aap, 395, 1077
+
     \bibitem[Chang et al.(2015)]{Chang2015} Chang, C., Busha, M.~T., Wechsler, R.~H.,
@@
     %% D %%
+    \bibitem[Dawson et al.(2016)]{Dawson2016} Dawson, W.~A., Schneider, M.~D., 
+             Tyson, J.~A., \& Jee, M.~J.\ 2016, \apj, 816, 11
+
     \bibitem[Dressler et al.(2012)]{Dressler2012} Dressler, A., Spergel, D., Mountain,
@@
              2002, \aap, 395, 1061
-
-    \bibitem[Calabretta \& Greisen(2002b)]{WCS2} Calabretta, M.~R., \& Greisen, E.~W.\
-             2002, \aap, 395, 1077
 

### 2017-04-28 draft/ms_v5.tex
Make it clear about accuracy v.s. precision

@@
     pipeline. 
-    For stars, we achieve 1\% photometry at $i{\sim}18.0$ mag and 7\% photometry at
-    $i{\sim}25.5$ in the $i$-band (corresponding to statistical accuracies of 
-    ${\sim}0.01$ and ${\sim}0.06$ mag respectively).  
+    For stars, we achieve 1\% photometric precision at $i{\sim}18.0$ mag and 7\%
+    precision at $i{\sim}25.5$ in the $i$-band (corresponding to statistical scatters 
+    of ${\sim}0.01$ and ${\sim}0.06$ mag respectively).  
     For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
-    achieves 7\% photometry at $i{\sim}20.0$ mag and 11\% photometry at $i{\sim}25.0$ 
-    in the $i$-band (corresponding to statistical accuracies of ${\sim}0.14$ and 
-    ${\sim}0.20$ mag respectively). 
+    achieves 7\% photometric precision at $i{\sim}20.0$ mag and 11\% precision at 
+    $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters of 
+    ${\sim}0.14$ and ${\sim}0.20$ mag respectively). 
     We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
@@
         Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
-        $g$-band) of synthetic stars and the $log(S/N)$ measured by \hscpipe{} PSF
+        $g$-band) of synthetic stars and the $\log (S/N)$ measured by \hscpipe{} PSF
         photometry.
@@
     We randomly inject ${\sim}100,000$ stars into each \tract{} in all five bands. 
+    Typically, there are ${\sim}80000$ stars with $i_{\mathrm{PSF}}<26.0$ in one HSC 
+    \tract{}. 
     Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the 
@@
     \texttt{goodSeeing} and \texttt{badSeeing} \tracts{} separately because it
-    is important to understand how the seeing condition affects photometric accuracy 
+    is important to understand how the seeing conditions affects photometric accuracy 
     as well as to test whether \hscpipe{} can deliver unbiased photometry under 
@@
     average seeing conditions.
-    At the same time, it is worth reminding HSC data users that the detection
-    limit will show spatial variations due to the seeing conditions.
-
-%% ------------------------------------------------------------------------------------ %%
-\subsubsection{Accuracy of PSF magnitudes}
-
-    We now investigate the accuracy of the PSF magnitude in each of the five bands
+    However, it is worth reminding HSC data users that the detection
+    limit will exhibit spatial variations due to the seeing conditions.
+
+%% ------------------------------------------------------------------------------------ %%
+\subsubsection{Precision and Accuracy of PSF magnitudes}
+
+    We now investigate the performance of the PSF photometry in each of the five bands
     independently. 
     Fig \ref{fig:psf_mag} shows the difference between the input magnitude versus the
-    \hscpipe{} \forced{} PSF magnitude as a function of input magnitude.
+    \hscpipe{} \forced{} PSF magnitude ($\Delta \mathrm{mag}_{\mathrm{PSF}}$) as a 
+    function of input magnitude. 
+    We separate these stars into seven input magnitude bins.  
+    In each bin, we characterize the \textbf{precision} of the PSF magnitude using 
+    the standard deviation of the $\Delta \mathrm{mag}_{\mathrm{PSF}}$ distribution.
+    Meanwhile, we characterize the \textbf{accuracy} of the PSF magnitude via the 
+    mean magnitude difference in each bin. 
+    This also informs us whether the PSF photometry is biased at certain input 
+    magnitude.
 

### 2017-04-28 draft/ms_v5.tex
PSF magnitude

@@
     We separate these stars into seven input magnitude bins.  
-    In each bin, we characterize the \textbf{precision} of the PSF magnitude using 
-    the standard deviation of the $\Delta \mathrm{mag}_{\mathrm{PSF}}$ distribution.
-    Meanwhile, we characterize the \textbf{accuracy} of the PSF magnitude via the 
-    mean magnitude difference in each bin. 
+    In each bin, we characterize the statistical \textbf{precision} of the PSF 
+    magnitude using the standard deviation of the $\Delta \mathrm{mag}_{\mathrm{PSF}}$ 
+    distribution.
+    Meanwhile, we characterize the statistical \textbf{accuracy} of the PSF magnitude 
+    via the mean magnitude difference in each bin. 
     This also informs us whether the PSF photometry is biased at certain input 
@@
     The overall performance of the \hscpipe{} \forced{} PSF magnitude is excellent. 
-    The median $i$-band magnitude difference for the \tract{} with 0.45\asec{} seeing 
+    The median $i$-band PSf magnitude precision for the \texttt{goodSeeing} \tract{} 
     is ${\sim}0.015$ mag (${\sim}1.5$\%) at $i_{\mathrm{Input}}{\sim}19.0$ mag. 
-    At $i_{\mathrm{Input}}{\sim}24.0$ mag, the average accuracy of the PSF magnitude is 
-    ${\sim}3$\% level (${\sim}0.036$ mag average difference).
-    At $i_{\mathrm{Input}}{\sim}25.2$ mag, the average accuracy decreases to
+    At $i_{\mathrm{Input}}{\sim}24.0$ mag, the precision of the PSF magnitude is 
+    at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
+    At $i_{\mathrm{Input}}{\sim}25.2$ mag, the precision decreases to
     ${\sim}7$\% with an average ${\sim}0.072$ mag difference.
 
-    The accuracy of the PSF photometry for the bad-seeing \tract{} shows a similar 
+    The precision of PSF magnitude for the \texttt{badSeeing} \tract{} shows similar 
     performance at $i_{\mathrm{Input}}<23.5$ mag. 
-    At fainter magnitudes, the accuracy slightly degrades. 
-    The bad-seeing \tract{} displays a performance of ${\sim}5$\% accuracy at
-    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% accuracy at
+    At fainter magnitudes, the precision slightly degrades. 
+    The \texttt{badSeeing} \tract{} has ${\sim}5$\% precision at
+    $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% precision at
     $i_{\mathrm{Input}}{\sim}25.2$ mag.
-    \citet{HSCDR1} evaluates the accuracy of PSF photometry via external comparisons
-    with the PS1, PV2, and SDSS data at $i<21$ mag, and finds a 1-2\% level accuracy,
+    \citet{HSCDR1} evaluates the precision of PSF magnitude via external comparisons
+    with the PS1, PV2, and SDSS data at $i<21$ mag, and finds it at 1-2\% level,
     which is consistent with our results. 
@@
     lack of imaging matched to HSC depths.
-    The results from \synpipe{} hence provide useful evaluations of the accuracy of 
-    the HSC photometry down to our detection limit\footnote{Strictly speaking, the 
-    uncertainties reported here should be considered as the lower limit because 
-    \synpipe{} currently does not consider PSF modeling uncertainties}.
-
-    Figure \ref{fig:psf_mag} also shows that the accuracy of the PSF photometry is 
+    The results from \synpipe{} hence provide useful evaluations of the precision of 
+    the HSC photometry down to our detection limit, though, strictly speaking, the 
+    precision reported here should be considered as upper limits because 
+    \synpipe{} currently does not consider the systematic uncertainties in PSF 
+    modeling.
+
+    Figure \ref{fig:psf_mag} also shows that the precision of the PSF photometry is 
     not filter dependent. 
-    The accuracy of forced PSF magnitudes in $r$ and $z$ is similar to the $i$-band. 
-    For $r$ band we find 1.5-4.0\% at $r_{\mathrm{Input}} < 24.0$ mag and ${\sim}8$\% 
-    at $r_{\mathrm{Input}}{\sim}25.2$. 
-    For $z$-band we find 1.0-5.0\% at $z_{\mathrm{Input}} < 24.0$ mag and ${\sim}10$\% 
-    down to $z_{\mathrm{Input}}{\sim}25.2$ mag).
-
-    The accuracy in the $g$ and $y$ bands becomes slightly worse at the very faint end. 
-    For $g$ band, the accuracy is 1.5-7.0\% at $g_{\mathrm{Input}} < 24.0$ mag and is
+    The precision of \forced{} PSF magnitudes in $r$ and $z$ is similar to the results
+    for $i$-band. 
+    For $r$ band we find 1.5-4.0\% precision at $r_{\mathrm{Input}} < 24.0$ mag and 
+    ${\sim}8$\% precision at $r_{\mathrm{Input}}{\sim}25.2$. 
+    For $z$-band we find 1.0-5.0\% precision at $z_{\mathrm{Input}} < 24.0$ mag and 
+    ${\sim}10$\% precision down to $z_{\mathrm{Input}}{\sim}25.2$ mag).
+
+    The precision for $g$ and $y$ bands becomes slightly worse at the very faint end. 
+    For $g$ band, the precision is 1.5-7.0\% at $g_{\mathrm{Input}} < 24.0$ mag and is
     ${\sim}13$\% down to $25.2$ mag.
-    For $y$ band, we find 1.5-5.0\% accuracy at $y_{\mathrm{Input}} < 23.0$ mag and
+    For $y$ band, we find 1.5-5.0\% precision at $y_{\mathrm{Input}} < 23.0$ mag and
     ${\sim}12$\% down to $24.0$ mag. 
@@
 
-    The PSF photometry for relatively isolated stars is unbiased in the $i$ and $z$ 
-    bands down to faint magnitudes. 
-    For the $g$, $r$, and $y$ bands, we find small offsets between the input and 
-    recovered magnitude. 
+%% ------------------------------------------------------------------------------------ %%
+
+    The PSF photometry for relatively isolated stars is accurate and unbiased in $i$ 
+    and $z$ bands down to faint magnitudes. 
+    For the $g$, $r$, and $y$ bands, we find mean $\Delta \mathrm{mag}_{\mathrm{PSF}}$
+    that are close to the PSF flux errors estimated by \hscpipe{}.  
     \hscpipe{} tends to underestimate the fluxes of stars in these bands by 
@@
 	On average, \hscpipe{} systematically underestimates the total fluxes of stars 
-	that are subject to blending effects by $0.05$--$0.10$ mag at a fixed input magnitude.
+	that are subject to blending effects by $0.05$--$0.10$ mag at a fixed input 
+	magnitude.
     We see the same effect in all bands, and the impact of blendedness becomes
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsubsection{Accuracy of PSF colors}
+\subsubsection{Precision and Accuracy of PSF colors}
 

### 2017-04-28 draft/ms_v5.tex
PSF color

@@
         Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
-        $g$-band) of synthetic stars and the $\log (S/N)$ measured by \hscpipe{} PSF
-        photometry.
+        $g$-band) of synthetic stars and the $\log (\mathrm{S}/\mathrm{N})$ measured 
+        by \hscpipe{} PSF photometry.
         Hexagonal binned density plots and contours show the distributions for
@@
         from good and bad seeing \tracts{}.
-        Highly blended objects are highlighted using scattered plots.
+        Highly blended objects are highlighted using scattered points.
         The long-dashed lines mark zero magnitude difference, while the pairs of
@@
         The magnitude differences between the \unforced{} and \forced{}
-        PSF photometry for synthetic stars in $g$- (\textbf{left} and $y$-band
+        PSF photometry for synthetic stars in $g$ (\textbf{left}) and $y$ band
         (\textbf{right}).
@@
     \begin{center}
-        \includegraphics[width=\textwidth]{fig/synpipe_psf_color}
+        \includegraphics[width=15cm]{fig/synpipe_psf_color}
     \end{center}
@@
     The results from \synpipe{} hence provide useful evaluations of the precision of 
-    the HSC photometry down to our detection limit, though, strictly speaking, the 
+    the HSC photometry down to our detection limit\footnote{Strictly speaking, the 
     precision reported here should be considered as upper limits because 
     \synpipe{} currently does not consider the systematic uncertainties in PSF 
-    modeling.
+    modeling. But this effect should be subdominant.}
 
@@
 	an indication of photometric uncertainties arising from inaccurate astrometric 
-	calibrations and PSF modeling across different bands. 
+	calibrations and PSF modeling across different bands\footnote{On average, the 
+	centroids are more accurate in \forced{} photometry as they are defined using 
+	the band with higher \s2n{}}. 
 	Figure \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} 
 	PSF photometry for the $g$ and the $y$ band. 
-	The overall differences are small ($<0.01$ mag) .
+	The overall differences are small ($<0.01$ mag). 
+	At very faint end ($g_{\mathrm{Input}}>24.0$ mag and $g_{\mathrm{Input}}>23.5$
 
@@
 
-    In Fig \ref{fig:psf_color}, we evaluate the accuracy of the \forced{} $(g-i)$
-    and $(i-y)$ PSF colors by comparing the error in color measurements with the input magnitudes colors. Figure  \ref{fig:psf_color} shows that \hscpipe{} provides accurate and unbiased PSF color
-    estimates for synthetic stars with realistic color distributions down to very 
-    faint magnitudes. The average uncertainty for $(g-i)$ is  ${\sim}0.025$ mag for $i_{\mathrm{Input}}{\sim}19.0$. This uncertainty increases to ${\sim}0.11$ mag at
-    $i_{\mathrm{Input}}{\sim}24.0$ mag.
-The $(i-y)$ color displays similar uncertainties.
-Figure \ref{fig:psf_color} also shows that the accuracy of the PSF colors do not depend on the input colors of the synthetic stars or the seeing conditions.
-For instance, the accuracy of $(g-i)$ for the bad-seeing \tract{} is only
-    slightly worse in the very faint end (${\sim}0.14$ mag at
-    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the 
-    good-seeing \tract{}.
-
-Figure \ref{fig:psf_cdist} displays the uncertainties in PSF colors  by comparing the color distributions of the input synthetic star sample to the recovered color distributions.
+    In Fig \ref{fig:psf_color}, we evaluate the precision and accuracy of the 
+    \forced{} $(g-i)$ and $(i-y)$ PSF colors by comparing the differences between input 
+    and output colors ($\Delta \mathrm{Color}$) with both the input magnitudes and 
+    colors. 
+    Figure \ref{fig:psf_color} shows that \hscpipe{} provides precise and accurate PSF 
+    colors for synthetic stars with realistic color distributions down to very 
+    faint magnitudes. 
+    The average precision for $(g-i)$ is ${\sim}0.025$ mag at 
+    $i_{\mathrm{Input}}{\sim}19.0$. 
+    The scatter increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}24.0$ mag.  
+    The $(i-y)$ color displays similar precision. 
+    The \forced{} PSF color measurements are not biased through the entire ranges of 
+    input magnitudes and colors.
+
+    Figure \ref{fig:psf_color} shows that the precision of PSF colors do not depend 
+    the seeing conditions. 
+    For instance, the precision of $(g-i)$ for the \texttt{badSeeing} \tract{} is 
+    only slightly worse at the very faint end (${\sim}0.14$ mag at
+    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the \texttt{goodSeeing} \tract{}.
+
+    Figure \ref{fig:psf_cdist} displays the precision of PSF colors by comparing the 
+    color distributions of the input sample to the recovered color distributions. 
     Using four different colors and two color--color planes, we show that the 
@@
 
-    As for highly blended stars, Fig \ref{fig:psf_color} also shows that highly blended stars have larger uncertainties in their colors compared to isolated stars.
-At fixed input magnitude, the  uncertainty in $(g-i)$ is ${\sim}0.1$ mag larger for highly blened stars, Also, for blended stars, $(g-i)$ shows a bias towards bluer colors, while $(i-y)$ shows a bias towards redder colors.
-However, such biases appear to be less severe in terms of colors than in terms of magnitudes.
+    As for highly blended stars, Fig \ref{fig:psf_color} also shows that highly blended 
+    stars have worse precision and accuracy in their colors compared to isolated stars. 
+    At fixed input magnitude, the precision in $(g-i)$ is ${\sim}0.1$ mag worse for 
+    highly blended stars.  
+    Also, for blended stars, $(g-i)$ shows a bias towards bluer colors, while $(i-y)$ 
+    shows a bias towards redder colors. 
+    However, such biases appear to be less severe in terms of colors than in terms of
+    PSF magnitudes.
 
@@
         Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
-        $g$-band) of synthetic galaxies $log(S/N)$ as measured by \hscpipe{} \cmodel{} photometry. Lines and contours are similar to Fig \ref{fig:star_sn}
+        $g$-band) of synthetic galaxies $\log (\mathrm{S}/\mathrm{N})$ as measured 
+        by \hscpipe{} \cmodel{} photometry. 
+        Lines and contours are similar to Fig \ref{fig:star_sn}
         }
@@
     \caption{
-        Accuracies of the \texttt{hscpipe} \cmodel{} photometry for synthetic
+        Accuracies of the \hscpipe{} \cmodel{} photometry for synthetic
         galaxies measured by the difference between input and output \forced{}
@@
         The magnitude differences between the \unforced{} and \forced{}
-        \cmodel{} photometry for synthetic galaxies in $g$- (\textbf{left} and
-        $y$-band (\textbf{right}).
-        The lines and contours legend is identical to the plots in Fig \ref{fig:psf_diff}.
+        \cmodel{} photometry for synthetic galaxies in $g$ (\textbf{left}) and
+        $y$ band (\textbf{right}).
+        The lines and contours legend is identical to the plots in Fig 
+        \ref{fig:psf_diff}.
         }
@@
     version of the SDSS \cmodel{} photometry.
-    For more details, please see Bosch\etal (in prep.).
-    In short, \cmodel{} tries fits object using both a de~Vaucouleurs and an exponential profile.
-The \cmodel{} algorithm then fits a linear combination of these two best fit models.
-Despite the limitations of the \cmodel{} method (e.g., sensitivity to the background
-    subtraction and to deblending failures), it can deliver robust PSF-corrected fluxes and
-    colors for galaxies.
-
-    We randomly inject ${\sim}40,000$ synthetic galaxies into each
-    \tract{}; and, using an approach similar to that for synthetic stars, we select 
+    For details about the \cmodel{} algorithm, please see description in Section 
+    \ref{ssec:hscpipe} and Bosch\etal (in prep.).
+    Despite the limitations of the \cmodel{} method (e.g., sensitivity to the 
+    background subtraction and to deblending failures), it can deliver robust 
+    PSF-corrected fluxes and colors for galaxies.
+
+    Typical \tract{} in the Wide layer contains ${\sim}400000$ extended objects with 
+    $i_{\mathrm{CModel}} < 25.5$ mag. 
+        We randomly inject ${\sim}40,000$ synthetic galaxies into each \tract{}.
+
+    so we inject additional ${\sim}10$\% extended 
+    objects to the images. 
+    Using an approach similar to that for synthetic stars, we select 
     galaxy samples for photometric comparisons. Synthetic galaxies that are located within 2 pixels 

### 2017-04-28 draft/ms_v5.tex
cModel S/N

@@
         by \hscpipe{} \cmodel{} photometry. 
-        Lines and contours are similar to Fig \ref{fig:star_sn}
+        Lines and contours are similar to Fig \ref{fig:star_sn}.
+        The truncation in $i$ band input magnitude is caused by the magnitude limit 
+        of COSMOS galaxies used in this test. 
         }
@@
     \begin{center}
-        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_color}
+        \includegraphics[width=15cm]{fig/synpipe_galaxy_color}
     \end{center}
@@
         colors separately.
-        The \textbf{left} column shows the relation between input magnitude (x-axis) and
+        The \textbf{left} column shows the relation between input magnitude (x--axis) and
         the color difference, and the \textbf{right} column uses the input colors as
@@
     $i_{\mathrm{CModel}} < 25.5$ mag. 
-        We randomly inject ${\sim}40,000$ synthetic galaxies into each \tract{}.
-
-    so we inject additional ${\sim}10$\% extended 
-    objects to the images. 
-    Using an approach similar to that for synthetic stars, we select 
-    galaxy samples for photometric comparisons. Synthetic galaxies that are located within 2 pixels 
-    of the centroids of real objects are removed from the sample  (these represent ${\sim}3$--$7$\% of the input sample).
-After imposing quality cuts on the  recovered synthetic galaxy sample (see Appendix \ref{app:qc} for details), we have ${\sim}30,000$
-    galaxies in each \tract{}.
-
-    We find that \hscpipe{} mis-classifies less than $1$\% of these objects as point sources
-    in the good-seeing \tract{}.
+    We randomly inject ${\sim}40,000$ synthetic galaxies (additional ${\sim}10$\%) 
+    into each \tract{}, and will not create over-crowded situation.
+    Using similar approach for synthetic stars, we select galaxy samples for 
+    photometric comparisons. 
+    Synthetic galaxies that are located within 2 pixels of the centroids of real 
+    objects are removed from the sample (they represent ${\sim}3$--$7$\% of the 
+    input sample). 
+    After imposing quality cuts on the recovered synthetic galaxy sample 
+    (see Appendix \ref{app:qc} for details), we have ${\sim}30,000$ galaxies in 
+    each \tract{}.
+
+    We find that \hscpipe{} mis-classifies lower than $1$\% of these objects as 
+    point sources in the good-seeing \tract{}.
     But the fraction of misclassified galaxies increases to $4$\% in the
-    bad-seeing \tract{}. We will discuss star/galaxy separation further in Section \ref{ssec:sg}.
-
-    We define a sample of highly blended galaxies  by imposing the cut $b>0.05$.
+    bad-seeing \tract{}. 
+    We will discuss star/galaxy separation further in Section \ref{ssec:sg}.
+
+    We define a sample of highly blended galaxies by imposing the cut 
+    $b>0.05$\footnote{We already removed the ambiguously blended objects. 
+    These objects have high blendedness, but are still distinctive.}.
     Due to the extended nature of galaxies, the $b$ distribution of synthetic 
-    galaxies is more skewed toward high values (especially for the bad-seeing \tract{}) compared to the b distribution of stars.
+    galaxies is more skewed toward high values (especially for the \texttt{badSeeing}
+    \tract{}) compared to the b distribution of stars.
     About $7$--$9$\% of synthetic galaxies are highly blended with $b>0.05$.
-    The fraction is only slightly higher in the bad-seeing \tract{}, and the
-    $g$-band has the highest fraction of highly blended galaxies \alexie{I don't understand here.
-Is this just a question of seeing?
-Is thid because the g-band has worse seeing.
-It seems in contradiction with the previous phrase.}.
-In our plots, we will highlight highly blended galaxies and we will discuss blending effects further in Section \ref{ssec:blendedness}.
+    The fraction is slightly higher in the \texttt{badSeeing} \tract{}, and 
+    therefore the $g$ band also has higher fraction of highly blended galaxies.
+    In our plots, we will highlight highly blended galaxies and will discuss 
+    blending effects further in Section \ref{ssec:blendedness}.
 
@@
 
-    Figure \ref{fig:cmodel_sn} shows the relation between the input
-    magnitudes and the \s2n{} of synthetic galaxies.
-The  \s2n{} is the ratio  of the \cmodel{} flux and its uncertainty.
-The \s2n{} used here is the average one for extended object.
-\alexie{What do you mean here?
-You have a clound of points for each object, not a mean value of SN per mag bin.
-Needs to be calrified.}
-
- Figure  \ref{fig:cmodel_sn} shows  that the \cmodel{} photometry displays a well-behaved relation between input magnitude and output \s2n{}.
+    Figure \ref{fig:cmodel_sn} shows the relation between the input magnitudes and the 
+    \s2n{} of synthetic galaxies.  
+    The \s2n{} is the ratio  of the \cmodel{} flux and the flux error measured by 
+    \hscpipe{}.
+    Here the adopted \s2n{} corresponds to the average \s2n{} over entire footprint. 
+    The center of the galaxy typically has high \s2n{} than this value.
+
+    Figure \ref{fig:cmodel_sn} shows that the \cmodel{} photometry displays a 
+    well-behaved relation between input magnitude and output \s2n{}.  
     Compared to stars, the \s2n{} from \cmodel{} for synthetic galaxies shows a larger
     scatter at fixed input magnitude. 
-This is likely due to the fact that galaxies have a wider range in sizes and shapes than point sources.
+    This is likely due to the fact that galaxies have a wider range in sizes and shapes 
+    than point sources.  
     In $i$ band, a typical $25.2$ mag galaxy has \s2n{}${\sim}20$ from \cmodel{}, but 
-    there are also galaxies at the same magnitude which have \s2n{} below 5. The HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag but the 
+    there are also galaxies at the same magnitude which have \s2n{} below 5. 
+    The HSC Wide layer can detect galaxies as faint as $i{\sim}26.0$ mag but the 
     sample becomes incomplete at these faint magnitudes.
-    It also introduces a selection bias if galaxies with certain structural properties  (e.g., more extended and lower surface brightness)
-    are harder to detect than others.
+    This also introduces a selection bias if galaxies with certain structural 
+    properties (e.g., more extended and lower surface brightness) are harder to detect
+    than others.
     HSC survey data users who want to select flux-limited galaxy samples,
     or who intend to study the population of faint (e.g., high-$z$) galaxies should
-    keep this in mind.  Finally, we also find that  a worse seeing leads to a lower \s2n{} at fixed magnitude 
-    (see Fig \ref{fig:psf_s2n} for $i$-band).
+    keep this in mind.  
+    Finally, we also find that a worse seeing leads to a lower \s2n{} at fixed 
+    magnitude (see Fig \ref{fig:psf_s2n} for $i$-band).
 

### 2017-04-28 draft/ms_v5.tex
CModel magnitude

@@
 %% ------------------------------------------------------------------------------------ %%
-\subsubsection{Accuracy of the \cmodel{} magnitude}
-
-    Fig \ref{fig:cmodel_mag} shows the photometric uncertainties of the
-    \cmodel{} magnitudes in each band using the same format as Fig \ref{fig:psf_mag}.
+\subsubsection{Precision and Accuracy of the \cmodel{} magnitude}
+
+    Fig \ref{fig:cmodel_mag} shows the precision and accuracy of \cmodel{} magnitude 
+    in each band using the same format as Fig \ref{fig:psf_mag}.
 
@@
     $i_{\mathrm{Input}}=25.2$ mag.
-    Compared to the PSF photometry for stars, the uncertainties of \cmodel{} show larger 
-    scatter for galaxies, which is expected given the diversity of galaxy shapes and sizes which adds complexity to the model-fitting process.
-    At the same time, Figure \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in \hscpipe{} provides unbiased and consistent 
-    photometry for galaxies across different bands and seeing conditions.
-
-The typical $i$-band flux accuracy for \forced{} \cmodel{} is ${\sim}7-9$\% in the good-seeing \tract{} at $i_{\mathrm{Input}}<24.0$ mag.
-This moderately degrades to ${\sim}11$\% at $25.0$ mag.
-The performance is similar in the $i$-band bad-seeing \tract{}.
-At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the median magnitude offset
-    between output and input values changes from \plus{}$0.041$ mag to
-    \minus{}$0.005$ mag, which suggests that \forced{} \cmodel{} photometry is
-    unbiased down to the very faint end.
+    Compared to the PSF photometry for stars, the statistical uncertainties of \cmodel{} 
+    magnitudes are larger for galaxies, which is expected given the diversity of galaxy 
+    shapes and sizes that adds complexity to the model-fitting process.
+    At the same time, Figure \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in
+    \hscpipe{} provides unbiased and consistent photometry for galaxies across 
+    different bands and seeing conditions.
+
+    The typical precision of $i$-band flux using \forced{} \cmodel{} is at 
+    ${\sim}7-9$\% level in the \texttt{goodSeeing} \tract{} at 
+    $i_{\mathrm{Input}}<24.0$ mag. 
+    It moderately degrades to ${\sim}11$\% at $25.0$ mag. 
+    The performance is similar in $i$ band for the \texttt{badSeeing} \tract{}. 
+    At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the accuracies of \forced{} \cmodel{}
+    magnitudes change from \plus{}$0.041$ mag to \minus{}$0.005$ mag, which suggest
+    that \forced{} \cmodel{} photometry is unbiased down to the very faint end.
 
@@
     larger than the flux errors from \hscpipe{}, which does not take into account the 
-    systematic uncertainties involved in the modeling fitting process. Even though our synthetic galaxy sample is  comprised of objects with simple single-\ser{} models, 
-    \cmodel{} algorithm can only approximate them to a certain accuracy because of the background noise, deblending uncertainties, and priors imposed on model parameters.
-Given that real galaxies are more complex in structure, the uncertainties derived from our \synpipe{} tests should be treated as lower limits.
-
-\alexie{What does this say about the values of SN from CMODEL then? If the unceratinties are underestimated, then the SN is overestimated? By how much? WOrth commenting on here?}
-
-%% ------------------------------------------------------------------------------------ %%
-
-    The accuracy of \forced{} \cmodel{} photometry is consistent across all filters.
-    For the$g$, $r$, and $z$ bands, the photometric uncertainties are very similar to
+    systematic uncertainties involved in the modeling fitting process. 
+    Even though our synthetic galaxy sample is comprised of objects with simple 
+    single-\ser{} models, \cmodel{} algorithm can only approximate them to a certain 
+    accuracy because of the background noise, deblending uncertainties, and priors 
+    imposed on model parameters. 
+    Given that real galaxies are more complex in structure, our quoted uncertainties 
+    should be treated as lower limits.
+
+%% ------------------------------------------------------------------------------------ %%
+
+    The precision of \forced{} \cmodel{} photometry is consistent across all filters.
+    For the $g$, $r$, and $z$ bands, the statistical uncertainties are very similar to
     $i$-band results between $20.0$ and $25.0$ mag.
@@
     across the entire input magnitude range.
-    The uncertainties for the $y$ band are slightly worse, ranging from 9\% to 17\% in the
+    The precision for the $y$ band is slightly worse, ranging from 9\% to 17\% in the
     same magnitude bins.
     In addition, the \forced{} \cmodel{} tends to overestimate the total flux in 
-    the $y$ band at $>24.0$ mag. This bias in the $y$ band flux is equal to  \minus{}0.06 at $24.0$ mag to \minus{}0.22
-    mag at 25.0 mag. Worse seeing conditions and a  higher background noise level mean that it is more
+    the $y$ band at $>24.0$ mag. 
+    This bias in the $y$ band flux is equal to \minus{}0.06 at $24.0$ mag to 
+    \minus{}0.22 mag at 25.0 mag. 
+    Worse seeing conditions and a higher background noise level mean that it is more
     difficult to detect faint objects in the $y$ band.
@@
 
-Our synthetic galaxy sample is dominated by faint galaxies.
-Hence, we have poor statistics for bright galaxies.
-However, we do find that at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry starts to systematically underestimate total fluxes.
+    Our synthetic galaxy sample is dominated by faint galaxies 
+    ($i_{\mathrm{Input}} > 24.0$ mag) that are crucial to key scientific goals of the 
+    HSC survey.
+    But it also means poor statistics for bright galaxies. 
+    We do find that at $i_{\mathrm{Input}}<20.0$, the \forced{} \cmodel{} photometry 
+    starts to systematically underestimate total fluxes. 
     Based on external comparisons, the behavior of \cmodel{} for bright galaxies may 
-    depend on galaxy types (e.g., \citealt{HSCDR1}).  Also, at bright magnitudes, another known issue is that the current \hscpipe{} (e.g., \hscpipe{} over-deblends around bright 
-    objects.
-Inappropriately weight priors in \cmodel{}) may also lead to poorer photometric quality for bright galaxies.
-Finally, at the imaging depth of HSC ($>29.0$\sb{} in the Wide Layer $i$ band),  \cmodel{} may simply not be a good choice for modeling bright
-    galaxies (e.g., for massive elliptical galaxies; see Huang\etal in prep.~for 
-    more details).
-
-We also find that highly blended galaxies tend to have systematically underestimated total 
-    fluxes (with an average offset ${\sim}0.1$ mag) and larger photometric uncertainties in all five bands. However,  the contrast between relatively isolated and highly blended galaxies
-    in photometric performance is not as stark as for synthetic
-    stars (Fig \ref{fig:psf_mag}).
+    depend on galaxy types (e.g., \citealt{HSCDR1}).  
+    Also, at bright end, another known issue is that the current \hscpipe{}
+    over-deblends around bright objects. 
+    Inappropriately weight priors in \cmodel{} also leads to poorer photometric 
+    quality for bright galaxies.  
+    Finally, at the imaging depth of HSC ($>29.0$\sb{} in the Wide Layer $i$ band),  
+    \cmodel{} may simply not be a good choice for modeling bright galaxies 
+    (e.g., massive elliptical galaxies; see Huang\etal in prep.~for more details).
+
+    We also find that highly blended galaxies tend to have systematically 
+    underestimated total fluxes (with an average offset ${\sim}0.1$ mag) and 
+    higher statistical uncertainties in all five bands. 
+    However, the contrast between relatively isolated and highly blended galaxies
+    in photometric performance is not as stark as for synthetic stars 
+    (Fig \ref{fig:psf_mag}).
 
     We also test the \unforced{} \cmodel{} photometry in all five bands, and the
-    results suggest similar accuracies.
-
-    Fig \ref{fig:cmodel_diff} compared the difference between  \forced{} and \unforced{} \cmodel{} in $g$ and $y$.
-We find that  \forced{} and \unforced{} \cmodel{} shows similar trends.
-The main  noticeable trend is that galaxies brighter than $24.0$ mag in $g$ band, have systematically brighter \forced{} \cmodel{} magnitudes.
-This suggests that the \forced{} \cmodel{} is more accurate in the $g$ band.
+    results suggest similar precision.
+    Fig \ref{fig:cmodel_diff} compares the difference between \forced{} and \unforced{} 
+    \cmodel{} in $g$ and $y$ bands.  
+    The main noticeable trend is that galaxies brighter than $24.0$ mag in the $g$ band 
+    have systematically brighter \forced{} \cmodel{} magnitudes, which suggests that 
+    the \forced{} \cmodel{} is more accurate in the $g$ band as the model parameters 
+    are determined using band with higher \s2n{}.
 

### 2017-04-28 draft/ms_v5.tex
CModel colors

@@
     Wide layer.
+    The slopes and scatters of these relations are very similar to the ones using 
+    real stars on these two \tracts{}.
 
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsubsection{Accuracy of the \cmodel{} color}
-
-    Consistent and accurate five-band \cmodel{} colors from \hscpipe{} are crucial  for photometric redshift and spectral energy distribution (SED) estimates.
-They are also key, for example, to the selection of high-$z$ Lyman-break galaxies (LBG) .
-
-    Fig \ref{fig:cmodel_color} evaluates the  accuracy of \forced{} $(g-i)$ and $(i-y)$ \cmodel{} colors using the same format as Figure Fig \ref{fig:psf_color}.
+\subsubsection{Precision and Accuracy of the \cmodel{} color}
+
+    Precise and unbiased five-band \cmodel{} colors from \hscpipe{} are crucial for
+    photometric redshift estimates and spectral energy distribution (SED) fitting 
+    results. 
+    They are also key, for example, to the selection of high-$z$ Lyman-break 
+    galaxies (LBG).
+
+    Fig \ref{fig:cmodel_color} evaluates the precision and accuracy of \forced{} 
+    $(g-i)$ and $(i-y)$ \cmodel{} colors using the same format as 
+    Fig \ref{fig:psf_color}. 
     We find that \hscpipe{} provides reliable \cmodel{} colors for synthetic 
     galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
-    For $(g-i)$ colors, the average uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ mag
-    is ${\sim}0.04$ mag.
-    The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
+    For $(g-i)$ colors, the statistical uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ 
+    mag is ${\sim}0.04$ mag.
+    The statistical uncertainty increases to ${\sim}0.11$ mag at 
+    $i_{\mathrm{Input}}{\sim}25.0$ mag.
     The $(i-y)$ colors show similar results.
@@
     is slightly overestimated.
-    As mentioned above, this is not surprising given the shallower $y$ band imaging depth.
-Highly blended galaxies have larger uncertainties in their colors compared to isolated galaxies.
+    As mentioned above, this is not surprising given the shallower $y$ band 
+    imaging depth. 
+    Highly blended galaxies are less precise in their \forced{} \cmodel{} colors 
+    compared to isolated galaxies.  
     Highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
@@
 
-Figure  \ref{fig:cmodel_cdist} compare the input color--color distributions with the recovered color distributions.
-The general 2--D distributions are well recovered but the accuracy is not as good as for stars, especially in the $(i-z)$ vs.
-$(z-y)$ plane.
-    This is expected given the narrow dynamical ranges of these colors in the redder filters.
+    Fig \ref{fig:cmodel_cdist} compare the input color--color distributions with the
+    recovered ones. 
+    The general 2--D distributions are well recovered but the precision is not as 
+    good as for stars, especially in the $(i-z)$ vs. $(z-y)$ plane.
+    This is expected given the narrow dynamical ranges of these colors in the redder 
+    filters.
     The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
@@
     We note that our synthetic galaxies do not have color gradients.  
-In reality, color gradients will complicate the situation and hence the uncertainties shown here should be considered as lower limits.
+    In reality, color gradients will complicate the situation and hence the statistical 
+    uncertainties shown here should be considered as lower limits.
 

### 2017-04-28 draft/ms_v5.tex
Other performances

@@
 %% ------------------------------------------------------------------------------------ %%
+\subsection{Limitations and Caveats}
+    \label{ssec:caveats}
+
+    %% Caveats
+    The limitations of the current \synpipe{} include the following:
+
+    \begin{enumerate}
+
+        \item \citet{HSCDR1} points out that \hscpipe{} tends to over-subtract the
+            background around bright objects.
+            Unfortunately, \synpipe{} now takes the original background subtraction on
+            the single-\visit{} image for granted; hence, it lacks the capability to
+            test or help improve this problem.
+
+        \item  \synpipe{} simply adopts the PSF measured by \hscpipe{} and
+            uses it as a model of point source and PSF convolution for a galaxy.
+            Hence, it cannot be used to test how the uncertainty of the PSF modeling
+            affects the photometry and shape measurements.
+            This could be important for regions with exquisite seeing 
+            (e.g. FWHM${\sim}0.4$\asec{}) that makes the
+            PSF modeling difficult, and for accurate WL measurements 
+            (see \citealt{HSCDR1}).
+
+        \item \synpipe{} works in a ``unit'' of \visit{} for a single-exposure
+            test, and uses a \tract{} to test \coadd{} images.
+            In the case of tests that focus on specific regions that are much smaller 
+            than the size of a \visit{} or a \tract{} (e.g., quality of photometry
+            around rich galaxy clusters), using \synpipe{} often leads to
+            low efficiency.
+
+    \end{enumerate}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
 %% Fig: Star Sample
@@
     in the $g$- and $i$-bands. 
-    This Figure shows the expected \s2n{} of stars as a function of magnitude in the 
+    This figure shows the expected \s2n{} of stars as a function of magnitude in the 
     Wide layer.
@@
 
-    Figure \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
+    Fig \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
     sources at fixed input magnitude.
@@
 
-    Figure \ref{fig:psf_mag} also shows that the precision of the PSF photometry is 
+    Fig \ref{fig:psf_mag} also shows that the precision of the PSF photometry is 
     not filter dependent. 
@@
 
-	However, Figure \ref{fig:psf_mag} also shows that blending has a strong impact on 
+	However, Fig \ref{fig:psf_mag} also shows that blending has a strong impact on 
 	photometry.  
@@
 	the band with higher \s2n{}}. 
-	Figure \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} 
+	Fig \ref{fig:psf_diff} shows the difference between \forced{} and \unforced{} 
 	PSF photometry for the $g$ and the $y$ band. 
@@
     colors. 
-    Figure \ref{fig:psf_color} shows that \hscpipe{} provides precise and accurate PSF 
+    Fig \ref{fig:psf_color} shows that \hscpipe{} provides precise and accurate PSF 
     colors for synthetic stars with realistic color distributions down to very 
@@
 
-    Figure \ref{fig:psf_color} shows that the precision of PSF colors do not depend 
+    Fig \ref{fig:psf_color} shows that the precision of PSF colors do not depend 
     the seeing conditions. 
@@
 
-    Figure \ref{fig:psf_cdist} displays the precision of PSF colors by comparing the 
+    Fig \ref{fig:psf_cdist} displays the precision of PSF colors by comparing the 
     color distributions of the input sample to the recovered color distributions. 
@@
 
-    Figure \ref{fig:cmodel_sn} shows the relation between the input magnitudes and the 
+    Fig \ref{fig:cmodel_sn} shows the relation between the input magnitudes and the 
     \s2n{} of synthetic galaxies.  
@@
 
-    Figure \ref{fig:cmodel_sn} shows that the \cmodel{} photometry displays a 
+    Fig \ref{fig:cmodel_sn} shows that the \cmodel{} photometry displays a 
     well-behaved relation between input magnitude and output \s2n{}.  
@@
     shapes and sizes that adds complexity to the model-fitting process.
-    At the same time, Figure \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in
+    At the same time, Fig \ref{fig:cmodel_mag} shows that the \cmodel{} algorithm in
     \hscpipe{} provides unbiased and consistent photometry for galaxies across 
@@
         (\textbf{right}). 
-We show the differences between the input R.A and Dec and the coordinates measured on the \coadd{} images.
-Hexagonal bins (filled histogram) and contours (solid-line histogram) are for synthetic objects from \tracts{} with good and bad seeing conditions,
+        We show the differences between the input R.A and Dec and the coordinates 
+        measured on the \coadd{} images. 
+        Hexagonal bins (filled histogram) and contours (solid-line histogram) are 
+        for synthetic objects from \tracts{} with good and bad seeing conditions, 
         respectively.
-        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines. \alexie{Need one phrase here. Always give the take home message in the caption. We find that xxxxxx .}
+        $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.     
+        \song{We find that xxxxxx}.
         }
@@
     \caption{Evaluation of the \hscpipe{} star--galaxy separation scheme. 
-Star--galaxy separation is based on the the magnitude difference between the PSF and \cmodel{} photometry.
+        Star--galaxy separation is based on the the magnitude difference between the 
+        PSF and \cmodel{} photometry. 
         The plot on the \textbf{left} (a) corresponds to synthetic stars. 
@@
         objects in \tracts{} with bad and good seeing conditions, respectively.
-        The plot on the \textbf{right} (b) corresponds to synthetic 
-        galaxies.
+        The plot on the \textbf{right} (b) corresponds to synthetic galaxies.
         Hexagonal bins (filled histogram) and contours (solid-line histogram)
-        are for galaxies from good- and bad-seeing \tracts{}, respectively.
-        The scatter plot and dashed-line histogram highlight synthetic galaxies that are
-        misclassified as point sources.}
+        are for galaxies from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{},
+        respectively.
+        The scatter plot and dashed-line histogram highlight synthetic galaxies that 
+        are misclassified as point sources.}
     \label{fig:sg}
@@
     \caption{
-        Relation between the $\log(\mathrm{Blendedness})$ parameter
+        Relation between the $\log_{10} (\mathrm{Blendedness})$ parameter
         and the photometric accuracy f synthetic stars (\textbf{upper row}, a and 
@@
         $(g-i)$ colors.
-        Hexagonal bins and contours show results for good- and bad-seeing
-        \tracts{}, respectively.
-        $\log(\mathrm{Blendedness}) = -1.0$ is marked using a vertical dashed line.
+        Hexagonal bins and contours show results for \texttt{goodSeeing} and
+        \texttt{badSeeing} \tracts{}, respectively.
+        $\log_{10} (\mathrm{Blendedness}) = -1.0$ is marked using a vertical dashed 
+        line.
         }
@@
         galaxies using \cmodel{} photometry.
-        The \textbf{left} (a) plot shows the relation between the input $(b/a)$ and the
-        uncertainty in $(b/a)$.
-        The \textbf{right} (b) plot shows the relation between input magnitude and the undertainty in $(b/a)$.
-        Contours are for the default test with \texttt{usePixelWeights=False}, and hexagonal bins correspond to \texttt{usePixelWeights=True}.
+        The \textbf{left} (a) plot shows the relation between the input $(b/a)$ and 
+        the uncertainty in $(b/a)$.
+        The \textbf{right} (b) plot shows the relation between input magnitude and 
+        the undertainty in $(b/a)$.
+        Contours are for the default test with \texttt{usePixelWeights=False}, and 
+        hexagonal bins correspond to \texttt{usePixelWeights=True}.
         }
@@
 
-\section{Other Performace Tests}
+\section{Other Performance Tests}
     \label{sec:others}
 
-    In this section, we turn our attention to astrometric calibration, star-galaxy separation, blending effects, and galaxy shape measurements.
-
-    %to demonstrate the range of topics \synpipe{}
-    %can test.
+    In this section, we turn our attention to astrometric calibration, star-galaxy 
+    separation, blending effects, and galaxy shape measurements.
 
@@
 
-    We inject synthetic objects into single-\visit{} images using the initial (and less accurate) astrometric calibration.
+    We inject synthetic objects into single-\visit{} images using the initial (and 
+    less accurate) astrometric calibration.
     During the image stacking step, the joint calibration process improves the
@@
     Therefore, differences between the input and output coordinates from \synpipe{}
-    can help us understand systematic effects related to the image stacking step.
-\alexie{Not clear what we are testing here exactly?
-Is this an absolute astrometric calibratio for HSC....?
-Or is this showing how much change there is in the refined astrometric solution??}
-
-    Fig \ref{fig:astrometry} shows the distribution of astrometric offsets for synthetic stars and galaxies in good- and bad-seeing \tracts{}.
+    can help us understand how much has the joint calibration step changes the 
+    astrometric calibration.
+
+    Fig \ref{fig:astrometry} shows the distribution of astrometric offsets for 
+    synthetic stars and galaxies in \texttt{goodSeeing} and \texttt{badSeeing} 
+    \tracts{}.
     We find small systematic offsets at the ${\sim}10$--20 mas level.
     The two \tracts{} show different systematic offsets.
-    In the same \tracts{}, synthetic stars and galaxies show similar offsets, but the scatter for galaxies is slightly larger than stars due to their extended nature.
-\alexie{Need a final take home message here.
-What have we learned?}
+    In the same \tracts{}, synthetic stars and galaxies show similar offsets, but 
+    the scatter for galaxies is slightly larger than stars due to their extended 
+    nature.
 
@@
 
-    Star--galaxy separation becomes increasingly difficult at faint magnitudes ($i<24.0$ mag).
+    Star--galaxy separation becomes increasingly difficult at faint magnitudes 
+    ($i<24.0$ mag).
     In \hscpipe{}, the star--galaxy classification primarily depends on the 
@@
 
-    Fig \ref{fig:sg} shows the current status of our star--galaxy classification scheme.  Figure  \ref{fig:sg} shows the difference between PSF and \cmodel{}
-    magnitudes as a function of  input magnitude.
-We find that $20$\% of synthetic stars at $i_{\mathrm{Input}}>23.0$ mag are misclassified as extended objects, while only a tiny fraction of faint synthetic galaxies ($i_{\mathrm{Input}}>24.0$) are
-    misclassified as stars. This confirms that the current star--galaxy classification strategy in \hscpipe{}
-    results in a galaxy sample with \textbf{high completeness} and at star sample
+    Fig \ref{fig:sg} shows the current status of our star--galaxy classification 
+    scheme.  
+    Fig \ref{fig:sg} shows the difference between PSF and \cmodel{} magnitudes as a 
+    function of input magnitude. 
+    We find that $20$\% of synthetic stars at $i_{\mathrm{Input}}>23.0$ mag are 
+    misclassified as extended objects, while only a tiny fraction of faint synthetic 
+    galaxies ($i_{\mathrm{Input}}>24.0$) are misclassified as stars. 
+    This confirms that the current star--galaxy classification strategy in \hscpipe{}
+    results in a galaxy sample with \textbf{high completeness} and a star sample
     with \textbf{high purity}.
 
-    It is also clear that seeing condition strongly modifies the distributions
+    It is also clear that the seeing condition strongly modifies the distributions
     of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$. 
-Worse seeing conditions make star-galaxy separation more challenging.
-The completeness and purity of galaxy and star samples at the faint end will depend on seeing conditions.
-
-    In the next data release, \hscpipe{} will include an improved star--galaxy classifier which will be based on a machine learning method that takes both shape \alexie{size?} and color 
-    information into account.
+    Worse seeing condition makes star-galaxy separation more challenging. 
+    The completeness and purity of galaxy and star samples at the faint end will 
+    depend on seeing conditions.
+
+    In the next data release, \hscpipe{} will include an improved star--galaxy 
+    classifier which will be based on a machine learning method that takes both 
+    size and color information into account.
 
@@
 
- Fig \ref{fig:blend} shows the $b$ parameter versus uncertainties in magnitudes and colors. For both PSF and \cmodel{} magnitude distributions, we can see clear trends that 
+    Fig \ref{fig:blend} shows the $b$ parameter versus the difference between input and
+    output values for both magnitudes and colors. 
+    For both PSF and \cmodel{} magnitude distributions, we can see clear trends that 
     total fluxes are systematically underestimated for highly blended ($b>0.05$ for 
@@
     This effect is particularly strong for stars.
-    As for colors, higher values of $b$ results in higher uncertainties for both
-    stars and galaxies, but the trends are different for each.
-    Highly blended stars have clearly overestimated \alexie{redder? bluer? what does overestimated mean} $(g-i)$ colors. Highly blended galaxies seem to have  $(g-i)$ colors that are bluer than the 
+
+    As for colors, higher values of $b$ results in higher statistical uncertainties 
+    for both stars and galaxies, but the trends are different for each.
+    Highly blended stars have clearly redder $(g-i)$ colors than the input values. 
+    Highly blended galaxies seem to have $(g-i)$ colors that are bluer than the 
     true values.
@@
     released by \hscpipe{}.
-    We therefore caution HSC users to treat the highly blended object with
+    We therefore remind the HSC users to treat the highly blended object with
     greater caution.
@@
 
-    In SDSS,  structural parameters like size and shape from \cmodel{} are often
-    used to study the evolution galaxies.
-    Although the \cmodel{} in \hscpipe{} follows a very similar algorithm, its primary
+    In SDSS, structural parameters like size and shape from \cmodel{} are often used to 
+    study the evolution galaxies.
+    Although the \cmodel{} in \hscpipe{} follows a similar algorithm, its primary
     goal now is to provide accurate and consistent magnitude and color in all five
-    HSC filters for a vast majority of faint, small galaxies.
+    bands for a vast majority of faint, small galaxies.
     To improve the stability of \cmodel{} for these low-\s2n{} and barely resolved
     galaxies, \hscpipe{} uses Bayesian priors on galaxy sizes and axis ratios. 
-However, the current implementation of these priors has a flaw \alexie{Is this just that the prior is wrong?
-Can we just say that the prior is wrong?} that leads to a severe  underesaimte in the sizes and axis ratios of galaxies.
-
-    Figure \ref{fig:galaxy_ba} demonstrates this issue and compares the  input and measured values of the  \cmodel{} axis ratio.
-Here, $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ is a \alexie{the weighted sum?
-The eighted mean?} combination of the
-    axis ratios estimated by the exponential and de Vaucouleurs models weighted by 
-    their flux ratio.
-
-    Using our \synpipe{} tests, we discovered that one issue is related to the  \cmodel{} \texttt{usePixelWeight} configuration. This option which decides whether to
-    use a per-pixel variances as weights in the nonlinear fit. By default, \hscpipe{} chooses \texttt{usePixelWeight}$=$\texttt{False}.
-    As one can see, this leads to a significantly overestimated axis ratio for almost
-    all galaxies with $i_{\mathrm{Input}}>21.5$ mag\footnote{It also leads to an
-    underestimated half-light radius for these galaxies.}.
-    At the same time, we also repeat the \synpipe{} run for galaxies with
+    However, the current implementation of these priors has a serious bug and leads 
+    to severe underestimated sizes and ellipticities of galaxies.
+
+    Fig \ref{fig:galaxy_ba} demonstrates this issue and compares the input and 
+    measured values of the \cmodel{} axis ratio. 
+    Here, $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ is the flux-weighted sum of the
+    axis ratios estimated by exponential and de Vaucouleurs models.
+
+    Using our \synpipe{} tests, we discovered that the bug related to the priors only 
+    presents when \texttt{usePixelWeight} configuration is set to \texttt{False} during 
+    the data reduction. 
+    The parameter controls whether or not the per-pixel variance information is used 
+    during the model fitting process.  
+    As one can see, this leads to significantly overestimated axis ratios for almost
+    all galaxies\footnote{It also leads to underestimated half-light radius for the same
+    galaxies.}.
+    We repeat the \synpipe{} run for galaxies with 
     \texttt{usePixelWeight}$=$\texttt{True}, and this change clearly mitigates
-    the problem. When we use \texttt{usePixelWeight}$=$\texttt{True},
+    the problem. 
+    When we use \texttt{usePixelWeight}$=$\texttt{True},
     $({\mathrm{b}/\mathrm{a}})_{\mathrm{CModel}}$ provides an unbiased axis ratio 
     estimation for galaxies with $i_{\mathrm{Input}}< 24.0$ mag.
-This  is a good example  that  demonstrates how the \synpipe{} framework is a valuable tool  for quality control and that can be used to improve \hscpipe{}.
-
-    For the current HSC data release, we warn users against using the sizes and shapes from \cmodel{} to study the structural properties of galaxies with $i_{\mathrm{Input}}>21.5$.
-
-%    At the same time, \synpipe{} will try to help \hscpipe{} improve the details
-%    of the \cmodel{} so that it can provide more useful structural information 
-%    without hurting its photometric performance.
+    This change is still related to the bug in priors.  
+    The actual effect of using per-pixel variance should be very small.  
+    The next version of \hscpipe{} will fix this bug, and \synpipe{} will help evaluate 
+    the precisions of shape and size measurements. 
+    This is a good example that demonstrates how the \synpipe{} framework is valuable  
+    for quality control and that can be used to improve \hscpipe{}.
+
+    For the current HSC data release, we warn users against using the sizes and shapes 
+    from \cmodel{} to study the structural properties of galaxies.
 
@@
     continues to produce increasingly larger amounts of high-quality imaging data.
-    To help achieve the designed goals of the survey and to facilitate scientific investigations, we have developed \synpipe{}, a flexible framework based on
-    \hscpipe{} and that can be used to perform quality control on the 
-    HSC pipeline outputs. \synpipe{} operates by injecting synthetic stars and galaxies into single-\visit{} images. 
-    These data are then processed by \hscpipe{} to generate a \coadd{} images and to perform photometry measurements.
-With this  approach,  \synpipe{} can be used as an end-to-end and realistic test of the full  data reduction process.
-In this paper, we  use  two \tracts{} in the HSC Wide layer with
-    representative seeing conditions (good and bad \alexie{repeat the numbers here}) to test the general behaviors of HSC
-    photometry for both stars and galaxies.
+    To help achieve the designed goals of the survey and to facilitate scientific 
+    investigations, we have developed \synpipe{}, a flexible framework based on
+    \hscpipe{} and that can be used to perform quality control on the HSC pipeline 
+    outputs. 
+    \synpipe{} operates by injecting synthetic stars and galaxies into single-\visit{}
+    images. 
+    These data are then processed by \hscpipe{} to generate \coadd{} images and to 
+    perform photometric measurements. 
+    With this approach, \synpipe{} can be used as an end-to-end and realistic test of 
+    the full data reduction process. 
+    In this paper, we use two \tracts{} in the HSC Wide layer with representative 
+    seeing conditions (\texttt{goodSeeing} with FWHM$=0.45$\asec{} seeing; 
+    \texttt{badSeeing} with FWHM$=0.70$\asec{} seeing) to test the general behaviors 
+    of HSC photometry for both stars and galaxies.
 
@@
 
-        \item The \forced{} PSF photometry provides excellent \alexie{isn't really a god word. Unbiased? Accurate?} measurements of magnitude and color for isolated stars at $18.0 < i < 25.0$.
-            The typical uncertainty of HSC forced PSF photometry for stars ranges
-            from 0.01 mag at $i{\sim}18.0$ mag to 0.08 mag at $i{\sim}25.0$
-            mag (1\%-7\% accuracy in the $i$-band).
+        \item The \forced{} PSF photometry provides precise and accurate 
+            measurements of magnitude and color for isolated stars at 
+            $18.0 < i < 25.0$.
+            The typical statistical uncertainties of HSC forced PSF photometry for 
+            stars ranges from 0.01 mag at $i{\sim}18.0$ mag to 0.08 mag at 
+            $i{\sim}25.0$ mag (1\%-7\% precision in the $i$-band).
             The \forced{} PSF photometry can accurately recover the color--color
@@
             $20.0 < i < 25.0$ mag.
-            The average accuracy of \forced{} \cmodel{} magnitude ranges from
-            ${\sim}7$\% at $i{\sim}20.0$ mag to ${\sim}10$\% at $i{\sim}25.0$.
-            The \forced{} \cmodel{} colors for galaxies are accurate and unbiased.
-            The accuracy of galaxy colors do not dependence on input magnitude \alexie{What does this mean? They become more inaccurate at fainter magnitue, right? So it does depend on color.} or
-            color.
-
-        \item The \forced{} PSF and \cmodel{} photometry are robust against moderate changes in the seeing conditions, despite the fact that worse seeing leads to a lower
-            $\mathrm{S}/\mathrm{N}$ at fixed input magnitude.
-
-        \item Blending ($b>0.1$) has an impact on the accuracy of both PSF and \cmodel{}
-            photometry, especially for stars.
-            For highly blended stars, the \forced{} PSF photometry overestimates the magnitudes of stars on average by 0.1–-0.2 mag.
+            The statistical uncertainties of \forced{} \cmodel{} magnitude ranges 
+            from ${\sim}7$\% at $i{\sim}20.0$ mag to ${\sim}10$\% at $i{\sim}25.0$.
+            The \forced{} \cmodel{} colors for galaxies are precise and are 
+            consistent across in all five bands.
+            They also do not show biases with input magnitudes and colors.
+
+        \item The \forced{} PSF and \cmodel{} photometry are robust against 
+            moderate changes in the seeing conditions, despite the fact that worse 
+            seeing leads to a lower $\mathrm{S}/\mathrm{N}$ at fixed input magnitude.
+
+        \item Blending ($b>0.05$) has an impact on the accuracy of both PSF and 
+            \cmodel{} photometry, especially for stars.
+            For highly blended stars, the \forced{} PSF photometry overestimates 
+            the magnitudes of stars on average by 0.1–-0.2 mag.
             For galaxies, blending effects typically add an additional 0.05 mag
-            uncertainty in both magnitude and color estimates.
+            statistical uncertainty in both magnitude and color estimates.
+
     \end{enumerate}
@@
     \vspace{0.5cm}
-    \noindent We also high-light several known issues with the  current version of \hscpipe{}:
+    \noindent We also high-light several known issues with the current version 
+    of \hscpipe{}:
 
@@
 
-        \item The performance of the current star--galaxy separation algorithm in \hscpipe{}
-            is not perfect,  and degrades at fainter magnitudes and with poor seeing
-            conditions.
+        \item The performance of the current star--galaxy separation algorithm in 
+            \hscpipe{} is not perfect, and degrades at fainter magnitudes and with 
+            poor seeing conditions.
             The fraction of stars that are misclassified as extended objects is still
-            quite high ($>20$\% at $i> 22.5$ mag).
-
-        \item The nominal \cmodel{} setting  (\texttt{usePixelWeights=True}) results
+            quite high. 
+            $>20$\% of the synthetic stars at $i> 22.5$ mag are misclassified
+            \footnote{Note that this does not mean high fraction of contamination 
+            in the galaxy sample. Please see Bosch\etal (in prep.) for more 
+            details.}
+
+        \item The bug in priors on structural parameters and the 
+            \texttt{usePixelWeights=False} nominal setting in \cmodel{} result in         
             in very biased estimates of the shapes and sizes for galaxies. 
-The axis ratio of a galaxy using \cmodel{} is highly overestimated and the effective radius is typically underestimated.
-Galaxy shapes and sizes can be more well measured with the \texttt{usePixelWeights=True} option.
-            However, that choice may impact the accuracy of the deblender, which we 
-            will test in the future.
+            The axis ratio from \cmodel{} is highly overestimated and the effective 
+            radius is typically underestimated.  
+            This issue hence can also affect the accuracy of star--galaxy 
+            classification.
+
     \end{enumerate}
 
-    The HSC collaboration is working on improving these issues for future versions of \hscpipe{} and for subsequent data releases.
+    The HSC collaboration is working on improving these issues for future versions
+    of \hscpipe{} and for subsequent data releases.
 
@@
     Here we focused on characterizing the photometric performance of \hscpipe{}.  
-However,  \synpipe{} is a flexible tool and is being used for a range of other applications.
-For instance,  Murata\etal (in prep.) use \synpipe{} to characterize the level of blending in the HSC Wide Layer.
-\citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of  M31 HSC to search for microlensing events.
-\synpipe{} is also currently being used to estimate the completeness of  high-$z$ LBG and Lyman- $\alpha$ emitters (Ono\etal in prep.; Konno\etal in prep.),  to check the completeness of  high-$z$ LBG pairs as a function of pair separation (Harikane\etal in prep.), to test the completeness of low surface--brightness dwarf galaxies selections (Greco\etal in prep.),and to test magnifications effects around nearby clusters (Chiu\etal in prep.).
-
-    %% Caveats
-
-    \alexie{The stuff below should not go here. Move it into the bulk of the draft in Section 4}.
-
-    The limitations of the current \synpipe{} include the following:
-
-    \begin{enumerate}
-
-        \item \citet{HSCDR1} points out that \hscpipe{} tends to over-subtract the
-            background around bright objects.
-            Unfortunately, \synpipe{} now takes the original background subtraction on
-            the single-\visit{} image for granted; hence, it lacks the capability to
-            test or help improve this problem.
-
-        \item  \synpipe{} simply adopts the PSF measured by \hscpipe{} and
-            uses it as a model of point source and PSF convolution for a galaxy.
-            Hence, it cannot be used to test how the uncertainty of the PSF modeling
-            affects the photometry and shape measurements.
-            This could be important for regions with exquisite seeing 
-            (e.g. FWHM${\sim}0.4$\asec{}) that makes the
-            PSF modeling difficult, and for accurate WL measurements.
-
-        \item \synpipe{} works in a ``unit'' of \visit{} for a single-exposure
-            test, and uses a \tract{} to test \coadd{} images.
-            In the case of tests that focus on specific regions that are much smaller 
-            than the size of a \visit{} or a \tract{} (e.g., quality of photometry
-            around rich galaxy clusters), using \synpipe{} often leads to
-            low efficiency.
-
-    \end{enumerate}
+    However, \synpipe{} is a flexible tool and is being used for a range of other     
+    applications. 
+    For instance, Murata\etal (in prep.) uses \synpipe{} to characterize the level of
+    blending in the HSC Wide Layer.  
+    \citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of M31 HSC 
+    to search for microlensing events. 
+    \synpipe{} is also currently being used to estimate the completeness of high-$z$ 
+    LBG and Lyman-$\alpha$ emitters (Ono\etal in prep.; Konno\etal in prep.), to 
+    check the completeness of high-$z$ LBG pairs as a function of pair separation 
+    (Harikane\etal in prep.), to test the completeness of low surface--brightness 
+    dwarf galaxies selections (Greco\etal in prep.), and to test magnifications effects
+    around nearby clusters (Chiu\etal in prep.).
 
@@
     the image stacking process. 
-Hence, a future implementation of \synpipe{} will include the option of injecting objects directly into  \coadd{} images which will speed up the generation of synthetic data sets.
-The results shown in this paper demonstrate the  utility of the \synpipe{} framework in order to perform end-to-end quality control on pipeline products to the level of accuracy needed by large panchromatic surveys.
+    Hence, a future implementation of \synpipe{} will include the option of injecting 
+    objects directly onto \coadd{} images which will speed up the generation of 
+    synthetic data sets. 
+    The results shown in this paper demonstrate the utility of the \synpipe{} framework
+    in order to perform end-to-end quality control on pipeline products to the level 
+    of accuracy needed by large panchromatic surveys.
 
@@
     http://dm.lsstcorp.org.
+
+    % Personal fundings
+    This work is in part supported by JSPS KAKENHI (Grant Number 26800093, 15H03654, 
+    and JP17H01131) as well as MEXT Grant-in-Aid for Scientific Research on Innovative 
+    Areas (No. 15H05887, 15H05892, 15H05893, 15K21733).  
+    RM is supported by the US Department of Energy Early Career Award Program.
+    RyM is financially supported by the University of Tokyo-Princeton strategic 
+    partnership grant and Advanced Leading Graduate Course for Photon Science (ALPS).
 
@@
 
-    To select synthetic stars and galaxies from the HSC survey data in order to test the photometry,
-    we apply some basic quality control cuts.
+    To select synthetic stars and galaxies from the HSC survey data in order to test
+    the photometry, we apply some basic quality control cuts.
 
@@
     band
-    ($\mathtt{(\#gri\ \geq\ 4)\ and\ (\#yz\ \geq\ 6)\ and\ (Limiting\ imag> 25.6)}$).
+    ($\mathtt{(\#gri\ \geq\ 4)\ and\ (\#yz\ \geq\ 6)\ and\ (Limiting\ imag> 25.6)}$;
+    see \citealt{HSCDR1} for details).
     Since the two \tracts{} we used in this work are almost entirely covered in
@@
         \item[ ] \texttt{ iflags\_pixel\_clipped\_any==False }
-        \item[ ] \texttt{ iflags\_pixel\_bright\_object\_center ==False }
+        \item[ ] \texttt{ iflags\_pixel\_bright\_object\_center==False }
 

### 2017-04-28 draft/ms_v5.tex
Almost ready

@@
 
+	The precisions and accuracies of \forced{} PSF magnitudes shown here are 
+	summarized in Table \ref{tab:mag}
+
 %% ------------------------------------------------------------------------------------ %%
@@
     PSF magnitudes.
+
+	The statistical uncertainties of \forced{} PSF colors are summarized in 
+	Table \ref{tab:color}
 
@@
 
-% ALEXIE: not necessary
-    %The majority of the galaxies in our synthetic galaxy samples are  are faint
-    %($i_{\mathrm{Input}} > 24.0$ mag) and small ($R_{\mathrm{e}} < 0.5$\asec).
-    %It is very challenging to obtain accurate photometry good photometric quality of these galaxies, which 
-    %is crucial to key scientific goals of the HSC survey.
-    %The selected samples do not provide enough bright or large galaxies to test.
-    %Therefore, we will supplement results for these galaxies using better samples
-    %in the future.
-
 %% ------------------------------------------------------------------------------------ %%
@@
 
+	The precisions and accuracies of \forced{} \cmodel{} magnitudes shown here are 
+	summarized in Table \ref{tab:mag}
+
 %% ------------------------------------------------------------------------------------ %%
@@
     uncertainties shown here should be considered as lower limits.
+
+	The statistical uncertainties of \forced{} \cmodel{} colors are summarized in 
+	Table \ref{tab:color}
 
@@
         $\Delta\mathrm{R.A}=0$ and $\Delta\mathrm{Dec}=0$ are marked by dashed lines.     
-        \song{We find that xxxxxx}.
+        It shows that the initial astrometric calibration is already very accurate,  
+        and it also suggests that \hscpipe{} can find the centroids of stars and 
+        galaxies with precisions that are consistent with the astrometric calibration
+        uncertainty under moderately different seeing conditions.
         }
@@
     can help us understand how much has the joint calibration step changes the 
-    astrometric calibration.
+    astrometric calibration, and how well can \hscpipe{} measure the central 
+    coordinates of stars and galaxies.
 
@@
     \tracts{}.
-    We find small systematic offsets at the ${\sim}10$--20 mas level.
-    The two \tracts{} show different systematic offsets.
-    In the same \tracts{}, synthetic stars and galaxies show similar offsets, but 
-    the scatter for galaxies is slightly larger than stars due to their extended 
-    nature.
+    We find small systematic offsets at the ${\sim}10$--20 mas level, which is similar 
+    to the uncertainties of astrometric calibration quoted in \citet{HSCDR1}.
+    The two \tracts{} show different systematic offsets, while the synthetic stars and
+    galaxies show coherent offsets in the same \tract{}.
+    This shows that the initial astrometric calibration of HSC has very reasonable 
+    accuracy.  
+    It also suggests that \hscpipe{} can find the centroids of stars and galaxies 
+    with precisions that are consistent with the astrometric calibration uncertainty
+    under moderately different seeing conditions.
 

### 2017-04-28 draft/ms_v5.tex
Placeholder for tables

@@
         Hexagonal binned density plots and contours show the distributions for
-        stars in both the good- and bad-seeing \tracts{}. 
+        stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
         Highly blended stars are highlighted using scatter plots.
@@
         Hexagonal binned density plots and contours are for the synthetic galaxies 
-        from good and bad seeing \tracts{}.
+        from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.
         Highly blended objects are highlighted using scattered points.
@@
         The right panel in each plot shows the distributions of the magnitude 
-        differences for objects in good (filled) and bad (solid line) seeing \tracts{}.
+        differences for objects in \texttt{goodSeeing} (filled) and \texttt{badSeeing}
+        (solid line) \tracts{}.
         The dashed lines identify the distribution of highly blended objects.
@@
     according to this criterion).
-    The fraction of highly blended stars slightly increases in the bad seeing \tract{}. 
+    The fraction of highly blended stars slightly increases in the \texttt{badSeeing} 
+    \tract{}. 
     The impact of blendedness will be discussed more in Section \ref{ssec:blendedness}.
@@
     sources at fixed input magnitude.
-    In $i$-band, the bad-seeing (0.7\asec{}) \tract{} shows systematically
-    lower \s2n{} than the good-seeing (0.5\asec{}) \tract{}.
+    In $i$-band, the \texttt{badSeeing} (0.70\asec{}) \tract{} shows systematically
+    lower \s2n{} than the \texttt{goodSeeing} (0.45\asec{}) \tract{}.
     The \s2n{} is similar for the two $g$-band \tracts{} because they share similar 
@@
 	The precisions and accuracies of \forced{} PSF magnitudes shown here are 
-	summarized in Table \ref{tab:mag}
+	summarized in Table \ref{tab:psfmag}
 
@@
 	The statistical uncertainties of \forced{} PSF colors are summarized in 
-	Table \ref{tab:color}
+	Table \ref{tab:psfcolor}
 
@@
     We find that \hscpipe{} mis-classifies lower than $1$\% of these objects as 
-    point sources in the good-seeing \tract{}.
+    point sources in the \texttt{goodSeeing} \tract{}.
     But the fraction of misclassified galaxies increases to $4$\% in the
-    bad-seeing \tract{}. 
+    \texttt{goodSeeing} \tract{}. 
     We will discuss star/galaxy separation further in Section \ref{ssec:sg}.
@@
 	The precisions and accuracies of \forced{} \cmodel{} magnitudes shown here are 
-	summarized in Table \ref{tab:mag}
+	summarized in Table \ref{tab:cmodelmag}
 
@@
 	The statistical uncertainties of \forced{} \cmodel{} colors are summarized in 
-	Table \ref{tab:color}
+	Table \ref{tab:cmodelcolor}
 
@@
         Hexagonal bins and filled histogram show distributions of correctly classified
-        synthetic stars in the good-seeing \tract{}.
+        synthetic stars in the \texttt{goodSeeing} \tract{}.
         The scatter plot (dashed-line histogram) and contour (solid-line histogram)
@@
 %% ------------------------------------------------------------------------------------ %%
+% Table 1 : Magnitudes for PSF
+\begin{table*}
+    \begin{center}
+    %% -------------------------------------------------------------------------------- %%
+    \begin{tabular}{| c | c | c | ccccccc |}
+    \hline
+    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
+    \cline{4-10}
+           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
+    \hline
+    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    \hline
+    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline
+    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline
+    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline
+    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline  
+    \end{tabular}
+    %% -------------------------------------------------------------------------------- %%
+    \end{center}
+    \caption{
+        \todo{Placeholder}
+        Summary of the precisions and accuracies of \forced{} PSF magnitudes in all 
+        five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
+    }
+        \label{tab:psfmag}
+\end{table*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+% Table 2 : PSF Color
+\begin{table*}
+    \begin{center}
+    %% -------------------------------------------------------------------------------- %%
+    \begin{tabular}{| c | c | c | ccccccc |}
+    \hline
+    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
+    \cline{4-10}
+           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
+    \hline
+    $(g-i)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            \cline{3-10}
+            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    \hline
+    $(i-y)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            \cline{3-10}
+            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline  
+    \end{tabular}
+    %% -------------------------------------------------------------------------------- %%
+    \end{center}
+    \caption{
+        \todo{Placeholder}
+        Summary of the precisions and accuracies of \forced{} PSF colors in both 
+        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
+        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
+    }
+        \label{tab:psfcolor}
+\end{table*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+% Table 3 : Magnitudes for cModel
+\begin{table*}
+    \begin{center}
+    %% -------------------------------------------------------------------------------- %%
+    \begin{tabular}{| c | c | c | ccccccc |}
+    \hline
+    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
+    \cline{4-10}
+           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
+    \hline
+    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    \hline
+    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline
+    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline
+    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline
+    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        \cline{3-10}
+        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline  
+    \end{tabular}
+    %% -------------------------------------------------------------------------------- %%
+    \end{center}
+    \caption{
+        \todo{Placeholder}
+        Summary of the precisions and accuracies of \forced{} \cmodel{} magnitudes in 
+        all five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
+    }
+        \label{tab:psfmag}
+\end{table*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+% Table 4 : CModel Color
+\begin{table*}
+    \begin{center}
+    %% -------------------------------------------------------------------------------- %%
+    \begin{tabular}{| c | c | c | ccccccc |}
+    \hline
+    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
+    \cline{4-10}
+           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
+    \hline
+    $(g-i)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            \cline{3-10}
+            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    \hline
+    $(i-y)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            \cline{3-10}
+            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \hline  
+    \end{tabular}
+    %% -------------------------------------------------------------------------------- %%
+    \end{center}
+    \caption{
+        \todo{Placeholder}
+        Summary of the precisions and accuracies of \forced{} \cmodel{} colors in both 
+        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
+        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
+    }
+        \label{tab:cmodelcolor}
+\end{table*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
 \begin{ack}
@@
 %% ------------------------------------------------------------------------------------ %%
-%%%%%%%%%%%: Possible Tables %%%%%%%%%%%%%
-%\input{table1.tex}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
 \label{lastpage}

### 2017-04-28 draft/ms_v5.tex
Add Masayuki to author list

@@
         Steven Bickerton \altaffilmark{2},
-        Satoshi Miyazaki \altaffilmark{6}, 
-        Jean Coupon \altaffilmark{7},
-        HSC Collaboration \altaffilmark{8}}
+        Satoshi Miyazaki \altaffilmark{6,7}, 
+        Jean Coupon \altaffilmark{8},
+        Masayuki Tanaka \altaffilmark{6}
+        }
 %% ------------------------------------------------------------------------------------ %%
@@
 
-\altaffiltext{6}{SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
+\altaffiltext{6}{National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
+     Tokyo 181--8588, Japan}
+
+\altaffiltext{7}{SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
     Tokyo, 181--8588, Japan}
 
-\altaffiltext{7}{Department of Astronomy, University of Geneva, ch. d'\'Ecogia 16, 
+\altaffiltext{8}{Department of Astronomy, University of Geneva, ch. d'\'Ecogia 16, 
     1290 Versoix, Switzerland}
-
-\altaffiltext{8}{Other affiliations}
 

### 2017-04-29 draft/ms_v5.tex
Draft for Table1

@@
         On the right hand side, we show the spatial relation between \texttt{tracts},
-        \texttt{patches}, and \texttt{visits}. 
-        The red colored box corresponds to one \texttt{tract} which has an area of 
+        \texttt{patches}, and \visits{}. 
+        The red colored box corresponds to one \tract{} which has an area of 
         about 1.5 deg$^2$. 
-        Large colored circles are \texttt{visits} (also commonly known as "pointings") 
+        Large colored circles are \visits{} (also commonly known as ``pointings'') 
         with small rectangles representing CCDs. 
         \texttt{patches} are represented by black dashed lines. 
-        One \texttt{tract} typically contains 81 \texttt{patches}.
+        One \tract{} typically contains 81 \texttt{patches}.
         }
@@
     \hline
-    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    $g$ & 0.45 & Precision & 0.016 & 0.017 & 0.019 & 0.023 & 0.029 & 0.043 & 0.078 \\
+        &      & Accuracy  & 0.008 & 0.009 & 0.009 & 0.009 & 0.008 & 0.007 & $\minus 0.003$ \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        & 0.70 & Precision & 0.016 & 0.018 & 0.019 & 0.021 & 0.026 & 0.039 & 0.091 \\
+        &      & Accuracy  & 0.007 & 0.006 & 0.006 & 0.005 & 0.004 & 0.003 & $\minus 0.002$ \\
     \hline
-    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    $r$ & 0.45 & Precision & 0.021 & 0.023 & 0.024 & 0.025 & 0.027 & 0.035 & 0.064 \\
+        &      & Accuracy  & 0.011 & 0.011 & 0.012 & 0.011 & 0.012 & 0.011 & 0.011 \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+        & 0.70 & Precision & 0.026 & 0.029 & 0.031 & 0.034 & 0.041 & 0.054 & 0.090 \\
+        &      & Accuracy  & 0.009 & 0.009 & 0.009 & 0.009 & 0.009 & 0.006 & 0.001 \\    
     \hline
-    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    $i$ & 0.45 & Precision & 0.015 & 0.015 & 0.017 & 0.018 & 0.020 & 0.030 & 0.047 \\
+        &      & Accuracy  & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+        & 0.70 & Precision & 0.012 & 0.013 & 0.014 & 0.016 & 0.022 & 0.043 & 0.050 \\
+        &      & Accuracy  & 0.001 & 0.002 & 0.002 & 0.002 & 0.002 & 0.001 & $\minus 0.012$ \\    
     \hline
-    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    $z$ & 0.45 & Precision & 0.011 & 0.013 & 0.014 & 0.016 & 0.025 & 0.053 & 0.094 \\
+        &      & Accuracy  & 0.002 & 0.002 & 0.002 & 0.003 & 0.003 & 0.005 & $\minus 0.001$ \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+        & 0.70 & Precision & 0.019 & 0.020 & 0.021 & 0.024 & 0.038 & 0.071 & 0.104 \\
+        &      & Accuracy  & 0.003 & 0.003 & 0.003 & 0.004 & 0.005 & 0.003 & $\minus 0.010$ \\    
     \hline
-    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    $y$ & 0.45 & Precision & 0.017 & 0.017 & 0.021 & 0.033 & 0.074 & 0.138 & -- \\
+        &      & Accuracy  & 0.006 & 0.006 & 0.006 & 0.006 & 0.000 & $\minus 0.001$ & -- \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+        & 0.70 & Precision & 0.019 & 0.019 & 0.023 & 0.037 & 0.077 & 0.153 & -- \\
+        &      & Accuracy  & 0.007 & 0.008 & 0.008 & 0.006 & 0.003 & $\minus 0.034$ & -- \\    
     \hline  

### 2017-04-30 draft/ms_v5.tex
Draft for Table2
Draft for Table3
Draft for Table4

--- 2017-04-28 draft/ms_v5.tex
@@
 \usepackage[usenames, dvipsnames]{xcolor}
+\usepackage{colortbl}
+\usepackage{multirow}
 
@@
 \newcommand{\minus}{\raisebox{.4\height}{\scalebox{.8}{-}}}
+\newcommand{\smag}{$\sigma_{\Delta\mathrm{mag}}$}
+\newcommand{\mmag}{$\left<{\Delta\mathrm{mag}}\right>$}
+\newcommand{\n}{$\minus$}
 
@@
     \hline
-    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    $g$ & 0.45 & \smag{} & 0.016 & 0.017 & 0.019 & 0.023 & 0.029 & 0.043 & 0.078 \\
+        &      & \mmag{}  & 0.008 & 0.009 & 0.009 & 0.009 & 0.008 & 0.007 & $\minus 0.003$ \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-    \hline
-    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        & 0.70 & \smag{} & 0.016 & 0.018 & 0.019 & 0.021 & 0.026 & 0.039 & 0.091 \\
+        &      & \mmag{}  & 0.007 & 0.006 & 0.006 & 0.005 & 0.004 & 0.003 & $\minus 0.002$ \\
+    \hline
+    $r$ & 0.45 & \smag{} & 0.021 & 0.023 & 0.024 & 0.025 & 0.027 & 0.035 & 0.064 \\
+        &      & \mmag{}  & 0.011 & 0.011 & 0.012 & 0.011 & 0.012 & 0.011 & 0.011 \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
-    \hline
-    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        & 0.70 & \smag{} & 0.026 & 0.029 & 0.031 & 0.034 & 0.041 & 0.054 & 0.090 \\
+        &      & \mmag{}  & 0.009 & 0.009 & 0.009 & 0.009 & 0.009 & 0.006 & 0.001 \\    
+    \hline
+    $i$ & 0.45 & \smag{} & 0.015 & 0.015 & 0.017 & 0.018 & 0.020 & 0.030 & 0.047 \\
+        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
-    \hline
-    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        & 0.70 & \smag{} & 0.012 & 0.013 & 0.014 & 0.016 & 0.022 & 0.043 & 0.050 \\
+        &      & \mmag{}  & 0.001 & 0.002 & 0.002 & 0.002 & 0.002 & 0.001 & $\minus 0.012$ \\    
+    \hline
+    $z$ & 0.45 & \smag{} & 0.011 & 0.013 & 0.014 & 0.016 & 0.025 & 0.053 & 0.094 \\
+        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.003 & 0.003 & 0.005 & $\minus 0.001$ \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
-    \hline
-    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+        & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.024 & 0.038 & 0.071 & 0.104 \\
+        &      & \mmag{}  & 0.003 & 0.003 & 0.003 & 0.004 & 0.005 & 0.003 & $\minus 0.010$ \\    
+    \hline
+    $y$ & 0.45 & \smag{} & 0.017 & 0.017 & 0.021 & 0.033 & 0.074 & 0.138 & -- \\
+        &      & \mmag{}  & 0.006 & 0.006 & 0.006 & 0.006 & 0.000 & $\minus 0.001$ & -- \\
         \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+        & 0.70 & \smag{} & 0.019 & 0.019 & 0.023 & 0.037 & 0.077 & 0.153 & -- \\
+        &      & \mmag{}  & 0.007 & 0.008 & 0.008 & 0.006 & 0.003 & $\minus 0.034$ & -- \\    
     \hline  
@@
         \todo{Placeholder}
-        Summary of the precisions and accuracies of \forced{} PSF magnitudes in all 
+        Summary of the \smag{}s and accuracies of \forced{} PSF magnitudes in all 
         five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
@@
     \hline
-    $(g-i)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+    $(g-i)$ & 0.45 & \smag{} & 0.023 & 0.026 & 0.037 & 0.054 & 0.077 & 0.105 & 0.117 \\
+            &      & \mmag{}  & 0.008 & 0.007 & 0.005 & 0.003 & $\minus 0.002$ & $\minus 0.009$ & $\minus 0.035$ \\
             \cline{3-10}
-            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-    \hline
-    $(i-y)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
+            & 0.70 & \smag{} & 0.021 & 0.025 & 0.033 & 0.051 & 0.075 & 0.105 & 0.137 \\
+            &      & \mmag{}  & 0.004 & 0.003 & 0.002 & 0.001 & $\minus 0.001$ & $\minus 0.002$ & 0.007 \\
+    \hline
+    $(i-y)$ & 0.45 & \smag{} & 0.019 & 0.020 & 0.022 & 0.031 & 0.058 & 0.109 & 0.189 \\
+            &      & \mmag{}  & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.002$ & 0.011 & 0.064 \\
             \cline{3-10}
-            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+            & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.031 & 0.057 & 0.123 & 0.221 \\
+            &      & \mmag{}  & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.005$ & $\minus 0.005$ & $\minus 0.002$ & $\minus 0.064$ \\    
     \hline  
@@
         \todo{Placeholder}
-        Summary of the precisions and accuracies of \forced{} PSF colors in both 
+        Summary of the \smag{}s and accuracies of \forced{} PSF colors in both 
         \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
@@
     %% -------------------------------------------------------------------------------- %%
-    \begin{tabular}{| c | c | c | ccccccc |}
-    \hline
-    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
-    \cline{4-10}
-           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
-    \hline
-    $g$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-    \hline
-    $r$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
-    \hline
-    $i$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
-    \hline
-    $z$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
-    \hline
-    $y$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        \cline{3-10}
-        & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-        &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    \begin{tabular}{| c | c | c | cccccc |}
+    \hline
+    Filter & Seeing & Statistics & \multicolumn{6}{|c|}{Input Magnitudes (mag)} \\
+    \cline{4-9}
+           & FWHM ($$\asec) &             & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
+    \hline
+    $g$ & 0.45 & \smag{} & 0.111 & 0.156 & 0.161 & 0.152 & 0.176 & 0.196 \\
+        &      & \mmag{}  & $\minus 0.060$ & $\minus 0.036$ & $\minus 0.004$ & 0.021 & 0.009 & $\minus 0.005$ \\
+        \cline{3-9}
+        & 0.70 & \smag{} & 0.137 & 0.161 & 0.138 & 0.147 & 0.181 & 0.202 \\
+        &      & \mmag{}  & 0.018 & $\minus 0.008$ & 0.029 & 0.040 & 0.028 & 0.012 \\
+    \hline
+    $r$ & 0.45 & \smag{} & 0.197 & 0.151 & 0.147 & 0.167 & 0.179 & 0.211  \\
+        &      & \mmag{}  & $\minus0.036$ & $\minus 0.015$ & 0.033 & 0.033 & 0.017 & 0.012  \\
+        \cline{3-9}
+        & 0.70 & \smag{} & 0.167 & 0.119 & 0.142 & 0.168 & 0.189 & 0.232 \\
+        &      & \mmag{}  & $\minus 0.024$ & 0.023 & 0.050 & 0.036 & 0.025 & 0.022 \\    
+    \hline
+    $i$ & 0.45 & \smag{} & 0.173 & 0.157 & 0.154 & 0.168 & 0.183 & 0.218 \\
+        &      & \mmag{}  & $\minus 0.023$ & 0.008 & 0.004 & 0.017 & $\minus 0.001$ & $\minus 0.006$ \\
+        \cline{3-9}
+        & 0.70 & \smag{} & 0.154 & 0.157 & 0.153 & 0.174 & 0.193 & 0.246 \\
+        &      & \mmag{}  & 0.017 & 0.043 & 0.040 & 0.021 & 0.003 & $\minus 0.013$ \\
+    \hline
+    $z$ & 0.45 & \smag{} & 0.171 & 0.176 & 0.165 & 0.182 & 0.201 & 0.241 \\
+        &      & \mmag{}  & $\minus0.006$ & 0.042 & 0.038 & 0.018 & $\minus 0.002$ & $\minus 0.012$ \\
+        \cline{3-9}
+        & 0.70 & \smag{} & 0.168 & 0.155 & 0.167 & 0.185 & 0.222 & 0.278 \\
+        &      & \mmag{}  & 0.027 & 0.046 & 0.045 & 0.028 & 0.009 & $\minus 0.034$ \\    
+    \hline
+    $y$ & 0.45 & \smag{} & 0.179 & 0.169 & 0.178 & 0.197 & 0.241 & 0.308 \\
+        &      & \mmag{}  & 0.011 & 0.056 & 0.044 & 0.014 & $\minus 0.067$ & $\minus 0.244$ \\
+        \cline{3-9}
+        & 0.70 & \smag{} & 0.169 & 0.164 & 0.169 & 0.194 & 0.253 & 0.315 \\
+        &      & \mmag{}  & 0.041 & 0.052 & 0.048 & 0.020 & $\minus 0.057$ & $\minus 0.299$ \\    
     \hline  
@@
         \todo{Placeholder}
-        Summary of the precisions and accuracies of \forced{} \cmodel{} magnitudes in 
+        Summary of the \smag{}s and accuracies of \forced{} \cmodel{} magnitudes in 
         all five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
@@
 % Table 4 : CModel Color
-\begin{table*}
+\begin{table}
     \begin{center}
     %% -------------------------------------------------------------------------------- %%
-    \begin{tabular}{| c | c | c | ccccccc |}
-    \hline
-    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
-    \cline{4-10}
-           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
-    \hline
-    $(g-i)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            \cline{3-10}
-            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-    \hline
-    $(i-y)$ & 0.45 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            \cline{3-10}
-            & 0.70 & Precision & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\
-            &      & Accuracy  & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 & 0.01 \\    
+    %\begin{tabular}{| c | c | c | cccccc |}
+    \begin{tabular}{| c | c | c | c | c | c | }
+    \hline
+    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
+    \cline{2-6}
+      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
+    \hline
+    (mag) & & (mag) & (mag) & (mag) & (mag) \\
+    \hline \hline
+    \rowcolor[gray]{.85} 20.0 & \smag{} &   0.068 & 0.051 &   0.072 &   0.046 \\
+    \rowcolor[gray]{.85}      & \mmag{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
+    \hline 
+    \rowcolor[gray]{1.0} 21.0 & \smag{} &   0.080 & 0.059 &   0.062 &   0.040 \\
+    \rowcolor[gray]{1.0}      & \mmag{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
+    \hline
+    \rowcolor[gray]{.85} 22.0 & \smag{} &   0.089 & 0.072 &   0.071 &   0.059 \\
+    \rowcolor[gray]{.85}      & \mmag{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
+    \hline
+    \rowcolor[gray]{1.0} 23.0 & \smag{} &   0.105 & 0.090 &   0.109 &   0.103 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
+    \hline
+    \rowcolor[gray]{.85} 24.0 & \smag{} &   0.136 & 0.127 &   0.175 &   0.170 \\
+    \rowcolor[gray]{.85}      & \mmag{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
+    \hline
+    \rowcolor[gray]{1.0} 25.0 & \smag{} &   0.179 & 0.185 &   0.227 &   0.241 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
     \hline
@@
         \label{tab:cmodelcolor}
-\end{table*}
+\end{table}
 %% ------------------------------------------------------------------------------------ %%

### 2017-04-30 draft/ms_v5.tex
New figure and table caption

@@
 \newcommand{\minus}{\raisebox{.4\height}{\scalebox{.8}{-}}}
-\newcommand{\smag}{$\sigma_{\Delta\mathrm{mag}}$}
-\newcommand{\mmag}{$\left<{\Delta\mathrm{mag}}\right>$}
+\newcommand{\smag}{$\sigma_{\Delta\mathrm{Mag}}$}
+\newcommand{\mmag}{$\left<{\Delta\mathrm{Mag}}\right>$}
+\newcommand{\scolor}{$\sigma_{\Delta\mathrm{Color}}$}
+\newcommand{\mcolor}{$\left<{\Delta\mathrm{Color}}\right>$}
 \newcommand{\n}{$\minus$}
@@
 %% ------------------------------------------------------------------------------------ %%
+%% Fig: Star Sample
+\begin{figure*}
+    \begin{center}
+        \includegraphics[width=\textwidth]{fig/synpipe_star_sample}
+    \end{center}
+    \caption{
+        Magnitude and color distributions of synthetic stars.
+        \textbf{Upper panel}: five-band magnitude distributions of the COSMOS
+        stars (filled histograms) and  resampled stars (dashed lines).
+        \textbf{Lower panel}: color-color distributions
+        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$). 
+        Filled-contours indicate COSMOS stars and open-contours indicate resampled stars.
+        }
+    \label{fig:star_sample}
+\end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
 \subsubsection{Injection of Synthetic Objects into Single-\visit{} Images}
@@
     \end{enumerate}
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-%% Fig: Star Sample
-\begin{figure*}
-    \begin{center}
-        \includegraphics[width=\textwidth]{fig/synpipe_star_sample}
-    \end{center}
-    \caption{
-        Magnitude and color distributions of synthetic stars.
-        \textbf{Upper panel}: five-band magnitude distributions of the COSMOS
-        stars (filled histograms) and  resampled stars (dashed lines).
-        \textbf{Lower panel}: color-color distributions
-        (left: $g-r$ v.s. $r-i$; right: $i-z$ v.s. $z-y$). 
-        Hexagonal bins indicate COSMOS stars and contours indicate resampled stars.
-        }
-    \label{fig:star_sample}
-\end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
         by \hscpipe{} PSF photometry.
-        Hexagonal binned density plots and contours show the distributions for
+        Filled-contours and open-contours show the distributions for
         stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
@@
         magnitude difference.
-        Hexagonal binned density plots and contours are for the synthetic galaxies 
+        Filled and open contours are for the synthetic galaxies 
         from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.
@@
         measured on the \coadd{} images. 
-        Hexagonal bins (filled histogram) and contours (solid-line histogram) are 
+        Filled-contours (filled histogram) and open-contours (solid-line histogram) are 
         for synthetic objects from \tracts{} with good and bad seeing conditions, 
@@
         The plot on the \textbf{left} (a) corresponds to synthetic stars. 
-        Hexagonal bins and filled histogram show distributions of correctly classified
+        Filled-contours and filled histogram show distributions of correctly classified
         synthetic stars in the \texttt{goodSeeing} \tract{}.
-        The scatter plot (dashed-line histogram) and contour (solid-line histogram)
+        The scatter plot (dashed-line histogram) and open-contour (solid-line histogram)
         show distributions of synthetic stars that are misclassified as extended
@@
         The plot on the \textbf{right} (b) corresponds to synthetic galaxies.
-        Hexagonal bins (filled histogram) and contours (solid-line histogram)
+        Filled-contours (filled histogram) and open-contours (solid-line histogram)
         are for galaxies from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{},
@@
         $(g-i)$ colors.
-        Hexagonal bins and contours show results for \texttt{goodSeeing} and
+        Filled-contours and open-contours show results for \texttt{goodSeeing} and
         \texttt{badSeeing} \tracts{}, respectively.
@@
         the undertainty in $(b/a)$.
-        Contours are for the default test with \texttt{usePixelWeights=False}, and 
-        hexagonal bins correspond to \texttt{usePixelWeights=True}.
+        Open-contours are for the default test with \texttt{usePixelWeights=False}, and 
+        filled-contours correspond to \texttt{usePixelWeights=True}.
         }
@@
     \caption{
-        \todo{Placeholder}
-        Summary of the \smag{}s and accuracies of \forced{} PSF magnitudes in all 
-        five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
+        Summary of precisions and accuracies of \forced{} PSF magnitudes in all 
+        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
+        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
+        the difference between output \forced{} PSF magnitude and input 
+        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:psf_mag}.
+        Here, the precision is described using the statistical uncertainties of 
+        $\Delta\mathrm{mag}$ within a series of input magnitude bins (\smag{}). 
+        The accuracy of PSF photometry in the same magnitude bin is described by the 
+        mean value of $\Delta\mathrm{mag}$.
         }
@@
     \hline
-    $(g-i)$ & 0.45 & \smag{} & 0.023 & 0.026 & 0.037 & 0.054 & 0.077 & 0.105 & 0.117 \\
-            &      & \mmag{}  & 0.008 & 0.007 & 0.005 & 0.003 & $\minus 0.002$ & $\minus 0.009$ & $\minus 0.035$ \\
+    $(g-i)$ & 0.45 & \scolor{} & 0.023 & 0.026 & 0.037 & 0.054 & 0.077 & 0.105 & 0.117 \\
+            &      & \mcolor{}  & 0.008 & 0.007 & 0.005 & 0.003 & $\minus 0.002$ & $\minus 0.009$ & $\minus 0.035$ \\
             \cline{3-10}
-            & 0.70 & \smag{} & 0.021 & 0.025 & 0.033 & 0.051 & 0.075 & 0.105 & 0.137 \\
-            &      & \mmag{}  & 0.004 & 0.003 & 0.002 & 0.001 & $\minus 0.001$ & $\minus 0.002$ & 0.007 \\
-    \hline
-    $(i-y)$ & 0.45 & \smag{} & 0.019 & 0.020 & 0.022 & 0.031 & 0.058 & 0.109 & 0.189 \\
-            &      & \mmag{}  & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.002$ & 0.011 & 0.064 \\
+            & 0.70 & \scolor{} & 0.021 & 0.025 & 0.033 & 0.051 & 0.075 & 0.105 & 0.137 \\
+            &      & \mcolor{}  & 0.004 & 0.003 & 0.002 & 0.001 & $\minus 0.001$ & $\minus 0.002$ & 0.007 \\
+    \hline
+    $(i-y)$ & 0.45 & \scolor{} & 0.019 & 0.020 & 0.022 & 0.031 & 0.058 & 0.109 & 0.189 \\
+            &      & \mcolor{}  & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.002$ & 0.011 & 0.064 \\
             \cline{3-10}
-            & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.031 & 0.057 & 0.123 & 0.221 \\
-            &      & \mmag{}  & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.005$ & $\minus 0.005$ & $\minus 0.002$ & $\minus 0.064$ \\    
+            & 0.70 & \scolor{} & 0.019 & 0.020 & 0.021 & 0.031 & 0.057 & 0.123 & 0.221 \\
+            &      & \mcolor{}  & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.005$ & $\minus 0.005$ & $\minus 0.002$ & $\minus 0.064$ \\    
     \hline  
@@
     \caption{
-        \todo{Placeholder}
-        Summary of the \smag{}s and accuracies of \forced{} PSF colors in both 
-        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
-        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
+        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
+        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
+        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
+        the difference between output \forced{} PSF color and input value 
+        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
+        Here, we describe the precision and accuracy of PSF color measurements using 
+        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
+        bins of input $i$ band magnitudes.
     }
@@
     \caption{
-        \todo{Placeholder}
-        Summary of the \smag{}s and accuracies of \forced{} \cmodel{} magnitudes in 
-        all five bands and in both \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
-    }
-        \label{tab:psfmag}
+        Summary of precisions and accuracies of \forced{} \cmodel{} magnitudes in all 
+        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
+        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
+        the difference between output \forced{} \cmodel{} magnitude and input 
+        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:cmodel_mag}.
+        Other details are the same with Table \ref{tab:psfmag}.}
+        \label{tab:cmodelmag}
 \end{table*}
@@
     \hline \hline
-    \rowcolor[gray]{.85} 20.0 & \smag{} &   0.068 & 0.051 &   0.072 &   0.046 \\
-    \rowcolor[gray]{.85}      & \mmag{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
-    \hline 
-    \rowcolor[gray]{1.0} 21.0 & \smag{} &   0.080 & 0.059 &   0.062 &   0.040 \\
-    \rowcolor[gray]{1.0}      & \mmag{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
-    \hline
-    \rowcolor[gray]{.85} 22.0 & \smag{} &   0.089 & 0.072 &   0.071 &   0.059 \\
-    \rowcolor[gray]{.85}      & \mmag{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
-    \hline
-    \rowcolor[gray]{1.0} 23.0 & \smag{} &   0.105 & 0.090 &   0.109 &   0.103 \\
-    \rowcolor[gray]{1.0}      & \mmag{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
-    \hline
-    \rowcolor[gray]{.85} 24.0 & \smag{} &   0.136 & 0.127 &   0.175 &   0.170 \\
-    \rowcolor[gray]{.85}      & \mmag{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
-    \hline
-    \rowcolor[gray]{1.0} 25.0 & \smag{} &   0.179 & 0.185 &   0.227 &   0.241 \\
-    \rowcolor[gray]{1.0}      & \mmag{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
+    \rowcolor[gray]{.85} 20.0 & \scolor{} &   0.068 & 0.051 &   0.072 &   0.046 \\
+    \rowcolor[gray]{.85}      & \mcolor{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
+    \hline 
+    \rowcolor[gray]{1.0} 21.0 & \scolor{} &   0.080 & 0.059 &   0.062 &   0.040 \\
+    \rowcolor[gray]{1.0}      & \mcolor{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
+    \hline
+    \rowcolor[gray]{.85} 22.0 & \scolor{} &   0.089 & 0.072 &   0.071 &   0.059 \\
+    \rowcolor[gray]{.85}      & \mcolor{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
+    \hline
+    \rowcolor[gray]{1.0} 23.0 & \scolor{} &   0.105 & 0.090 &   0.109 &   0.103 \\
+    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
+    \hline
+    \rowcolor[gray]{.85} 24.0 & \scolor{} &   0.136 & 0.127 &   0.175 &   0.170 \\
+    \rowcolor[gray]{.85}      & \mcolor{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
+    \hline
+    \rowcolor[gray]{1.0} 25.0 & \scolor{} &   0.179 & 0.185 &   0.227 &   0.241 \\
+    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
     \hline
@@
     \caption{
-        \todo{Placeholder}
-        Summary of the precisions and accuracies of \forced{} \cmodel{} colors in both 
-        \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.  
-        We show results for both $(g-i)$ and $(i-y)$ PSF colors.
+        Summary of precisions and accuracies of \forced{} \cmodel{} colors using 
+        $(g-i)$ and $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) 
+        and \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
+        the difference between output \forced{} \cmodel{} color and input value 
+        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:cmodel_color}.
+        Other details are the same with Table \ref{tab:psfcolor}.
     }

### 2017-04-30 draft/ms_v5.tex
New Table 2
Change the format for magnitude catalog

@@
     %% -------------------------------------------------------------------------------- %%
-    \begin{tabular}{| c | c | c | ccccccc |}
-    \hline
-    Filter &   Seeing    &  Statistics & \multicolumn{7}{|c|}{Input Magnitudes (mag)} \\
-    \cline{4-10}
-           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
-    \hline
-    $g$ & 0.45 & \smag{} & 0.016 & 0.017 & 0.019 & 0.023 & 0.029 & 0.043 & 0.078 \\
-        &      & \mmag{}  & 0.008 & 0.009 & 0.009 & 0.009 & 0.008 & 0.007 & $\minus 0.003$ \\
-        \cline{3-10}
-        & 0.70 & \smag{} & 0.016 & 0.018 & 0.019 & 0.021 & 0.026 & 0.039 & 0.091 \\
-        &      & \mmag{}  & 0.007 & 0.006 & 0.006 & 0.005 & 0.004 & 0.003 & $\minus 0.002$ \\
-    \hline
-    $r$ & 0.45 & \smag{} & 0.021 & 0.023 & 0.024 & 0.025 & 0.027 & 0.035 & 0.064 \\
-        &      & \mmag{}  & 0.011 & 0.011 & 0.012 & 0.011 & 0.012 & 0.011 & 0.011 \\
-        \cline{3-10}
-        & 0.70 & \smag{} & 0.026 & 0.029 & 0.031 & 0.034 & 0.041 & 0.054 & 0.090 \\
-        &      & \mmag{}  & 0.009 & 0.009 & 0.009 & 0.009 & 0.009 & 0.006 & 0.001 \\    
-    \hline
-    $i$ & 0.45 & \smag{} & 0.015 & 0.015 & 0.017 & 0.018 & 0.020 & 0.030 & 0.047 \\
-        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.002 & 0.003 \\
-        \cline{3-10}
-        & 0.70 & \smag{} & 0.012 & 0.013 & 0.014 & 0.016 & 0.022 & 0.043 & 0.050 \\
-        &      & \mmag{}  & 0.001 & 0.002 & 0.002 & 0.002 & 0.002 & 0.001 & $\minus 0.012$ \\    
-    \hline
-    $z$ & 0.45 & \smag{} & 0.011 & 0.013 & 0.014 & 0.016 & 0.025 & 0.053 & 0.094 \\
-        &      & \mmag{}  & 0.002 & 0.002 & 0.002 & 0.003 & 0.003 & 0.005 & $\minus 0.001$ \\
-        \cline{3-10}
-        & 0.70 & \smag{} & 0.019 & 0.020 & 0.021 & 0.024 & 0.038 & 0.071 & 0.104 \\
-        &      & \mmag{}  & 0.003 & 0.003 & 0.003 & 0.004 & 0.005 & 0.003 & $\minus 0.010$ \\    
-    \hline
-    $y$ & 0.45 & \smag{} & 0.017 & 0.017 & 0.021 & 0.033 & 0.074 & 0.138 & -- \\
-        &      & \mmag{}  & 0.006 & 0.006 & 0.006 & 0.006 & 0.000 & $\minus 0.001$ & -- \\
-        \cline{3-10}
-        & 0.70 & \smag{} & 0.019 & 0.019 & 0.023 & 0.037 & 0.077 & 0.153 & -- \\
-        &      & \mmag{}  & 0.007 & 0.008 & 0.008 & 0.006 & 0.003 & $\minus 0.034$ & -- \\    
-    \hline  
+    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
+    \hline
+    Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
+    \cline{2-12}
+    Magnitude & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
+    \hline
+    (mag) & & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) \\
+    \hline
+
+    \rowcolor[gray]{.85} 19.0 & \smag{} & 0.016 & 0.016  & 0.021 & 0.026 & 0.015 & 0.012 & 0.011 & 0.019 & 0.017 & 0.019 \\
+    \rowcolor[gray]{.85}      & \mmag{} & 0.008 & 0.008  & 0.011 & 0.009 & 0.002 & 0.001 & 0.002 & 0.003 & 0.006 & 0.007 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 20.0 & \smag{} & 0.017 & 0.018  & 0.023 & 0.029 & 0.015 & 0.013 & 0.013 & 0.020 & 0.017 & 0.019 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & 0.009 & 0.006  & 0.011 & 0.009 & 0.002 & 0.002 & 0.003 & 0.003 & 0.006 & 0.008 \\
+    \hline
+
+    \rowcolor[gray]{.85} 21.0 & \smag{} & 0.019 & 0.019  & 0.024 & 0.031 & 0.017 & 0.014 & 0.014 & 0.021 & 0.021 & 0.023 \\
+    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.006  & 0.012 & 0.009 & 0.002 & 0.002 & 0.002 & 0.003 & 0.006 & 0.008 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 22.0 & \smag{} & 0.023 & 0.021  & 0.025 & 0.034 & 0.018 & 0.016 & 0.016 & 0.024 & 0.033 & 0.037 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & 0.009 & 0.005  & 0.011 & 0.009 & 0.002 & 0.002 & 0.003 & 0.004 & 0.006 & 0.006 \\
+    \hline
+
+    \rowcolor[gray]{.85} 23.0 & \smag{} & 0.029 & 0.026  & 0.027 & 0.041 & 0.020 & 0.022 & 0.025 & 0.038 & 0.074 & 0.077 \\
+    \rowcolor[gray]{.85}      & \mmag{} & 0.008 & 0.004  & 0.012 & 0.009 & 0.002 & 0.002 & 0.003 & 0.005 & 0.000 & 0.003 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 24.0 & \smag{} & 0.043 & 0.039  & 0.035 & 0.054 & 0.030 & 0.043 & 0.053 & 0.071 &   0.138 &   0.153 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & 0.007 & 0.003  & 0.011 & 0.006 & 0.002 & 0.001 & 0.005 & 0.003 & \n0.001 & \n0.034 \\
+    \hline
+
+    \rowcolor[gray]{.85} 25.0 & \smag{} &   0.078 &   0.091  & 0.064 & 0.090 & 0.047 &   0.050 &   0.094 &   0.104 & -- & -- \\
+    \rowcolor[gray]{.85}      & \mmag{} & \n0.003 & \n0.002  & 0.011 & 0.001 & 0.003 & \n0.012 & \n0.001 & \n0.010 & -- & -- \\
+    \hline
+
     \end{tabular}
@@
 % Table 2 : PSF Color
-\begin{table*}
+\begin{table}
     \begin{center}
     %% -------------------------------------------------------------------------------- %%
-    \begin{tabular}{| c | c | c | ccccccc |}
-    \hline
-    Filter &   Seeing       &  Statistics & \multicolumn{4}{|c|}{Input $i$ band Magnitudes (mag)} \\
-    \cline{4-10}
-           & FWHM ($$\asec) &             & 19.0 & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
-    \hline
-    $(g-i)$ & 0.45 & \scolor{} & 0.023 & 0.026 & 0.037 & 0.054 & 0.077 & 0.105 & 0.117 \\
-            &      & \mcolor{}  & 0.008 & 0.007 & 0.005 & 0.003 & $\minus 0.002$ & $\minus 0.009$ & $\minus 0.035$ \\
-            \cline{3-10}
-            & 0.70 & \scolor{} & 0.021 & 0.025 & 0.033 & 0.051 & 0.075 & 0.105 & 0.137 \\
-            &      & \mcolor{}  & 0.004 & 0.003 & 0.002 & 0.001 & $\minus 0.001$ & $\minus 0.002$ & 0.007 \\
-    \hline
-    $(i-y)$ & 0.45 & \scolor{} & 0.019 & 0.020 & 0.022 & 0.031 & 0.058 & 0.109 & 0.189 \\
-            &      & \mcolor{}  & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.004$ & $\minus 0.002$ & 0.011 & 0.064 \\
-            \cline{3-10}
-            & 0.70 & \scolor{} & 0.019 & 0.020 & 0.021 & 0.031 & 0.057 & 0.123 & 0.221 \\
-            &      & \mcolor{}  & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.006$ & $\minus 0.005$ & $\minus 0.005$ & $\minus 0.002$ & $\minus 0.064$ \\    
+    \begin{tabular}{| c | c | c | c | c | c | }
+    \hline
+    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
+    \cline{2-6}
+      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
+    \hline
+    (mag) & & (mag) & (mag) & (mag) & (mag) \\
+    \hline
+    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.021 &   0.019 &   0.019 \\
+    \rowcolor[gray]{.85}      & \mcolor{} &   0.008 &   0.004 & \n0.004 & \n0.006 \\
+    \hline 
+    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.026 &   0.025 &   0.020 &   0.020 \\
+    \rowcolor[gray]{1.0}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
+    \hline
+    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.037 &   0.033 &   0.022 &   0.021 \\
+    \rowcolor[gray]{.85}      & \mcolor{} &   0.005 &   0.002 & \n0.004 & \n0.006 \\
+    \hline
+    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.054 &   0.051 &   0.031 &   0.031 \\
+    \rowcolor[gray]{1.0}      & \mcolor{} &   0.003 &   0.001 & \n0.001 & \n0.005 \\
+    \hline
+    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.077 &   0.075 &   0.058 &   0.057 \\
+    \rowcolor[gray]{.85}      & \mcolor{} & \n0.002 & \n0.001 & \n0.002 & \n0.005 \\
+    \hline
+    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.105 &   0.105 &   0.109 &   0.123 \\
+    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.009 & \n0.002 &   0.011 & \n0.002 \\
+    \hline
+    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.117 &   0.137 &   0.189 &   0.221 \\
+    \rowcolor[gray]{.85}      & \mcolor{} & \n0.005 &   0.007 &   0.064 & \n0.063 \\
     \hline
@@
         \label{tab:psfcolor}
-\end{table*}
+\end{table}
 %% ------------------------------------------------------------------------------------ %%
@@
     %% -------------------------------------------------------------------------------- %%
-    \begin{tabular}{| c | c | c | cccccc |}
-    \hline
-    Filter & Seeing & Statistics & \multicolumn{6}{|c|}{Input Magnitudes (mag)} \\
-    \cline{4-9}
-           & FWHM ($$\asec) &             & 20.0 & 21.0 & 22.0 & 23.0 & 24.0 & 25.0 \\
-    \hline
-    $g$ & 0.45 & \smag{} & 0.111 & 0.156 & 0.161 & 0.152 & 0.176 & 0.196 \\
-        &      & \mmag{}  & $\minus 0.060$ & $\minus 0.036$ & $\minus 0.004$ & 0.021 & 0.009 & $\minus 0.005$ \\
-        \cline{3-9}
-        & 0.70 & \smag{} & 0.137 & 0.161 & 0.138 & 0.147 & 0.181 & 0.202 \\
-        &      & \mmag{}  & 0.018 & $\minus 0.008$ & 0.029 & 0.040 & 0.028 & 0.012 \\
-    \hline
-    $r$ & 0.45 & \smag{} & 0.197 & 0.151 & 0.147 & 0.167 & 0.179 & 0.211  \\
-        &      & \mmag{}  & $\minus0.036$ & $\minus 0.015$ & 0.033 & 0.033 & 0.017 & 0.012  \\
-        \cline{3-9}
-        & 0.70 & \smag{} & 0.167 & 0.119 & 0.142 & 0.168 & 0.189 & 0.232 \\
-        &      & \mmag{}  & $\minus 0.024$ & 0.023 & 0.050 & 0.036 & 0.025 & 0.022 \\    
-    \hline
-    $i$ & 0.45 & \smag{} & 0.173 & 0.157 & 0.154 & 0.168 & 0.183 & 0.218 \\
-        &      & \mmag{}  & $\minus 0.023$ & 0.008 & 0.004 & 0.017 & $\minus 0.001$ & $\minus 0.006$ \\
-        \cline{3-9}
-        & 0.70 & \smag{} & 0.154 & 0.157 & 0.153 & 0.174 & 0.193 & 0.246 \\
-        &      & \mmag{}  & 0.017 & 0.043 & 0.040 & 0.021 & 0.003 & $\minus 0.013$ \\
-    \hline
-    $z$ & 0.45 & \smag{} & 0.171 & 0.176 & 0.165 & 0.182 & 0.201 & 0.241 \\
-        &      & \mmag{}  & $\minus0.006$ & 0.042 & 0.038 & 0.018 & $\minus 0.002$ & $\minus 0.012$ \\
-        \cline{3-9}
-        & 0.70 & \smag{} & 0.168 & 0.155 & 0.167 & 0.185 & 0.222 & 0.278 \\
-        &      & \mmag{}  & 0.027 & 0.046 & 0.045 & 0.028 & 0.009 & $\minus 0.034$ \\    
-    \hline
-    $y$ & 0.45 & \smag{} & 0.179 & 0.169 & 0.178 & 0.197 & 0.241 & 0.308 \\
-        &      & \mmag{}  & 0.011 & 0.056 & 0.044 & 0.014 & $\minus 0.067$ & $\minus 0.244$ \\
-        \cline{3-9}
-        & 0.70 & \smag{} & 0.169 & 0.164 & 0.169 & 0.194 & 0.253 & 0.315 \\
-        &      & \mmag{}  & 0.041 & 0.052 & 0.048 & 0.020 & $\minus 0.057$ & $\minus 0.299$ \\    
-    \hline  
+    \begin{tabular}{| c | c | c | c | c | c | c | c | c | c | c | c |}
+    \hline
+    Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
+    \cline{2-12}
+    Magnitude & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
+    \hline
+    (mag) & & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) & (mag) \\
+    \hline
+
+    \rowcolor[gray]{.85} 20.0 & \smag{} &   0.111 & 0.137  &   0.197 &   0.167 &   0.173 & 0.154 &    0.171 & 0.168 & 0.179 & 0.169 \\
+    \rowcolor[gray]{.85}      & \mmag{} & \n0.006 & 0.018  & \n0.036 & \n0.024 & \n0.023 & 0.017 & \n0.006 & 0.027 & 0.011 & 0.041 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 21.0 & \smag{} &   0.156 &   0.161  &   0.151 & 0.119 & 0.157 & 0.157 & 0.176 & 0.155 & 0.169 & 0.164 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & \n0.036 & \n0.008  & \n0.015 & 0.023 & 0.008 & 0.043 & 0.043 & 0.046 & 0.056 & 0.052 \\
+    \hline
+
+    \rowcolor[gray]{.85} 22.0 & \smag{} & 0.019 & 0.019  & 0.024 & 0.031 & 0.017 & 0.014 & 0.014 & 0.021 & 0.021 & 0.023 \\
+    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.006  & 0.012 & 0.009 & 0.002 & 0.002 & 0.002 & 0.003 & 0.006 & 0.008 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 23.0 & \smag{} &   0.161 & 0.138  & 0.147 & 0.167 & 0.168 & 0.174 & 0.182 & 0.185 & 0.197 & 0.194 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & \n0.004 & 0.029  & 0.033 & 0.033 & 0.036 & 0.021 & 0.018 & 0.028 & 0.014 & 0.020 \\
+    \hline
+
+    \rowcolor[gray]{.85} 24.0 & \smag{} & 0.176 & 0.181  & 0.179 & 0.189 &   0.183 & 0.193 &   0.201 & 0.222 &   0.241 &   0.253 \\
+    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.028  & 0.028 & 0.025 & \n0.001 & 0.003 & \n0.002 & 0.009 & \n0.067 & \n0.057 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 25.0 & \smag{} &   0.196 & 0.202  & 0.211 & 0.232 &   0.218 &   0.246 &   0.241 &   0.278 &   0.308 &   0.315 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & \n0.005 & 0.012  & 0.012 & 0.022 & \n0.006 & \n0.013 & \n0.012 & \n0.034 & \n0.224 & \n0.299 \\
+    \hline
+
     \end{tabular}
     %% -------------------------------------------------------------------------------- %%
+
     \end{center}
@@
     %% -------------------------------------------------------------------------------- %%
-    %\begin{tabular}{| c | c | c | cccccc |}
     \begin{tabular}{| c | c | c | c | c | c | }
@@
     (mag) & & (mag) & (mag) & (mag) & (mag) \\
-    \hline \hline
+    \hline
     \rowcolor[gray]{.85} 20.0 & \scolor{} &   0.068 & 0.051 &   0.072 &   0.046 \\

### 2017-04-30 draft/ms_v5.tex
Minor changes

@@
 %% ------------------------------------------------------------------------------------ %%
+%% Fig: Magnitude v.s S/N for stars
+\begin{figure*}
+    \begin{center}
+        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
+    \end{center}
+    \caption{
+        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
+        $g$-band) of synthetic stars and the $\log (\mathrm{S}/\mathrm{N})$ measured 
+        by \hscpipe{} PSF photometry.
+        Filled-contours and open-contours show the distributions for
+        stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
+        Highly blended stars are highlighted using scatter plots.
+        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
+        by \hscpipe{}.  
+        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
+        however we do not reach these magnitudes with our current synthetic stellar 
+        input catalog.
+        }
+    \label{fig:star_sn}
+\end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
 \subsection{Input Models for Stars and Galaxies}
@@
 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-%% Fig: Magnitude v.s S/N for stars
-\begin{figure*}
-    \begin{center}
-        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
-    \end{center}
-    \caption{
-        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
-        $g$-band) of synthetic stars and the $\log (\mathrm{S}/\mathrm{N})$ measured 
-        by \hscpipe{} PSF photometry.
-        Filled-contours and open-contours show the distributions for
-        stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
-        Highly blended stars are highlighted using scatter plots.
-        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
-        by \hscpipe{}.  
-        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
-        however we do not reach these magnitudes with our current synthetic stellar 
-        input catalog.
-        }
-    \label{fig:star_sn}
-\end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
 %% ------------------------------------------------------------------------------------ %%
+\subsection{PSF photometry of stars}
+    \label{ssec:psf}
+
+    In \hscpipe{}, the PSF magnitude is derived using a matched-filter method that
+    depends on the best-fit PSF model and uses third-order Lanczos interpolation to 
+    shift the PSF model.
+    The error of the PSF magnitude from \hscpipe{} only considers the per-pixel noise,
+    and does not include centroid uncertainties.
+    \hscpipe{} also estimates aperture correction for PSF photometry.
+    For more details please see Bosch\etal (in prep.).
+
+    We randomly inject ${\sim}100,000$ stars into each \tract{} in all five bands. 
+    Typically, there are ${\sim}80000$ stars with $i_{\mathrm{PSF}}<26.0$ in one HSC 
+    \tract{}. 
+    Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the 
+    centroids of real objects; we remove those stars from the sample to avoid confusion 
+    in the comparisons.
+    For matched stars, we select the primary detections 
+    (\texttt{detect.is-primary=True}) that have good photometric quality
+    (see Appendix \ref{app:qc} for details).
+    This gives us ${\sim}83,000$ stars in each \tract{}.
+
+    Next, we exclude stars that are misidentified by \hscpipe{} as extended
+    objects using the \texttt{classification.extendedness} parameter in each band.
+    The fraction of misclassification is ${\sim}10$--$20$\%, and clearly depends on
+    seeing conditions.
+    For the same reason, the $g$-band has the highest fraction of misclassification,
+    while $i$-band is recommended for selecting point sources.
+    The star--galaxy separation issue is discussed more in Section \ref{ssec:sg}.
+
+    In the following comparisons, we show the results from the
+    \texttt{goodSeeing} and \texttt{badSeeing} \tracts{} separately because it
+    is important to understand how the seeing conditions affects photometric accuracy 
+    as well as to test whether \hscpipe{} can deliver unbiased photometry under 
+    different seeing conditions.
+
+    Besides seeing, the degree to which an object is blended with other objects 
+    is another factor that influences photometric accuracy. 
+    To quantify the impact of blending effects, we use the ``blendedness'' 
+    parameter, $b$. 
+    This parameter describes how much any given object overlaps with neighboring 
+    objects (see Appendix \ref{app:defineb} and Murata\etal in prep.). 
+    We divide our sample according to the blendedness parameter. 
+    A value of $b=0$ corresponds to isolated objects whereas objects with $b=1$ 
+    complete overlap with other objects. 
+    Here we use $b>0.05$ to define highly blended stars (${\sim}4$--$9$\% are blended
+    according to this criterion).
+    The fraction of highly blended stars slightly increases in the \texttt{badSeeing} 
+    \tract{}. 
+    The impact of blendedness will be discussed more in Section \ref{ssec:blendedness}.
+
+%% ------------------------------------------------------------------------------------ %%
+\subsubsection{Relationship between stellar magnitude and \s2n{}}
+
+    The \s2n{} for PSF photometry is defined as
+    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
+    Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
+    in the $g$- and $i$-bands. 
+    This figure shows the expected \s2n{} of stars as a function of magnitude in the 
+    Wide layer.
+    The slopes and scatters of these relations are very similar to the ones using 
+    real stars on these two \tracts{}.
+
+    Fig \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
+    sources at fixed input magnitude.
+    In $i$-band, the \texttt{badSeeing} (0.70\asec{}) \tract{} shows systematically
+    lower \s2n{} than the \texttt{goodSeeing} (0.45\asec{}) \tract{}.
+    The \s2n{} is similar for the two $g$-band \tracts{} because they share similar 
+    seeing conditions.
+
+    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ 
+    and $i$ bands, which is consistent with the values found in \citet{HSCDR1} for 
+    average seeing conditions.
+    However, it is worth reminding HSC data users that the detection
+    limit will exhibit spatial variations due to the seeing conditions.
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
 %% Fig: Accuracies of the PSF color
@@
 %% ------------------------------------------------------------------------------------ %%
-\subsection{PSF photometry of stars}
-    \label{ssec:psf}
-
-    In \hscpipe{}, the PSF magnitude is derived using a matched-filter method that
-    depends on the best-fit PSF model and uses third-order Lanczos interpolation to 
-    shift the PSF model.
-    The error of the PSF magnitude from \hscpipe{} only considers the per-pixel noise,
-    and does not include centroid uncertainties.
-    \hscpipe{} also estimates aperture correction for PSF photometry.
-    For more details please see Bosch\etal (in prep.).
-
-    We randomly inject ${\sim}100,000$ stars into each \tract{} in all five bands. 
-    Typically, there are ${\sim}80000$ stars with $i_{\mathrm{PSF}}<26.0$ in one HSC 
-    \tract{}. 
-    Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the 
-    centroids of real objects; we remove those stars from the sample to avoid confusion 
-    in the comparisons.
-    For matched stars, we select the primary detections 
-    (\texttt{detect.is-primary=True}) that have good photometric quality
-    (see Appendix \ref{app:qc} for details).
-    This gives us ${\sim}83,000$ stars in each \tract{}.
-
-    Next, we exclude stars that are misidentified by \hscpipe{} as extended
-    objects using the \texttt{classification.extendedness} parameter in each band.
-    The fraction of misclassification is ${\sim}10$--$20$\%, and clearly depends on
-    seeing conditions.
-    For the same reason, the $g$-band has the highest fraction of misclassification,
-    while $i$-band is recommended for selecting point sources.
-    The star--galaxy separation issue is discussed more in Section \ref{ssec:sg}.
-
-    In the following comparisons, we show the results from the
-    \texttt{goodSeeing} and \texttt{badSeeing} \tracts{} separately because it
-    is important to understand how the seeing conditions affects photometric accuracy 
-    as well as to test whether \hscpipe{} can deliver unbiased photometry under 
-    different seeing conditions.
-
-    Besides seeing, the degree to which an object is blended with other objects 
-    is another factor that influences photometric accuracy. 
-    To quantify the impact of blending effects, we use the ``blendedness'' 
-    parameter, $b$. 
-    This parameter describes how much any given object overlaps with neighboring 
-    objects (see Appendix \ref{app:defineb} and Murata\etal in prep.). 
-    We divide our sample according to the blendedness parameter. 
-    A value of $b=0$ corresponds to isolated objects whereas objects with $b=1$ 
-    complete overlap with other objects. 
-    Here we use $b>0.05$ to define highly blended stars (${\sim}4$--$9$\% are blended
-    according to this criterion).
-    The fraction of highly blended stars slightly increases in the \texttt{badSeeing} 
-    \tract{}. 
-    The impact of blendedness will be discussed more in Section \ref{ssec:blendedness}.
-
-%% ------------------------------------------------------------------------------------ %%
-\subsubsection{Relationship between stellar magnitude and \s2n{}}
-
-    The \s2n{} for PSF photometry is defined as
-    $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
-    Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
-    in the $g$- and $i$-bands. 
-    This figure shows the expected \s2n{} of stars as a function of magnitude in the 
-    Wide layer.
-    The slopes and scatters of these relations are very similar to the ones using 
-    real stars on these two \tracts{}.
-
-    Fig \ref{fig:star_sn} show that seeing conditions impact the \s2n{} of point
-    sources at fixed input magnitude.
-    In $i$-band, the \texttt{badSeeing} (0.70\asec{}) \tract{} shows systematically
-    lower \s2n{} than the \texttt{goodSeeing} (0.45\asec{}) \tract{}.
-    The \s2n{} is similar for the two $g$-band \tracts{} because they share similar 
-    seeing conditions.
-
-    At \s2n{}$=5$, HSC Wide can detect stars as faint as ${\sim}26.5$ mag in both $g$ 
-    and $i$ bands, which is consistent with the values found in \citet{HSCDR1} for 
-    average seeing conditions.
-    However, it is worth reminding HSC data users that the detection
-    limit will exhibit spatial variations due to the seeing conditions.
-
-%% ------------------------------------------------------------------------------------ %%
 \subsubsection{Precision and Accuracy of PSF magnitudes}
@@
     In each bin, we characterize the statistical \textbf{precision} of the PSF 
-    magnitude using the standard deviation of the $\Delta \mathrm{mag}_{\mathrm{PSF}}$ 
-    distribution.
+    magnitude using the standard deviation of the distribution (\smag{}).
     Meanwhile, we characterize the statistical \textbf{accuracy} of the PSF magnitude 
-    via the mean magnitude difference in each bin. 
+    via the mean magnitude difference in each bin (\mmag{}). 
     This also informs us whether the PSF photometry is biased at certain input 
@@
 	The overall differences are small ($<0.01$ mag). 
-	At very faint end ($g_{\mathrm{Input}}>24.0$ mag and $g_{\mathrm{Input}}>23.5$
+	At very faint end ($g_{\mathrm{Input}}>24.0$ mag and $y_{\mathrm{Input}}>23.5$,
+	the \unforced{} photometry slightly overestimate the fluxes of stars comparing 
+	to the \forced{} photometry.
 
@@
     At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the accuracies of \forced{} \cmodel{}
-    magnitudes change from \plus{}$0.041$ mag to \minus{}$0.005$ mag, which suggest
+    magnitudes change from \plus{}$0.041$ mag to \minus{}$0.006$ mag, which suggest
     that \forced{} \cmodel{} photometry is unbiased down to the very faint end.
@@
     the $y$ band at $>24.0$ mag. 
-    This bias in the $y$ band flux is equal to \minus{}0.06 at $24.0$ mag to 
+    This bias in the $y$ band flux is equal to \minus{}0.07 at $24.0$ mag to 
     \minus{}0.22 mag at 25.0 mag. 

### 2017-04-30 draft/ms_v5.tex
Add table heads
Appendix: quality control

@@
     \hline 
+    \rowcolor[gray]{.85} \multicolumn{12}{|c|}{\large{Table}: Summary of \forced{} PSF Magnitude} \\
+    \hline \hline 
     Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
@@
     \hline
+    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} PSF Colors} \\
+    \hline \hline 
     \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
@@
     \hline
+    \rowcolor[gray]{.85} \multicolumn{12}{|c|}{\large{Table}: Summary of \forced{} \cmodel{} Magnitude} \\
+    \hline \hline 
     Input & Filter & \multicolumn{2}{|c|}{$g$} & \multicolumn{2}{|c|}{$r$} & \multicolumn{2}{|c|}{$i$} & \multicolumn{2}{|c|}{$z$} & \multicolumn{2}{|c|}{$y$} \\
@@
 
-    \rowcolor[gray]{.85} 22.0 & \smag{} & 0.019 & 0.019  & 0.024 & 0.031 & 0.017 & 0.014 & 0.014 & 0.021 & 0.021 & 0.023 \\
-    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.006  & 0.012 & 0.009 & 0.002 & 0.002 & 0.002 & 0.003 & 0.006 & 0.008 \\
-    \hline
-
-    \rowcolor[gray]{1.0} 23.0 & \smag{} &   0.161 & 0.138  & 0.147 & 0.167 & 0.168 & 0.174 & 0.182 & 0.185 & 0.197 & 0.194 \\
-    \rowcolor[gray]{1.0}      & \mmag{} & \n0.004 & 0.029  & 0.033 & 0.033 & 0.036 & 0.021 & 0.018 & 0.028 & 0.014 & 0.020 \\
+    \rowcolor[gray]{.85} 22.0 & \smag{} &   0.161 & 0.138  & 0.147 & 0.142 & 0.154 & 0.153 & 0.165 & 0.167 & 0.178 & 0.169 \\
+    \rowcolor[gray]{.85}      & \mmag{} & \n0.004 & 0.029  & 0.033 & 0.050 & 0.004 & 0.040 & 0.038 & 0.045 & 0.044 & 0.048 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 23.0 & \smag{} & 0.152 & 0.147  & 0.167 & 0.168 & 0.168 & 0.174 & 0.182 & 0.185 & 0.197 & 0.194 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & 0.021 & 0.040  & 0.033 & 0.036 & 0.017 & 0.021 & 0.018 & 0.028 & 0.014 & 0.020 \\
     \hline
@@
     \hline
+    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} \cmodel{} Colors} \\
+    \hline \hline 
     \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
@@
 
+    We apply quality control to the stars and galaxies selected from the HSC UltraDeep
+    COSMOS fields before we match them with the stars and models for galaxies from the 
+    \hst/ACS COSMOS data. 
+    The same quality control criteria are also used to select synthetic stars and 
+    galaxies from the \synpipe{} results before we perform photometric comparisons.
+
     To select synthetic stars and galaxies from the HSC survey data in order to test
@@
     the \texttt{FDFC} region, we did not apply this cut.
-    We did apply the following cuts to the matched synthetic objects.
+
+    Firstly, we make sure the object is a ``primary'' detection (in the inner part 
+    of \tract{} and \texttt{patch}; not a \texttt{parent} in the deblending process), 
+    is successfully deblended, has reliable centroid, and is not bothered by various 
+    of optical issues:
 
@@
 
-        \item[ ] \texttt{ idetect\_is\_primary==True }
-        \item[ ] \texttt{ ideblend\_skipped==False }
-        \item[ ] \texttt{ iflags\_badcentroid==False }
-        \item[ ] \texttt{ icentroid\_sdss\_flags==False }
-        \item[ ] \texttt{ iflags\_pixel\_edge==False }
-        \item[ ] \texttt{ iflags\_pixel\_interpolated\_center==False }
-        \item[ ] \texttt{ iflags\_pixel\_saturated\_center==False }
-        \item[ ] \texttt{ iflags\_pixel\_cr\_center==False }
-        \item[ ] \texttt{ iflags\_pixel\_bad==False }
-        \item[ ] \texttt{ iflags\_pixel\_suspect\_center==False }
-        \item[ ] \texttt{ iflags\_pixel\_clipped\_any==False }
-        \item[ ] \texttt{ iflags\_pixel\_bright\_object\_center==False }
+        \item[ ] \texttt{ detect\_is\_primary==True}
+        \item[ ] \texttt{ deblend\_skipped==False }
+        \item[ ] \texttt{ deblend\_nchild=0}
+        \item[ ] \texttt{ [grizy]flags\_badcentroid==False }
+        \item[ ] \texttt{ [grizy]centroid\_sdss\_flags==False }
+        \item[ ] \texttt{ [grizy]flags\_pixel\_edge==False }
+        \item[ ] \texttt{ [grizy]flags\_pixel\_interpolated\_center==False }
+        \item[ ] \texttt{ [grizy]flags\_pixel\_saturated\_center==False }
+        \item[ ] \texttt{ [grizy]flags\_pixel\_cr\_center==False }
+        \item[ ] \texttt{ [grizy]flags\_pixel\_bad==False }
+        \item[ ] \texttt{ [grizy]flags\_pixel\_suspect\_center==False }
+        \item[ ] \texttt{ [grizy]flags\_pixel\_clipped\_any==False }
+        \item[ ] \texttt{ [grizy]flags\_pixel\_bright\_object\_center==False }
+
+    \end{itemize}
+
+    \noindent For stars, we ensure the selected objects have useful PSF magnitude:
+
+    \begin{itemize}
+
+        \item[ ] \texttt{ [grizy]flux\_psf\_flags==False }
+
+    \end{itemize}
+
+    \noindent For galaxies, we also make sure useful \cmodel{} photometry is available:
+
+    \begin{itemize}
+
+        \item[ ] \texttt{ [grizy]cmodel\_flux\_flags==False }
 

### 2017-04-30 draft/ms_v5.tex
Minor changes in the abstract

@@
     pipeline. 
-    For stars, we achieve 1\% photometric precision at $i{\sim}18.0$ mag and 7\%
-    precision at $i{\sim}25.5$ in the $i$-band (corresponding to statistical scatters 
-    of ${\sim}0.01$ and ${\sim}0.06$ mag respectively).  
+    For stars, we achieve 1\% photometric precision at $i{\sim}19.0$ mag and 7\%
+    precision at $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters 
+    of ${\sim}0.01$ and ${\sim}0.05$ mag respectively).  
     For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
-    achieves 7\% photometric precision at $i{\sim}20.0$ mag and 11\% precision at 
+    achieves 9\% photometric precision at $i{\sim}20.0$ mag and 13\% precision at 
     $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters of 
-    ${\sim}0.14$ and ${\sim}0.20$ mag respectively). 
+    ${\sim}0.15$ and ${\sim}0.22$ mag respectively). 
     We show that both \forced{} PSF and \cmodel{} photometry yield unbiased color 
@@
     Third, the current \cmodel{} algorithm tends to strongly underestimate the 
-    half-light radius and ellipticities of galaxies with $i>21.5$ mag.
+    half-light radius and ellipticity of galaxy with $i>21.5$ mag.
 

### 2017-04-30 draft/ms_v5.tex
Minor changes

@@
 
-    Fig \ref{fig:cmodel_mag} shows the precision and accuracy of \cmodel{} magnitude 
-    in each band using the same format as Fig \ref{fig:psf_mag}.
+    Fig \ref{fig:cmodel_mag} shows the precision (\smag{}) and accuracy (\mmag{}) of 
+    \cmodel{} magnitude in each band using the same format as Fig \ref{fig:psf_mag}.
 
@@
     The typical precision of $i$-band flux using \forced{} \cmodel{} is at 
-    ${\sim}7-9$\% level in the \texttt{goodSeeing} \tract{} at 
+    ${\sim}8-10$\% level in the \texttt{goodSeeing} \tract{} at 
     $i_{\mathrm{Input}}<24.0$ mag. 
-    It moderately degrades to ${\sim}11$\% at $25.0$ mag. 
+    It moderately degrades to ${\sim}13$\% at $25.0$ mag. 
     The performance is similar in $i$ band for the \texttt{badSeeing} \tract{}. 
-    At $20.0 < i_{\mathrm{Input}} < 25.0$ mag, the accuracies of \forced{} \cmodel{}
-    magnitudes change from \plus{}$0.041$ mag to \minus{}$0.006$ mag, which suggest
-    that \forced{} \cmodel{} photometry is unbiased down to the very faint end.
+    At $20.0 < i_{\mathrm{Input}} < 24.0$ mag, the accuracies of \forced{} \cmodel{}
+    magnitudes change between \plus{}$0.017$ mag to \minus{}$0.023$ mag. 
+    At $24.0 < i_{\mathrm{Input}} < 25.5$ mag, \mmag{} is around $\minus0.006$ mag,
+    which suggest that \forced{} \cmodel{} photometry is unbiased down to the very 
+    faint end.
 
@@
     across the entire input magnitude range.
-    The precision for the $y$ band is slightly worse, ranging from 9\% to 17\% in the
+    The precision for the $y$ band is slightly worse, ranging from 10\% to 17\% in the
     same magnitude bins.
@@
     galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
-    For $(g-i)$ colors, the statistical uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ 
-    mag is ${\sim}0.04$ mag.
-    The statistical uncertainty increases to ${\sim}0.11$ mag at 
+    For $(g-i)$ colors, the statistical uncertainty at $i_{\mathrm{Input}}{\sim}20.0$ 
+    mag is ${\sim}0.07$ mag.
+    The statistical uncertainty increases to ${\sim}0.18$ mag at 
     $i_{\mathrm{Input}}{\sim}25.0$ mag.
-    The $(i-y)$ colors show similar results.
-
-    The performance of \forced{} \cmodel{} color does not depend on seeing and is 
-    unbiased for the entire range of magnitudes and colors that we have tested.
+    The $(i-y)$ colors show similar results, except the precision at 
+    $i_{\mathrm{Input}}>24.0$ mag becomes slightly worse.
+
+    The performance of \forced{} \cmodel{} color does not strongly depend on seeing 
+    and is unbiased for the entire range of magnitudes and colors that we have tested.
     The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
-    is slightly overestimated.
+    is systematically redder than the real values by $\plus0.05$ mag.
     As mentioned above, this is not surprising given the shallower $y$ band 

### 2017-05-01 draft/ms_v5.tex
Small section about the b parameter bug

@@
 \title{Characterization and Photometric Performance of the Hyper Suprime-Cam 
-       Software Pipeline.}
+       Software Pipeline}
 
@@
 
-    The Subaru Strategic Program (SSP) is an ambitious wide-area, multi-band survey
+    The Subaru Strategic Program (SSP) is an ambitious multi-band survey
     using the Hyper Suprime-Cam (HSC) on the Subaru telescope. 
@@
     The HSC data are reduced using a pipeline that builds on the prototype pipeline 
-    being designed by the Large Synoptic Survey Telescope’s Data Management system. 
+    for the Large Synoptic Survey Telescope. 
     We have developed a \texttt{Python}-based, flexible framework to inject synthetic
     galaxies into real HSC images called \synpipe{}. 
-    In this paper, we explain the design and implementation of \synpipe{} and generate 
+    Here we explain the design and implementation of \synpipe{} and generate 
     a sample of synthetic galaxies to examine the photometric performance of the HSC
@@
     region of ${\rm A}$.
+
+    The current version of \hscpipe{} contains a bug related to the calculation of $b$
+    parameter. 
+    For bright object (e.g. $i<23.0$ mag), its effect can be ignored.  
+    For fainter object, it mostly leads to underestimate of $b$ parameter by $< 12$\%, 
+    especially for objects with $-3.5 < \log_{10} b < -1.5$. 
+    This bug has been fixed for the future release of \hscpipe{} and HSC survey data. 
+    For the \synpipe{} tests here, it does not qualitatively change the conclusions 
+    related to the highly-blended objects and about the relationship between $b$ and
+    photometric precision. 
+    Please see Murata\etal (in prep.) and Bosch\etal (in prep.) for more details.
+
 %% ------------------------------------------------------------------------------------ %%

### 2017-05-01 draft/ms_v5.tex
Location of figures
Final changes before submission

@@
     pipeline. 
-    For stars, we achieve 1\% photometric precision at $i{\sim}19.0$ mag and 7\%
+    For stars, we achieve 1\% photometric precision at $i{\sim}19.0$ mag and 6\%
     precision at $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters 
-    of ${\sim}0.01$ and ${\sim}0.05$ mag respectively).  
+    of ${\sim}0.01$ and ${\sim}0.06$ mag respectively).  
     For synthetic galaxies with single-\ser{} profiles, forced \cmodel{} photometry
-    achieves 9\% photometric precision at $i{\sim}20.0$ mag and 13\% precision at 
+    achieves 13\% photometric precision at $i{\sim}20.0$ mag and 18\% precision at 
     $i{\sim}25.0$ in the $i$-band (corresponding to statistical scatters of 
@@
     Approximately ${\sim}3$--$4$\% of the stars are located within 2 pixels of the 
-    centroids of real objects; we remove those stars from the sample to avoid confusion 
-    in the comparisons.
+    centroids of real objects; we remove those stars from the sample to avoid
+    confusion in the comparisons.
     For matched stars, we select the primary detections 
@@
 %% ------------------------------------------------------------------------------------ %%
+%% Fig: Magnitude v.s S/N for galaxies
+\begin{figure*}
+    \begin{center}
+        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sn}
+    \end{center}
+    \caption{
+        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
+        $g$-band) of synthetic galaxies $\log (\mathrm{S}/\mathrm{N})$ as measured 
+        by \hscpipe{} \cmodel{} photometry. 
+        Lines and contours are similar to Fig \ref{fig:star_sn}.
+        The truncation in $i$ band input magnitude is caused by the magnitude limit 
+        of COSMOS galaxies used in this test. 
+        }
+    \label{fig:cmodel_sn}
+\end{figure*}
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
 \subsubsection{Precision and Accuracy of PSF magnitudes}
@@
     The median $i$-band PSf magnitude precision for the \texttt{goodSeeing} \tract{} 
-    is ${\sim}0.015$ mag (${\sim}1.5$\%) at $i_{\mathrm{Input}}{\sim}19.0$ mag. 
+    is ${\sim}0.014$ mag (${\sim}1.3$\%) at $i_{\mathrm{Input}}{\sim}19.0$ mag. 
     At $i_{\mathrm{Input}}{\sim}24.0$ mag, the precision of the PSF magnitude is 
-    at ${\sim}3$\% level (${\sim}0.036$ mag average difference).
-    At $i_{\mathrm{Input}}{\sim}25.2$ mag, the precision decreases to
-    ${\sim}7$\% with an average ${\sim}0.072$ mag difference.
+    at ${\sim}3$\% level (${\sim}0.030$ mag statistical scatter).
+    At $i_{\mathrm{Input}}{\sim}25.0$ mag, the precision decreases to
+    ${\sim}6$\% with an average ${\sim}0.062$ mag difference.
 
@@
     At fainter magnitudes, the precision slightly degrades. 
-    The \texttt{badSeeing} \tract{} has ${\sim}5$\% precision at
+    The \texttt{badSeeing} \tract{} has ${\sim}4$\% precision at
     $i_{\mathrm{Input}}{\sim}24.0$ mag and ${\sim}11$\% precision at
-    $i_{\mathrm{Input}}{\sim}25.2$ mag.
+    $i_{\mathrm{Input}}{\sim}25.0$ mag.
     \citet{HSCDR1} evaluates the precision of PSF magnitude via external comparisons
@@
     For $r$ band we find 1.5-4.0\% precision at $r_{\mathrm{Input}} < 24.0$ mag and 
-    ${\sim}8$\% precision at $r_{\mathrm{Input}}{\sim}25.2$. 
+    ${\sim}8$\% precision at $r_{\mathrm{Input}}{\sim}25.0$. 
     For $z$-band we find 1.0-5.0\% precision at $z_{\mathrm{Input}} < 24.0$ mag and 
-    ${\sim}10$\% precision down to $z_{\mathrm{Input}}{\sim}25.2$ mag).
+    ${\sim}10$\% precision down to $z_{\mathrm{Input}}{\sim}25.0$ mag).
 
@@
     For $g$ band, the precision is 1.5-7.0\% at $g_{\mathrm{Input}} < 24.0$ mag and is
-    ${\sim}13$\% down to $25.2$ mag.
+    ${\sim}13$\% down to $25.0$ mag.
     For $y$ band, we find 1.5-5.0\% precision at $y_{\mathrm{Input}} < 23.0$ mag and
@@
     \hscpipe{} tends to underestimate the fluxes of stars in these bands by 
-    ${\sim}0.01-0.02$ mag. 
+    ${\sim}0.01-0.02$ mag at $< 24.0$ mag. 
     The exact cause of this offset is unclear but the levels of bias is quite small 
@@
 	summarized in Table \ref{tab:psfmag}
+%% ------------------------------------------------------------------------------------ %%
 
@@
 
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-%% Fig: Magnitude v.s S/N for galaxies
-\begin{figure*}
-    \begin{center}
-        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sn}
-    \end{center}
-    \caption{
-        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
-        $g$-band) of synthetic galaxies $\log (\mathrm{S}/\mathrm{N})$ as measured 
-        by \hscpipe{} \cmodel{} photometry. 
-        Lines and contours are similar to Fig \ref{fig:star_sn}.
-        The truncation in $i$ band input magnitude is caused by the magnitude limit 
-        of COSMOS galaxies used in this test. 
-        }
-    \label{fig:cmodel_sn}
-\end{figure*}
 %% ------------------------------------------------------------------------------------ %%
@@
     Finally, we also find that a worse seeing leads to a lower \s2n{} at fixed 
-    magnitude (see Fig \ref{fig:psf_s2n} for $i$-band).
+    magnitude (see Fig \ref{fig:star_sn} for $i$-band).
 
@@
     The typical precision of $i$-band flux using \forced{} \cmodel{} is at 
-    ${\sim}8-10$\% level in the \texttt{goodSeeing} \tract{} at 
+    ${\sim}10-14$\% level in the \texttt{goodSeeing} \tract{} at 
     $i_{\mathrm{Input}}<24.0$ mag. 
-    It moderately degrades to ${\sim}13$\% at $25.0$ mag. 
+    It moderately degrades to ${\sim}18$\% at $25.0$ mag. 
     The performance is similar in $i$ band for the \texttt{badSeeing} \tract{}. 
@@
 
-    \rowcolor[gray]{.85} 19.0 & \smag{} & 0.016 & 0.016  & 0.021 & 0.026 & 0.015 & 0.012 & 0.011 & 0.019 & 0.017 & 0.019 \\
-    \rowcolor[gray]{.85}      & \mmag{} & 0.008 & 0.008  & 0.011 & 0.009 & 0.002 & 0.001 & 0.002 & 0.003 & 0.006 & 0.007 \\
-    \hline
-
-    \rowcolor[gray]{1.0} 20.0 & \smag{} & 0.017 & 0.018  & 0.023 & 0.029 & 0.015 & 0.013 & 0.013 & 0.020 & 0.017 & 0.019 \\
-    \rowcolor[gray]{1.0}      & \mmag{} & 0.009 & 0.006  & 0.011 & 0.009 & 0.002 & 0.002 & 0.003 & 0.003 & 0.006 & 0.008 \\
-    \hline
-
-    \rowcolor[gray]{.85} 21.0 & \smag{} & 0.019 & 0.019  & 0.024 & 0.031 & 0.017 & 0.014 & 0.014 & 0.021 & 0.021 & 0.023 \\
-    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.006  & 0.012 & 0.009 & 0.002 & 0.002 & 0.002 & 0.003 & 0.006 & 0.008 \\
-    \hline
-
-    \rowcolor[gray]{1.0} 22.0 & \smag{} & 0.023 & 0.021  & 0.025 & 0.034 & 0.018 & 0.016 & 0.016 & 0.024 & 0.033 & 0.037 \\
+    \rowcolor[gray]{.85} 19.0 & \smag{} & 0.017 & 0.017  & 0.021 & 0.022 & 0.014 & 0.011 & 0.011 & 0.019 & 0.016 & 0.019 \\
+    \rowcolor[gray]{.85}      & \mmag{} & 0.008 & 0.006  & 0.011 & 0.009 & 0.002 & 0.001 & 0.002 & 0.003 & 0.006 & 0.007 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 20.0 & \smag{} & 0.018 & 0.018  & 0.023 & 0.025 & 0.015 & 0.012 & 0.012 & 0.020 & 0.017 & 0.019 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & 0.009 & 0.005  & 0.011 & 0.009 & 0.002 & 0.002 & 0.003 & 0.003 & 0.006 & 0.008 \\
+    \hline
+
+    \rowcolor[gray]{.85} 21.0 & \smag{} & 0.019 & 0.018  & 0.024 & 0.026 & 0.017 & 0.014 & 0.014 & 0.021 & 0.021 & 0.022 \\
+    \rowcolor[gray]{.85}      & \mmag{} & 0.009 & 0.005  & 0.012 & 0.009 & 0.002 & 0.002 & 0.002 & 0.003 & 0.004 & 0.008 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 22.0 & \smag{} & 0.023 & 0.020  & 0.025 & 0.029 & 0.018 & 0.015 & 0.017 & 0.024 & 0.035 & 0.037 \\
     \rowcolor[gray]{1.0}      & \mmag{} & 0.009 & 0.005  & 0.011 & 0.009 & 0.002 & 0.002 & 0.003 & 0.004 & 0.006 & 0.006 \\
@@
 
-    \rowcolor[gray]{.85} 23.0 & \smag{} & 0.029 & 0.026  & 0.027 & 0.041 & 0.020 & 0.022 & 0.025 & 0.038 & 0.074 & 0.077 \\
-    \rowcolor[gray]{.85}      & \mmag{} & 0.008 & 0.004  & 0.012 & 0.009 & 0.002 & 0.002 & 0.003 & 0.005 & 0.000 & 0.003 \\
-    \hline
-
-    \rowcolor[gray]{1.0} 24.0 & \smag{} & 0.043 & 0.039  & 0.035 & 0.054 & 0.030 & 0.043 & 0.053 & 0.071 &   0.138 &   0.153 \\
-    \rowcolor[gray]{1.0}      & \mmag{} & 0.007 & 0.003  & 0.011 & 0.006 & 0.002 & 0.001 & 0.005 & 0.003 & \n0.001 & \n0.034 \\
-    \hline
-
-    \rowcolor[gray]{.85} 25.0 & \smag{} &   0.078 &   0.091  & 0.064 & 0.090 & 0.047 &   0.050 &   0.094 &   0.104 & -- & -- \\
-    \rowcolor[gray]{.85}      & \mmag{} & \n0.003 & \n0.002  & 0.011 & 0.001 & 0.003 & \n0.012 & \n0.001 & \n0.010 & -- & -- \\
+    \rowcolor[gray]{.85} 23.0 & \smag{} & 0.031 & 0.026  & 0.029 & 0.031 & 0.021 & 0.022 & 0.025 & 0.039 &   0.076 & 0.079 \\
+    \rowcolor[gray]{.85}      & \mmag{} & 0.008 & 0.004  & 0.011 & 0.009 & 0.002 & 0.002 & 0.003 & 0.005 & \n0.001 & 0.003 \\
+    \hline
+
+    \rowcolor[gray]{1.0} 24.0 & \smag{} & 0.049 & 0.038  & 0.036 & 0.046 & 0.030 & 0.046 & 0.056 & 0.082 &   0.147 &   0.146 \\
+    \rowcolor[gray]{1.0}      & \mmag{} & 0.007 & 0.003  & 0.010 & 0.007 & 0.002 & 0.001 & 0.005 & 0.003 & \n0.003 & \n0.033 \\
+    \hline
+
+    \rowcolor[gray]{.85} 25.0 & \smag{} &   0.119 &   0.108  & 0.087 & 0.107 & 0.062 &   0.103 &   0.124 &   0.152 & -- & -- \\
+    \rowcolor[gray]{.85}      & \mmag{} & \n0.010 & \n0.008  & 0.004 & 0.006 & 0.003 & \n0.009 & \n0.001 & \n0.010 & -- & -- \\
     \hline

### 2017-05-01 draft/ms_v5.tex
Update the PSF mag and color tables
Update figures for PSF photometry

@@
     faint magnitudes. 
-    The average precision for $(g-i)$ is ${\sim}0.025$ mag at 
+    The average precision for $(g-i)$ is ${\sim}0.023$ mag at 
     $i_{\mathrm{Input}}{\sim}19.0$. 
-    The scatter increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}24.0$ mag.  
+    The statistical scatter increases to ${\sim}0.16$ mag at 
+    $i_{\mathrm{Input}}{\sim}25.0$ mag.  
     The $(i-y)$ color displays similar precision. 
@@
     For instance, the precision of $(g-i)$ for the \texttt{badSeeing} \tract{} is 
-    only slightly worse at the very faint end (${\sim}0.14$ mag at
-    $i_{\mathrm{Input}}{\sim}24.0$ mag) compared to the \texttt{goodSeeing} \tract{}.
+    only slightly worse at the very faint end (${\sim}0.18$ mag at
+    $i_{\mathrm{Input}}{\sim}25.0$ mag) compared to the \texttt{goodSeeing} \tract{}.
 
@@
     \hline
-    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.021 &   0.019 &   0.019 \\
-    \rowcolor[gray]{.85}      & \mcolor{} &   0.008 &   0.004 & \n0.004 & \n0.006 \\
-    \hline 
-    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.026 &   0.025 &   0.020 &   0.020 \\
+    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.022 &   0.018 &   0.019 \\
+    \rowcolor[gray]{.85}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
+    \hline 
+    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.028 &   0.024 &   0.019 &   0.019 \\
     \rowcolor[gray]{1.0}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
     \hline
-    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.037 &   0.033 &   0.022 &   0.021 \\
-    \rowcolor[gray]{.85}      & \mcolor{} &   0.005 &   0.002 & \n0.004 & \n0.006 \\
-    \hline
-    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.054 &   0.051 &   0.031 &   0.031 \\
-    \rowcolor[gray]{1.0}      & \mcolor{} &   0.003 &   0.001 & \n0.001 & \n0.005 \\
-    \hline
-    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.077 &   0.075 &   0.058 &   0.057 \\
-    \rowcolor[gray]{.85}      & \mcolor{} & \n0.002 & \n0.001 & \n0.002 & \n0.005 \\
-    \hline
-    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.105 &   0.105 &   0.109 &   0.123 \\
-    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.009 & \n0.002 &   0.011 & \n0.002 \\
-    \hline
-    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.117 &   0.137 &   0.189 &   0.221 \\
-    \rowcolor[gray]{.85}      & \mcolor{} & \n0.005 &   0.007 &   0.064 & \n0.063 \\
+    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.034 &   0.031 &   0.022 &   0.022 \\
+    \rowcolor[gray]{.85}      & \mcolor{} &   0.006 &   0.002 & \n0.004 & \n0.006 \\
+    \hline
+    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.053 &   0.051 &   0.031 &   0.030 \\
+    \rowcolor[gray]{1.0}      & \mcolor{} &   0.004 &   0.001 & \n0.004 & \n0.005 \\
+    \hline
+    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.079 &   0.086 &   0.057 &   0.058 \\
+    \rowcolor[gray]{.85}      & \mcolor{} & \n0.004 & \n0.015 & \n0.001 & \n0.004 \\
+    \hline
+    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.116 &   0.122 &   0.111 &   0.112 \\
+    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.015 & \n0.001 &   0.009 &   0.004 \\
+    \hline
+    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.162 &   0.185 &   0.192 &   0.216 \\
+    \rowcolor[gray]{.85}      & \mcolor{} & \n0.044 & \n0.018 &   0.097 &   0.097 \\
     \hline

### 2017-08-16 draft/response_to_referee.txt
Response to the referee report; 1

We thank the referee for the careful reading and many valuable comments. Here we attached the updated draft
where important changes are highlighted in cyan.

We believe that all the comments and questions from the referee have been addressed, and below are the
detailed response to some of the referee's concerns.

0. About the general comment that this draft resembles a "technical supplement of the hscPipe paper", we
think:
    * SynPipe paper presents important evaluations of the curent HSC data.  These results are useful to
      the general users of HSC instrument.  Given that the hscPipe paper already contains lots of technical 
      details and is quite long, we believe that a separate paper can better draw people's attention to these
      results. 
    * As we now presented in the new Discussion section, as an independent software, SynPipe is being used for
      many scientific goals, both within and outside the SSP community.  For some of them (e.g. Murata et al.
      in prep. about the impact of blended objects in weak lensing analysis), SynPipe is the key technical
      component.  We think it is useful to have a separate paper as reference to the readers of these works
      and the future SynPipe users.  In addition, SynPipe has recently been adopted by the LSST community, and 
      will be used to test the performance of the LSST pipeline.  We think it is useful to summarize the
      developement of SynPipe on the HSC side as an independent paper. 
    * We would like to draw the referee's attention to papers with the similar purpose, e.g. Balrog for the
      DES survey (http://adsabs.harvard.edu/abs/2016MNRAS.457..786S). These papers are proved to be useful and
      well-cited for similar reasons as we stated above.

# 1.

# 8. p. 7-8: "High level reduction pipeline": as stated more clearly in the hscPipe technical paper (Bosch et
al. 2017). Low-level reduction involves basic image detrending and calibration; high-level processes involves
the ones that generate coadded images and science-ready catalogs.  Now use the same explanation here to be
consistent with the technical paper and provide more details.

# 9. "purity and completeness"

# Minor comments:

1. p.7: should be 'mas' not 'max', corrected.

2. p.10, about 'rectangular cutout': the images are stored in a 2-D array, hence has a rectangular nature to
it.  And, it is much easier to convolve the model and shift the 2-D rectangular array before we add them to
the HSC coadd images.  When we generate the model image array using GalSim, we try to make sure that all fluxes 
of the model is contained in the image. For galaxies, we cutout the model at 10 x Re of the Sersic model. This 
is fine for most galaxies, but still miss small fraction of light for galaxy with very high Sersic index.
First, we try to avoide model with very high Sersic index in the input catalog, as they are often problematic
models for real galaxies; Second, given the magnitude distribution of the model galaxies (most have i>23.0
mag), the results we are showing here are not sensitive to the flux distributions outside 10 x Re.  
The referee is correct that estimation of R_e could be sensitive to the very outskirt when Sersic index is
high, but we'd like to point out that the CModel method used in hscPipe does not use any pixel with
S/N < 5, and only provides n=4 model fits (dev) to the "footprint" of the galaxy.  We do not expect accurate
R_e estimates for high Sersic index galaxies in the beginning.

We add a footnote to briefly explain this choice.

3. p.11, about "noise": it is Poisson noise, and we state that clearly in the text.

4. p.13: We think the location and context of this figure makes it very clear that it is for the input
parameters.  Now we state that clearly in the caption.

5. Fig. 4 and 5: has been corrected.

6.

### 2017-08-16 draft/ms_sub_2.tex
Response to the referee report; 1

--- 2017-05-01 draft/ms_v5.tex
@@
 % Version 5; Edits from Alexie; Comments by Jim
-
-%% ------------------------------------------------------------------------------------ %%
-\documentclass[useamsfonts]{pasj01}
-\twocolumn
+% This is the single column version used for submission
+
+%% ------------------------------------------------------------------------------------ %%
+%\documentclass[useamsfonts]{pasj01}
+\documentclass[proof]{pasj01}
+%\twocolumn
 
@@
     Generally speaking, the PSF photometry is accurate at the 1--2\% level for bright 
-    stars, and the astrometry is accurate to ${\sim}10$ and 40 max internally and 
-    externally.
+    stars, and the astrometry is accurate to ${\sim}10$ and 40 \song{mas} internally 
+    and externally.
 
@@
     and is under active development.
-    Unlike most publicly available photometric pipelines, it involves high-level 
-    reduction processes that produce not only deep \coadd{} images but also a series 
-    of science-ready catalogs. 
+    \song{Unlike other publicly available photometric pipelines whose focus is the
+    low--level reduction processes such as detrending and calibrating the images,
+    it involves high-level reduction processes that produce not only deep \coadd{} 
+    images but also a series of science-ready catalogs.}  
     To perform tests of the data products that result from \hscpipe{}, \synpipe{} is 
@@
 
+            \item \song{For galaxy using any parametric model, we generate rectangular 
+                cutout image that contains all . 
+                The model image can be truncated at $N \times R_{\rm e}$ to reduce the 
+                size of the cutout and speed up the injection process. 
+                In this work, we truncate all \ser{} model at $12 \times R_{\rm e}$. 
+                The results presented here are not sensitive to this choice.}
+
             \item To inject real HST galaxy images, \synpipe{} calls the \galsim{}    
@@
     \caption{
-         \textbf{Upper panel}: five-band magnitude distributions of synthetic
-         galaxies. (\texttt{lower panel}; from left to right are the \ser{} index, 
-         axis ratio, effective radius in arcsec, the $g-r$ and $r-z$ colors).
+         \textbf{Upper panels} show the five-band magnitude distributions of synthetic
+         galaxies. 
+         \texttt{lower panels} \song{show the \textbf{input} parameters of the \ser{} 
+         model; from left to right are the input \ser{} index, axis ratio, effective 
+         radius in arcsec, the $g-r$ and $r-z$ colors}).
          }
@@
         stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
-        Highly blended stars are highlighted using scatter plots.
+        \song{Highly blended stars with $b > 0.05$} are highlighted using scatter plots.
         The gray dashed line marks $S/N = 5$ which is the detection threshold used 
@@
         from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.
-        Highly blended objects are highlighted using scattered points.
+        \song{Highly blended objects with $b > 0.05$} are highlighted using scattered 
+        points.
         The long-dashed lines mark zero magnitude difference, while the pairs of

### 2017-09-12 draft/response_to_referee.txt
Major issue 1

@@
 
+-----
 0. About the general comment that this draft resembles a "technical supplement of the hscPipe paper", we
@@
 
-# 1.
+-----
 
+# 1. Discussion:
+
+We agree with the referee that this work can benefit from a more detailed discussion, which we have added
+before the Summary section.  A few relevant points were included in the earlier Summary and Conclusion
+section, and have been moved to the new Discussion section.
+
+We emphasize the importance of such synthetic object pipeline for modern cosmology survey, explain again the
+philosophy of our desgin, and compare it with other efforts for testing the data reduction pipline.  
+Right now, SynPipe is specifically tailored for HSC images, but it will be included in the LSSTpipe in the
+near future.  We demonstrate the broad scientific topics that can benefit from SynPipe, and describe the
+on-going efforts for further improvements.
+
+-----
+# 2 Interpreter Language
+
+The referee is correct that, in general, C++ should be more efficient in the heavy duty data reduction process.
+However, SynPipe here mainly works as a special user interface to hscPipe, which is also use Python for
+high-level algorithm.  The reason for this choise is described in details in the Section 2 of the technical paper 
+for hscPipe (Bosch et al. 2017).  Below is the most relevant paragraph:
+
+    """
+    Both the LSST Data Management codebase and the HSC Pipeline are written in a combination of C++ and Python. 
+    Flexibility and extensibility are core development goals at all levels of the code-base: we have attempted 
+    to make virtually every algorithm not just configurable but replaceable (even by external code). 
+    This flexibility is important for LSST in part because many algorithmic choices in LSST processing still 
+    require significant research and are under active development.....
+
+    High-level algorithms are written in Python, primarily as subclasses of our Task class...
+
+    Low-level algorithms that perform direct pixel-level processing or other computationally intensive operations 
+    are written in C++....
+    """
+
+As the referee can see, flexibility and extensibility is the main reason that hscPipe choose to use Python as
+the high-level language.  GalSim also uses the same logic.  Since SynPipe 1) directly depends on hscPipe and
+GalSim; 2) will develop along with the hscPipe (and LSSTpipe in the future); 3) does not do any low-level
+computationally intensive operation, we think it is natural to follow this decision and use Python as our
+working language.
+
+The efficiency of SynPipe, as the referee mentioned, certaintly relates to the available cores of the CPU. 
+What we meant to explain is that, under the same computational condition, SynPipe test costs similar amount
+time as the real data reduction.  Most heavy duty is carried out by hscPipe, so using C or C++ for SynPipe
+will not increase the efficiency.  The most time-consuming part of SynPipe test is the injection of synthetic
+objects to the individual CCD image.  During this process, the most computationally intensive part is carried
+out by GalSim using C++, so using C or C++ for SynPipe here will not increase the efficiency much.  At the
+end, we would like to emphasize that the design of SynPipe currently focuses on testing data reduction in the
+most reaslistic way, in the future, we will gradually work on increase the efficiency of SynPipe.
+
+Following the suggestion by the referee, we now try to explain this better in Section 2.2, 
+Section 3.1, and Section 3.2.3.
+
+-----
+# 3.  Missing Definitions
+
+The referee is correct that some of these basic definitions should be explained better.  
+Most of these concepts are explained and discussed in great details in the hscPipe paper (Bosch et al. 2017)
+and the Data Release 1 Paper (Aihara et al. 2017).  We emphasize the basic definitions of these values at the
+end of the introduction section and point the authors to the Bosch+2017 paper for more details.
+
+-----
 # 8. p. 7-8: "High level reduction pipeline": as stated more clearly in the hscPipe technical paper (Bosch et
@@
 
+-----
 # 9. "purity and completeness"
 
+-----
 # Minor comments:

### 2017-09-12 draft/ms_v5.tex
Major issue 1

@@
 \usepackage{multirow}
-
+
 %% ------------------------------------------------------------------------------------ %%
@@
     (\citealt{Ivezic2008, Axelrod2010, Juric2015}) and is described in 
-    Bosch\etal (in prep.). 
+    Bosch\etal (2017). 
+    \song{To enhance the flexibility and extensibility of the pipeline, \hscpipe{} 
+    is written using a combination of C++ and Python. 
+    All computationally intensive pixel-level operations are performed in C++, 
+    high-level algorithm and user interface is written in Python.}
     DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. 
@@
     and is under active development.
-    Unlike most publicly available photometric pipelines, it involves high-level 
-    reduction processes that produce not only deep \coadd{} images but also a series 
-    of science-ready catalogs. 
+    \song{Unlike other publicly available photometric pipelines whose focus is the
+    low--level reduction processes such as detrending and calibrating the images,
+    it involves high-level reduction processes that produce not only deep \coadd{} 
+    images but also a series of science-ready catalogs.} 
     To perform tests of the data products that result from \hscpipe{}, \synpipe{} is 
@@
             scientific topics (see Section \ref{sec:summary} for details).
+
+        \item \song{\synpipe{} works as a special user interface to \hscpipe{}. 
+            It will keep developing along with the \hscpipe{} (and \textttt{LSSTpipe}
+            in the future). 
+            Since both \hscpipe{} and \galsim{} use Python as high-level language, 
+            we also choose to use Python for \synpipe{} to make the frequent 
+            interactions among them easy and straightforward. 
+            Most of the computationally expensive tasks are handled by the low-level 
+            algorithms in \hscpipe{} and \galsim{} in C++, the usage of Python will not 
+            affect the overall efficiency of \synpipe{}.
+            }
 
@@
 
+            \item \song{For galaxy using any parametric model, we generate 
+                rectangular cutout image too. 
+                The model image can be truncated at $N \times R_{\rm e}$ to reduce the 
+                size of the cutout and speed up the injection process. 
+                In this work, we truncate all \ser{} model at $10 \times R_{\rm e}$. 
+                The results presented here are not sensitive to this choice.}
+
             \item To inject real HST galaxy images, \synpipe{} calls the \galsim{}    
@@
             basis; \synpipe{} also crops the images when necessary.
-            When that task is complete, \synpipe{} adds appropriate noise to the 
+            When that task is complete, \synpipe{} adds \song{appropriate Poisson 
+            noise} to the 
             image based on the pixels it covers and the calibration information of 
@@
     Using the infrastructure provided by \hscpipe{}, the user can easily perform these 
-    steps in parallel, and the overall efficiency of \synpipe{} is similar to
-    the real data reduction process. 
+    steps in parallel.  
+    \song{
+    For \texttt{coadd} images that include the same number of single-\texttt{Visit} 
+    data, the overall efficiency of \synpipe{} is similar to the real data reduction
+    process under the same computational conditions (e.g. same number of cores). 
+    The \texttt{stack.py} and \texttt{multiBand.py} steps should cost very similar 
+    amount of time. 
+    The single-\texttt{Visit} process is replaced with the injection of synthetic 
+    objects. 
+    The speed of this step depends on the total number of fake objects injected and 
+    the type of the synthetic object (e.g. fake galaxy using \ser{} model costs more 
+    time than fake star).
+    For tests with reasonable density of fake objects per CCD (e.g. the tests in this 
+    work), the injection step costs slightly less time than the actual 
+    single-\texttt{Visit} data processing. 
+    }
     The data and catalog volumes is also similar to the original data reduction process.
@@
     \caption{
-         \textbf{Upper panel}: five-band magnitude distributions of synthetic
-         galaxies. (\texttt{lower panel}; from left to right are the \ser{} index, 
-         axis ratio, effective radius in arcsec, the $g-r$ and $r-z$ colors).
+         \textbf{Upper panels} show the five-band magnitude distributions of synthetic
+         galaxies. \texttt{lower panels} \song{
+         show the \textbf{input} parameters of the \ser{} 
+         model; from left to right are the input \ser{} index, axis ratio, effective 
+         radius in arcsec, the $g-r$ and $r-z$ colors}).
          }
@@
         stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
-        Highly blended stars are highlighted using scatter plots.
+        Highly blended stars \song{with $b>0.05$} are highlighted using scatter 
+        plots.
         The gray dashed line marks $S/N = 5$ which is the detection threshold used 
@@
         from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.
-        Highly blended objects are highlighted using scattered points.
+        Highly blended stars \song{with $b>0.05$} are highlighted using scattered 
+        points.
         The long-dashed lines mark zero magnitude difference, while the pairs of
@@
 %% ------------------------------------------------------------------------------------ %%
+\section{Discussion}
+    \label{sec:discussion}
+
+    \todo{More discussions}
+%% ------------------------------------------------------------------------------------ %%
+    %% Other applications
+    \song{
+    Here we focused on characterizing the photometric performance of \hscpipe{}.  
+    However, \synpipe{} is a flexible tool and is being used for a range of other     
+    applications. 
+    For instance, Murata\etal (in prep.) uses \synpipe{} to characterize the level of
+    blending in the HSC Wide Layer.  
+    \citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of M31 HSC 
+    to search for microlensing events. 
+    \synpipe{} is also currently being used to estimate the completeness of high-$z$ 
+    LBG and Lyman-$\alpha$ emitters (Ono\etal in prep.; Konno\etal in prep.), to 
+    check the completeness of high-$z$ LBG pairs as a function of pair separation 
+    (Harikane\etal in prep.), to test the completeness of low surface--brightness 
+    dwarf galaxies selections (Greco\etal in prep.), and to test magnifications effects
+    around nearby clusters (Chiu\etal in prep.).
+    }
+
+    %% Future developments
+    \song{
+    Both \hscpipe{} and \synpipe{} are undergoing active development. 
+    Our plan is to update \synpipe{} to provide a photometric benchmark for
+    each HSC survey data release, which will help improve \hscpipe{}.
+    At the same time, we are also working on improving the efficiency of \synpipe{}.
+    Many users are not necessarily concerned with the subtle effects involved in 
+    the image stacking process. 
+    Hence, a future implementation of \synpipe{} will include the option of injecting 
+    objects directly onto \coadd{} images which will speed up the generation of 
+    synthetic data sets. 
+    The results shown in this paper demonstrate the utility of the \synpipe{} framework
+    in order to perform end-to-end quality control on pipeline products to the level 
+    of accuracy needed by large panchromatic surveys. 
+    }
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
+
+%% ------------------------------------------------------------------------------------ %%
 \section{Summary and Conclusion}
@@
     of \hscpipe{} and for subsequent data releases.
-
-%% ------------------------------------------------------------------------------------ %%
-
-%% ------------------------------------------------------------------------------------ %%
-    %% Other applications
-    Here we focused on characterizing the photometric performance of \hscpipe{}.  
-    However, \synpipe{} is a flexible tool and is being used for a range of other     
-    applications. 
-    For instance, Murata\etal (in prep.) uses \synpipe{} to characterize the level of
-    blending in the HSC Wide Layer.  
-    \citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of M31 HSC 
-    to search for microlensing events. 
-    \synpipe{} is also currently being used to estimate the completeness of high-$z$ 
-    LBG and Lyman-$\alpha$ emitters (Ono\etal in prep.; Konno\etal in prep.), to 
-    check the completeness of high-$z$ LBG pairs as a function of pair separation 
-    (Harikane\etal in prep.), to test the completeness of low surface--brightness 
-    dwarf galaxies selections (Greco\etal in prep.), and to test magnifications effects
-    around nearby clusters (Chiu\etal in prep.).
-
-    %% Future developments
-    Both \hscpipe{} and \synpipe{} are undergoing active development. 
-    Our plan is to update \synpipe{} to provide a photometric benchmark for
-    each HSC survey data release, which will help improve \hscpipe{}.
-    At the same time, we are also working on improving the efficiency of \synpipe{}.
-    Many users are not necessarily concerned with the subtle effects involved in 
-    the image stacking process. 
-    Hence, a future implementation of \synpipe{} will include the option of injecting 
-    objects directly onto \coadd{} images which will speed up the generation of 
-    synthetic data sets. 
-    The results shown in this paper demonstrate the utility of the \synpipe{} framework
-    in order to perform end-to-end quality control on pipeline products to the level 
-    of accuracy needed by large panchromatic surveys.
 

### 2017-09-12 draft/response_to_referee.txt
Comment 2 3

@@
 
+<1> HSC pipeline performs multi-step photometric calibrations against the Pan-STARRS system, hence all the
+fluxes and magnitudes measured by hscPipe are already calibrated into the AB magnitude system.  Therefore, the
+pixel values on the calibrated single-Visit and coadd images can be directly related to fluxes in physical
+unit, and can be converted into magnitudes using a simple calibration zeropoint (27.0).  Users of HSC survey
+data should not worry that the definition of magnitude is affected by filter or exposure time.
+Through out this work, we assume that all magnitudes of synthetic objects are also in AB system, and they are 
+converted into fluxes using the same zeropoint.
+
+<2> The CCD processing provides us calibrated exposures that include both the detrended, background-subtracted
+image and an image containing per-pixel estimate of the variance. The following coaddition process also takes
+the variance information into account, uses the inverse of the mean variance of the input images to set the
+weights for coaddition, and calculates the per-pixel variance for the coadd images. Both the PSF and CModel
+photometry take these variance images into account, and provide meaningful estimations of flux error for the
+coadd images.  
+    - The HSC pipeline uses matched-filter method to estimate the PSF fluxes.  Per-pixel variance information
+      is taken into account when estimating the flux error.  Please see Section 4.9.5 of Bosch+2017 for more
+      technical details.  
+    - The HSC CModel photometry is modified and improved based on the SDSS version.  It fits linear
+      combination of two basic parametric models to the 2-D flux distribution of galaxy after taking PSF
+      convolution into account.  It has the advantage of providing consistent multiband photometry for
+      extended objects and having reliable performance for very faint object. 
+      Please see Section 4.9.9 and Appendix 2 of Bosch+2017 for technical details of the CModel algorithm. 
+    - For CModel photometry, it is optional to use per-pixel inverse square root of the variance information
+      as weights during the fitting (when usePixelWeights=True).  By default, usePixelWeights=False, and a
+      constant weight is used for an object.  Again we will refer the reader to Bosch+2017 for more details
+      about this.
+
+<3> We understand the referee's concern, and it is true that based on statistics of photons, we could have
+more clear definition of signal-to-noise ratio (S/N).  However, in practice, it is not realistic to use "photon
+number" for statistics or separately account for the noise from readout, dark, and sky background.  Each CCD
+on the camira has four amplifiers that have slightly different effective gain; individual CCD images need to
+be detrended, calibrated, and background subtracted before coaddition; single exposures with different seeings
+are warped before they are coadded into a final image using appropriate weighting.  All these processes make
+it difficult to trace back to the origianl photon statistics.  For instance, on the coadd image, there are
+covariances between adjacent pixels due to the warping process.  On the other hand, hscPipe calibrates the
+pixels values on both coadd and single-Visit images to physically meaningful flux scale, and provides
+correponding variance information that reflect the per-pixel uncertainties after all these complex reduction
+steps.  Based on this design, scientific user of HSC data can use the flux value and its uncertainty from
+hscPipe to estimate the S/N of the object under certain photometric method.  
+    - Throughout this work, S/N is defined as the ration between a flux measurement and its uncertainty (flux
+      / flux_err).  Same definition is adopted by both Bosch+2017 (hscPipe paper) and Aihara+2017 (HSC DR1
+      paper), along with a series of science papers.  
+    - Under this definition, 5 sigma detection corresponds to a S/N=5 flux measurement under certain
+      photometric method.  The same concept is adopted by both Bosch+2017 (hscPipe paper) and Aihara+2017 
+      (HSC DR1 paper), along with a series of science papers. 
+    - Both the PSF and CModel photometry algorithms convolve a model for the true object’s morphology with 
+      the effective PSF model at the position of the object, which maximizes S/N (see Bosch+2017)
+
+The changes of text related to this comment are: 
+    - At the end of Introduction section, we make it clear that we are using AB system, and explain the
+      definiton of S/N and Nxsigma detection.  
+    - At the end of Section 2.2, we provide more details related to the flux measurements for PSF and CModel
+      photometry.  We also refer the reader to Bosch+2017 for more technical details. 
+    - Section 6.4: slightly more details about the usePixelWeights option and reference to hscPipe paper.
+
+-----
+# 4. CModel algorithm
+
+We agree with the referee that the details of CModel algorithm should be explained better.  However, limited
+by the scope of this work, we can not afford to show all the technical details.  As mentioned, we expanded
+
 -----

### 2017-09-12 draft/ms_v5.tex
Comment 2 3

@@
 \usepackage{multirow}
-
+
 %% ------------------------------------------------------------------------------------ %%
@@
 
+    \song{
+    Throughout this work, all magnitudes are in AB system (\citealt{Oke1974}). 
+    Signal--to--noise ratio (\s2n{}) is defined as the ratio between a flux measurement 
+    using certain algorithm (e.g. PSF, \cmodel{}) and its corresponding flux uncertainty 
+    from \hscpipe{} ($\mathrm{Flux}/\sigma(\mathrm{Flux})$).  
+    At the same time, a $5\sigma$ detection is equivalent to a flux measurement with 
+    \s2n{}$=5$ using certain algorithm.  
+    Such definitions are adopted in other works using HSC SSP data 
+    (e.g. \citealt{Bosch2017, HSCDR1}).
+    } 
     The code for \synpipe{}, along with documentation and examples, is made available
@@
             \cmodel{} photometry. 
-            The \texttt{psf} photometry should provide the most appropriate magnitudes 
-            and colors for point sources, while the \cmodel{} should be used for 
-            galaxies.
+            \song{
+            Both the \psf{} and \cmodel{} photometry algorithms take the PSF convolution 
+            effect into account, and hence can provide consistent \forced{} photometry 
+            across all bands and maximizes \s2n{}.  
+            Although their accuracies depend on the accuracy of the PSF model and 
+            the applicability of the adopted models, they still provide the most useful 
+            flux information for stars and galaxies, especially for objects with 
+            low-\s2n{}. 
+            Please see Section~4 and Appendix~2 of \citet{Bosch2017} for detailed 
+            descriptions of these algorithms.  
+            }
 
@@
 
-                \item \hscpipe{} uses matched-filter method to derive PSF magnitude 
+                \item \song{
+                    Details of the HSC \psf{} photometry can be found in 
+                    Section~4.9.5 of \citet{Bosch2017}. 
+                    In short, 
+                    }
+                    \hscpipe{} uses matched-filter method to derive PSF magnitude 
                     with the centroid fixed. 
@@
                     of the star, then divide by the effective area of the PSF model.
-
-                \item The HSC \cmodel{} algorithm is described in Bosch\etal (in prep), 
-                    and is based on the version for the SDSS \cmodel{} magnitude 
+                    \song{
+                    It considers the per-pixel variance information when estimating 
+                    the flux error. 
+                    Flux uncertainty due to the uncertainty of centroid is ignored 
+                    since it is subdominant even when \s2n{} is low. 
+                    }
+
+                \item \song{
+                    Details about the HSC \cmodel{} photometry can be found in 
+                    Section~4.9.9 and Appendix~2 of \citet{Bosch2017}. 
+                    }
+                    It is based on the version for the SDSS \cmodel{} magnitude 
                     (\citealt{Lupton2001, Abazajian2004}). 
-                    It fits objects using both a de~Vaucouleurs and an exponential 
-                    profiles convolved with the PSF model.  
-                    \cmodel{} then linearly combines the two results to find the best 
-                    fit to the galaxy image. 
-                    \cmodel{} magnitudes are designed to yield accurate fluxes and 
-                    colors for galaxies. 
-                    Star--galaxy classification is also performed based on the 
+                    \song{
+                    It fits an object using both elliptical model with an exponential 
+                    profile and de~Vaucouleurs profile with free amplitudes and shapes. 
+                    Then it fits a linear combination of both models to the image while 
+                    only allowing the amplitude of each component to change.  
+                    The last step provides the \cmodel{} flux and flux error used in 
+                    this work. 
+                    This \cmodel{} flux can be roughly seen as the linear interpolation 
+                    between exponential and de~Vaucouleurs models. 
+                    Although these models are often not the most appropriate models for 
+                    real galaxies, this method is shown to be robust and efficient, 
+                    especially for poorly--resolved and/or low \s2n{} galaxies. 
+                    }
+                    Star--galaxy classification now is also performed based on the 
                     difference between \texttt{psf} and \cmodel{}{} magnitudes.
@@
     the data reduction. 
-    The parameter controls whether or not the per-pixel variance information is used 
-    during the model fitting process.  
+    \song{
+    Please see \citet{Bosch2017} (Section 4.4.9 and Appendix 2) for more details about
+    the fitting algorithm of \cmodel{}.  
+    In short, when \texttt{usePixelWeight} is set to \texttt{True}, \cmodel{} algorithm 
+    will uses the per--pixel square root of the variance map for \texttt{coadd} image as 
+    weights during the fitting.  
+    When \texttt{usePixelWeight} is \texttt{False}, a constant weight will be used 
+    instead.
+    }  
     As one can see, this leads to significantly overestimated axis ratios for almost
@@
     from \cmodel{} to study the structural properties of galaxies.
-
 %% ------------------------------------------------------------------------------------ %%
@@
 
+    \bibitem[Bosch et al.(2017)]{Bosch2017} Bosch, J., Armstrong, R., Bickerton, S., 
+            et al.\ 2017, arXiv:1705.06766
+
     \bibitem[Bovy Jo et al.(2011)]{Bovy2011} Bovy Jo, Hogg, D.~W., \& Roweis,
@@
              et al.\ 2017, arXiv:1701.02151
+
+    %% O %%
+    \bibitem[Oke(1974)]{Oke1974} Oke, J.~B.\ 1974, \apjs, 27, 21
 

### 2017-09-13 draft/response_to_referee.txt
Comment 4 5 6 7

@@
 by the scope of this work, we can not afford to show all the technical details.  As mentioned, we expanded
+the description in Section 2.2, and points the readers to the relevant sections in Bosch+2017.
+
+Related to the referee's detailed comments: 
+    - We should clearly point out that good performace of cModel photometry is **not** a natural consequence
+      of hscPipe, and hscPipe **does not** use GalSim model for galaxy photometry.  These are two completely
+      independent software, and SynPipe interacts with them at different stages of the test.  In our tests, the
+      synthetic galaxy is described using single-Sersic profile, and is generated using GalSim.  For hscPipe,
+      we test CModel photometry which uses very different model assumptions and algorithms for galaxy photometry. 
+      It first fits an exponential model to the image with both the shape and the amplitude free. 
+      Then it fits a de Vaucouleurs model in the same way.  As last step, it fits both models 
+      simultaneously, keeping their ellipses fixed at the results from the previous two fits, and 
+      allowing only the two amplitudes to vary.
+      Also, in CModel, both of these models are actually described by multi-Gaussian approximations to allow
+      fast convolution (e.g. Hog & Lang 2013, Sheldon 2014).  
+      The CModel algorithm is not designed to model detailed flux distributions of galaxies accurately, but to
+      provide robust and efficient photometry for large amount of galaxies, especially for the poorly-resolved
+      and/or low S/N ones.  
+    - Although these tests are much more than just "internal consistency", we should mention that 1)
+      single-Sersic is still oversimplified model for real galaxies; 2) we assume that there is no error is
+      PSF modelling.  These are the limitations of our current tests, and we mention them in the discussion
+      section now.  
+    - About the central pixel value of Sersic model, please refer to Rowe et al. (2015; 
+      http://www.sciencedirect.com/science/article/pii/S221313371500013X) for details of this code.  
+      The Section 5.3 and Section 6 explain the integration over pixels and image rendering method in great
+      details.  We should point out that synthetic galaxies generated by GalSim have been used for various
+      photometric and weak lensing tests.  The algorithms involved should be considered well tested.
+
+We modify the text in the following way: 
+    - Section 3.2.1: We point the readers to the relevant sections in Rowe+2015 for more details. 
+    - At the end of Section 4.2, we clearly point out that CModel uses very different model assumptions, hence
+      we are not only testing the internal consistency of CModel pipeline. 
+    - In the discussion section, we add discussion about the limitation of our single-Sersic model test.
+
+-----
+# 5. Fig 4 and 9.
+
+We understand the referee's point that random noises from photon statistics could be useful for comparison.
+
+However, as we pointed out earlier, given the design of the camera, observational strategy, and the complex
+processes of data reduction, it is impossible to make statistics based on the "input photon number".  
+Each pixel on the coadd image consists of information from CCDs with different characteristics and from
+separated exposures under different seeing and sky conditions.  These individual exposures are first detrended,
+calibrated, background subtracted, and warped before they are coadded using weights that are related to their
+variance information.  Given these reasons, it is not realistic to conduct tests using photo number and random
+statistical errors as the referee requested.
+
+Meanwhile, we should point out that, since hscPipe (and LSSTpipe in the future) is designed to provide
+high-level science-ready results for users, it carefully calibrates the fluxes into AB magnitude system
+(absolute flux level), which is physically more meaningful and convinient.  In addition, the hscPipe tries to
+provide per-pixel variance information for both single-Visit and coadd images, which includes statistical
+uncertainties from sources mentioned and not mentioned by the referee (e.g. correction of brighter-fatter
+effect, crosstalk, cosmic-ray removal, number of single-visit images that go into the coadd etc.).
+For coadd image, the variance plane provided by hscPipe should be treated as a summary of all statistical
+errors, and all the flux error in hscPipe is estimated based on it.  Notice that, for both PSF and CModel
+photometry, the estimation of statistical uncertainty is not as straightfoward as for aperture photometry.
+And it is not realistic for us to provide independent estimations for each object.
+
+As mentioned earlier, such definition of S/N has been adopted within the HSC SSP collaboration, and has
+been used for multiple technical and scientific purposes.  Therefore, we think the S/N plotted in Fig 4 and 
+Fig 9 are the most meaningful and useful ones for HSC data user.
+
+We slightly modify the text to explain the definition of S/N and flux error better: 
+    - In Section 5.1.1, we explain the PSF flux error in more details.
+    - In Section 5.2.1, we explain that for extended objects modeled by CModel, definition of S/N is not as
+      straightforward as point sources.  Here we choose to use the CModel flux and flux error to simply
+      demonstrate the typical "significancy" of galaxies at fixed magnitude, and show that hscPipe can
+      relibaly detect and measure flux for galaxies down to certain magnitude.  We also mention that
+      uncertainty of CModel flux is dominated by systematics, and here the flux error only summarises the
+      statistical ones.  Therefore, our tests should provide more realistic estimation of average flux error
+      (including both systematic and statistical ones) for galaxy at certain magnitude.
+
+-----
+# 6. Pure statistical errors in figures.
+
+We agree with the referee that it is very useful to compare with the statistical uncertainties.  However, as
+we explained for comment #5,
+
+-----
+# 7. Precision and accuracy of PSF magnitude
 
@@
 6.
+
+-----
+8. P.29
+
+Yes, it should be (i-z) color, and has been corrected.
+
+-----
+9. Astrometric Calibration Fig 14
+
+HSC image has pixel scale of 0.168 arcsec/pixel.  We use arcsec as unit since when evaluating the astrometric
+calibration for HSC DR1, arcsec or mas are used in Aihara+2017.  Information about pixel scale is added to the
+caption of the figure and the text.

### 2017-09-13 draft/ms_v5.tex
Comment 4 5 6 7

@@
             $g_2$, see \citealt{Rowe2015} for more details).
+            \song{ 
+            To correctly generate synthetic image of \ser{} or double-\ser{} galaxy
+            model, it is not trivial to carefully consider details in pixel 
+            integration (especially for central pixel) and image rendering process.  
+            Details about these can be found in Section 5 and Section 6 of 
+            \citet{Rowe2015}.
+            }
 
@@
     \ser{} index, axis ratio, and position angle.
-    Although the single-\ser{} model is not always the best choice for describing 
-    galaxies, its flexibility enables it to reasonably describe the flux distribution 
-    of most galaxies.
-    Also, its simplicity makes it easy for us to diagnose potential problems with the 
-    \cmodel{} photometry.
+    \song{
+    It is worth noting that although single-\ser{} profile is still oversimplified model 
+    compared to the complexity in real galaxies, they are flexible enough to broadly 
+    describe the flux distributions of most galaxies, and test the \cmodel{} algorithm 
+    who models galaxy in very different way.
+    In addition, single-\ser{} model is simple enough to ensure straightforward 
+    diagnostic of potential systematic issues of \cmodel{} algorithm. 
+    }
     We exclude a tiny fraction (${\sim}4$\%) of ill-behaved models that have a very 
@@
     \hscpipe{} also estimates aperture correction for PSF photometry.
-    For more details please see Bosch\etal (in prep.).
+    For more details please see \citet{Bosch2017}.
 
@@
     $\mathrm{Flux}_{\mathrm{PSF}}/\mathrm{Flux\_Err}_{\mathrm{PSF}}$ in each band. 
+    \song{
+    The flux error here is estimated based on the per-pixel variance information that
+    summaries statistical uncertainties from various sources. 
+    However, systematical one like the centroid uncertainty is not taken into account 
+    as it should be subdominant even at low-\s2n{}. 
+    As mentioned earlier, such definition of PSF \s2n{} is adopted by \citet{HSCDR1} 
+    and \citet{Bosch2017}.
+    }
     Figure \ref{fig:star_sn} shows the relationship between stellar magnitude and \s2n{} 
@@
     limit will exhibit spatial variations due to the seeing conditions.
+    \song{
+    In addition, the image warping process introduces covariance across pixels into 
+    \texttt{coadd} images, and leads to slightly underestimated the flux error.  
+    Therefore, it is useful to compare the statistical results from our tests with the 
+    average PSF flux error at fixed input magnitude.  
+    }
 %% ------------------------------------------------------------------------------------ %%
@@
     \hscpipe{}.
+    \song{
+    For extended object with all kinds of flux distributions, definition of \s2n{} is 
+    not as straightforward as for point sources.  
     Here the adopted \s2n{} corresponds to the average \s2n{} over entire footprint. 
     The center of the galaxy typically has high \s2n{} than this value.    
+    We adopt this definition as the main purpose here is to demonstrate the overall 
+    ``significancy'' of galaxy down to certain magnitude. 
+    }
 
@@
 
+    \song{
+    The \cmodel{} flux error also only considers statistical uncertainties provided by 
+    the variance information. 
+    For galaxy photometry based on 2-D model, one can expect the error budget is 
+    dominated by systematical ones involved in the fitting process.  
+    Therefore, statistical tests like the one presented here can provide more insights 
+    about the accuracy of \cmodel{} photometry.  
+    }
+
 %% ------------------------------------------------------------------------------------ %%
@@
     The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
-    colors at the very ``blue'' end, while overestimating the $(i-y)$ color at the very
-    red end.
+    colors at the very ``blue'' end, while overestimating the \song{
+    $(i-z)$ color}
+    at the very red end.
 
@@
         measured on the \coadd{} images. 
+        \song{
+        HSC \coadd{} image has pixel scale of 0.168\asec{} per pixel. 
+        }
         Filled-contours (filled histogram) and open-contours (solid-line histogram) are 
@@
     \tracts{}.
+    \song{
+    Note that HSC \coadd{} image has pixel size of 0.168\asec{} per pixel. 
+    }
     We find small systematic offsets at the ${\sim}10$--20 mas level, which is similar 
@@
     For both PSF and \cmodel{} magnitude distributions, we can see clear trends that 
-    total fluxes are systematically underestimated for highly blended ($b>0.05$ for 
-    stars or $0.1$ for galaxies) objects.
+    total fluxes are systematically underestimated for highly blended \song{($b>0.05$)} 
+    objects.
     This effect is particularly strong for stars.

### 2017-09-13 draft/response_to_referee.txt
Most major comments

@@
 
-We agree with the referee that it is very useful to compare with the statistical uncertainties.  However, as
-we explained for comment #5,
+We agree with the referee that it is very useful to compare with the statistical uncertainties. 
+However, as we explained for comment #5, "pure statistical random errors" based on photon 
+statistics are not very practical to get from hscPipe.
+
+Instead, the flux error from hscPipe for both PSF and CModel photometry are relied on the
+detailed variance information that summarize most of the statistical errors. These flux or
+magnitude error are also provided to the HSC data user as the most frequently used
+information on photometric uncertainties, it is useful to compare them with the results of
+our SynPipe tests.
+
+On Fig 5, 6, 7, 10, 11, 12, and 15, we have overplot a pair of grey dashed lines that
+outline the running median of statistical uncertainties measured by the hscPipe (in
+positive and negative form).  For magnitude, we simply use the magnitude error provided by
+hscPipe, for color, we add the magnitude uncertainties for both bands in quadrature.
+
+Given the realistic situation, we think these comparisons cover the requirements by the
+referee, although are not exactly the same.  We did not specifically mentioned these
+comparesions because the results are exactly as we expected based on the algorithms
+themselves: for PSF photometry, the statistical uncertainties from hscPipe are similar but
+still slightly lower compared to the median uncertainties from SynPipe test; For CModel,
+the statistical flux errors from hscPipe are smaller compared to the uncertainties from
+SynPipe test as systematic uncertainties (model-dependent errors) dominate the real error
+budget of CModel photometry.
+
+We now briefly mention these comparisons in each section to draw readers attention to
+these information.
 
@@
 # 7. Precision and accuracy of PSF magnitude
+
+We believe this comment is also covered by the previous one.  For PSF magnitude, the
+statistical uncertainties obtained by hscPipe is similar but still slightly lower than the
+photometric uncertainties based on the SynPipe test.  As mentioned, due to the correlated
+noise from the image warping and coadding process, the statistical uncertainties of PSF
+flux measured by hscPipe is likely to be over-optimistic.
+
+Relevant text has been added to Section 5.1.2 and 5.1.3.
 
@@
 
+We agree with the referee that the purity and completeness tests are very important for
+survey like this, and SynPipe can be a useful tool for this purpose.
+
+At the same time, careful tests for this purpose are beyond the scope of this paper, where
+we simply want to demonstrate the application of SynPipe and provide simple photometric
+benchmark tests for stars and galaxies.  Following the suggestions from the referee, we
+add more discussions about this in the discussion section.  And here are the main points:
+    - Detection limits and completeness are normally defined for point sources.  As we
+      show using the PSF S/N, it depends on the seeing condition and show spatial changes 
+      across the 
+    - Detection completeness of point sources for HSC DR1 is investigated in Aihara+2017
+      (see Section 5.7) using a different method. 
+    - The efficiency 
+    -
+
 -----
@@
 
+----
 1. p.7: should be 'mas' not 'max', corrected.
 
+----
 2. p.10, about 'rectangular cutout': the images are stored in a 2-D array, hence has a rectangular nature to
@@
 
-3. p.11, about "noise": it is Poisson noise, and we state that clearly in the text.
+----
+3. p.11, about "noise":
 
-4. p.13: We think the location and context of this figure makes it very clear that it is for the input
+It is Poisson noise, and we state that clearly in the text.
+
+----
+4. p.13:
+
+We think the location and context of this figure makes it very clear that it is for the input
 parameters.  Now we state that clearly in the caption.
 
+----
 5. Fig. 4 and 5: has been corrected.
 
-6.
+----
+6. p.22:
 
------
+For stars, we think the likely reasons for this are: 
+    - There are actually very small fraction of stars with those extreme colors, which
+
+----
+7.
+
+----
 8. P.29
@@
 
------
+----
 9. Astrometric Calibration Fig 14
@@
 caption of the figure and the text.
+
+----
+10. the definition of highly blended
+
+The referee is correct, that we should use consistent definition for highly blended
+objects, which is b>0.05.  We have make it consistent across the draft.
+
+---- 
+11. Table 1, 2, 3, and 4

### 2017-09-13 draft/ms_v5.tex
Most major comments

@@
     modeling. But this effect should be subdominant.}
+    \song{
+    On Fig~\ref{fig:psf_mag}, we also compare the \synpipe{} test results with the 
+    median \psf{} magnitude error obtained by \hscpipe{} in each bin after taking 
+    the aperture correction (see Section~4.9.2 in \citealt{Bosch2017}) uncertainty 
+    into account (pairs of grey long-dashed lines on each plot). 
+    We find that, for \psf{} photometry, the flux errors from \hscpipe{} are very 
+    close to what we estimate using \synpipe{} once the aperture correction 
+    error is considered.
+    Without the aperture correction error, it seems that \hscpipe{} underestimate 
+    the statistical uncertainties of \psf{} magnitude, most likely due to the 
+    correlated noises introduced during the image warping and stacking step.
+    }
 
@@
 	The statistical uncertainties of \forced{} PSF colors are summarized in 
-	Table \ref{tab:psfcolor}
+	Table \ref{tab:psfcolor}. 
+	\song{
+	On Fig~\ref{fig:psf_color}, we also compare the \synpipe{} results with the 
+	uncertainties of \psf{} color obtained by \hscpipe{} (pair of grey long-dashed 
+	lines). 
+	Here, we simply add the magnitude errors from both bands in quadrature. 
+	We find that the average uncertainties of \psf{} color from \hscpipe{} are 
+	consistent with the results of \synpipe{} test. 
+	Although we should emphasize again that the uncertainties of PSF models are not 
+	taken into account. 
+    }
 
@@
     For details about the \cmodel{} algorithm, please see description in Section 
-    \ref{ssec:hscpipe} and Bosch\etal (in prep.).
+    \ref{ssec:hscpipe} and \citet{Bosch2017}.
     Despite the limitations of the \cmodel{} method (e.g., sensitivity to the 
@@
 	The precisions and accuracies of \forced{} \cmodel{} magnitudes shown here are 
-	summarized in Table \ref{tab:cmodelmag}
+	summarized in Table \ref{tab:cmodelmag}. 
+	\song{
+	Similar to \psf{} photometry, here we also compare the average \cmodel{} magnitude 
+	error provided by \hscpipe{} in each magnitude bin with our \synpipe{} test results
+	(pairs of grey long-dashed lines on each plot). 
+	The \cmodel{} magnitude error in \hscpipe{} only considers the statistical 
+	uncertainties based on the variance information. 
+	As expected, the real error budget for \cmodel{} magnitude is dominated by 
+	systematics in the model fitting process, and the \cmodel{} flux uncertainties 
+	from \hscpipe{} are underestimated. 
+	We stress that user of \cmodel{} photometry should take this into consideration.
+	}
 
@@
 	The statistical uncertainties of \forced{} \cmodel{} colors are summarized in 
-	Table \ref{tab:cmodelcolor}
+	Table \ref{tab:cmodelcolor}. 
+	\song{
+	We also compare the \cmodel{} color uncertainties estimated by \hscpipe{} with 
+	our \synpipe{} results. 
+	We still simply add the magnitude error from each band in quadrature.
+	For $(g-i)$ color, we see that the statistical uncertainties of \cmodel{} colors 
+	are very similar to the \synpipe{} results. 
+	This is consistent with the design of the \forced{} \cmodel{} algorithm, where 
+	precisions are expected to be much better for colors than for fluxes themselves 
+	(see Section 4.9.9 of \citealt{Bosch2017}).
+	For $(i-y)$ color, we can draw similar conclusion except for the faint end 
+	($i>24.0$ mag), where the uncertainties from \synpipe{} test become higher than 
+	the statistical uncertainties from \hscpipe{}. 
+	This is likely due to the scattered light in $y$--band that has not been accounted 
+	for (see Section~5.8.14 in \citealt{HSCDR1}). 
+	}
 
@@
     \cmodel{} photometry in $i$-band.
-    For more details about this algorithm, please see Bosch\etal (in prep.).
+    For more details about this algorithm, please see \citet{Bosch2017}.
 
@@
             \footnote{Note that this does not mean high fraction of contamination 
-            in the galaxy sample. Please see Bosch\etal (in prep.) for more 
+            in the galaxy sample. Please see \citet{Bosch2017} for more 
             details.}
@@
     introduces the blendedness parameter: $b$ (\texttt{[grizy]blendedness\_abs\_flux}).
-    We briefly define  $b$ below; please refer to Bosch\etal (in prep.) and Murata\etal 
+    We briefly define  $b$ below; please refer to \citet{Bosch2017} and Murata\etal 
     (in prep.) for more details.
@@
     photometric precision. 
-    Please see Murata\etal (in prep.) and Bosch\etal (in prep.) for more details.
+    Please see Murata\etal (in prep.) and \citet{Bosch2017} for more details.
 

### 2017-09-13 draft/response_to_referee.txt
A few minor comments

@@
 we simply want to demonstrate the application of SynPipe and provide simple photometric
-benchmark tests for stars and galaxies.  Following the suggestions from the referee, we
-add more discussions about this in the discussion section.  And here are the main points:
-    - Detection limits and completeness are normally defined for point sources.  As we
-      show using the PSF S/N, it depends on the seeing condition and show spatial changes 
-      across the 
-    - Detection completeness of point sources for HSC DR1 is investigated in Aihara+2017
+benchmark tests for stars and galaxies.
+
+Following the suggestions from the referee, we modify the text with more discussions on
+this, and here are the main points:
+    - Section 4.2: We explain that it is beyond the scope of this work to look into this
+      carefully.  Detection limits and completeness are normally defined for point sources.  
+      As we show using the PSF S/N, it depends on the seeing condition and show spatial 
+      changes which requires more careful designs and higher density of fake stars. 
+      Detection completeness of point sources for HSC DR1 is investigated in Aihara+2017
       (see Section 5.7) using a different method. 
     - The efficiency
-    -
 
@@
 
-For stars, we think the likely reasons for this are: 
-    - There are actually very small fraction of stars with those extreme colors, which
+For stars, first, fraction of stars with such extreme colors are very low.  The
+discrepency can barely be noticed on the comparisons of 1-D color distributions. 
+We think the likely reasons for this are: 
+    - There are still scattered light on the y-band images that are not accounted for.
+      This known prolblem can affect the accuracy of y-band photometry and is discussed in 
+      Section 5.8.14 in Aihara+2017. 
+    - Background level is much higher in z and y-band, and background subtraction could
+      suffer from higher uncertainties.  Right now, SynPipe can still not test the impact
+      of background subtraction on photometry, and it will be investigated in the future. 
+    - We modify text in Section 5.1.3 to breifly explain this.
+
+As for galaxies, the same background and y-band scatter light issues also exist.  However,
+the dynamical ranges for i-z and z-y colors are narrower.  Also the CModel color
+uncertainties are higher than the PSF ones.  Both of these factors make it harder to spot
+discrepencies of color distributions.  However, we still see discrenpencies between the
+input and recovered z-y colors. 
+    - We expand the discussion in Section 5.2.3 a little to address this issue.
 
 ----
-7.
+7. p.22
 
@@
 
-Yes, it should be (i-z) color, and has been corrected.
+Actually it should be (z-y) color, and has been corrected.
 

### 2017-09-13 draft/ms_v5.tex
A few minor comments

@@
     color-color space.
+    \song{
+    It is worth noting that \synpipe{} test using synthetic stars can also help 
+    determine the detection limit and point sources completeness of the HSC data. 
+    However, both of them depend on seeing or background conditions, and show 
+    spatial variations that need to be considered.  
+    It normally requires higher density of synthetic objects to carefully test this 
+    and is beyond the scope of this work.  
+    Please see Section~5.6 and Section~5.7 of \citet{HSCDR1} for investigation of 
+    this topic for HSC SSP DR1 using different method.
+    }
 
@@
     and the color-color distributions.
+    \song{
+    On the $(i-z)$-$(z-y)$ color plane, stars with extreme colors are not well 
+    recovered.  
+    Fraction of these stars is very low, and it could relate to the scattered 
+    light in $y$-band that is still unaccounted for (see Section~5.8.14 of 
+    \citealt{HSCDR1}). 
+    }
 
@@
     colors at the very ``blue'' end, while overestimating the \song{
-    $(i-z)$ color}
+    $(z-y)$ color}
     at the very red end.
+    \song{
+    The same $y$-band scattered light issue also affects the \cmodel{} photometry. 
+    The background levels are also higher in the $z$- and $y$-band, which could lead 
+    to higher uncertainties from background subtraction.  
+    Unfortunately, \synpipe{} is not yet equipped to test the impact of background 
+    subtraction on photometry, and the issues with the $(z-y)$ colors will be 
+    investigated later. 
+    }
 

### 2017-09-13 draft/response_to_referee.txt
All minor comments

@@
       (see Section 5.7) using a different method. 
-    - The efficiency
+    - Misclassification is briefly discussed in Section 6.2. The design of our tests and the 
+      number density of synthetic galaxies are not perfect to thoroughly test the star-galaxy 
+      separation. So our results just demonstrate the capability and briefly discuss the 
+      current situation for star/galaxy separation.  We find that, right now, hscPipe tends 
+      to provide a very complete sample for galaxy but with considerable fraction of star 
+      contamination at the faint end.  In Aihara+2017, the star/galaxy separation issue 
+      is discussed in Section 5.7, where they draw the same conclusion using different 
+      method. 
+    - The current method adopted by hscPipe focuses on the magnitude different between PSF 
+      and CModel photometry and is known to have limitations (see Section 4.9.10 of 
+      Bosch+2017) and issues (e.g. the one related to the current CModel algorithm; see 
+      Appendix 2 in Bosch+2017).  All these conclusions are reflected in our simple test. 
+      On the other hand, hscPipe team is working on replacing the star/galaxy separation 
+      algorithm with a much improved one (based on extreme deconvolution method, also 
+      see Section of 4.9.10 of Bosch+2017).  We will test its performance after the next 
+      data release. 
+    - We expand the discussion in Section 6.2 to provide more information about star/galaxy 
+      separation tests and emphasize the importance of such tests as suggested by the referee.
 
@@
 
+The referee is correct that, for highly blended stars, the biases on their PSF colors are 
+still quite big.  What we meant here is that the biases for PSF magnitude are much worse 
+as the total fluxes of blended stars are highly underestimated.  As for PSF colors, 
+although there are still long tails that indicate the biases, at least the peak of the 
+distributions are around zero now.  We adjust this sentence to make it more clear.
+
+As for general comments for PSF photometry of highly blended stars.  Unfortunately we are 
+not perfectly clear what causes this issue.  It is clearly related to the performace of 
+debelnder in hscPipe, which is know to still have issue and is being improved now 
+(please see Section 4.8 of Bosch+2017).  Given the depth of HSC survey, the situation for 
+object deblending becomes much more tricky.  At this point, we have to leave this as a 
+caveat.  PSF magnitude is still considered the best photometry for point sources, but we 
+will remind the users to avoid using it for highly blended objects.  The text has been 
+modified to reflect this point.
+
 ----
@@
 11. Table 1, 2, 3, and 4
+
+The statistical uncertainty is actually the standard deviation of (mag_output - mag_input)
+within each input magnitude bin.  This is the what we used to describe "precision". 
+For accuracy, we use the mean value of magnitude difference in each input magnitude bin.
+
+All the captions of tables have been updated to make it more clear.

### 2017-09-13 draft/ms_v5.tex
All minor comments

@@
     highly blended stars.  
-    Also, for blended stars, $(g-i)$ shows a bias towards bluer colors, while $(i-y)$ 
-    shows a bias towards redder colors. 
-    However, such biases appear to be less severe in terms of colors than in terms of
-    PSF magnitudes.
+    \song{
+    Unlike \psf{} magnitudes, where the distributions of magnitude differences 
+    for highly--blended stars are clearly off, the distributions of \psf{} color 
+    differences do peaks around zero.  
+    Although the long asymmetric tails still indicate severe biases of \psf{} colors 
+    for blended stars: $(g-i)$ color is clearly biased towards bluer colors, while 
+    $(i-y)$ color shows bias towards redder values.
+    The performances of \psf{} magnitude and color are still poor for highly-blended 
+    stars in the current version of \hscpipe{}.  
+    Object deblending becomes much more challenging at the depth of HSC SSP, and 
+    the current deblending algorithm is known to have problems 
+    (see Section~4.8 of \citealt{Bosch2017}) that could cause the problem here. 
+    The deblending algorithm is also being constantly updated now, and we will keep 
+    using \synpipe{} to evaluate its performance. 
+    }
 
@@
     \cmodel{} photometry in $i$-band.
-    For more details about this algorithm, please see \citet{Bosch2017}.
+    \song{
+    Such method has its limitation and only works well down to $i\sim 24$ mag 
+    (see Section 4.9.10 of \citealt{Bosch2017}).  
+    For fainter extended objects, the difference between these two magnitudes become
+    seeing- and model-dependent. 
+    Moreover, right now, \hscpipe{} simply uses 
+    $(m_{\mathrm{PSF}}-m_{\mathrm{CModel}})>0.0164$ mag to separate star and galaxies.  
+    }
 
@@
     with \textbf{high purity}.
-
     It is also clear that the seeing condition strongly modifies the distributions
@@
     depend on seeing conditions. 
-
-    In the next data release, \hscpipe{} will include an improved star--galaxy 
-    classifier which will be based on a machine learning method that takes both 
-    size and color information into account.
+    \song{
+    In \citet{HSCDR1}, the star--galaxy separation issue is tested in a small field 
+    but under different seeing conditions and imaging depths (see their Section~5.7). 
+    The overall conclusions are the same with ours, the efficiency and accuracy of 
+    the current star--galaxy separation algorithm are reasonable at $i<23.0$ mag, but 
+    depend on both seeing and depth.  
+    We should point out that careful evaluation of star--galaxy separation algorithm 
+    and the completeness of both types of objects are important to several scientific 
+    topics of HSC SSP. 
+    It deserve test at larger scale that covers different observational conditions and 
+    with higher number density of objects. 
+    It will be a major effort and is beyond the scope of this work.
+    At the same time, \hscpipe{} will replace the current star--galaxy separation 
+    algorithm with a much improved version that provides actual probability of being 
+    star or galaxy (also see Section~4.9.10 in \citealt{Bosch2017}).  
+    It will be available for the future data release, and will be tested by \synpipe{}. 
+    }
 
@@
         five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
-        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
-        the difference between output \forced{} PSF magnitude and input 
-        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:psf_mag}.
-        Here, the precision is described using the statistical uncertainties of 
+        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics 
+        \song{
+        (standard deviation and mean value)
+        }
+        of the difference between output \forced{} 
+        PSF magnitude and input value ($\Delta\mathrm{mag}$) shown in 
+        Fig \ref{fig:psf_mag}.
+        \song{
+        Here, the precision is described using the \textbf{standard deviation} of 
         $\Delta\mathrm{mag}$ within a series of input magnitude bins (\smag{}). 
         The accuracy of PSF photometry in the same magnitude bin is described by the 
-        mean value of $\Delta\mathrm{mag}$.
+        \textbf{mean value} of $\Delta\mathrm{mag}$.
+        }
         }
@@
         $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
-        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
-        the difference between output \forced{} PSF color and input value 
+        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the 
+        \song{
+        standard deviation and mean value
+        } 
+        of the difference between output \forced{} PSF color and input value 
         ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
         Here, we describe the precision and accuracy of PSF color measurements using 
-        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
+        the \song{standard deviation} and mean values of $\Delta\mathrm{Color}$ in 
         bins of input $i$ band magnitudes.
@@
         five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
-        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
-        the difference between output \forced{} \cmodel{} magnitude and input 
+        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the 
+        \song{
+        standard deviation and mean value 
+        }
+        of the difference between output \forced{} \cmodel{} magnitude and input 
         value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:cmodel_mag}.
@@
         $(g-i)$ and $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) 
-        and \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
-        the difference between output \forced{} \cmodel{} color and input value 
+        and \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the 
+        \song{
+        standard deviation and mean value 
+        }
+        of the difference between output \forced{} \cmodel{} color and input value 
         ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:cmodel_color}.

### 2017-09-14 draft/ms_v6.tex
Update the draft

--- 2017-09-13 draft/ms_v5.tex
@@
 % Version 5; Edits from Alexie; Comments by Jim
+% Version 6; Edits from SH; responses to the referee report
 
@@
 \def\synpipe{\texttt{SynPipe}}
-\def\cmodel{\texttt{cModel}}
+\def\cmodel{\texttt{CModel}}
+\def\psf{\texttt{PSF}}
 \def\forced{\texttt{forced}}
@@
         \item \song{\synpipe{} works as a special user interface to \hscpipe{}. 
-            It will keep developing along with the \hscpipe{} (and \textttt{LSSTpipe}
+            It will keep developing along with the \hscpipe{} (and \texttt{LSSTpipe}
             in the future). 
@@
 
-    \todo{More discussions}
-%% ------------------------------------------------------------------------------------ %%
-    %% Other applications
+    \song{
+    Motivated mainly by observational cosmology and time-domain astrophysics, we are 
+    witnessing an exciting time for modern imaging survey.  
+    At the same time, more and more sophisticated observational strategy and complex 
+    data reduction process adopted by these surveys require more careful tests to 
+    fully understand all systematic issues and thoroughly evaluate the qualities of 
+    scientific outputs. 
+    In this work, we present \synpipe, a Python-based framework to test the performance
+    of \hscpipe{} for HSC SSP. 
+    }
+
+    \song{
+    Similar tools have been developed for DES (\citealt{DES2005}). 
+    For instance, \citet{Chang2015} designed a forward-modeling simulation framework 
+    to test the ``transfer function'' (from photons to tabulated photometric 
+    measurements) of DES data reduction pipeline using simulated images. 
+    In a different effort, \citet{Suchyta2016} developed \texttt{BALROG}, a software
+    that characterizes measurement biases in DES data reduction through injecting fake
+    objects on the coadded DES images.  
+    Comparing to these works, the main advantage of \synpipe{} is that it 
+    \emph{enables us to conduct tests under more realistic situations.}
+    Injecting synthetic objects to real single-exposure image, and follow the entire 
+    data reduction process (including image warping and stacking process) make sure that 
+    all realistic features on the image and systematics in each step of data reduction 
+    can be taken into account.
+    }
+
     \song{
@@
     around nearby clusters (Chiu\etal in prep.).
+    Moreover, \synpipe{} is not being incorporated into the data reduction pipeline
+    for LSST, and will also be used to test its performance in the future.
     }
@@
     \song{
-    Both \hscpipe{} and \synpipe{} are undergoing active development. 
-    Our plan is to update \synpipe{} to provide a photometric benchmark for
-    each HSC survey data release, which will help improve \hscpipe{}.
+    Both \hscpipe{} and \synpipe{} are undergoing active development and still face 
+    some problems and limitations. 
+    At the current stage, \synpipe{} can still not test the impact of background 
+    subtraction and PSF model on the performance of photometry.  
+    For a more comprehensive summary of the current caveat of HSC data, please 
+    see Section~5.8 of \citet{HSCDR1}. 
+    In the next section, we will also summarize the issues with \hscpipe{} that are 
+    identified by our \synpipe{} tests.
+    }
+
+    \song{
+    In the near future, we plan to update \synpipe{} to provide a photometric benchmark 
+    for each HSC SSP data release and help improve \hscpipe{} along the way.
     At the same time, we are also working on improving the efficiency of \synpipe{}.
@@
     synthetic data sets. 
-    The results shown in this paper demonstrate the utility of the \synpipe{} framework
-    in order to perform end-to-end quality control on pipeline products to the level 
-    of accuracy needed by large panchromatic surveys. 
     }
@@
     of HSC photometry for both stars and galaxies.
+    The results shown in this paper demonstrate the utility of the \synpipe{} framework
+    in order to perform end-to-end quality control on pipeline products to the level 
+    of accuracy needed by large panchromatic surveys.
 

### 2017-09-17 draft/ms_resub.tex
The version for resubmission

--- 2017-09-13 draft/ms_v5.tex
@@
 % Version 5; Edits from Alexie; Comments by Jim
-
-%% ------------------------------------------------------------------------------------ %%
-\documentclass[useamsfonts]{pasj01}
-\twocolumn
+% Version 6; Edits from SH; responses to the referee report
+% Version 7; Edits from Rachel Mandelbaum, Alexie Leauthaud
+% Version: For resubmission
+
+%% ------------------------------------------------------------------------------------ %%
+%\documentclass[useamsfonts]{pasj01}
+\documentclass[proof]{pasj01}
+%\twocolumn
 
@@
 \def\synpipe{\texttt{SynPipe}}
-\def\cmodel{\texttt{cModel}}
+\def\cmodel{\texttt{CModel}}
 \def\forced{\texttt{forced}}
 \def\coadd{\texttt{coadd}}
+\def\psf{\texttt{PSF}}
 \def\unforced{\texttt{unforced}}
@@
     \song{
-    Throughout this work, all magnitudes are in AB system (\citealt{Oke1974}). 
+    Throughout this work, all magnitudes are in the AB system (\citealt{Oke1974}). 
     Signal--to--noise ratio (\s2n{}) is defined as the ratio between a flux measurement 
-    using certain algorithm (e.g. PSF, \cmodel{}) and its corresponding flux uncertainty 
+    using a specific algorithm (e.g. PSF, \cmodel{}) and its corresponding flux uncertainty 
     from \hscpipe{} ($\mathrm{Flux}/\sigma(\mathrm{Flux})$).  
-    At the same time, a $5\sigma$ detection is equivalent to a flux measurement with 
-    \s2n{}$=5$ using certain algorithm.  
-    Such definitions are adopted in other works using HSC SSP data 
+    A $5\sigma$ detection is equivalent to a flux measurement with 
+    \s2n{}$=5$ using the chosen flux measurement algorithm.  
+    The same definitions were adopted in other work using HSC SSP data 
     (e.g. \citealt{Bosch2017, HSCDR1}).
@@
     Bosch\etal (2017). 
-    \song{To enhance the flexibility and extensibility of the pipeline, \hscpipe{} 
+    \song{To enhance the flexibility and modularity of the pipeline, \hscpipe{} 
     is written using a combination of C++ and Python. 
     All computationally intensive pixel-level operations are performed in C++, 
-    high-level algorithm and user interface is written in Python.}
+    while high-level connections between routines and the user interface are written in Python.}
     DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. 
@@
             effect into account, and hence can provide consistent \forced{} photometry 
-            across all bands and maximizes \s2n{}.  
-            Although their accuracies depend on the accuracy of the PSF model and 
-            the applicability of the adopted models, they still provide the most useful 
+            across all bands and maximize \s2n{}.  
+            Although their accuracy depends on the accuracy of the PSF model and choice of a model, they still provide the most useful 
             flux information for stars and galaxies, especially for objects with 
@@
                     Flux uncertainty due to the uncertainty of centroid is ignored 
-                    since it is subdominant even when \s2n{} is low. 
+                    since it is subdominant even when the \s2n{} is low. 
                     }
@@
                     }
-                    It is based on the version for the SDSS \cmodel{} magnitude 
+                    It is based on the algorithm used for the SDSS \cmodel{} magnitude 
                     (\citealt{Lupton2001, Abazajian2004}). 
                     \song{
-                    It fits an object using both elliptical model with an exponential 
+                    It fits an object using elliptical models with an exponential 
                     profile and de~Vaucouleurs profile with free amplitudes and shapes. 
@@
         \item \song{\synpipe{} works as a special user interface to \hscpipe{}. 
-            It will keep developing along with the \hscpipe{} (and \textttt{LSSTpipe}
+            It will keep developing along with the \hscpipe{} (and \texttt{LSSTpipe}
             in the future). 
-            Since both \hscpipe{} and \galsim{} use Python as high-level language, 
+            Since both \hscpipe{} and \galsim{} use Python as their high-level language, 
             we also choose to use Python for \synpipe{} to make the frequent 
             interactions among them easy and straightforward. 
-            Most of the computationally expensive tasks are handled by the low-level 
-            algorithms in \hscpipe{} and \galsim{} in C++, the usage of Python will not 
+            Most of the computationally expensive tasks are handled by low-level 
+            algorithms in \hscpipe{} and \galsim{} that are written in C++.  As a result, the fact that high-level routines are written in Python does not 
             affect the overall efficiency of \synpipe{}.
@@
             \song{ 
-            To correctly generate synthetic image of \ser{} or double-\ser{} galaxy
-            model, it is not trivial to carefully consider details in pixel 
-            integration (especially for central pixel) and image rendering process.  
+            To generate a synthetic image of a \ser{} or double-\ser{} galaxy
+            model with a high level of numerical accuracy, the pixel integration (especially for central pixel) and image rendering process must be carefully handled.  
             Details about these can be found in Section 5 and Section 6 of 
-            \citet{Rowe2015}.
+            \citet{Rowe2015}, with validation of numerical accuracy also shown in that paper.
             }
@@
 
-            \item \song{For galaxy using any parametric model, we generate 
-                rectangular cutout image too. 
+            \item \song{For galaxies using any parametric model, we also generate 
+                rectangular cutout images. 
                 The model image can be truncated at $N \times R_{\rm e}$ to reduce the 
                 size of the cutout and speed up the injection process. 
-                In this work, we truncate all \ser{} model at $10 \times R_{\rm e}$. 
+                In this work, we truncate all \ser{} models at $10 \times R_{\rm e}$. 
                 The results presented here are not sensitive to this choice.}
@@
     data, the overall efficiency of \synpipe{} is similar to the real data reduction
-    process under the same computational conditions (e.g. same number of cores). 
-    The \texttt{stack.py} and \texttt{multiBand.py} steps should cost very similar 
-    amount of time. 
+    process under the same computational conditions (e.g., same number of cores). 
+    The \texttt{stack.py} and \texttt{multiBand.py} steps take similar 
+    amounts of time. 
     The single-\texttt{Visit} process is replaced with the injection of synthetic 
@@
     The speed of this step depends on the total number of fake objects injected and 
-    the type of the synthetic object (e.g. fake galaxy using \ser{} model costs more 
-    time than fake star).
-    For tests with reasonable density of fake objects per CCD (e.g. the tests in this 
-    work), the injection step costs slightly less time than the actual 
+    the type of the synthetic object (e.g., a fake galaxy using a \ser{} model costs more 
+    time than a fake star).
+    For tests with a reasonable density of fake objects per CCD (e.g., the tests in this 
+    work), the injection step takes slightly less time than the actual 
     single-\texttt{Visit} data processing. 
@@
     It is worth noting that \synpipe{} test using synthetic stars can also help 
-    determine the detection limit and point sources completeness of the HSC data. 
-    However, both of them depend on seeing or background conditions, and show 
-    spatial variations that need to be considered.  
-    It normally requires higher density of synthetic objects to carefully test this 
-    and is beyond the scope of this work.  
+    determine the detection limit and point source completeness of the HSC data. 
+    However, both of those quantities depend on the seeing and background conditions, so their  
+    spatial variations must be considered.  
+    Doing so requires a higher density of synthetic objects than was used here, and is beyond the scope of this work.  
     Please see Section~5.6 and Section~5.7 of \citet{HSCDR1} for investigation of 
-    this topic for HSC SSP DR1 using different method.
+    this topic for HSC SSP DR1 using a different method.
     }
@@
     \song{
-    It is worth noting that although single-\ser{} profile is still oversimplified model 
-    compared to the complexity in real galaxies, they are flexible enough to broadly 
-    describe the flux distributions of most galaxies, and test the \cmodel{} algorithm 
-    who models galaxy in very different way.
-    In addition, single-\ser{} model is simple enough to ensure straightforward 
-    diagnostic of potential systematic issues of \cmodel{} algorithm. 
+    It is worth noting that although the single-\ser{} profile is still an oversimplified model 
+    compared to the complexity in real galaxies, it is flexible enough to broadly 
+    describe the flux distributions of most galaxies, and test the \cmodel{} algorithm -- which models the galaxy profile in a different way.
+    In addition, the single-\ser{} model is sufficiently simple to serve as a  straightforward 
+    diagnostic of potential systematic issues of the \cmodel{} algorithm. 
     }
@@
     The flux error here is estimated based on the per-pixel variance information that
-    summaries statistical uncertainties from various sources. 
-    However, systematical one like the centroid uncertainty is not taken into account 
+    summarizes statistical uncertainties from various sources. 
+    However, the flux uncertainty due to the centroid uncertainty is not taken into account, 
     as it should be subdominant even at low-\s2n{}. 
-    As mentioned earlier, such definition of PSF \s2n{} is adopted by \citet{HSCDR1} 
+    As mentioned earlier, this definition of PSF \s2n{} is adopted by \citet{HSCDR1} 
     and \citet{Bosch2017}.
@@
     \song{
-    In addition, the image warping process introduces covariance across pixels into 
-    \texttt{coadd} images, and leads to slightly underestimated the flux error.  
+    In addition, the image warping process introduces covariance between pixels into 
+    \texttt{coadd} images, and leads to slightly underestimated flux errors.  
     Therefore, it is useful to compare the statistical results from our tests with the 
@@
     On Fig~\ref{fig:psf_mag}, we also compare the \synpipe{} test results with the 
-    median \psf{} magnitude error obtained by \hscpipe{} in each bin after taking 
-    the aperture correction (see Section~4.9.2 in \citealt{Bosch2017}) uncertainty 
-    into account (pairs of grey long-dashed lines on each plot). 
+    median \psf{} magnitude error obtained by \hscpipe{} in each bin after taking into account 
+    the uncertainty in the aperture correction (see Section~4.9.2 in \citealt{Bosch2017}) -- see the pairs of grey long-dashed lines on each plot. 
     We find that, for \psf{} photometry, the flux errors from \hscpipe{} are very 
@@
     error is considered.
-    Without the aperture correction error, it seems that \hscpipe{} underestimate 
-    the statistical uncertainties of \psf{} magnitude, most likely due to the 
-    correlated noises introduced during the image warping and stacking step.
+    Without the aperture correction error, it seems that \hscpipe{} underestimates
+    the statistical uncertainties of \psf{} magnitudes, most likely due to the 
+    correlated noise introduced during the image warping and stacking step.
     }
@@
     recovered.  
-    Fraction of these stars is very low, and it could relate to the scattered 
+    The fraction of these stars is very low, and their poor recovery could relate to the scattered 
     light in $y$-band that is still unaccounted for (see Section~5.8.14 of 
@@
     Unlike \psf{} magnitudes, where the distributions of magnitude differences 
-    for highly--blended stars are clearly off, the distributions of \psf{} color 
-    differences do peaks around zero.  
-    Although the long asymmetric tails still indicate severe biases of \psf{} colors 
-    for blended stars: $(g-i)$ color is clearly biased towards bluer colors, while 
-    $(i-y)$ color shows bias towards redder values.
-    The performances of \psf{} magnitude and color are still poor for highly-blended 
+    for highly--blended stars are clearly biased, the distributions of \psf{} color 
+    differences do peak around zero.  
+    However, the long asymmetric tails still indicate severe biases of \psf{} colors 
+    for blended stars: the $(g-i)$ color is clearly biased towards bluer colors, while the 
+    $(i-y)$ color shows a bias towards redder values.
+    The performance of \psf{} magnitudes and colors are still poor for highly-blended 
     stars in the current version of \hscpipe{}.  
-    Object deblending becomes much more challenging at the depth of HSC SSP, and 
-    the current deblending algorithm is known to have problems 
-    (see Section~4.8 of \citealt{Bosch2017}) that could cause the problem here. 
+    Object deblending becomes much more challenging at the depth of the HSC SSP, and 
+    the current deblending algorithm is known to have limitations 
+    (see Section~4.8 of \citealt{Bosch2017}) that could cause the problem shown here. 
     The deblending algorithm is also being constantly updated now, and we will keep 
@@
 	On Fig~\ref{fig:psf_color}, we also compare the \synpipe{} results with the 
-	uncertainties of \psf{} color obtained by \hscpipe{} (pair of grey long-dashed 
+	uncertainties of the \psf{} color obtained by \hscpipe{} (pair of grey long-dashed 
 	lines). 
@@
 	We find that the average uncertainties of \psf{} color from \hscpipe{} are 
-	consistent with the results of \synpipe{} test. 
-	Although we should emphasize again that the uncertainties of PSF models are not 
+	consistent with the results of the \synpipe{} test. 
+	Again, we emphasize that the uncertainties of the PSF models are not 
 	taken into account. 
@@
     \song{
-    For extended object with all kinds of flux distributions, definition of \s2n{} is 
+    For extended object with a wide variety of light profiles, the definition of \s2n{} is 
     not as straightforward as for point sources.  
-    Here the adopted \s2n{} corresponds to the average \s2n{} over entire footprint. 
-    The center of the galaxy typically has high \s2n{} than this value.    
-    We adopt this definition as the main purpose here is to demonstrate the overall 
-    ``significancy'' of galaxy down to certain magnitude. 
+    Here the adopted \s2n{} corresponds to the average \s2n{} over the entire footprint. 
+    The center of the galaxy typically has higher \s2n{} than this value.    
+    We adopt this definition, as the main purpose here is to demonstrate the overall 
+    ``significance'' of the galaxy detections down to a certain magnitude. 
     }
@@
     the variance information. 
-    For galaxy photometry based on 2-D model, one can expect the error budget is 
-    dominated by systematical ones involved in the fitting process.  
+    For galaxy photometry based on a 2-D model, its quite often that the true error 
+    budget is dominated by systematic effects during the fitting process 
+    (e.g. choice of model assumption, priors for parameters, uncertainty of PSF model, 
+    and uncertainty in background subtraction).
     Therefore, statistical tests like the one presented here can provide more insights 
@@
 	uncertainties based on the variance information. 
-	As expected, the real error budget for \cmodel{} magnitude is dominated by 
-	systematics in the model fitting process, and the \cmodel{} flux uncertainties 
-	from \hscpipe{} are underestimated. 
-	We stress that user of \cmodel{} photometry should take this into consideration.
+	Apparently, the \cmodel{} flux uncertainties from \hscpipe{} underestimate the true
+	uncertainty of the photometry.  
+    Although it is possible that \hscpipe{} is too optimistic about the statistical 
+    uncertainties (e.g. correlated noise across pixels), the more likely situation is 
+    still that the real error budget of \cmodel{} magnitude is dominated by 
+	systematics in the model fitting process.  
+	We stress that users of \cmodel{} photometry should take this into consideration.
 	}
@@
     The same $y$-band scattered light issue also affects the \cmodel{} photometry. 
-    The background levels are also higher in the $z$- and $y$-band, which could lead 
+    The background levels are also higher in the $z$- and $y$-bands, which could lead 
     to higher uncertainties from background subtraction.  
@@
     \song{
-    Such method has its limitation and only works well down to $i\sim 24$ mag 
+    This method has limitation and only works well down to $i\sim 24$ mag 
     (see Section 4.9.10 of \citealt{Bosch2017}).  
@@
     but under different seeing conditions and imaging depths (see their Section~5.7). 
-    The overall conclusions are the same with ours, the efficiency and accuracy of 
+    The overall conclusions are the same as ours: the efficiency and accuracy of 
     the current star--galaxy separation algorithm are reasonable at $i<23.0$ mag, but 
@@
     topics of HSC SSP. 
-    It deserve test at larger scale that covers different observational conditions and 
-    with higher number density of objects. 
-    It will be a major effort and is beyond the scope of this work.
+    It should be tested on a larger scale, in a way that covers different observational conditions and 
+    with a higher number density of objects. 
+    This will be a major effort and is beyond the scope of this work.
     At the same time, \hscpipe{} will replace the current star--galaxy separation 
-    algorithm with a much improved version that provides actual probability of being 
+    algorithm with a much improved version that provides an actual probability of being 
     star or galaxy (also see Section~4.9.10 in \citealt{Bosch2017}).  
@@
     the fitting algorithm of \cmodel{}.  
-    In short, when \texttt{usePixelWeight} is set to \texttt{True}, \cmodel{} algorithm 
-    will uses the per--pixel square root of the variance map for \texttt{coadd} image as 
+    In short, when \texttt{usePixelWeight} is set to \texttt{True}, the \cmodel{} algorithm 
+    will use the per--pixel square root of the variance map for \texttt{coadd} image as 
     weights during the fitting.  
@@
 
-    \todo{More discussions}
-%% ------------------------------------------------------------------------------------ %%
-    %% Other applications
+    \song{
+    Motivated mainly by observational cosmology and time-domain astrophysics, we are 
+    witnessing an exciting time for modern imaging surveys.  
+    Increasingly sophisticated observational strategies and complex 
+    data reduction processes adopted by these surveys require careful tests to  understand the dominant systematic issues and thoroughly evaluate the quality of 
+    scientific catalogs. 
+    In this work, we present \synpipe, a Python-based framework to test the performance
+    of \hscpipe{} for the HSC SSP. 
+    }
+
+    \song{
+    Similar tools have been developed for DES (\citealt{DES2005}). 
+    For instance, \citet{Chang2015} designed a forward-modeling simulation framework 
+    to test the ``transfer function'' (from photons to tabulated photometric 
+    measurements) of DES data reduction pipeline using simulated images. 
+    In a different effort, \citet{Suchyta2016} developed \texttt{BALROG}, a software
+    that characterizes measurement biases in DES data reduction by injecting fake
+    objects on the coadded DES images.  
+    Compared to these studies, the main advantage of \synpipe{} is that it 
+    \emph{enables us to conduct tests in real galaxy images using the same pipeline as used for science purposes.}
+    It injects synthetic objects to real single-exposure images, and follows the entire 
+    data reduction process (including image warping and stacking process) make sure that 
+    all realistic features on the image and systematics in each step of data reduction 
+    can be taken into account.
+    }
+
     \song{
@@
     applications. 
-    For instance, Murata\etal (in prep.) uses \synpipe{} to characterize the level of
+    For instance, Murata\etal (in prep.) use \synpipe{} to characterize the level of
     blending in the HSC Wide Layer.  
-    \citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of M31 HSC 
+    \citet{Niikura2017} apply \synpipe{} to high-cadence HSC observations of M31 HSC images
     to search for microlensing events. 
@@
     (Harikane\etal in prep.), to test the completeness of low surface--brightness 
-    dwarf galaxies selections (Greco\etal in prep.), and to test magnifications effects
+    dwarf galaxies selections (Greco\etal in prep.), and to test magnification effects
     around nearby clusters (Chiu\etal in prep.).
+    Moreover, \synpipe{} is now being incorporated into the data reduction pipeline
+    for LSST, and will also be used to test its performance in the future.
     }
@@
     \song{
-    Both \hscpipe{} and \synpipe{} are undergoing active development. 
-    Our plan is to update \synpipe{} to provide a photometric benchmark for
-    each HSC survey data release, which will help improve \hscpipe{}.
+    Both \hscpipe{} and \synpipe{} are undergoing active development and still face  certain limitations. 
+    Currently, \synpipe{} cannot test the impact of background 
+    subtraction and PSF model on the performance of photometry.  
+    For a more comprehensive summary of the current caveats of HSC data, please 
+    see Section~5.8 of \citet{HSCDR1}. 
+    In the following section, we summarize the issues with \hscpipe{} that have been 
+    identified by our \synpipe{} tests.
+    }
+
+    \song{
+    In the near future, we plan to update \synpipe{} to provide a photometric benchmark 
+    for each HSC SSP data release to help improve \hscpipe{}.
     At the same time, we are also working on improving the efficiency of \synpipe{}.
@@
     Hence, a future implementation of \synpipe{} will include the option of injecting 
-    objects directly onto \coadd{} images which will speed up the generation of 
+    objects directly onto \coadd{} images, which will speed up the generation of 
     synthetic data sets. 
-    The results shown in this paper demonstrate the utility of the \synpipe{} framework
-    in order to perform end-to-end quality control on pipeline products to the level 
-    of accuracy needed by large panchromatic surveys. 
     }
